### 2020-04-22 paper.tex
Init commit

\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A Decentralized Pub/Sub System for Trusted Machine Economy}

\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
\IEEEauthorblockA{\textit{dept. of CSIE} \\
\textit{National Cheng Kung University}\\
Tainan City, Taiwan (R.O.C.) \\
jkrvivian@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
\IEEEauthorblockA{\textit{dept. of CSIE} \\
\textit{National Cheng Kung University}\\
Tainan City, Taiwan (R.O.C.) \\
jserv@ccns.ncku.edu.tw}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
\IEEEauthorblockA{\textit{dept. of CSIE} \\
\textit{National Cheng Kung University}\\
Tainan City, Taiwan (R.O.C.) \\
chiaheng@gmail.com}
}

\maketitle

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
publish/subscribe, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

\section{Introduction}
%TODO: cite examples
In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly, and such technologies can be widely used in various fields, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}. As the physical and digital assets are deeply intertwined, the interactions among digital twins act as data exchanges.\cite{digitaltwin} With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is essential to build a secure, reliable and scalable data sharing services.

The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers. Broker is a centralized group that arrange the communication between the publishers and subscribers. However, the centralized architecture brings potential vulnerabilities and security issues:

\begin{enumerate}
	\item Central point of failure. 
	The broker is usually held by a single organization. If the centralized server is crashed or attacked, the services will not be available. 	
	\item Data integrity.
	As broker controls the interaction between publishers and subscribers, an unreliable or compromised broker can easily tamper data streams. 
	\item Anonymity and privacy.
	Broker matches publishers and subscribers in order to relay data streams to corresponding entities. The unreliable broker can expose the subscribers' interests and personal information of both entities.  
\end{enumerate}

\section{Related Work}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Smart Contract, usesrs can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quilatiy control are not included.

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interested data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data. Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middlewares in the model and to provide a reputation-based fairness payment strategy on blockcahin. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. The reputation system and the punishment rules against malicous acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.

Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

\section{System Architecture}
The proposed data subscription framework\cite{MyDataMarketplace} is a decentralized architecture with data providers, data subscribers and brokers that interact between data providers and subscribers, including data publishment, product metadata generation and trading process.

\subsection{Participants}
There are three major roles in the decentralized data marketplace (Fig.~\ref{fig:system_design}).

\begin{itemize}
\item \textbf{Data Provider: }
Data providers generate and preserve streaming data, and are willing to provide streaming data to subscribers. Providers can use the subscription fee paid by subscribers to improve the quality of their service.
\item \textbf{Subscribers: }
Subscribers aspire to obtain streaming data to promote the value of their service. However, it is a significant challenge for most subscribers to collect the desired data by themselves, so they look to purchasing the streaming data from data providers.
\item \textbf{Broker: }
Brokers represent data providers and subscribers to perform blockchain computing tasks and are expected to have higher resource. The brokers are requested to handle the product launching and subscription process, and brokerage fees is charged in each process.
\end{itemize}

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{system_design}
    \caption{The system design of a decentralized architecture which consists of data providers, subscribers and brokers.}
    \label{fig:system_design}
\end{figure}

\subsection{Components}
There are several building blocks in the proposed design to meet the expectations: 1) emit and access encrypted data stream; 2) retrieve transaction data for audit; 3) digital identity for all participants; and 4) enforcement of transparency and traceability.

\subsubsection{Masked Authenticated Messaging}
IOTA is a feeless cryptocurrency designed for IoT while MAM is the second layer data communication protocol built on top of the IOTA network, the Tangle. MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
With MAM, the rights of accessing data is traded instead of a copy of data itself, which gives a flexibilty for subscribers to obtain data anywhere anywhen that subscribers do not need additional storage to store the data it buy.

In the IOTA protocol, seed is the identifier of its owner. An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle. With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.

Either channel or endpoint is like a singly-linked list. The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint. Each address of a message can be derived from the previous one. A user can create multiple channels and multiple endpoints under the same channel. The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint. This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point. Fig.~\ref{fig:mam_struct} shows the architecture of MAM.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_struct}
    \caption{The concept of MAM.}
    \label{fig:mam_struct}
\end{figure}

The authentication in MAM includes source and data authentication. Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender. These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions. However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation. Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.

%use case illustration
Data providers are the primary role to interact with the MAM. With a seed, a provider can start creating a channel and endpoint. As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy. Also data providers can a make product preview which is public and not encrypted on MAM. In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID. By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages. Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.

The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world. Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data. And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data. This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.

While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system. See Fig.~ \ref{fig:launching_product}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

\subsubsection{TangleID}
The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint. With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C. Posting DID documents on MAM channel makes TangleID a GDPR-compliant system\cite{GDPR}. Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.

A public/private key pair and an IOTA seed are generated in TangleID. The public MAM channel is created with the seed and its MAM channel ID becomes part of the unique user ID, which at the same time serves as DID with the purpose of publishing the public key of the entity. Private key along with the IOTA seed is stored in the local database of the entity. The public/private key pair can be used in secure message sharing within users and digital signature.

The digital identities are also used to establish trust between the communication partners. This is done on two levels to prove that the communication partner owns the DID and the partner can, optionally, proof that it is a trusted participant. This authentication process happens during the first messages of interaction. In order for one partner to listen to another, it authenticates the messages. The DID ownership authentication is done by proving a digitally signed copy of the DID document.

The authentication of trust between the two parties is based on a Verifiable Credential, given out by a trusted issuer for the receiving party. If the receiving party does not trust the issuer, the credential is deemed worthless. If the party is recognized, the credential is verified and the messages will be labelled as trusted. In order to acquire this credential, the party needs to contact the issuer and ask for the credential. The issuer will need to know the DID of the party. If they decide to give out the credential, the issuer will sign the credential and send it encrypted over the blockchain to the requesting party's communication address. This is listed as a Service Endpoint (DID standard) in the DID Document of the requesting party.

\subsubsection{Ethereum Smart Contract}
The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and enforceable. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address. Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers. Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers. The further details of key exchangement will be illustrated in Section~\ref{section:trading}.

\subsubsection{Blind Signature}
There is an inherent risk in revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses. Therefore, a blind signature is used to prevent session key copying for such circumstances. A blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. Fig.~\ref{fig:blind_signature} illustrates the steps of blind signature. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signatures during the process of adding new products for data providers, in order to send the secret key of the MAM channel to the smart contract without knowing it.

\begin{figure}[!t]
	\centering
	\includegraphics[width=2. in]{blind_signature}
	\caption{The scheme of blind signature.}
	\label{fig:blind_signature}
\end{figure}

RSA blind signature\cite{cryptoNote} is used in our research. The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$. To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.

\begin{equation}
C = r^e m
\end{equation}

The signer signs the blinding message with private key $d$.

\begin{equation}
S = C^d
\end{equation}

$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.

\begin{equation}
\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
\end{equation}

The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.

\section{Trading Model}
In the following, we describe the data trading process in detail. To participate a data marketplace, data providers and subscribers have to first register. Then,  the data provider can launch its product on the marketplace. Once a product is launched, it is searchable on IPFS where brokers upload the information of the product and can be subsequently traded. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

\subsection{Set up}
At the beginning, all participant need to register on TangleID in order to get a DID document and public/private key pairs. The DID document is shared within the following operations to perform authentication, key exchangement and secure communication.

\subsection{Trading}
\label{section:trading}

The entire trading process is as shown in Fig.~\ref{fig:trading_product}. Once a subscriber wants to subscribe certain streaming data that is generated, he/she has to pay subscription fee to the Product Contract and will be automatically added to the subscriber list by the smart contract.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{trading_product}
    \caption{The process for the product trading.}
    \label{fig:trading_product}
\end{figure}

In the proposed architecture, the "access" to specific data stream is traded instead of giving out the raw data copies. Subscribers can retrieve data on MAM at any time without equipping extra storage to preserve data, and one can also query for arbitrary section of data rather downloading them all. Thus, the most important part of trading process is to give the session key $k$, the encryption key of data stream, to the subscribers. In order to exchange data, Azaria et al\cite{Medrec} seek an off-chain solution which is based on an end-to-end communication to ensure the efficiency and low costs. However, it is hard to avoid that the data source is unavailable or the sender sends incorrect data intentionally. Instead of the off-chain solution, we use smart contract to transfer the session key\cite{3tierDataMarket} that not only ensures the consistency of the session key, the availability of the source and the traceability of the record, but also prevents malicious participants to cheat others. With the help of brokers and smart contracts, both providers and subscribers do not need to be online at the same time to proceed the trading process.

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}

\begin{lstlisting}[caption={Update encryption key}, label={lst:key_exchange}, frame=single]
function addEncryptKey(
  address _subscriber,
  string memory _encryptKey
) public {
  require(
      msg.sender == provider,
      "Only provider can add blindedKey."
  );
  require(
      subscriber2Purchase[_subscriber].isKeyAdded == false,
      "One encryptKey has been added."
  );
  subscriber2Purchase[_subscriber].encryptKey = _encryptKey;
  subscriber2Purchase[_subscriber].isKeyAdded = true;
  emit newEncryptKey(_subscriber, _encryptKey);
}
\end{lstlisting}

The trading process is shown in Fig.~\ref{fig:key_exchange}. The data provider can obtain public keys of each subscriber from the DID document. For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract by calling $addEncryptKey()$ (Listing \ref{lst:key_exchange}). Subscribers listen to the $newEncryptKey$ event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{key_exchange}
    \caption{Session key exchange process between the data provider and subscriber.}
    \label{fig:key_exchange}
\end{figure}

Subscribers can obtain the broker's public key on the DID document as well, so they can verify that the validation of signature and the session key is the only one certified by the broker. Afterward, with the MAM channel ID and session key $k$, subscribers can obtain the data.

\subsection{Refunding}

It is probable that the streaming data sources are delayed or even interrupted after the subscribers pay the subscription fee. To protect subscriber rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel. If the expected data is not available, subscribers can request refunds. We assume that a very small percentage of subscribers in the product contract are irrational and/or malicious. When a subscriber consents to refund, he can vote at any time. After the ratio of consent votes of refunding is higher than the $threshold$, the subscription fee is proportionally transferred to the data provider, broker and every subscriber. Fig.~\ref{fig:refund} shows the refund process.

\begin{figure}[!t]
	\centering
	\includegraphics[width=1.5in]{refund}
	\caption{The process of refund.}
	\label{fig:refund}
\end{figure}

The subscription fee can be prorated as below:

\begin{equation}
    F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) -F_{t}
\end{equation}

\begin{equation}
    F_{Broker}(i) = N price \frac{i-1}{M} F_{b} -F_{t}
\end{equation}

\begin{equation}
    F_{Subscriber}(i) = price \frac{M-i+1}{M} -F_{t}
\end{equation}

where $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of subscribers in this contract.

To refund or withdraw subscription fees from the smart contract, the data provider, broker, and subscriber send a transaction to execute the smart contract and are responsible for the transaction fee. We assume that only a half of the expected records are published to the MAM channel. When $F_{b}$ is 5\%, the data provider and broker can withdraw half of the total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider. For subscribers, they can receive half of the subscription fee refunded which should be deducted from the transaction fee.

Considering the situation that one of the subscribers requests a refund in the future, when the subscriber is disappointed with the data quality, he/she may request a refund.

\section{Evaluations}
It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle. Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle. Therefore, in the following evaluations, all devices run with client library only.

\subsection{MAM Performance Evaluation}
MAM is a secure and validatable data storage of the proposed architecture. And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections. The interactions between data providers and MAM can be frequent. Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.

In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and data attachment to endpoints. To perform the evaluation assessment, a personal computer (PC, 3.2GHz 64-bit 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (1.2 GHz 64-bit quad-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.

\subsubsection{Channel / Endpoint Creation}
The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint. A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data. The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}. The time duration for each \textit{height} is the average time of running 100 rounds.

\begin{table}[htbp]
	\caption{Time measurement of channel creation}
	\label{tab:channel_create}
	\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
		\hline
		1 & 0.26183 & 2.908702 \\ 
		2 & 0.524076 & 5.805524 \\ 
		3 & 1.045942 & 11.555660 \\ 
		4 & 2.092989 & 23.178036 \\ 
		5 & 4.19515 & 46.164079\\ 
		6 & 8.361586 & 92.320173\\ 
		7 & 16.651607 & 185.292243\\
		\hline
	\end{tabular}
	\end{center}
\end{table}

\begin{table}[htbp]
	\caption{Time measurement of endpoint creation}
	\label{tab:endpoint_create}
	\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
		\hline
		1 & 0.256425 & 2.887064 \\ 
		2 & 0.505679 & 5.767912 \\ 
		3 & 0.999524 & 11.550455 \\ 
		4 & 1.994017 & 23.260508 \\ 
		5 & 3.965007 & 46.748366 \\ 
		6 & 7.918925 & 93.182975 \\ 
		7 & 16.561419 & 186.064562 \\
		\hline
	\end{tabular}
	\end{center}
\end{table}

The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_create}
    \caption{Time cost of MAM creation.}
    \label{fig:mam_create}
\end{figure}

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
\begin{itemize}
	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify. IOTA uses a Hashcash\cite{Hashcash} based puzzle.
\end{itemize}

Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform. Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint. The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a possible range.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_send}
    \caption{Time cost of sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios. Furthermore, sensors with the low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM and even trading process with subscribers simultaneously.

Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator\cite{TA}. Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator. However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{ta_structure}
    \caption{The structure of Tangle-accelerator.}
    \label{fig:ta_struct}
\end{figure}

\section{Conclusions}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}

### 2020-04-28 paper.tex
Modify first paragraph of Introduction

@@
 \begin{IEEEkeywords}
-publish/subscribe, decentralization, Distributed Ledger Technology
+Data Marketeplace, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 %TODO: cite examples
-In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly, and such technologies can be widely used in various fields, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}.
-As the physical and digital assets are deeply intertwined, the interactions among digital twins act as data exchanges.\cite{digitaltwin} With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is essential to build a secure, reliable and scalable data sharing services.
+In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly.
+As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving} and brings up new business models where data is considered as tradeable digital assets.
+With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
+And data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform.
 

### 2020-04-28 paper.tex
Add requirements of DM in Introduction

@@
 In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly.
-As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving} and brings up new business models where data is considered as tradeable digital assets.
+As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
 With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-And data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform.
+Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.
 
+Among the challenges of data marketplace\cite{BigDataMarket}, our proposed decentralized data marketplace in\cite{MyDataMarketplace} focuses on the following issues:
+
+\begin{itemize}
+	\item \textbf{Scalability}. 
+1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
+	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
+	\item \textbf{Confidentiality}. 
+1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
+	\item \textbf{Privacy}. 1) Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
+	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilatiy control. 
+\end{itemize}
+
+% may be removed
 The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.

### 2020-04-29 paper.tex
Reference our previous proposed DM

@@
 
-Among the challenges of data marketplace\cite{BigDataMarket}, our proposed decentralized data marketplace in\cite{MyDataMarketplace} focuses on the following issues:
-
+Among the challenges of data marketplace\cite{BigDataMarket}, we beleive the following four requirements and bases of a data marketplace system:
 \begin{itemize}
@@
 \end{itemize}
+
+In contrast to centralized architectures in [CITE_centralized_DM], our proposed decentralized data marketplace \cite{MyDataMarketplace} focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfils the aforementioned requirements.
 

### 2020-05-03 deprecated.tex
Add description of DM and why MAM

--- 2020-04-28 paper.tex
@@
-\documentclass[conference]{IEEEtran}
-
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{listings}
-\graphicspath{{./images/}}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-
-\title{A Decentralized Pub/Sub System for Trusted Machine Economy}
-
-\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jkrvivian@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jserv@ccns.ncku.edu.tw}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-chiaheng@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{IEEEkeywords}
-Data Marketeplace, decentralization, Distributed Ledger Technology
-\end{IEEEkeywords}
-
-\section{Introduction}
-%TODO: cite examples
-In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly.
-As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving} and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-And data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform.
-
+% may be removed
 The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
@@
 \end{enumerate}
-
-\section{Related Work}
-The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
-A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.
-
-M.
-B.
-Abdullahi and G.
-Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
-Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
-Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system.
-Also the storage is not well illustrated in the work.
-G.
-S.
-Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Smart Contract, usesrs can perform data validation easily, and brokers can keep track of data status.
-But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
-The economics incentives that can encourage the publishers to participate the system and pay more attention on the quilatiy control are not included.
-
-In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
-The subscribers request publisher directly and ask them to save a cache space for interested data.
-The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
-Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middlewares in the model and to provide a reputation-based fairness payment strategy on blockcahin.
-The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-The reputation system and the punishment rules against malicous acts of subscribers and publishers.
-Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
-Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
-
-Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-However, no cryptographic system is applied for user-uploaded files.
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
-Files are duplicated in multiple nodes to prevent data loss.
-
-\section{System Architecture}
-The proposed data subscription framework\cite{MyDataMarketplace} is a decentralized architecture with data providers, data subscribers and brokers that interact between data providers and subscribers, including data publishment, product metadata generation and trading process.
-
-\subsection{Participants}
-There are three major roles in the decentralized data marketplace (Fig.~\ref{fig:system_design}).
-
-\begin{itemize}
-\item \textbf{Data Provider: }
-Data providers generate and preserve streaming data, and are willing to provide streaming data to subscribers.
-Providers can use the subscription fee paid by subscribers to improve the quality of their service.
-\item \textbf{Subscribers: }
-Subscribers aspire to obtain streaming data to promote the value of their service.
-However, it is a significant challenge for most subscribers to collect the desired data by themselves, so they look to purchasing the streaming data from data providers.
-\item \textbf{Broker: }
-Brokers represent data providers and subscribers to perform blockchain computing tasks and are expected to have higher resource.
-The brokers are requested to handle the product launching and subscription process, and brokerage fees is charged in each process.
-\end{itemize}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{system_design}
-    \caption{The system design of a decentralized architecture which consists of data providers, subscribers and brokers.}
-    \label{fig:system_design}
-\end{figure}
-
-\subsection{Components}
-There are several building blocks in the proposed design to meet the expectations: 1) emit and access encrypted data stream; 2) retrieve transaction data for audit; 3) digital identity for all participants; and 4) enforcement of transparency and traceability.
-
-\subsubsection{Masked Authenticated Messaging}
-IOTA is a feeless cryptocurrency designed for IoT while MAM is the second layer data communication protocol built on top of the IOTA network, the Tangle.
-MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
-With MAM, the rights of accessing data is traded instead of a copy of data itself, which gives a flexibilty for subscribers to obtain data anywhere anywhen that subscribers do not need additional storage to store the data it buy.
-
-In the IOTA protocol, seed is the identifier of its owner.
-An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
-With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
-
-Either channel or endpoint is like a singly-linked list.
-The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint.
-Each address of a message can be derived from the previous one.
-A user can create multiple channels and multiple endpoints under the same channel.
-The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point.
-Fig.~\ref{fig:mam_struct} shows the architecture of MAM.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
-The authentication in MAM includes source and data authentication.
-Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
-However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation.
-Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.
-
-%use case illustration
-Data providers are the primary role to interact with the MAM.
-With a seed, a provider can start creating a channel and endpoint.
-As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy.
-Also data providers can a make product preview which is public and not encrypted on MAM.
-In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID.
-By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages.
-Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.
-
-The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world.
-Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data.
-And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data.
-This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.
-
-While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system.
-See Fig.~ \ref{fig:launching_product}.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
-
-\subsubsection{TangleID}
-The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint.
-With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
-Posting DID documents on MAM channel makes TangleID a GDPR-compliant system\cite{GDPR}.
-Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.
-
-A public/private key pair and an IOTA seed are generated in TangleID.
-The public MAM channel is created with the seed and its MAM channel ID becomes part of the unique user ID, which at the same time serves as DID with the purpose of publishing the public key of the entity.
-Private key along with the IOTA seed is stored in the local database of the entity.
-The public/private key pair can be used in secure message sharing within users and digital signature.
-
-The digital identities are also used to establish trust between the communication partners.
-This is done on two levels to prove that the communication partner owns the DID and the partner can, optionally, proof that it is a trusted participant.
-This authentication process happens during the first messages of interaction.
-In order for one partner to listen to another, it authenticates the messages.
-The DID ownership authentication is done by proving a digitally signed copy of the DID document.
-
-The authentication of trust between the two parties is based on a Verifiable Credential, given out by a trusted issuer for the receiving party.
-If the receiving party does not trust the issuer, the credential is deemed worthless.
-If the party is recognized, the credential is verified and the messages will be labelled as trusted.
-In order to acquire this credential, the party needs to contact the issuer and ask for the credential.
-The issuer will need to know the DID of the party.
-If they decide to give out the credential, the issuer will sign the credential and send it encrypted over the blockchain to the requesting party's communication address.
-This is listed as a Service Endpoint (DID standard) in the DID Document of the requesting party.
-
-\subsubsection{Ethereum Smart Contract}
-The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
-The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All conditions and states established in the contract are transparent and enforceable.
-The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
-
-The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address.
-Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers.
-Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers.
-The further details of key exchangement will be illustrated in Section~\ref{section:trading}.
-
-\subsubsection{Blind Signature}
-There is an inherent risk in revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses.
-Therefore, a blind signature is used to prevent session key copying for such circumstances.
-A blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-Fig.~\ref{fig:blind_signature} illustrates the steps of blind signature.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signatures during the process of adding new products for data providers, in order to send the secret key of the MAM channel to the smart contract without knowing it.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=2. in]{blind_signature}
-	\caption{The scheme of blind signature.}
-	\label{fig:blind_signature}
-\end{figure}
-
-RSA blind signature\cite{cryptoNote} is used in our research.
-The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
-To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
-
-\begin{equation}
-C = r^e m
-\end{equation}
-
-The signer signs the blinding message with private key $d$.
-
-\begin{equation}
-S = C^d
-\end{equation}
-
-$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
-
-\begin{equation}
-\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
-\end{equation}
-
-The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
-
-\section{Trading Model}
-In the following, we describe the data trading process in detail.
-To participate a data marketplace, data providers and subscribers have to first register.
-Then,  the data provider can launch its product on the marketplace.
-Once a product is launched, it is searchable on IPFS where brokers upload the information of the product and can be subsequently traded.
-The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
-
-\subsection{Set up}
-At the beginning, all participant need to register on TangleID in order to get a DID document and public/private key pairs.
-The DID document is shared within the following operations to perform authentication, key exchangement and secure communication.
-
-\subsection{Trading}
-\label{section:trading}
-
-The entire trading process is as shown in Fig.~\ref{fig:trading_product}.
-Once a subscriber wants to subscribe certain streaming data that is generated, he/she has to pay subscription fee to the Product Contract and will be automatically added to the subscriber list by the smart contract.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{trading_product}
-    \caption{The process for the product trading.}
-    \label{fig:trading_product}
-\end{figure}
-
-In the proposed architecture, the "access" to specific data stream is traded instead of giving out the raw data copies.
-Subscribers can retrieve data on MAM at any time without equipping extra storage to preserve data, and one can also query for arbitrary section of data rather downloading them all.
-Thus, the most important part of trading process is to give the session key $k$, the encryption key of data stream, to the subscribers.
-In order to exchange data, Azaria et al\cite{Medrec} seek an off-chain solution which is based on an end-to-end communication to ensure the efficiency and low costs.
-However, it is hard to avoid that the data source is unavailable or the sender sends incorrect data intentionally.
-Instead of the off-chain solution, we use smart contract to transfer the session key\cite{3tierDataMarket} that not only ensures the consistency of the session key, the availability of the source and the traceability of the record, but also prevents malicious participants to cheat others.
-With the help of brokers and smart contracts, both providers and subscribers do not need to be online at the same time to proceed the trading process.
-
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
-\lstset{style=solidity}
-
-\begin{lstlisting}[caption={Update encryption key}, label={lst:key_exchange}, frame=single]
-function addEncryptKey(
-  address _subscriber,
-  string memory _encryptKey
-) public {
-  require(
-      msg.sender == provider,
-      "Only provider can add blindedKey."
-  );
-  require(
-      subscriber2Purchase[_subscriber].isKeyAdded == false,
-      "One encryptKey has been added."
-  );
-  subscriber2Purchase[_subscriber].encryptKey = _encryptKey;
-  subscriber2Purchase[_subscriber].isKeyAdded = true;
-  emit newEncryptKey(_subscriber, _encryptKey);
-}
-\end{lstlisting}
-
-The trading process is shown in Fig.~\ref{fig:key_exchange}.
-The data provider can obtain public keys of each subscriber from the DID document.
-For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract by calling $addEncryptKey()$ (Listing \ref{lst:key_exchange}).
-Subscribers listen to the $newEncryptKey$ event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{key_exchange}
-    \caption{Session key exchange process between the data provider and subscriber.}
-    \label{fig:key_exchange}
-\end{figure}
-
-Subscribers can obtain the broker's public key on the DID document as well, so they can verify that the validation of signature and the session key is the only one certified by the broker.
-Afterward, with the MAM channel ID and session key $k$, subscribers can obtain the data.
-
-\subsection{Refunding}
-
-It is probable that the streaming data sources are delayed or even interrupted after the subscribers pay the subscription fee.
-To protect subscriber rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel.
-If the expected data is not available, subscribers can request refunds.
-We assume that a very small percentage of subscribers in the product contract are irrational and/or malicious.
-When a subscriber consents to refund, he can vote at any time.
-After the ratio of consent votes of refunding is higher than the $threshold$, the subscription fee is proportionally transferred to the data provider, broker and every subscriber.
-Fig.~\ref{fig:refund} shows the refund process.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=1.5in]{refund}
-	\caption{The process of refund.}
-	\label{fig:refund}
-\end{figure}
-
-The subscription fee can be prorated as below:
-
-\begin{equation}
-    F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Broker}(i) = N price \frac{i-1}{M} F_{b} -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Subscriber}(i) = price \frac{M-i+1}{M} -F_{t}
-\end{equation}
-
-where $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of subscribers in this contract.
-
-To refund or withdraw subscription fees from the smart contract, the data provider, broker, and subscriber send a transaction to execute the smart contract and are responsible for the transaction fee.
-We assume that only a half of the expected records are published to the MAM channel.
-When $F_{b}$ is 5\%, the data provider and broker can withdraw half of the total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
-For subscribers, they can receive half of the subscription fee refunded which should be deducted from the transaction fee.
-
-Considering the situation that one of the subscribers requests a refund in the future, when the subscriber is disappointed with the data quality, he/she may request a refund.
-
-\section{Evaluations}
-It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
-Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle.
-Therefore, in the following evaluations, all devices run with client library only.
-
-\subsection{MAM Performance Evaluation}
-MAM is a secure and validatable data storage of the proposed architecture.
-And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections.
-The interactions between data providers and MAM can be frequent.
-Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-
-In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and data attachment to endpoints.
-To perform the evaluation assessment, a personal computer (PC, 3.2GHz 64-bit 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (1.2 GHz 64-bit quad-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
-
-\subsubsection{Channel / Endpoint Creation}
-The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint.
-A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total.
-The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required.
-In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
-The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}.
-The time duration for each \textit{height} is the average time of running 100 rounds.
-
-\begin{table}[htbp]
-	\caption{Time measurement of channel creation}
-	\label{tab:channel_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.26183 & 2.908702 \\ 
-		2 & 0.524076 & 5.805524 \\ 
-		3 & 1.045942 & 11.555660 \\ 
-		4 & 2.092989 & 23.178036 \\ 
-		5 & 4.19515 & 46.164079\\ 
-		6 & 8.361586 & 92.320173\\ 
-		7 & 16.651607 & 185.292243\\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Time measurement of endpoint creation}
-	\label{tab:endpoint_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.256425 & 2.887064 \\ 
-		2 & 0.505679 & 5.767912 \\ 
-		3 & 0.999524 & 11.550455 \\ 
-		4 & 1.994017 & 23.260508 \\ 
-		5 & 3.965007 & 46.748366 \\ 
-		6 & 7.918925 & 93.182975 \\ 
-		7 & 16.561419 & 186.064562 \\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}.
-Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
-On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above.
-And the performance of PC remains acceptable even \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{mam_create}
-    \caption{Time cost of MAM creation.}
-    \label{fig:mam_create}
-\end{figure}
-
-\subsubsection{Messages Publishment}
-Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
-\begin{itemize}
-	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
-	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network.
-A computationally hard puzzle to solve, but easy to verify.
-IOTA uses a Hashcash\cite{Hashcash} based puzzle.
-\end{itemize}
-
-Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
-The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a possible range.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{mam_send}
-    \caption{Time cost of sending a message through MAM.}
-    \label{fig:mam_send}
-\end{figure}
-
-The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
-Furthermore, sensors with the low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM and even trading process with subscribers simultaneously.
-
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator\cite{TA}.
-Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration.
-Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator.
-However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{ta_structure}
-    \caption{The structure of Tangle-accelerator.}
-    \label{fig:ta_struct}
-\end{figure}
-
-\section{Conclusions}
-By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2020-05-03 paper.tex
Add description of DM and why MAM

--- 2020-04-28 paper.tex
@@
 
-Among the challenges of data marketplace\cite{BigDataMarket}, our proposed decentralized data marketplace in\cite{MyDataMarketplace} focuses on the following issues:
-
+Among the challenges of data marketplace\cite{BigDataMarket}, we conclude the following four essential requirements of a data marketplace system:
 \begin{itemize}
@@
 1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
-	\item \textbf{Privacy}. 1) Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
-	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilatiy control. 
+	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
+	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilaty control. 
 \end{itemize}
 
-% may be removed
-The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
-In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers.
-Broker is a centralized group that arrange the communication between the publishers and subscribers.
-However, the centralized architecture brings potential vulnerabilities and security issues:
+In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
+Moreover, a decentralized architecture can better adapts the dynamic roles than centralized one.
 
-\begin{enumerate}
-	\item Central point of failure. 
-	The broker is usually held by a single organization. If the centralized server is crashed or attacked, the services will not be available. 	
-	\item Data integrity.
-	As broker controls the interaction between publishers and subscribers, an unreliable or compromised broker can easily tamper data streams. 
-	\item Anonymity and privacy.
-	Broker matches publishers and subscribers in order to relay data streams to corresponding entities.
-The unreliable broker can expose the subscribers' interests and personal information of both entities.
-\end{enumerate}
+\subsection{Towards Decentralized Data Marketplace}
+In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly  Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Message (MAM)\cite{MAM}.
+
+The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
+Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities of centralized pub/sub models, for instance, central point of failure, if the centralized server is crashed or attacked, the services will not be available.
+Therefore, we adopted decentralized pub/sub with no organization holding brokers, and the brokers are only responsible for data transmission and agreement establishment.
+Furthermore, the communication between entities is built via brokers, which prevents sensitive information leaks.
+Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.
+
+Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated.
+This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality.
+Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.
+
+Another key component MAM is viewed as the data storage of data marketplace which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT.
+MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
+Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the  disconnection does not exist, participants can retrieve the authoraized data streams anytime.
+
+\subsection{Choice of Data Storage}
+In our proposed architecture, MAM is the data storage where the data assets is reserved.
+However, the operations of MAM are time-consuming for IoT devices, which are evaluated in Section CITE-EVALUATION-SECTION.
+We assume the data assets are stored in distributed data storage systems built on top of peer-to-peer (P2P) networks maintained by multiple nodes, which avoid the central point failure and security issues of central databases.
+Among the existing distributed storage studied in Section CITE-RELATED-WORK, different backup mechanisms and access controls strategies are proposed, however, the keys managed by participant is hard to be as small as possible especially for data streams, which is one of the scalability requirement of data marketplace mentioned above.
+
+\subsection{Contributions}
+
+\subsection{Paper Organization}
 

### 2020-05-05 deprecated.tex
Reduce the length of our DM description

@@
 \end{enumerate}
+
+% move belows to background-archi
+The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
+Connections of participants are built via brokers, which can avert sensitive information leaks in order to establish communication.
+Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities, for instance, the services are paralyzed if the server is crashed or attacked.
+Therefore, we adopted decentralized pub/sub model with no organization holding brokers.
+Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.
+
+Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated.
+This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality.
+Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.

### 2020-05-05 paper.tex
Reduce the length of our DM description

@@
 
-\subsection{Towards Decentralized Data Marketplace}
 In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Message (MAM)\cite{MAM}.
-
-The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
-Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities of centralized pub/sub models, for instance, central point of failure, if the centralized server is crashed or attacked, the services will not be available.
-Therefore, we adopted decentralized pub/sub with no organization holding brokers, and the brokers are only responsible for data transmission and agreement establishment.
-Furthermore, the communication between entities is built via brokers, which prevents sensitive information leaks.
-Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.
-
-Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated.
-This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality.
-Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.
-
-Another key component MAM is viewed as the data storage of data marketplace which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT.
-MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
-Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the  disconnection does not exist, participants can retrieve the authoraized data streams anytime.
+The pub/sub model features the scalability and resource-effieciency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
+Lastly, MAM as the data storage not only ensures the data integrity, enables access control and provides a scalable key management.
+The three keys of decentralized data marketplace meet the requirements metioned previously.
 
@@
 In our proposed architecture, MAM is the data storage where the data assets is reserved.
-However, the operations of MAM are time-consuming for IoT devices, which are evaluated in Section CITE-EVALUATION-SECTION.
-We assume the data assets are stored in distributed data storage systems built on top of peer-to-peer (P2P) networks maintained by multiple nodes, which avoid the central point failure and security issues of central databases.
-Among the existing distributed storage studied in Section CITE-RELATED-WORK, different backup mechanisms and access controls strategies are proposed, however, the keys managed by participant is hard to be as small as possible especially for data streams, which is one of the scalability requirement of data marketplace mentioned above.
+MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT.
+MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
+Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authoraized data streams anytime.
 

### 2020-05-06 deprecated.tex
Finish the initial version of Introduction

@@
 Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.
+
+In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT.
+MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
+Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authoraized data streams anytime.
+
+% MAM performance
+optimizing layers of MAM and compare the performance of different cryptosystems.
+Furthermore, we take offloading MAM operations to brokers as another solution to reduce the workload of IoT devices, since the brokers are considered to have higher computating power.
+In Section CITE-TA-SECTION, the security issues and methods of offloading will be discussed carefully.

### 2020-05-06 paper.tex
Finish the initial version of Introduction

@@
 In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly.
-As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
+As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
 With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
@@
 	\item \textbf{Scalability}. 
-1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
+1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys and entry points of data products managed by participants should be as small as possible. 
 	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
@@
 Moreover, a decentralized architecture can better adapts the dynamic roles than centralized one.
+See Fig.~\ref{fig:system_design}.
 
-In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Message (MAM)\cite{MAM}.
+In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}.
 The pub/sub model features the scalability and resource-effieciency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
-Lastly, MAM as the data storage not only ensures the data integrity, enables access control and provides a scalable key management.
-The three keys of decentralized data marketplace meet the requirements metioned previously.
+Lastly, MAM as the data storage not only ensures the data integrity, enables access control and provides a scalable key and data management.
+These three keys meet the requirements metioned previously.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{system_design}
+    \caption{The system design of a decentralized data marketplace which consists of data providers, subscribers and brokers.}
+    \label{fig:system_design}
+\end{figure}
 
 \subsection{Choice of Data Storage}
-In our proposed architecture, MAM is the data storage where the data assets is reserved.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT.
-MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
-Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authoraized data streams anytime.
+Data storage is an important element of data marketplace where the data assets are reserved.
+We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes.
+Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed.
+Among the existing distributed storage mentioned in Section.
+CITE-RELATED-WORK, different architectures, back-up mechanisms and access controls strategies are proposed.
+Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.
+
+In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT.
+MAM allows users to put encrypted data streams into \textbf{channel}s and \textbf{endpoint}s, which consist of zero-value transactions on the Tangle.
+With an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
+Assuming the length of data stream is 7, and each record is encrypted with the same key.
+With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
+
+\begin{table}[htbp]
+	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
+	\label{tab:mam_scalability}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
+		\hline
+		keys & 1 & 1 \\ 
+		\hline
+		entry points & 1 & 7 \\ 
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
+Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
 
 \subsection{Contributions}
+The contributions in the paper are summarized as follow:
+\begin{itemize}
+	\item Standing on our proposed decentralized data marketplace, we review several decentralized data marketplace architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
+    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
+We also compare the perfomance of exchanging different cryptosystems.
+	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
+\end{itemize}
 
 \subsection{Paper Organization}
+The rest of this paper is organized as follows.
+In Section RELATED-WORK, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
+In Section BACKGROUND, the architecture of our proposed decentralized data marketplace is illustrated.
+In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained.
+The analysis and improvement of MAM are given in Section MAM-EXP.
+In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully.
+Finally, we conclude the paper in Section CONCLUSION.
 
@@
 \end{itemize}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{system_design}
-    \caption{The system design of a decentralized architecture which consists of data providers, subscribers and brokers.}
-    \label{fig:system_design}
-\end{figure}
 

### 2020-05-11 paper.tex
Rename subscribers to consumers
Fix typo

@@
     \includegraphics[width=3.in]{system_design}
-    \caption{The system design of a decentralized data marketplace which consists of data providers, subscribers and brokers.}
+    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
     \label{fig:system_design}
@@
 But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
-The economics incentives that can encourage the publishers to participate the system and pay more attention on the quilatiy control are not included.
+The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.
 

### 2020-05-12 paper.tex
Add DM architecture and smart contract

@@
 The rest of this paper is organized as follows.
+In Section BACKGROUND, the architecture of our proposed decentralized data marketplace is illustrated.
 In Section RELATED-WORK, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
-In Section BACKGROUND, the architecture of our proposed decentralized data marketplace is illustrated.
 In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained.
@@
 Finally, we conclude the paper in Section CONCLUSION.
+
+\section{Background}
+In this section, we review the architecture of decentralized data marketplace and the two key components, Ethereum Smart Contract and MAM.
+
+\subsection{Participants in Decentralized Data Marketplace}
+There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+Fig.~\ref{fig:system_design}
+
+\begin{itemize}
+\item \textbf{Data Provider: }
+Data providers can either generate, filter ,or process streaming data.
+The price of data products can They can make use of subscription fee that earned via trading for maintaining the equipment and improving the quality of data.
+\item \textbf{Data Consumer: }
+Data consumers are entities that are willing to buy data streams or high quality data sets.
+As data streams can be used in various applications and researches, it is hard to collect data from scratch.
+Thus, purchase is the fastest way to reach the goal.
+\item \textbf{Broker: }
+Brokers are responsible for building agreement between data providers and consumers.
+Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
+\end{itemize}
+
+\subsection{Ethereum Smart Contract}
+Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
+It also provides a decentralized virtual machine that can perform the smart contract which is written by turing complete scripting
+language.
+
+The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
+The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
+All conditions and states established in the contract are transparent and enforceable.
+The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
+
+% to be removed
+The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address.
+Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers.
+Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers.
+The further details of key exchangement will be illustrated in Section~\ref{section:trading}.
 
@@
 The proposed data subscription framework\cite{MyDataMarketplace} is a decentralized architecture with data providers, data subscribers and brokers that interact between data providers and subscribers, including data publishment, product metadata generation and trading process.
-
-\subsection{Participants}
-There are three major roles in the decentralized data marketplace (Fig.~\ref{fig:system_design}).
-
-\begin{itemize}
-\item \textbf{Data Provider: }
-Data providers generate and preserve streaming data, and are willing to provide streaming data to subscribers.
-Providers can use the subscription fee paid by subscribers to improve the quality of their service.
-\item \textbf{Subscribers: }
-Subscribers aspire to obtain streaming data to promote the value of their service.
-However, it is a significant challenge for most subscribers to collect the desired data by themselves, so they look to purchasing the streaming data from data providers.
-\item \textbf{Broker: }
-Brokers represent data providers and subscribers to perform blockchain computing tasks and are expected to have higher resource.
-The brokers are requested to handle the product launching and subscription process, and brokerage fees is charged in each process.
-\end{itemize}
 
@@
 This is listed as a Service Endpoint (DID standard) in the DID Document of the requesting party.
-
-\subsubsection{Ethereum Smart Contract}
-The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
-The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All conditions and states established in the contract are transparent and enforceable.
-The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
-
-The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address.
-Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers.
-Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers.
-The further details of key exchangement will be illustrated in Section~\ref{section:trading}.
-
-\subsubsection{Blind Signature}
-There is an inherent risk in revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses.
-Therefore, a blind signature is used to prevent session key copying for such circumstances.
-A blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-Fig.~\ref{fig:blind_signature} illustrates the steps of blind signature.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-In our system design, brokers would perform blind signatures during the process of adding new products for data providers, in order to send the secret key of the MAM channel to the smart contract without knowing it.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=2. in]{blind_signature}
-	\caption{The scheme of blind signature.}
-	\label{fig:blind_signature}
-\end{figure}
-
-RSA blind signature\cite{cryptoNote} is used in our research.
-The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
-To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
-
-\begin{equation}
-C = r^e m
-\end{equation}
-
-The signer signs the blinding message with private key $d$.
-
-\begin{equation}
-S = C^d
-\end{equation}
-
-$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
-
-\begin{equation}
-\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
-\end{equation}
-
-The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
 

### 2020-05-13 paper.tex
Fix typos

--- 2020-05-11 paper.tex
@@
 %TODO: cite examples
-In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly.
-As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.
+In the Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly.
+As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
+With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
+Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.
 
@@
 	\item \textbf{Scalability}. 
-1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys and entry points of data products managed by participants should be as small as possible. 
+1) The performance of data marketplace should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
 	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
@@
 1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
-	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
-	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilaty control. 
+	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
+	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
 \end{itemize}
@@
 In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
-Moreover, a decentralized architecture can better adapts the dynamic roles than centralized one.
+Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one.
 See Fig.~\ref{fig:system_design}.
 
-In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}.
-The pub/sub model features the scalability and resource-effieciency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
-Lastly, MAM as the data storage not only ensures the data integrity, enables access control and provides a scalable key and data management.
-These three keys meet the requirements metioned previously.
+In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger technologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}.
+The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
+Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+These three keys meet the requirements mentioned previously.
 

### 2020-05-13 paper.tex
Modify Background smart contract

--- 2020-05-12 paper.tex
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{system_design}
-    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
-    \label{fig:system_design}
-\end{figure}
-
 \subsection{Choice of Data Storage}
@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{system_design}
+    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
+    \label{fig:system_design}
+\end{figure}
+
 \section{Background}
-In this section, we review the architecture of decentralized data marketplace and the two key components, Ethereum Smart Contract and MAM.
+In this section, we review the architecture of decentralized data marketplace and the two key components in the system, Ethereum Smart Contract and MAM.
 
@@
 There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others.
+In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
 Fig.~\ref{fig:system_design}
@@
 \item \textbf{Data Provider: }
-Data providers can either generate, filter ,or process streaming data.
-The price of data products can They can make use of subscription fee that earned via trading for maintaining the equipment and improving the quality of data.
+Data providers are the ones that generate, or filter streaming data, and set the data price based on the different types of data.
+With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
 \item \textbf{Data Consumer: }
-Data consumers are entities that are willing to buy data streams or high quality data sets.
-As data streams can be used in various applications and researches, it is hard to collect data from scratch.
-Thus, purchase is the fastest way to reach the goal.
+Data consumers are entities that are willing to buy data streams.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
 \item \textbf{Broker: }
-Brokers are responsible for building agreement between data providers and consumers.
+Brokers are responsible for building an agreement between data providers and consumers.
 Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
@@
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. 
-It also provides a decentralized virtual machine that can perform the smart contract which is written by turing complete scripting
-language.
+It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines.
+A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
+All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it will be executed automatically without any third-parties and it is uninterruptible.
 
-The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract.
-The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All conditions and states established in the contract are transparent and enforceable.
-The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
-
-% to be removed
-The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address.
-Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers.
-Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers.
-The further details of key exchangement will be illustrated in Section~\ref{section:trading}.
+With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived.
+\textbf{Product Contract} is made for the product launching and trading process in the decentralized data marketplace.
+The information of data products such as MAM channel ID (the data entry point), data price, time period and the broker-verified encryption key are listed on Product Contract.
+Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
+Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of both providers and subscribers.
 

### 2020-05-13 deprecated.tex
Add Background MAM

@@
 In Section CITE-TA-SECTION, the security issues and methods of offloading will be discussed carefully.
+
+\subsection{Masked Authenticated Messaging}
+MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to IOTA ledger, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
+With MAM, the rights of data access is traded instead of a copy of data itself, which eliminates the need for data consumers to have additional storage.
+
+In the IOTA protocol, \textbf{seed} is the identifier of its owner.
+An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
+With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
+
+Either channel or endpoint is like a singly-linked list.
+The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint.
+Each address of a message can be derived from the previous one.
+A user can create multiple channels and multiple endpoints under the same channel.
+The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point.
+Fig.~\ref{fig:mam_struct} shows the architecture of MAM.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
+\end{figure}
+
+The authentication in MAM includes source and data authentication.
+Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation.
+Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.
+
+%use case illustration
+Data providers are the primary role to interact with the MAM.
+With a seed, a provider can start creating a channel and endpoint.
+As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy.
+Also data providers can a make product preview which is public and not encrypted on MAM.
+In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID.
+By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages.
+Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.
+
+The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world.
+Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data.
+And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data.
+This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.
+
+While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system.
+See Fig.~ \ref{fig:launching_product}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
+\end{figure}

### 2020-05-13 paper.tex
Add Background MAM

@@
 
+\subsection{Masked Authenticated Messaging}
+MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to IOTA ledger, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
+With MAM, the rights of data access is traded instead of a copy of data itself, which eliminates the need for data consumers to have additional storage.
+
+In the IOTA protocol, \textbf{seed} is the identifier of its owner.
+An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
+With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
+
+Either channel or endpoint is like a singly-linked list.
+The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint.
+Each address of a message can be derived from the previous one.
+A user can create multiple channels and multiple endpoints under the same channel.
+The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point.
+Fig.~\ref{fig:mam_struct} shows the architecture of MAM.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
+\end{figure}
+
+The authentication in MAM includes source and data authentication.
+Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation.
+Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.
+
+%to be modify
+Data providers are the primary role to interact with the MAM.
+With a seed, a provider can start creating a channel and endpoint.
+As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy.
+Also data providers can a make product preview which is public and not encrypted on MAM.
+In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID.
+By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages.
+Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.
+
+The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world.
+Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data.
+And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data.
+This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.
+
+While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system.
+See Fig.~ \ref{fig:launching_product}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
+\end{figure}
+
 \section{Related Work}
@@
 There are several building blocks in the proposed design to meet the expectations: 1) emit and access encrypted data stream; 2) retrieve transaction data for audit; 3) digital identity for all participants; and 4) enforcement of transparency and traceability.
-
-\subsubsection{Masked Authenticated Messaging}
-IOTA is a feeless cryptocurrency designed for IoT while MAM is the second layer data communication protocol built on top of the IOTA network, the Tangle.
-MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
-With MAM, the rights of accessing data is traded instead of a copy of data itself, which gives a flexibilty for subscribers to obtain data anywhere anywhen that subscribers do not need additional storage to store the data it buy.
-
-In the IOTA protocol, seed is the identifier of its owner.
-An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
-With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
-
-Either channel or endpoint is like a singly-linked list.
-The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint.
-Each address of a message can be derived from the previous one.
-A user can create multiple channels and multiple endpoints under the same channel.
-The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point.
-Fig.~\ref{fig:mam_struct} shows the architecture of MAM.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
-The authentication in MAM includes source and data authentication.
-Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
-However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation.
-Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.
-
-%use case illustration
-Data providers are the primary role to interact with the MAM.
-With a seed, a provider can start creating a channel and endpoint.
-As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy.
-Also data providers can a make product preview which is public and not encrypted on MAM.
-In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID.
-By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages.
-Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.
-
-The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world.
-Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data.
-And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data.
-This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.
-
-While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system.
-See Fig.~ \ref{fig:launching_product}.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
 

### 2020-05-15 paper.tex
Modify Background MAM

@@
 \subsection{Masked Authenticated Messaging}
-MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to IOTA ledger, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
-With MAM, the rights of data access is traded instead of a copy of data itself, which eliminates the need for data consumers to have additional storage.
+MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control.
+With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.
 
@@
 An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
-With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
+With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
 
 Either channel or endpoint is like a singly-linked list.
-The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint.
-Each address of a message can be derived from the previous one.
-A user can create multiple channels and multiple endpoints under the same channel.
-The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point.
-Fig.~\ref{fig:mam_struct} shows the architecture of MAM.
+The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
+Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
+A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
+The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+
+A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
 
@@
 
-The authentication in MAM includes source and data authentication.
-Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+The authentication in MAM includes two aspects: source and data.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
 These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
-However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation.
-Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.
+However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
+Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
 
-%to be modify
-Data providers are the primary role to interact with the MAM.
-With a seed, a provider can start creating a channel and endpoint.
-As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy.
-Also data providers can a make product preview which is public and not encrypted on MAM.
-In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID.
-By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages.
-Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.
-
-The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world.
-Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data.
-And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data.
-This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.
-
-While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system.
-See Fig.~ \ref{fig:launching_product}.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
@@
 Once a subscriber wants to subscribe certain streaming data that is generated, he/she has to pay subscription fee to the Product Contract and will be automatically added to the subscriber list by the smart contract.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
+\end{figure}
 

### 2020-05-23 paper.tex
Add data marketplace workflow to Background

@@
 The rest of this paper is organized as follows.
-In Section BACKGROUND, the architecture of our proposed decentralized data marketplace is illustrated.
-In Section RELATED-WORK, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
+In Section~\ref{section:background}, the architecture of our proposed decentralized data marketplace is illustrated.
+In Section~\ref{section:relatedWork}, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
 In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained.
@@
 \section{Background}
-In this section, we review the architecture of decentralized data marketplace and the two key components in the system, Ethereum Smart Contract and MAM.
-
-\subsection{Participants in Decentralized Data Marketplace}
-There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others.
-In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-Fig.~\ref{fig:system_design}
-
-\begin{itemize}
-\item \textbf{Data Provider: }
-Data providers are the ones that generate, or filter streaming data, and set the data price based on the different types of data.
-With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
-\item \textbf{Data Consumer: }
-Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
-\item \textbf{Broker: }
-Brokers are responsible for building an agreement between data providers and consumers.
-Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
-\end{itemize}
+\label{section:background}
+In this section, we review Ethereum Smart Contract, MAM, the architecture and workflow of decentralized data marketplace.
 
@@
 
+\subsection{Participants in Decentralized Data Marketplace}
+There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others.
+In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+Fig.~\ref{fig:system_design}
+
+\begin{itemize}
+\item \textbf{Data Provider: }
+Data providers are the ones that generate streaming data and set the data price based on the different types of data.
+With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
+\item \textbf{Data Consumer: }
+Data consumers are entities that are willing to buy data streams.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
+\item \textbf{Broker: }
+Brokers are responsible for building an agreement between data providers and consumers.
+Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
+\end{itemize}
+
+\subsection{Trading Models of Decentralized Data Marketplace}
+\subsubsection{Set Up}
+All participants need to register on TangleID\cite{TangleID}, a self-soverign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
+
+\subsubsection{Launch Data Products}
+To launch a data product, data providers need to create a MAM channel/endpoint and a Product Contract.
+However, considering IoT devices have no ability to handle both uploading data to MAM and interacting Ethereum smart contracts while collecting continuous data with low computing power, these works are offloaded to brokers.
+
+The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract.
+As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract.
+This provides an approach for data consumers to verify the encryption key that avoid data providers frauding data consumers with a wrong one.
+The workflow is shown in Fig.~\ref{fig:launching_product}.
+
+Data providers start uploading data once the MAM channel/endpoint are created, each MAM message contains encrypted contexts along with signatures which allows data consumers to check the integrity.
+In addition, one can perform the signature validation without the encryption key on MAM.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
+\end{figure}
+
+\subsubsection{Trading}
+Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retreive it from Product Contract.
+
+Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants.
+Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
+The key sending process is shown in Fig.~\ref{fig:key_exchange}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{key_exchange}
+    \caption{Encryption key exchangement process.}
+    \label{fig:key_exchange}
+\end{figure}
+
+\subsubsection{Refunding}
+Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after recieving the subscription fee.
+Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective.
+The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
+When the refund procedure is launched, all consumers start voting based on their opinions on the data product.
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
+
 \section{Related Work}
+\label{section:relatedWork}
 The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
@@
 Files are duplicated in multiple nodes to prevent data loss.
-
-\section{System Architecture}
-The proposed data subscription framework\cite{MyDataMarketplace} is a decentralized architecture with data providers, data subscribers and brokers that interact between data providers and subscribers, including data publishment, product metadata generation and trading process.
-
-\subsection{Components}
-There are several building blocks in the proposed design to meet the expectations: 1) emit and access encrypted data stream; 2) retrieve transaction data for audit; 3) digital identity for all participants; and 4) enforcement of transparency and traceability.
-
-\subsubsection{TangleID}
-The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint.
-With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C.
-Posting DID documents on MAM channel makes TangleID a GDPR-compliant system\cite{GDPR}.
-Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.
-
-A public/private key pair and an IOTA seed are generated in TangleID.
-The public MAM channel is created with the seed and its MAM channel ID becomes part of the unique user ID, which at the same time serves as DID with the purpose of publishing the public key of the entity.
-Private key along with the IOTA seed is stored in the local database of the entity.
-The public/private key pair can be used in secure message sharing within users and digital signature.
-
-The digital identities are also used to establish trust between the communication partners.
-This is done on two levels to prove that the communication partner owns the DID and the partner can, optionally, proof that it is a trusted participant.
-This authentication process happens during the first messages of interaction.
-In order for one partner to listen to another, it authenticates the messages.
-The DID ownership authentication is done by proving a digitally signed copy of the DID document.
-
-The authentication of trust between the two parties is based on a Verifiable Credential, given out by a trusted issuer for the receiving party.
-If the receiving party does not trust the issuer, the credential is deemed worthless.
-If the party is recognized, the credential is verified and the messages will be labelled as trusted.
-In order to acquire this credential, the party needs to contact the issuer and ask for the credential.
-The issuer will need to know the DID of the party.
-If they decide to give out the credential, the issuer will sign the credential and send it encrypted over the blockchain to the requesting party's communication address.
-This is listed as a Service Endpoint (DID standard) in the DID Document of the requesting party.
-
-\section{Trading Model}
-In the following, we describe the data trading process in detail.
-To participate a data marketplace, data providers and subscribers have to first register.
-Then,  the data provider can launch its product on the marketplace.
-Once a product is launched, it is searchable on IPFS where brokers upload the information of the product and can be subsequently traded.
-The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.
-
-\subsection{Set up}
-At the beginning, all participant need to register on TangleID in order to get a DID document and public/private key pairs.
-The DID document is shared within the following operations to perform authentication, key exchangement and secure communication.
-
-\subsection{Trading}
-\label{section:trading}
-
-The entire trading process is as shown in Fig.~\ref{fig:trading_product}.
-Once a subscriber wants to subscribe certain streaming data that is generated, he/she has to pay subscription fee to the Product Contract and will be automatically added to the subscriber list by the smart contract.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{trading_product}
-    \caption{The process for the product trading.}
-    \label{fig:trading_product}
-\end{figure}
-
-In the proposed architecture, the "access" to specific data stream is traded instead of giving out the raw data copies.
-Subscribers can retrieve data on MAM at any time without equipping extra storage to preserve data, and one can also query for arbitrary section of data rather downloading them all.
-Thus, the most important part of trading process is to give the session key $k$, the encryption key of data stream, to the subscribers.
-In order to exchange data, Azaria et al\cite{Medrec} seek an off-chain solution which is based on an end-to-end communication to ensure the efficiency and low costs.
-However, it is hard to avoid that the data source is unavailable or the sender sends incorrect data intentionally.
-Instead of the off-chain solution, we use smart contract to transfer the session key\cite{3tierDataMarket} that not only ensures the consistency of the session key, the availability of the source and the traceability of the record, but also prevents malicious participants to cheat others.
-With the help of brokers and smart contracts, both providers and subscribers do not need to be online at the same time to proceed the trading process.
-
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
-\lstset{style=solidity}
-
-\begin{lstlisting}[caption={Update encryption key}, label={lst:key_exchange}, frame=single]
-function addEncryptKey(
-  address _subscriber,
-  string memory _encryptKey
-) public {
-  require(
-      msg.sender == provider,
-      "Only provider can add blindedKey."
-  );
-  require(
-      subscriber2Purchase[_subscriber].isKeyAdded == false,
-      "One encryptKey has been added."
-  );
-  subscriber2Purchase[_subscriber].encryptKey = _encryptKey;
-  subscriber2Purchase[_subscriber].isKeyAdded = true;
-  emit newEncryptKey(_subscriber, _encryptKey);
-}
-\end{lstlisting}
-
-The trading process is shown in Fig.~\ref{fig:key_exchange}.
-The data provider can obtain public keys of each subscriber from the DID document.
-For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract by calling $addEncryptKey()$ (Listing \ref{lst:key_exchange}).
-Subscribers listen to the $newEncryptKey$ event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{key_exchange}
-    \caption{Session key exchange process between the data provider and subscriber.}
-    \label{fig:key_exchange}
-\end{figure}
-
-Subscribers can obtain the broker's public key on the DID document as well, so they can verify that the validation of signature and the session key is the only one certified by the broker.
-Afterward, with the MAM channel ID and session key $k$, subscribers can obtain the data.
-
-\subsection{Refunding}
-
-It is probable that the streaming data sources are delayed or even interrupted after the subscribers pay the subscription fee.
-To protect subscriber rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel.
-If the expected data is not available, subscribers can request refunds.
-We assume that a very small percentage of subscribers in the product contract are irrational and/or malicious.
-When a subscriber consents to refund, he can vote at any time.
-After the ratio of consent votes of refunding is higher than the $threshold$, the subscription fee is proportionally transferred to the data provider, broker and every subscriber.
-Fig.~\ref{fig:refund} shows the refund process.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=1.5in]{refund}
-	\caption{The process of refund.}
-	\label{fig:refund}
-\end{figure}
-
-The subscription fee can be prorated as below:
-
-\begin{equation}
-    F_{DataProvider}(i) = N price \frac{i-1}{M} (1-F_{b}) -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Broker}(i) = N price \frac{i-1}{M} F_{b} -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Subscriber}(i) = price \frac{M-i+1}{M} -F_{t}
-\end{equation}
-
-where $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of subscribers in this contract.
-
-To refund or withdraw subscription fees from the smart contract, the data provider, broker, and subscriber send a transaction to execute the smart contract and are responsible for the transaction fee.
-We assume that only a half of the expected records are published to the MAM channel.
-When $F_{b}$ is 5\%, the data provider and broker can withdraw half of the total subscription fee from the smart contract and 5\% of the subscription fee belongs to the broker while the remaining belongs to the data provider.
-For subscribers, they can receive half of the subscription fee refunded which should be deducted from the transaction fee.
-
-Considering the situation that one of the subscribers requests a refund in the future, when the subscriber is disappointed with the data quality, he/she may request a refund.
 

### 2020-05-30 paper.tex
Update thesis title
Add Abstract

@@
 
-\title{A Decentralized Pub/Sub System for Trusted Machine Economy}
+\title{A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading}
+% Chinese title: 針對物聯網資料交易的去中心化基礎建設
 
@@
 \begin{abstract} 
-
+The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources.
+For instance, smart meter data can assist in energy transition.
+Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location.
+Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy.
+In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges.
+This approach can efficiently enhance the degree of transparency and scalability.
+The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers.
+Finally, we implement and elevuate the performance of the prototype.
 \end{abstract}
@@
 %TODO: cite examples
-In the Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly.
+In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly.
 As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
@@
 
-In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger technologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}.
+In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}.
 The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.

### 2020-05-31 paper.tex
Fix typo

@@
 The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers.
-Finally, we implement and elevuate the performance of the prototype.
+Finally, we implement and evaluate the performance of the prototype.
 \end{abstract}
@@
 Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed.
-Among the existing distributed storage mentioned in Section.
-CITE-RELATED-WORK, different architectures, back-up mechanisms and access controls strategies are proposed.
+Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed.
 Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.
 
+%scalability
 In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT.
@@
 \end{table}
+
+%classify
+With the channel and endpoint structures, users can easily categorized data streams with respect to different types and usages.
+For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
+
+%data trace
+Moreover, data tracability is an important security issue that allows users to track the changes of data.
+Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
 

### 2020-06-01 paper.tex
Change paper structures

@@
 
+\subsection{Contributions}
+The contributions in the paper are summarized as follow:
+\begin{itemize}
+	\item Standing on our proposed decentralized data marketplace, we review several decentralized data marketplace architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
+    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
+We also compare the perfomance of exchanging different cryptosystems.
+	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
+\end{itemize}
+
+\subsection{Paper Organization}
+The rest of this paper is organized as follows.
+In Section~\ref{section:background}, the architecture of our proposed decentralized data marketplace is illustrated.
+In Section~\ref{section:relatedWork}, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
+In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained.
+The analysis and improvement of MAM are given in Section MAM-EXP.
+In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully.
+Finally, we conclude the paper in Section CONCLUSION.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{system_design}
+    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
+    \label{fig:system_design}
+\end{figure}
+
+\section{Related Work}
+\label{section:relatedWork}
+% pub/sub
+\subsection{Data exchangement mechanism for IoT}
+The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
+A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
+A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.
+
+M.
+B.
+Abdullahi and G.
+Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
+Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
+Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
+However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system.
+Also the storage is not well illustrated in the work.
+G.
+S.
+Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
+With the help of Smart Contract, usesrs can perform data validation easily, and brokers can keep track of data status.
+But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
+The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.
+
+In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
+The subscribers request publisher directly and ask them to save a cache space for interested data.
+The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
+Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
+Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middlewares in the model and to provide a reputation-based fairness payment strategy on blockcahin.
+The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
+The reputation system and the punishment rules against malicous acts of subscribers and publishers.
+Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
+Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
+
+\subsection{Decentralized Data Marketplace Infrastructure}
+% decentralized DM
+
+\subsection{Distributed Storage System}
+% distributed data storage
+Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
+Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
+Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage.
+IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
+However, no cryptographic system is applied for user-uploaded files.
+Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
+Files are duplicated in multiple nodes to prevent data loss.
+
+\section{System Design Thinking}
+\subsection{The Architecture}
+% TODO: pub/sub model selection
+% use IPFS as searching indexes
 \subsection{Choice of Data Storage}
@@
 Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.
+
+% MAM
+MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control.
+With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.
+
+In the IOTA protocol, \textbf{seed} is the identifier of its owner.
+An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
+With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
+
+Either channel or endpoint is like a singly-linked list.
+The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
+Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
+A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
+The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+
+A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
+\end{figure}
+
+The authentication in MAM includes two aspects: source and data.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
+Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
+
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
@@
 
-\subsection{Contributions}
-The contributions in the paper are summarized as follow:
-\begin{itemize}
-	\item Standing on our proposed decentralized data marketplace, we review several decentralized data marketplace architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
-    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
-We also compare the perfomance of exchanging different cryptosystems.
-	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
-\end{itemize}
+% alternative solution => IPFS(data) + MAM(index)
 
-\subsection{Paper Organization}
-The rest of this paper is organized as follows.
-In Section~\ref{section:background}, the architecture of our proposed decentralized data marketplace is illustrated.
-In Section~\ref{section:relatedWork}, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
-In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained.
-The analysis and improvement of MAM are given in Section MAM-EXP.
-In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully.
-Finally, we conclude the paper in Section CONCLUSION.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{system_design}
-    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
-    \label{fig:system_design}
-\end{figure}
-
-\section{Background}
-\label{section:background}
-In this section, we review Ethereum Smart Contract, MAM, the architecture and workflow of decentralized data marketplace.
-
-\subsection{Ethereum Smart Contract}
+\subsection{Enable Automated Trading Process}
+% Ethereum Smart Contract
+% use ethereum smart contract => IOTA smart contracts are still under development
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. 
@@
 
-\subsection{Masked Authenticated Messaging}
-MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.
-
-In the IOTA protocol, \textbf{seed} is the identifier of its owner.
-An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
-With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
-
-Either channel or endpoint is like a singly-linked list.
-The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
-Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
-A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
-The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
-
-A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
-The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
-However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
-Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
-
+\section{Decentralized Data Marketplace Case Study}
 \subsection{Participants in Decentralized Data Marketplace}
@@
 Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
-
-\section{Related Work}
-\label{section:relatedWork}
-The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
-A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.
-
-M.
-B.
-Abdullahi and G.
-Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
-Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
-Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system.
-Also the storage is not well illustrated in the work.
-G.
-S.
-Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Smart Contract, usesrs can perform data validation easily, and brokers can keep track of data status.
-But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
-The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.
-
-In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
-The subscribers request publisher directly and ask them to save a cache space for interested data.
-The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
-Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middlewares in the model and to provide a reputation-based fairness payment strategy on blockcahin.
-The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-The reputation system and the punishment rules against malicous acts of subscribers and publishers.
-Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
-Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
-
-Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-However, no cryptographic system is applied for user-uploaded files.
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
-Files are duplicated in multiple nodes to prevent data loss.
 

### 2020-06-01 paper.tex
Minor tweaks

@@
 % TODO: pub/sub model selection
+There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others.
+In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+Fig.~\ref{fig:system_design}
+
+\begin{itemize}
+\item \textbf{Data Provider: }
+Data providers are the ones that generate streaming data and set the data price based on the different types of data.
+With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
+\item \textbf{Data Consumer: }
+Data consumers are entities that are willing to buy data streams.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
+\item \textbf{Broker: }
+Brokers are responsible for building an agreement between data providers and consumers.
+Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
+\end{itemize}
+
 % use IPFS as searching indexes
@@
 \section{Decentralized Data Marketplace Case Study}
-\subsection{Participants in Decentralized Data Marketplace}
-There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others.
-In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-Fig.~\ref{fig:system_design}
-
-\begin{itemize}
-\item \textbf{Data Provider: }
-Data providers are the ones that generate streaming data and set the data price based on the different types of data.
-With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
-\item \textbf{Data Consumer: }
-Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
-\item \textbf{Broker: }
-Brokers are responsible for building an agreement between data providers and consumers.
-Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
-\end{itemize}
-
-\subsection{Trading Models of Decentralized Data Marketplace}
+Trading Models of Decentralized Data Marketplace
 \subsubsection{Set Up}

### 2020-06-02 paper.tex
Add related work: data trading

@@
 % pub/sub
-\subsection{Data exchangement mechanism for IoT}
+\subsection{Data exchange mechanism for IoT}
 The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
@@
 
-\subsection{Decentralized Data Marketplace Infrastructure}
-% decentralized DM
+\subsection{Trusted IoT Trading Infrastructure}
+Multiple infrastructures of trusted data marketplace for IoT data trading has been proposed.
+Paolo Missier et.
+al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables the trading with Ethereum smart contracts.
+The brokers are only responsible for data transmission but matching publishers and subscribers as standard pub/sub model in order to adapt flexible agreement between participants.
+However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, referring as TrackerDB, is guarateed to be tamperproof but the risk of single point failure still exists.
+
+\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its own responsibility, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
+% TODO:補一個 MAM 訂閱未來資料的敘述
+
+In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments.
+The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality.
+Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures.
+The Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
+
+A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams on the Tangle via MAM protocol as well.
+Yet the data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
+Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
+Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
+Moreover, it is difficult to filter out the interested information.
+
+Two technical architectures for data trading are directly relevant to our work.
+\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS.
+Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract.
+Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach.
+Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions.
+Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage.
+The access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
+Also, the details of trading are not illustrated in this paper.
 
 \subsection{Distributed Storage System}
-% distributed data storage
 Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.

### 2020-06-04 paper.tex

@@
 A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
-A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.
+A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.
 
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Smart Contract, usesrs can perform data validation easily, and brokers can keep track of data status.
+With the help of Ethereum smart contract, usesrs can perform data validation easily, and brokers can keep track of data status.
 But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
@@
 \subsection{Trusted IoT Trading Infrastructure}
-Multiple infrastructures of trusted data marketplace for IoT data trading has been proposed.
+Multiple infrastructures for trusted IoT data trading have been proposed.
 Paolo Missier et.
-al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables the trading with Ethereum smart contracts.
-The brokers are only responsible for data transmission but matching publishers and subscribers as standard pub/sub model in order to adapt flexible agreement between participants.
+al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
+The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
+Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
 However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, referring as TrackerDB, is guarateed to be tamperproof but the risk of single point failure still exists.
@@
 \cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its own responsibility, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
 While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
-% TODO:補一個 MAM 訂閱未來資料的敘述
+
+In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities.
+IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
+\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS, a content-based addressing distributed storage system.
+Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement.
+This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
 
@@
 Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures.
-The Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
+The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
 
-A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams on the Tangle via MAM protocol as well.
-Yet the data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
+A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well.
+The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
 Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
 Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
-Moreover, it is difficult to filter out the interested information.
+Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.
 
-Two technical architectures for data trading are directly relevant to our work.
 \cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS.
@@
 Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage.
-The access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
 Also, the details of trading are not illustrated in this paper.

### 2020-06-04 paper.tex
Modify Introduction and move IOTA DM to related work

@@
 \section{Introduction}
-%TODO: cite examples
 In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly.
@@
 With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.
+Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.
 
-Among the challenges of data marketplace\cite{BigDataMarket}, we conclude the following four essential requirements of a data marketplace system:
+Among the challenges of data trading platform\cite{BigDataMarket}, we conclude the following four essential requirements:
 \begin{itemize}
 	\item \textbf{Scalability}. 
-1) The performance of data marketplace should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
+1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
 	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
@@
 
-In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
+In contrast to centralized architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a decentralized data trading infrastructure which aims for processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
 Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one.
@@
 
-In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}.
+We investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}.
 The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
@@
 \begin{itemize}
-	\item Standing on our proposed decentralized data marketplace, we review several decentralized data marketplace architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
+	\item Standing on our proposed decentralized data trading infrastructure, we review several decentralized data trading architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
     \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
@@
 The rest of this paper is organized as follows.
-In Section~\ref{section:background}, the architecture of our proposed decentralized data marketplace is illustrated.
-In Section~\ref{section:relatedWork}, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed.
-In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained.
+In Section~\ref{section:relatedWork}, some related work of data exchange mechanisms for IoT, decentralized data trading infrastructures and distributed data storage are analyzed.
+In Section ARCHI, the design thinking of proposed data trading architecture.
+In Section ARCHI, the trading models are well explained.
 The analysis and improvement of MAM are given in Section MAM-EXP.
@@
     \includegraphics[width=3.in]{system_design}
-    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
+    \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
     \label{fig:system_design}
@@
 
+%TODO: cite IOTAIdustryMarketplace
 \section{Related Work}
@@
 
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation is built on top of IOTA, which targets IoT data streams trading.
+Data streams are stored via MAM and data payment is paid in IOTA.
+Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace.
 In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments.

### 2020-06-04 paper.tex
Cite IPFS in first appearance

@@
 IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
-\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS, a content-based addressing distributed storage system.
+\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
 Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement.
@@
 Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage.
+Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
 IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.

### 2020-06-10 deprecated.tex
Add data marketplace workflow to Background
Modify Abstract

@@
+\begin{abstract} 
+The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources.
+For instance, smart meter data can assist in energy transition.
+Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location.
+Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy.
+In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges.
+This approach can efficiently enhance the degree of transparency and scalability.
+The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers.
+Finally, we implement and evaluate the performance of the prototype.
+\end{abstract}
+
 % may be removed
@@
 \end{figure}
+
+\subsection{Components}
+There are several building blocks in the proposed design to meet the expectations: 1) emit and access encrypted data stream; 2) retrieve transaction data for audit; 3) digital identity for all participants; and 4) enforcement of transparency and traceability.

### 2020-06-10 paper.tex
Modify Abstract

@@
 \begin{abstract} 
+%cite IoT data subscription economy
 The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources.
-For instance, smart meter data can assist in energy transition.
-Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location.
-Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy.
-In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges.
+The real-time data exchangements among devices forms a publish/subscribe relationship of streaming data that increases the importance and difficulties of dynamic data ownership and identity verification.
+Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system.
+Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any server or participants.
+In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure, in order to address the technical challenges.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers.
-Finally, we implement and evaluate the performance of the prototype.
+The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
+Finally, the prototype is implemented and evaluated.
 \end{abstract}

### 2020-06-10 paper.tex
Modify Introduction

@@
 Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system.
-Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any server or participants.
+Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
 In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure, in order to address the technical challenges.
@@
 \section{Introduction}
-In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly.
+In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly.
 As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.
+With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
+Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.
 
@@
 
-In contrast to centralized architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a decentralized data trading infrastructure which aims for processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
-Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one.
+In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a novel data trading infrastructure which aims for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
+As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
+For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication.
+While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.
+Therefore, a publish/subscribe model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.
+
+Proving the identity as well as the ownership of data is a challenging issue among various roles and large scale of platform.
+In current systems, trusted third-party authority like CA is widely adopted to certify each member.
+However, building trust upon CA is dangerous and fragile.
+The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion.
+Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
+
+Thus, the data trading platform for IoT towards a decentralized design. In this paper, 
+we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
 See Fig.~\ref{fig:system_design}.
-
-We investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}.
+The system collaborates Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}.
 The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
 Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+A self-soverign identity system TangleID\cite{TangleID} is built on top of MAM as well.
 These three keys meet the requirements mentioned previously.

### 2020-06-10 deprecated.tex
Modify choice of data storage

@@
 \end{abstract}
+
+\subsection{choice of data storage}
+We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes.
+Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed.
+Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed.
+Yet the keys and addresses of data managed by participants are hard to be as small as possible for data streams, and it is difficult to verify arbitrary data pieces, track data streams and categorize.
 

### 2020-06-10 paper.tex
Modify choice of data storage

@@
 \subsection{Choice of Data Storage}
-Data storage is an important element of data marketplace where the data assets are reserved.
-We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes.
-Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed.
-Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed.
-Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.
+Data storage is the trust basis of data trading platforms where the data assets are reserved.
+Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
+Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
+In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
+Also, on top of MAM, a self-soverign identity system is built to prove the participants' identities without any trusted authorities.
+Furthermore, MAM fulfills the requirements of scalability which reduce the number of keys and addresses that need to be managed by participants, and confidentiality that provides access control.
 
-% MAM
 MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control.
 With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.
-
 In the IOTA protocol, \textbf{seed} is the identifier of its owner.

### 2020-06-13 deprecated.tex
Add SaaS description

@@
 \end{abstract}
+
+Aware of the development of big data science, Radwa et.
+al.\cite{BigDataaaS} proposed the concept of big data science as a service framework which combines data resources, cloud computing platform and machine learning softwares as building blocks and makes them different subscription services.
+As more and more platforms and services release, interoperability is arising as a main issue.
+However, a data trading platform is still the missing piece which data and rewards are traded for innovation.
 

### 2020-06-13 paper.tex
Minor tweak
Add SaaS description

@@
 
-In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a novel data trading infrastructure which aims for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
+%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
+In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.
-Therefore, a publish/subscribe model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.
+Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.
 
-Proving the identity as well as the ownership of data is a challenging issue among various roles and large scale of platform.
+% SaaS
+The economic incentive model in our proposed IoT data trading platform works as subscription service.
+The subscription-based models (e.g.
+software-as-a-service (SaaS) and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
+The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
+\cite{SaaS} pointed out that the strength of the relationships between consumers and providers depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
+
+%trustless
+Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
 In current systems, trusted third-party authority like CA is widely adopted to certify each member.

### 2020-06-13 paper.tex
Modify Introduction

@@
 
-%trustless
+%trustless & automated
+%trust: 對系統、對身份、對資料
+In data trading platforms, there are two major aspects that need trust: identity, data ownership and trading.
 Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
@@
 Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
+Besides CA and storage, the subscrition history of data consumer reveals his/hers interests and the exposure of personal information during trading process against GDPR as well.
+The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
+We adopt DLTs to resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLT is transparent, immutable, and enforced automatically.
+Furthermore, consider handling the tasks and trading process at the same time is too heavy for a low-level device, the automated execution of smart contracts allow devices focus on their jobs while gaining the rewards.
 
-Thus, the data trading platform for IoT towards a decentralized design. In this paper, 
-we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
+Thus, the data trading platform for IoT towards a decentralized and trustless design.
+In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
 See Fig.~\ref{fig:system_design}.
-The system collaborates Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}.
-The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency.
-Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
-A self-soverign identity system TangleID\cite{TangleID} is built on top of MAM as well.
-These three keys meet the requirements mentioned previously.
+The system collaborates pub/sub model and different DLTs to meet requirements mentioned previously.
+The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on smart contracts with transparency and enforcement.
+Lastly, an end-to-end encryption protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
 

### 2020-06-14 paper.tex
Modify Introduction

@@
 %trust: 對系統、對身份、對資料
-In data trading platforms, there are two major aspects that need trust: identity, data ownership and trading.
+In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
 Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
@@
 The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
-We adopt DLTs to resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLT is transparent, immutable, and enforced automatically.
-Furthermore, consider handling the tasks and trading process at the same time is too heavy for a low-level device, the automated execution of smart contracts allow devices focus on their jobs while gaining the rewards.
 
@@
 See Fig.~\ref{fig:system_design}.
-The system collaborates pub/sub model and different DLTs to meet requirements mentioned previously.
-The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on smart contracts with transparency and enforcement.
-Lastly, an end-to-end encryption protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically.
+The trading processes are automated with smart contracts, which allows devices focus on their jobs while gaining the rewards.
+Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
 

### 2020-06-14 paper.tex
Minor tweaks

@@
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources.
-The real-time data exchangements among devices forms a publish/subscribe relationship of streaming data that increases the importance and difficulties of dynamic data ownership and identity verification.
+The real-time data exchangements among devices forms a publish/subscribe (pub/sub) relationship of streaming data which devices can transform the data exchangement into subscription-based services.
+However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
 Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system.
 Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
-In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure, in order to address the technical challenges.
+Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automatic subscription procedures is also required.
+In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
@@
 The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-\cite{SaaS} pointed out that the strength of the relationships between consumers and providers depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
+\cite{SaaS} pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 

### 2020-06-14 paper.tex
Add more description of relationship of MAM and roles

@@
 % TODO: pub/sub model selection
-There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others.
-In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-Fig.~\ref{fig:system_design}
+There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+As shown in Fig.~\ref{fig:system_design}.
 
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
-Also, on top of MAM, a self-soverign identity system is built to prove the participants' identities without any trusted authorities.
-Furthermore, MAM fulfills the requirements of scalability which reduce the number of keys and addresses that need to be managed by participants, and confidentiality that provides access control.
+In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
 
-MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.
-In the IOTA protocol, \textbf{seed} is the identifier of its owner.
-An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle.
-With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
+In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
 
-Either channel or endpoint is like a singly-linked list.
+\begin{itemize}
+    \item \textbf{Scalability}: for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \item \textbf{Integrity}: 
+	\begin{itemize}    	
+    	\item messages published to DLT are tamperproof that against malicious modification. 
+    	\item messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
+    \end{itemize}
+    \item \textbf{Confidentiality}:
+    \begin{itemize}    	
+    	\item The encrypted data are uploaded that only participants that have keys can decrypt. 
+    	\item The authorized users can retrieve data streams, since data is written on DLT which can be queried as long as the IOTA network is alive.
+    	\item MAM provides forward-secrecy.
+The entry points of future data can be derived, but it's impossible to trace back those in the past.
+This feature prevents adversaries from retrieving published history even if the key is revealed.
+    \end{itemize}
+\end{itemize}
+
+MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
+With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
 The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
@@
 Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.

### 2020-06-17 paper.tex

@@
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-
 Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
@@
 %scalability
-In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT.
-MAM allows users to put encrypted data streams into \textbf{channel}s and \textbf{endpoint}s, which consist of zero-value transactions on the Tangle.
-With an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+The importance of scalable key and data entry points management increases as the service operating over time.
+In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
 Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
@@
 %classify
-With the channel and endpoint structures, users can easily categorized data streams with respect to different types and usages.
+The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
 For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.

### 2020-06-17 deprecated.tex
fix typos

@@
 Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy.
-In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges.
 This approach can efficiently enhance the degree of transparency and scalability.
@@
 \subsection{choice of data storage}
-We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes.
+We assume such storage system should be distributed which runs on the peer-to-peer network maintaining by multiple nodes.
 Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed.
@@
 % may be removed
-The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
+The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-efficiency.
 In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers.
@@
 % move belows to background-archi
-The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.
+The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-efficiency.
 Connections of participants are built via brokers, which can avert sensitive information leaks in order to establish communication.
@@
 This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality.
-Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.
+Also, the interactions among different actors are transparent and validatable by automatically recording them on Ethereum Smart Contracts.
 

### 2020-06-18 paper.tex
Add blind signature description

@@
 The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
-Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
 The real-time data exchangements among devices forms a publish/subscribe (pub/sub) relationship of streaming data which devices can transform the data exchangement into subscription-based services.
@@
 Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automatic subscription procedures is also required.
-In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
+In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
@@
 In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly.
-As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
+As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
 With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.
-
-Among the challenges of data trading platform\cite{BigDataMarket}, we conclude the following four essential requirements:
-\begin{itemize}
-	\item \textbf{Scalability}. 
-1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
-	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
-	\item \textbf{Confidentiality}. 
-1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
-	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
-	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
-\end{itemize}
+Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.
 
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements.
+In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscrition history of data consumer reveals his/hers interests and the exposure of personal information during trading process against GDPR as well.
+Besides CA and storage, the subscrition history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
 The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
 
-Thus, the data trading platform for IoT towards a decentralized and trustless design.
+Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
+\begin{itemize}
+	\item \textbf{Scalability}. 
+1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
+	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
+	\item \textbf{Confidentiality}. 
+1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
+	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
+	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
+\end{itemize}
+
+Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
 In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
@@
 \section{System Design Thinking}
-\subsection{The Architecture}
-% TODO: pub/sub model selection
+\subsection{Data trading platform players}
 There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
@@
 \end{itemize}
+
+We adopt the brokered infrastructure for three reasons.
+Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system.
+Furthermore, if either side is offline, the proceeding tasks have to stop and start over.
+With brokers, the unfinished work can be cached or accomplished.
+Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
+The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum info like its identifier and public key.
+Third, as brokers running on machines in a stable network and electricity environment, besides matching procedures, participants on resource-constrained devices can offload the computation tasks to brokers.
+In our proposed protocol, devices can delegate the uploading and trading processes to brokers after signing the data, and brokers can perform verifiable checks without knowing the contents.
 
@@
 \subsection{Enable Automated Trading Process}
-% Ethereum Smart Contract
-% use ethereum smart contract => IOTA smart contracts are still under development
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
@@
 A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it will be executed automatically without any third-parties and it is uninterruptible.
+All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
 
 With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived.
-\textbf{Product Contract} is made for the product launching and trading process in the decentralized data marketplace.
-The information of data products such as MAM channel ID (the data entry point), data price, time period and the broker-verified encryption key are listed on Product Contract.
+In our system, \textbf{Product Contract} is made for the product launching and trading.
+The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
+See Listing.
+\ref{lst:constructor}.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of both providers and subscribers.
+Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.
+
+The transparency of smart contracts bring advantages for data providers and consumers.
+One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
+For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
+The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
+
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
+contract Product {
+    address public broker;
+    address public provider;
+    bool isBrokerWithdraw;
+    bool isProviderWithdraw;
+    address[] consumers;
+
+    struct Purchase {
+        bool affirmativeVote;
+        bool isConsumerWithdraw;
+        bool isKeyAdded;
+        string encryptKey;
+    }
+    mapping(address => Purchase) public consumer2Purchase;
+
+    uint public price;
+    uint public totalAmount;
+    uint public brokerage;
+    uint public threshold;
+    string public channelRoot;
+    string public endPoint;
+    uint public totalNumber;
+    uint public uploadedNumber;
+    uint public affirmativeVotes;
+    string blindedKey;
+    string signedBlindedKey;
+
+    enum State {Launched, KeyCertified, Finished, Refunded}
+    State public state;
+}
+\end{lstlisting}
+
+\subsection{Enable delegation of computation tasks to broker}
+To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
+However, the resources of low-level devices are precious which should be used to focus on its jobs.
+Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
+
+The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
+To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it.
+Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
+Figure \ref{fig:blind_signature} illustrates the steps of blind signature.
+The resulting message, along with the blinding factor, can be later verified with the signer's public key.
+% TODO: redraw blind signature diagram
+% TODO: broker 進行簽章的必要性
+
+RSA blind signature\cite{cryptoNote} is used in our research.
+The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
+To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
+
+\begin{equation}
+C = r^e m
+\end{equation}
+
+The signer signs the blinding message with his private key $d$.
+
+\begin{equation}
+S = C^d
+\end{equation}
+
+$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
+
+\begin{equation}
+\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
+\end{equation}
+
+The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
+
+\subsection{Enable delegation of computation tasks to broker}
+To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
+However, the resources of low-level devices precious which should be used to focus on its jobs.
+Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
+
+The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
+To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it.
+Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
+Figure \ref{fig:blind_signature} illustrates the steps of blind signature.
+The resulting message, along with the blinding factor, can be later verified with the signer's public key.
+% TODO: redraw blind signature diagram
+% TODO: broker 進行簽章的必要性
+
+RSA blind signature\cite{cryptoNote} is used in our research.
+The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
+To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
+
+\begin{equation}
+C = r^e m
+\end{equation}
+
+The signer signs the blinding message with his private key $d$.
+
+\begin{equation}
+S = C^d
+\end{equation}
+
+$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
+
+\begin{equation}
+\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
+\end{equation}
+
+The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
 

### 2020-06-22 paper.tex
Add advantages for participants of using smart contracts
Reorganize Abstract and Introduction
Update title
Add more description about SaaS

@@
 
-\title{A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading}
+\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
 % Chinese title: 針對物聯網資料交易的去中心化基礎建設
@@
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchangements among devices forms a publish/subscribe (pub/sub) relationship of streaming data which devices can transform the data exchangement into subscription-based services.
+The real-time data exchangements among devices are periodically that only data in a specific time period is interested.
+Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
+Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
+This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
 However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
@@
 % SaaS
-The economic incentive model in our proposed IoT data trading platform works as subscription service.
+The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage.
 The subscription-based models (e.g.
-software-as-a-service (SaaS) and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
+SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
+And for service consumers, they can subscribe and unsubscirbe the services at will at anytime.
 The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-\cite{SaaS} pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
+In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 
@@
 
-\subsection{Enable delegation of computation tasks to broker}
-To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the resources of low-level devices precious which should be used to focus on its jobs.
-Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
-
-The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it.
-Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-Figure \ref{fig:blind_signature} illustrates the steps of blind signature.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-% TODO: redraw blind signature diagram
-% TODO: broker 進行簽章的必要性
-
-RSA blind signature\cite{cryptoNote} is used in our research.
-The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
-To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
-
-\begin{equation}
-C = r^e m
-\end{equation}
-
-The signer signs the blinding message with his private key $d$.
-
-\begin{equation}
-S = C^d
-\end{equation}
-
-$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
-
-\begin{equation}
-\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
-\end{equation}
-
-The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
-
 \section{Decentralized Data Marketplace Case Study}

### 2020-06-22 paper.tex

@@
 Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
-Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automatic subscription procedures is also required.
+Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
 In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.

### 2020-06-23 deprecated.tex
Refactor Related Work
* Combine similar works into one paragraph
* Eliminate statesments of IOTA (move to Chap 3)
* Rephrase

@@
 However, a data trading platform is still the missing piece which data and rewards are traded for innovation.
+
+% related work, trusted IoT trading platform
+% MAM -> with IOTA
+In the following researches, Masked Authenticated Messaging (MAM) is regarded as a secure data transmission layer and data storage which provides access control, tamperproof and authentication functionalities.
+IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
+
+Researches below adopt MAM as data storage and transmit the data with it as well.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation, targets for IoT data streams trading.
+Data streams are stored via MAM and data payment is paid in IOTA.
+Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace.
+O.
+Lamtzidis and J.
+Gialelis \cite{IOTASensorNode} propose a distributed sensor node (SN) system to exchange data and establish a data monetization economy paradigm.
+Sensor nodes upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments.
+The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality.
+Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures.
+The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
+And the pricing strategy is rather simple, which do not take subscription based diagram into consideration.
+
+A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well.
+The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
+Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
+Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
+Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.
+
+Zichichi et al.\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and the distributed storage IPFS.
+Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract.
+Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach.
+Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions.
+Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
+Also, the details of trading are not illustrated in this paper.
 

### 2020-06-23 paper.tex
Refactor Related Work
* Combine similar works into one paragraph
* Eliminate statesments of IOTA (move to Chap 3)
* Rephrase

@@
 Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system.
+However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system.
 Also the storage is not well illustrated in the work.
@@
 
+A.
+Colman et al.
 \cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables.
@@
 
-In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities.
-IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
-\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement.
-This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by linking the messages to a list.
+Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
+Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement.
+This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} is a smart transportation system.
+The authors offer a key and entry point management with MAM that minimize the information that data producers need to hold.
+Also, the trading procedure is automated and enforced with Ethereum smart contracts.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading are not illustrated in this paper.
 
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation is built on top of IOTA, which targets IoT data streams trading.
-Data streams are stored via MAM and data payment is paid in IOTA.
+Researches below adopt MAM as data storage and transmit data with it as well.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation, targets for IoT data streams trading.
+Data streams are stored via MAM and paid in IOTA.
 Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace.
-In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments.
-The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality.
-Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures.
+O.
+Lamtzidis and J.
+Gialelis \cite{IOTASensorNode} proposed a distributed sensor node (SN) system to exchange data and establish a data monetization economy paradigm.
+The Back-End server helps SNs to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality.
+Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
 The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-
-A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well.
-The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
-Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
-Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
-Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.
-
-\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS.
-Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract.
-Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach.
-Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions.
-Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
-Also, the details of trading are not illustrated in this paper.
+And the pricing strategy is rather simple, which do not take subscription based diagram into consideration.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM, and specific tags are added in transaction as an index for different usages, such as payment check and product information search.
+However, once the data amount grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
+Moreover, it is difficult to filter out the interested information and to prevent adversaries spamming transactions.
 
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
+In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
 MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.

### 2020-06-28 paper.tex
Reword
Add subscription concerns to related work

@@
 Colman et al.
-\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+\cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
 While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
 
-In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by linking the messages to a list.
+In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by tailoring messages to a channel.
 Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
@@
 This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} is a smart transportation system.
-The authors offer a key and entry point management with MAM that minimize the information that data producers need to hold.
-Also, the trading procedure is automated and enforced with Ethereum smart contracts.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading are not illustrated in this paper.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offer a key and entry points management with MAM that minimize the information which data producers need to hold.
+Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and iteractions between providers and consumers are not illustrated in this paper.
 
-Researches below adopt MAM as data storage and transmit data with it as well.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation, targets for IoT data streams trading.
-Data streams are stored via MAM and paid in IOTA.
-Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace.
+Researches below adopt MAM as data storage and a secure data transmission layer.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
+Service requesters call for proposal of interested data and accept/reject proposals from service providers.
+After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
+This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
+Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
+
 O.
 Lamtzidis and J.
-Gialelis \cite{IOTASensorNode} proposed a distributed sensor node (SN) system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps SNs to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality.
+Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
+The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality.
 Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
 The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-And the pricing strategy is rather simple, which do not take subscription based diagram into consideration.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM, and specific tags are added in transaction as an index for different usages, such as payment check and product information search.
-However, once the data amount grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
-Moreover, it is difficult to filter out the interested information and to prevent adversaries spamming transactions.
+And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
 

### 2020-06-28 paper.tex
Fix typo

@@
 Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality.
+The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to its quality.
 Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.

### 2020-06-28 paper.tex
Move some MAM description to Chap 4 & add figures

--- 2020-06-23 paper.tex
@@
 Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system.
+However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system.
 Also the storage is not well illustrated in the work.
@@
 
-A.
-Colman et al.
 \cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables.
@@
 
-In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by linking the messages to a list.
-Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement.
-This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} is a smart transportation system.
-The authors offer a key and entry point management with MAM that minimize the information that data producers need to hold.
-Also, the trading procedure is automated and enforced with Ethereum smart contracts.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading are not illustrated in this paper.
+In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities.
+IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
+\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
+Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement.
+This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
 
-Researches below adopt MAM as data storage and transmit data with it as well.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation, targets for IoT data streams trading.
-Data streams are stored via MAM and paid in IOTA.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation is built on top of IOTA, which targets IoT data streams trading.
+Data streams are stored via MAM and data payment is paid in IOTA.
 Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace.
-O.
-Lamtzidis and J.
-Gialelis \cite{IOTASensorNode} proposed a distributed sensor node (SN) system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps SNs to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality.
-Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
+In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments.
+The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality.
+Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures.
 The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-And the pricing strategy is rather simple, which do not take subscription based diagram into consideration.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM, and specific tags are added in transaction as an index for different usages, such as payment check and product information search.
-However, once the data amount grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
-Moreover, it is difficult to filter out the interested information and to prevent adversaries spamming transactions.
+
+A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well.
+The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
+Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
+Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
+Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.
+
+\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS.
+Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract.
+Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach.
+Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions.
+Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
+Also, the details of trading are not illustrated in this paper.
 
@@
 \section{System Design Thinking}
-\subsection{Data trading platform players}
+\subsection{Data subscription-based trading platform players}
 There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
 But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-As shown in Fig.~\ref{fig:system_design}.
+As shown in Fig.~\ref{fig:pub_sub_model}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{pub_sub_model}
+    \caption{The players in data subsciption-based trading platform consists of data providers, data consumers and brokers.}
+    \label{fig:pub_sub_model}
+\end{figure}
 
@@
 
-% use IPFS as searching indexes
 \subsection{Choice of Data Storage}
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
+In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
 MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
 
@@
 \begin{itemize}
-    \item \textbf{Scalability}: for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
     \item \textbf{Integrity}: 
 	\begin{itemize}    	
-    	\item messages published to DLT are tamperproof that against malicious modification. 
-    	\item messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
+    	\item Messages published to the Tangle are tamperproof that against malicious modification. 
+    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
     \end{itemize}
@@
     	\item The encrypted data are uploaded that only participants that have keys can decrypt. 
-    	\item The authorized users can retrieve data streams, since data is written on DLT which can be queried as long as the IOTA network is alive.
+    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
     	\item MAM provides forward-secrecy.
@@
 
-MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
-The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
-Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
-A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
-The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
+The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle.
+This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source.
+See Fig.~\ref{fig:channel_and_key} for illustration.
+Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
 
-A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
-
-\begin{figure}[!t]
+\begin{figure*}[!t]
     \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
-The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
-However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
-Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
-
-%scalability
-The importance of scalable key and data entry points management increases as the service operating over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
-Assuming the length of data stream is 7, and each record is encrypted with the same key.
-With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
-
-\begin{table}[htbp]
-	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
-	\label{tab:mam_scalability}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
-		\hline
-		keys & 1 & 1 \\ 
-		\hline
-		entry points & 1 & 7 \\ 
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-%classify
-The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
-
-%data trace
-Moreover, data tracability is an important security issue that allows users to track the changes of data.
-Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
-MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
-
-The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
-Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
+    \includegraphics[width=\linewidth]{channel_and_key}
+    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
+Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
+    \label{fig:channel_and_key}
+\end{figure*}
 
 % alternative solution => IPFS(data) + MAM(index)
+\subsection{Digital Identity}
+Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
 
@@
 The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
+
+\section{Masked Authenticate Messaging}
+Data storage is the trust basis of data trading platforms where the data assets are reserved.
+Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
+Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
+In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
+
+MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
+With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
+The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
+Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
+A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
+The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+
+A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
+\end{figure}
+
+The authentication in MAM includes two aspects: source and data.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
+Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
+
+%scalability
+The importance of scalable key and data entry points management increases as the service operating over time.
+In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
+Assuming the length of data stream is 7, and each record is encrypted with the same key.
+With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
+
+\begin{table}[htbp]
+	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
+	\label{tab:mam_scalability}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
+		\hline
+		keys & 1 & 1 \\ 
+		\hline
+		entry points & 1 & 7 \\ 
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+%classify
+The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
+For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
+
+%data trace
+Moreover, data tracability is an important security issue that allows users to track the changes of data.
+Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
+
+The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
+Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
 

### 2020-06-28 paper.tex
Add digital identity

@@
 \subsection{Digital Identity}
-Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
+The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
+In our architecture, a self-soverign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
+TangleID is built on top of MAM where change log of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
+The identity information such as public key, unique identifiers of services and metadatas consist a DID document.
 One can easily prove himself by sharing the identifier on MAM without any authority.
+
+Through TangleID, every entity gets a public/private key pair, the location of DID document and the seed that generates the DID document MAM public channel.
+The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
+During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
 

### 2020-06-28 paper.tex
Add TangleID figure
Adjust figure position
Add a figure that shows the relation between smart contract and MAM

@@
     \centering
-    \includegraphics[width=3.in]{pub_sub_model}
+    \includegraphics[width=3.5in]{pub_sub_model}
     \caption{The players in data subsciption-based trading platform consists of data providers, data consumers and brokers.}
@@
 In our proposed protocol, devices can delegate the uploading and trading processes to brokers after signing the data, and brokers can perform verifiable checks without knowing the contents.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{channel_and_key}
+    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
+Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
+    \label{fig:channel_and_key}
+\end{figure*}
 
@@
 
-\begin{figure*}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
-Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
-    \label{fig:channel_and_key}
-\end{figure*}
-
 % alternative solution => IPFS(data) + MAM(index)
@@
 During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
+See Fig.~\ref{fig:TangleID}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{TangleID}
+    \caption{Data provider sends the encryption key of data products to data consumer.
+The encryption key is encrypted with data consumer's public key on DID document that only the consumer can retreive.}
+    \label{fig:TangleID}
+\end{figure}
 
 \subsection{Enable Automated Trading Process}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=5in]{smart_contract_mam}
+    \caption{The identity information and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
+Participants can easily retrieve information via Product Contract and proceed trading.}
+    \label{fig:smart_contract_mam}
+\end{figure*}
+
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
@@
 The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
-See Listing.
-\ref{lst:constructor}.
+Listing.
+\ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
@@
 
-\begin{figure}[!t]
+\begin{figure}[h]
     \centering

### 2020-06-30 deprecated.tex
Redraw figures and add more captions

--- 2020-06-17 deprecated.tex
@@
 There are several building blocks in the proposed design to meet the expectations: 1) emit and access encrypted data stream; 2) retrieve transaction data for audit; 3) digital identity for all participants; and 4) enforcement of transparency and traceability.
+
+\subsection{Enable delegation of computation tasks to broker}
+To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
+However, the resources of low-level devices are precious which should be used to focus on its jobs.
+Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
+
+The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
+To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it.
+Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
+Figure \ref{fig:blind_signature} illustrates the steps of blind signature.
+The resulting message, along with the blinding factor, can be later verified with the signer's public key.
+% TODO: redraw blind signature diagram
+
+RSA blind signature\cite{cryptoNote} is used in our research.
+The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
+To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
+
+\begin{equation}
+C = r^e m
+\end{equation}
+
+The signer signs the blinding message with his private key $d$.
+
+\begin{equation}
+S = C^d
+\end{equation}
+
+$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
+
+\begin{equation}
+\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
+\end{equation}
+
+The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.

### 2020-06-30 paper.tex
Redraw figures and add more captions

@@
 In our architecture, a self-soverign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
-TangleID is built on top of MAM where change log of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
+TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
 The identity information such as public key, unique identifiers of services and metadatas consist a DID document.
@@
 
-Through TangleID, every entity gets a public/private key pair, the location of DID document and the seed that generates the DID document MAM public channel.
+Through TangleID, containing public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
@@
     \includegraphics[width=3.5in]{TangleID}
-    \caption{Data provider sends the encryption key of data products to data consumer.
-The encryption key is encrypted with data consumer's public key on DID document that only the consumer can retreive.}
+    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
+The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
+When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchangement.
+The data provider can then retrieve the consumer's public key and encrypt the content with it.
+After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
     \label{fig:TangleID}
@@
 \subsection{Enable Automated Trading Process}
-
 \begin{figure*}[t]
     \centering
-    \includegraphics[width=5in]{smart_contract_mam}
-    \caption{The identity information and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.}
+    \includegraphics[width=4in]{smart_contract_mam}
+    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
+Participants can easily retrieve information via Product Contract and proceed trading.
+For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color.
+The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
     \label{fig:smart_contract_mam}
@@
 
-\subsection{Enable delegation of computation tasks to broker}
+\subsection{Enable computation tasks delegation to broker with privacy}
 To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
@@
 
-The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it.
-Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign.
-Figure \ref{fig:blind_signature} illustrates the steps of blind signature.
-The resulting message, along with the blinding factor, can be later verified with the signer's public key.
-% TODO: redraw blind signature diagram
-% TODO: broker 進行簽章的必要性
-
-RSA blind signature\cite{cryptoNote} is used in our research.
-The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$.
-To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.
-
-\begin{equation}
-C = r^e m
-\end{equation}
-
-The signer signs the blinding message with his private key $d$.
-
-\begin{equation}
-S = C^d
-\end{equation}
-
-$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.
-
-\begin{equation}
-\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
-\end{equation}
-
-The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
+The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
+To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest to brokers.
+Note that the broker need to sign the digest, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The key upload times is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the session key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.
 

### 2020-06-30 paper.tex
Add key upload description and figure

@@
 \subsection{Enable computation tasks delegation to broker with privacy}
-To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
+To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
 However, the resources of low-level devices are precious which should be used to focus on its jobs.
@@
 The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest to brokers.
-Note that the broker need to sign the digest, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest as well as the signature to brokers.
+Broker can first verify the signature from data provider with the public key on DID document.
+If it's valid, then the broker uploads the key, otherwise the process is aborted.
+Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
 The key upload times is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the session key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrate the key upload to Product Contract via a broker.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{key_upload}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
+After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
+    \label{fig:key_upload}
+\end{figure}
+
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy.
+The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
@@
 
+\subsection{TA - endpoint}
+\label{section:ta_endpoint}
+
 \section{Decentralized Data Marketplace Case Study}
@@
 \subsection{MAM Performance Evaluation}
+\label{section:mam_performance}
 MAM is a secure and validatable data storage of the proposed architecture.

### 2020-06-30 paper.tex
Fix grammar

--- 2020-06-28 paper.tex
@@
 
-\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+A.
+Colman et al.
+\cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
 While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
 
-In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities.
-IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
-\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement.
-This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by tailoring messages to a channel.
+Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
+Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement.
+This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offer a key and entry points management with MAM that minimize the information which data producers need to hold.
+Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and iteractions between providers and consumers are not illustrated in this paper.
 
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation is built on top of IOTA, which targets IoT data streams trading.
-Data streams are stored via MAM and data payment is paid in IOTA.
-Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace.
-In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments.
-The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality.
-Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures.
+Researches below adopt MAM as data storage and a secure data transmission layer.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
+Service requesters call for proposal of interested data and accept/reject proposals from service providers.
+After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
+This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
+Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
+
+O.
+Lamtzidis and J.
+Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
+The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to its quality.
+Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
 The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-
-A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well.
-The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
-Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
-Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned.
-Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.
-
-\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS.
-Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract.
-Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach.
-Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions.
-Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from.
-Also, the details of trading are not illustrated in this paper.
+And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
 
@@
 \section{System Design Thinking}
-\subsection{Data subscription-based trading platform players}
+\subsection{Data trading platform players}
 There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
 But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-As shown in Fig.~\ref{fig:pub_sub_model}.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{pub_sub_model}
-    \caption{The players in data subsciption-based trading platform consists of data providers, data consumers and brokers.}
-    \label{fig:pub_sub_model}
-\end{figure}
+As shown in Fig.~\ref{fig:system_design}.
 
@@
 
-\begin{figure*}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
-Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
-    \label{fig:channel_and_key}
-\end{figure*}
-
+% use IPFS as searching indexes
 \subsection{Choice of Data Storage}
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
+In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
 MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
 
@@
 \begin{itemize}
-    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \item \textbf{Scalability}: for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
     \item \textbf{Integrity}: 
 	\begin{itemize}    	
-    	\item Messages published to the Tangle are tamperproof that against malicious modification. 
-    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
+    	\item messages published to DLT are tamperproof that against malicious modification. 
+    	\item messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
     \end{itemize}
@@
     	\item The encrypted data are uploaded that only participants that have keys can decrypt. 
-    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
+    	\item The authorized users can retrieve data streams, since data is written on DLT which can be queried as long as the IOTA network is alive.
     	\item MAM provides forward-secrecy.
@@
 
-MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle.
-This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source.
-See Fig.~\ref{fig:channel_and_key} for illustration.
-Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
+With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
+The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
+Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
+A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
+The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+
+A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
+\end{figure}
+
+The authentication in MAM includes two aspects: source and data.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
+Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
+
+%scalability
+The importance of scalable key and data entry points management increases as the service operating over time.
+In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
+Assuming the length of data stream is 7, and each record is encrypted with the same key.
+With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
+
+\begin{table}[htbp]
+	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
+	\label{tab:mam_scalability}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
+		\hline
+		keys & 1 & 1 \\ 
+		\hline
+		entry points & 1 & 7 \\ 
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+%classify
+The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
+For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
+
+%data trace
+Moreover, data tracability is an important security issue that allows users to track the changes of data.
+Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
+
+The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
+Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
 
 % alternative solution => IPFS(data) + MAM(index)
-\subsection{Digital Identity}
-The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
-In our architecture, a self-soverign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
-TangleID is built on top of MAM where change log of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
-The identity information such as public key, unique identifiers of services and metadatas consist a DID document.
-One can easily prove himself by sharing the identifier on MAM without any authority.
-
-Through TangleID, every entity gets a public/private key pair, the location of DID document and the seed that generates the DID document MAM public channel.
-The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
-See Fig.~\ref{fig:TangleID}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{TangleID}
-    \caption{Data provider sends the encryption key of data products to data consumer.
-The encryption key is encrypted with data consumer's public key on DID document that only the consumer can retreive.}
-    \label{fig:TangleID}
-\end{figure}
 
 \subsection{Enable Automated Trading Process}
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=5in]{smart_contract_mam}
-    \caption{The identity information and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.}
-    \label{fig:smart_contract_mam}
-\end{figure*}
-
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
@@
 The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
-Listing.
-\ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+See Listing.
+\ref{lst:constructor}.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
@@
 The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
-
-\section{Masked Authenticate Messaging}
-Data storage is the trust basis of data trading platforms where the data assets are reserved.
-Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
-Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
-
-MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
-The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
-Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
-A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
-The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
-
-A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
-The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
-However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
-Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
-
-%scalability
-The importance of scalable key and data entry points management increases as the service operating over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
-Assuming the length of data stream is 7, and each record is encrypted with the same key.
-With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
-
-\begin{table}[htbp]
-	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
-	\label{tab:mam_scalability}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
-		\hline
-		keys & 1 & 1 \\ 
-		\hline
-		entry points & 1 & 7 \\ 
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-%classify
-The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
-
-%data trace
-Moreover, data tracability is an important security issue that allows users to track the changes of data.
-Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
-MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
-
-The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
-Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
 

### 2020-06-30 paper.tex
Rephrase

@@
 \subsection{Trusted IoT Trading Infrastructure}
-Multiple infrastructures for trusted IoT data trading have been proposed.
-Paolo Missier et.
-al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
+Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
+al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.

### 2020-07-01 paper.tex
Fix grammar error

@@
 This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offer a key and entry points management with MAM that minimize the information which data producers need to hold.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
 Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.

### 2020-07-01 paper.tex
Remove TrackerDB

@@
 Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
-However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, referring as TrackerDB, is guarateed to be tamperproof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guarateed to be tamperproof but the risk of single point failure still exists.
 

### 2020-07-01 deprecated.tex
fix typo and remove tailing space

--- 2020-06-23 deprecated.tex
@@
 % MAM -> with IOTA
-In the following researches, Masked Authenticated Messaging (MAM) is regarded as a secure data transmission layer and data storage which provides access control, tamperproof and authentication functionalities.
-IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
+In the following researches, Masked Authenticated Messaging (MAM) is regarded as a secure data transmission layer and data storage which provides access control, tamper-proof and authentication functionalities.
+IOTA is a DAG-based DLT that allows attaching zero value transactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.
 
@@
 A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well.
-The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from.
+The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retrieve and show the product information on a map where data consumers can select from.
 Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check.
@@
 MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control.
-Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authoraized data streams anytime.
+Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authorized data streams anytime.
 
@@
 optimizing layers of MAM and compare the performance of different cryptosystems.
-Furthermore, we take offloading MAM operations to brokers as another solution to reduce the workload of IoT devices, since the brokers are considered to have higher computating power.
+Furthermore, we take offloading MAM operations to brokers as another solution to reduce the workload of IoT devices, since the brokers are considered to have higher computational power.
 In Section CITE-TA-SECTION, the security issues and methods of offloading will be discussed carefully.

### 2020-07-02 paper.tex
Correct the delegator of MAM operations to TA

@@
 
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy.
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.

### 2020-07-02 paper.tex
Make Chap4 to MAM

--- 2020-07-01 paper.tex
@@
 \section{Masked Authenticate Messaging}
-Data storage is the trust basis of data trading platforms where the data assets are reserved.
-Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
-Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
+MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
+The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
+With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
 
-MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
-The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
-Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
-A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
-The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+\subsection{The Message Streams}
+A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
+To publish a MAM message to channel, MAM deploys MSS to sign the message payload, and the root of the Merkle tree is used as the ID of the channel.
+Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
 
-A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
+The publishers can decide whether to turn the encryption on and off to protect messages.
+If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
+For validation check, subscribers can validate the signature added in the signature section of MAM bundle.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
+\subsection{Enable Access Control and Authentication}
 The authentication in MAM includes two aspects: source and data.
@@
 
+\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Platform}
 %scalability
+\subsubsection{A Scalable Keys and Data Entry Points Management}
 The importance of scalable key and data entry points management increases as the service operating over time.
@@
 %classify
+\subsubsection{Data Sreams Classification}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
@@
 %data trace
+\subsubsection{A Traceable Data Stream}
 Moreover, data tracability is an important security issue that allows users to track the changes of data.
@@
 
-The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
-Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
-
-\subsection{TA - endpoint}
+\subsection{Delegate MAM operations to Tangle-accelerator}
 \label{section:ta_endpoint}
+MAM builds a secure and authenticated communication protocol on top of multiple cyptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 

### 2020-07-02 paper.tex
Correct the delegator of MAM operations to TA

@@
 
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy.
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.

### 2020-07-02 paper.tex
typo

--- 2020-07-02 paper.tex
@@
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchangements among devices are periodically that only data in a specific time period is interested.
+The real-time data exchange among devices are periodically that only data in a specific time period is interested.
 Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
@@
 Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
-In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
@@
 \begin{IEEEkeywords}
-Data Marketeplace, decentralization, Distributed Ledger Technology
+Data Marketplace, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
-And for service consumers, they can subscribe and unsubscirbe the services at will at anytime.
+And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
 The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
@@
 Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscrition history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
+Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
 The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
@@
     \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
-We also compare the perfomance of exchanging different cryptosystems.
+We also compare the performance of exchanging different cryptosystems.
 	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
@@
 
-%TODO: cite IOTAIdustryMarketplace
+%TODO: cite IOTAIndustryMarketplace
 \section{Related Work}
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Ethereum smart contract, usesrs can perform data validation easily, and brokers can keep track of data status.
+With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
 But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
@@
 Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middlewares in the model and to provide a reputation-based fairness payment strategy on blockcahin.
+Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-The reputation system and the punishment rules against malicous acts of subscribers and publishers.
+The reputation system and the punishment rules against malicious acts of subscribers and publishers.
 Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
@@
 Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
-However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guarateed to be tamperproof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
 
@@
 Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
-While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
+While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
 
-In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by tailoring messages to a channel.
+In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
 Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement.
+Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
 This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
@@
 Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and iteractions between providers and consumers are not illustrated in this paper.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
 
@@
 Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to its quality.
+The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
 Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
@@
     \includegraphics[width=3.5in]{pub_sub_model}
-    \caption{The players in data subsciption-based trading platform consists of data providers, data consumers and brokers.}
+    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
     \label{fig:pub_sub_model}
@@
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
@@
 MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored.
+Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
 One can easily prove himself by sharing the identifier on MAM without any authority.
@@
 	\begin{itemize}    	
-    	\item Messages published to the Tangle are tamperproof that against malicious modification.
+        \item Messages published to the Tangle are tamper-proof that against malicious modification.
     	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
@@
 The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
-In our architecture, a self-soverign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
+In our architecture, a self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
 TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
-The identity information such as public key, unique identifiers of services and metadatas consist a DID document.
+The identity information such as public key, unique identifiers of services and metadata consists a DID document.
 One can easily prove himself by sharing the identifier on MAM without any authority.
@@
 The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
-When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchangement.
+When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
 The data provider can then retrieve the consumer's public key and encrypt the content with it.
@@
 
-With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived.
+With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
 In our system, \textbf{Product Contract} is made for the product launching and trading.
@@
 
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
@@
 For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entry points of the data steams should be reserved.
 
 %data trace
-Moreover, data tracability is an important security issue that allows users to track the changes of data.
+Moreover, data traceability is an important security issue that allows users to track the changes of data.
 Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
@@
 The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies.
-Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.
+In this paper, we evaluate the performance of MAM, and improve the efficiency with different strategies.
+Also, we take offloading the computation tasks to brokers as another possible approach for IoT devices, since brokers are considered to have higher computational power.
 
@@
 
+\subsubsection{Plight for Low-level edge device}
+
 \section{Decentralized Data Marketplace Case Study}
@@
 \subsubsection{Set Up}
-All participants need to register on TangleID\cite{TangleID}, a self-soverign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
+All participants need to register on TangleID\cite{TangleID}, a self-sovereign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
 
@@
 As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers frauding data consumers with a wrong one.
+This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest data consumers with a wrong one.
 The workflow is shown in Fig.~\ref{fig:launching_product}.
@@
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retreive it from Product Contract.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retrieve it from Product Contract.
 
@@
     \includegraphics[width=3.5in]{key_exchange}
-    \caption{Encryption key exchangement process.}
+    \caption{Encryption key exchange process.}
     \label{fig:key_exchange}
@@
 \subsubsection{Refunding}
-Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after recieving the subscription fee.
+Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after receiving the subscription fee.
 Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective.

### 2020-07-02 paper.tex
Enhance MAM description

--- 2020-07-02 paper.tex
@@
 \usepackage{cite}
+\usepackage{float}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 See Fig.~\ref{fig:channel_and_key} for illustration.
+
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload, and the root of the Merkle tree is used as the ID of the channel.
+To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel ID = root$ i.e., the MSS Merkle root.
 Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
@@
 \subsection{Enable Access Control and Authentication}
+The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
 The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
+These are achieved through the MSS and One-way hash functions.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Platform}
+\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
 %scalability
 \subsubsection{A Scalable Keys and Data Entry Points Management}
-The importance of scalable key and data entry points management increases as the service operating over time.
+The importance of scalable key and data entry points management increases over time.
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
@@
 Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem.
 
@@
 \subsubsection{A Traceable Data Stream}
-Moreover, data tracability is an important security issue that allows users to track the changes of data.
+Data tracability is an important security issue that allows users to track the changes of data.
 Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.

### 2020-07-02 paper.tex

--- 2020-07-02 paper.tex
@@
 \section{Masked Authenticate Messaging}
-Data storage is the trust basis of data trading platforms where the data assets are reserved.
-Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
-Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
+MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
+The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
+With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
 
-MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
-The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
-Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
-A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
-The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
+\subsection{The Message Streams}
+A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
+To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel ID = root$ i.e., the MSS Merkle root.
+Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
 
-A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
+The publishers can decide whether to turn the encryption on and off to protect messages.
+If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
+For validation check, subscribers can validate the signature added in the signature section of MAM bundle.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
-\end{figure}
-
+\subsection{Enable Access Control and Authentication}
+The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
 The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
+These are achieved through the MSS and One-way hash functions.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
+\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
 %scalability
-The importance of scalable key and data entry points management increases as the service operating over time.
+\subsubsection{A Scalable Keys and Data Entry Points Management}
+The importance of scalable key and data entry points management increases over time.
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
@@
 %classify
+\subsubsection{Data Sreams Classification}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
 For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entry points of the data steams should be reserved.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem.
 
 %data trace
-Moreover, data traceability is an important security issue that allows users to track the changes of data.
+\subsubsection{A Traceable Data Stream}
+Data tracability is an important security issue that allows users to track the changes of data.
 Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
@@
 
-The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-In this paper, we evaluate the performance of MAM, and improve the efficiency with different strategies.
-Also, we take offloading the computation tasks to brokers as another possible approach for IoT devices, since brokers are considered to have higher computational power.
-
-\subsection{TA - endpoint}
+\subsection{Delegate MAM operations to Tangle-accelerator}
 \label{section:ta_endpoint}
+MAM builds a secure and authenticated communication protocol on top of multiple cyptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 

### 2020-07-03 paper.tex
Fix typo
Add mam structure figure

@@
 
-\section{Masked Authenticate Messaging}
+\section{Masked Authenticated Messaging}
 MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
@@
 A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel ID = root$ i.e., the MSS Merkle root.
+To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
 Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
+Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{mam_structure}
+    \caption{A user can generate multiple channels, which can then generate multiple endpoints.
+The IDs of channel and endpoint are the roots of different Merkle trees in MSS.
+The "central endpoint" has ID, where $endpoint\ ID = channel\ ID$}
+    \label{fig:mam_structure}
+\end{figure}
 

### 2020-07-03 paper.tex
Add description of seed and update mam figure

@@
 To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
+The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
 Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
@@
     \includegraphics[width=3.5in]{mam_structure}
-    \caption{A user can generate multiple channels, which can then generate multiple endpoints.
+    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints.
 The IDs of channel and endpoint are the roots of different Merkle trees in MSS.
-The "central endpoint" has ID, where $endpoint\ ID = channel\ ID$}
+The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
     \label{fig:mam_structure}

### 2020-07-03 paper.tex
Move paragraph to the corresponding section

@@
 
-The publishers can decide whether to turn the encryption on and off to protect messages.
-If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
-For validation check, subscribers can validate the signature added in the signature section of MAM bundle.
-
 \subsection{Enable Access Control and Authentication}
 The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
+If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
 The authentication in MAM includes two aspects: source and data.
 Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
-These are achieved through the MSS and One-way hash functions.
+These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of MAM bundle.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.

### 2020-07-04 paper.tex
Strengthen trading model

--- 2020-07-03 paper.tex
@@
 \usepackage{cite}
-\usepackage{float}
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{algorithmic,algorithm}
 \usepackage{graphicx}
@@
 See Fig.~\ref{fig:channel_and_key} for illustration.
-
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
 
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
-\section{Masked Authenticated Messaging}
-MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
-The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
+\section{Masked Authenticate Messaging}
+Data storage is the trust basis of data trading platforms where the data assets are reserved.
+Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
+Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
+In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
+
+MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
+The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
+Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
+A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
+The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
 
-\subsection{The Message Streams}
-A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
-Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
-This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
-Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
 
@@
     \centering
-    \includegraphics[width=3.5in]{mam_structure}
-    \caption{A user can generate multiple channels, which can then generate multiple endpoints.
-The IDs of channel and endpoint are the roots of different Merkle trees in MSS.
-The "central endpoint" has ID, where $endpoint\ ID = channel\ ID$}
-    \label{fig:mam_structure}
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
 \end{figure}
 
-The publishers can decide whether to turn the encryption on and off to protect messages.
-If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
-For validation check, subscribers can validate the signature added in the signature section of MAM bundle.
-
-\subsection{Enable Access Control and Authentication}
-The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
 The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
-These are achieved through the MSS and One-way hash functions.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
 %scalability
-\subsubsection{A Scalable Keys and Data Entry Points Management}
-The importance of scalable key and data entry points management increases over time.
+The importance of scalable key and data entry points management increases as the service operating over time.
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
@@
 %classify
-\subsubsection{Data Sreams Classification}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
 For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entry points of the data steams should be reserved.
 
 %data trace
-\subsubsection{A Traceable Data Stream}
-Data tracability is an important security issue that allows users to track the changes of data.
+Moreover, data traceability is an important security issue that allows users to track the changes of data.
 Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
@@
 
-\subsection{Delegate MAM operations to Tangle-accelerator}
+The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this paper, we evaluate the performance of MAM, and improve the efficiency with different strategies.
+Also, we take offloading the computation tasks to brokers as another possible approach for IoT devices, since brokers are considered to have higher computational power.
+
+\subsection{TA - endpoint}
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cyptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 
@@
 
-\section{Decentralized Data Marketplace Case Study}
-Trading Models of Decentralized Data Marketplace
-\subsubsection{Set Up}
-All participants need to register on TangleID\cite{TangleID}, a self-sovereign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
+\section{Decentralized Subscription-based Data Trading Case Study}
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
 
-\subsubsection{Launch Data Products}
-To launch a data product, data providers need to create a MAM channel/endpoint and a Product Contract.
-However, considering IoT devices have no ability to handle both uploading data to MAM and interacting Ethereum smart contracts while collecting continuous data with low computing power, these works are offloaded to brokers.
+\subsection{Prerequisite}
+All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication.
+An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.
 
-The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract.
-As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest data consumers with a wrong one.
+\subsection{Launch Data Products}
+To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
+For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
+And brokers are responsible for Product Contract creation.
+
+The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract.
+This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
 The workflow is shown in Fig.~\ref{fig:launching_product}.
-
-Data providers start uploading data once the MAM channel/endpoint are created, each MAM message contains encrypted contexts along with signatures which allows data consumers to check the integrity.
-In addition, one can perform the signature validation without the encryption key on MAM.
+Finally, data providers can start uploading data.
 
@@
 
-\subsubsection{Trading}
-Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retrieve it from Product Contract.
+\subsection{Trading}
+Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
 
-Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants.
+Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public.
 Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
 The key sending process is shown in Fig.~\ref{fig:key_exchange}.
+The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
 
@@
 
-\subsubsection{Refunding}
-Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after receiving the subscription fee.
+\subsection{Unsubscribe to Data Products}
+Data consumers can unsubscribe to data products when they're not interested anymore.
+Product Contract hold an unsubscribe list to record the unsubscribers.
+When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
+The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract.
+Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
+The updated key is uploaded to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+
+\begin{equation}
+\label{equation:unsubscribe_provider}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}) -F_{t}
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_broker}
+    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_consumer}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+\end{equation}
+
+\subsection{Launch a Refund}
+Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
 Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective.
-The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
-When the refund procedure is launched, all consumers start voting based on their opinions on the data product.
+When the refund procedure is launched, all consumers vote to decide whether the refund is established.
 Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
+
+\begin{equation}
+    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+\end{equation}
 

### 2020-07-04 paper.tex
Add unsubscription and refund figure

@@
 $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract.
+And $F_{extra}$ is the extra fee charged for unsubscription, since brokers need extra fee to go through the key changing procedure.
+
 Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
-The updated key is uploaded to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
 
@@
 \label{equation:unsubscribe_provider}
-    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}) -F_{t}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{extra}) -F_{t} 
 \end{equation}
@@
 \label{equation:unsubscribe_consumer}
-    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{extra}) -F_{t}
 \end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{unsubscribe}
+    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
+Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
+    \label{fig:unsubscribe}
+\end{figure}
 
@@
 Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
-Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective.
+Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
 When the refund procedure is launched, all consumers vote to decide whether the refund is established.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
+See Fig.~\ref{fig:refund}.
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following:
 
@@
 \end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.5in]{refund}
+    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
+Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \label{fig:refund}
+\end{figure}
 

### 2020-07-04 paper.tex

--- 2020-07-03 paper.tex
@@
 For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
 To do the classification in other distributed storage also encounters the aforementioned scalability problem.
@@
 \subsubsection{A Traceable Data Stream}
-Data tracability is an important security issue that allows users to track the changes of data.
+Data traceability is an important security issue that allows users to track the changes of data.
 Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
@@
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cyptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
+MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
 To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 
-\subsubsection{Plight for Low-level edge device}
+\subsubsection{Infrastructure}
+To build the system, MQTT is chosen as the communication protocol.
+MQTT protocol utilizes much more lightweight packet than HTTP protocol has.
+The topic-based publish-subscribe pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on low-level edge devices with limited bandwidth.
+The publish-subscribe model decouples publishers and subscribers in many ways:
+
+\begin{itemize}
+    \item Space decoupling: Both publisher and subscriber don't need to know each other.
+    \item Time decoupling: Publishers and subscribers do not need to run at the same time.
+    \item Synchronization decoupling: Operations are decoupled from the publisher and subscriber.
+If we can decouple the operations, then the endpoint doesn’t need to maintain the connection until receive the response.
+Message from endpoint can be served as send-and-forget fashion.
+\end{itemize}
+
+\subsubsection{End-to-End-Encryption}
+Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message.
+To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol.
+The plaintext will be encrypted with this lightweight end-to-end-encryption.
+The E2EE process ensures only authorized subscribers can read the messages published on MAM.
+
+%pic
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{MAM_E2EE}
+    \caption{The process of E2EE.}
+    \label{fig:MAM_E2EE}
+\end{figure*}
+
+In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the whole E2EE process we present. The following section addresses the process.
+
+\begin{enumerate}
+    \item Generate symmetric key with unique device identifier and Message Authentication Code (MAC) of the previous message.
+If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message.
+Key Derivation Function (KDF) is used to generate the symmetric keys.
+    \item Compute the Message Authentication Code (MAC) of current message with Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
+    \item Apply the generated symmetric key to encrypt plaintext.
+    \item Concatenate the MAC of current message would and the MAC of previous message, and then the result will be signed with digital signature algorithm.
+    \item Send the ciphertext along with signed MAC.
+\end{enumerate}
+
+\subsubsection{Register Machine}
+User with channel seed can acquire channel chain ownership.
+Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows tangle-accelerator to publish messages on MAM channel chain.
+Asymmetric encryption is utilizing during the process of exchanging Seed.
+Digital signature should be taken at the same time to ensure data integrity.
+Once seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
+Thus, seed isn't needed to be exposed during communication after an edge device is successfully registered.
+
+\subsubsection{Issues in End-to-End-Encryption}
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met a few challenges in the E2EE we proposed.
+
+\paragraph{Linear Time to Read Message}
+It is linear time to decrypt message instead of constant time.
+Nevertheless, there is one way to speed up the message decryption process.
+A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
+This procedure can reduce the time spending on internet communication.
+
+\paragraph{Spam on Message Channel Chain}
+Tampering the messages which have conducted E2EE would be a challenging mission.
+However, spamming would be the critical issue participants may meet under this architecture.
+It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
+Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
+Spam would cause subscribers wasting plenty of time on decrypting useless messages.
+To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
 

### 2020-07-05 paper.tex
Add an figure to show the overview of E2EE
Use plural

@@
 To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{delegation}
+    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegate MAM operations to Tangle-accelerator.}
+    \label{fig:delegation}
+\end{figure}
 
@@
 \begin{enumerate}
-    \item Generate symmetric key with unique device identifier and Message Authentication Code (MAC) of the previous message.
+    \item Generate symmetric keys with unique device identifier and Message Authentication Code (MAC) of the previous message.
 If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message.

### 2020-07-05 paper.tex
Cite MQTT
Fix grammar

@@
 
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
@@
     \includegraphics[width=\linewidth]{delegation}
-    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegate MAM operations to Tangle-accelerator.}
+    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
     \label{fig:delegation}
@@
 \subsubsection{Infrastructure}
-To build the system, MQTT is chosen as the communication protocol.
+To build the system, MQTT\cite{MQTT} is chosen as the communication protocol.
 MQTT protocol utilizes much more lightweight packet than HTTP protocol has.

### 2020-07-05 paper.tex
Rename extra fee to cancellation fee in Unsubscription section

--- 2020-07-04 paper.tex
@@
 
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
-\section{Masked Authenticated Messaging}
-MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
-The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
+\section{Masked Authenticate Messaging}
+Data storage is the trust basis of data trading platforms where the data assets are reserved.
+Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
+Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
+In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
+
+MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
+The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
+Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
+A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
+The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
 
-\subsection{The Message Streams}
-A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
-The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
-Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
-This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
-Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
+This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
 
@@
     \centering
-    \includegraphics[width=3.5in]{mam_structure}
-    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints.
-The IDs of channel and endpoint are the roots of different Merkle trees in MSS.
-The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
-    \label{fig:mam_structure}
+    \includegraphics[width=2.5in]{mam_struct}
+    \caption{The concept of MAM.}
+    \label{fig:mam_struct}
 \end{figure}
 
-\subsection{Enable Access Control and Authentication}
-The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
-If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
 The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
-These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of MAM bundle.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
+These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
 %scalability
-\subsubsection{A Scalable Keys and Data Entry Points Management}
-The importance of scalable key and data entry points management increases over time.
+The importance of scalable key and data entry points management increases as the service operating over time.
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
@@
 %classify
-\subsubsection{Data Sreams Classification}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
@@
 Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entry points of the data steams should be reserved.
 
 %data trace
-\subsubsection{A Traceable Data Stream}
-Data traceability is an important security issue that allows users to track the changes of data.
+Moreover, data traceability is an important security issue that allows users to track the changes of data.
 Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
@@
 
-\subsection{Delegate MAM operations to Tangle-accelerator}
+The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this paper, we evaluate the performance of MAM, and improve the efficiency with different strategies.
+Also, we take offloading the computation tasks to brokers as another possible approach for IoT devices, since brokers are considered to have higher computational power.
+
+\subsection{TA - endpoint}
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 
-\subsubsection{Infrastructure}
-To build the system, MQTT is chosen as the communication protocol.
-MQTT protocol utilizes much more lightweight packet than HTTP protocol has.
-The topic-based publish-subscribe pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on low-level edge devices with limited bandwidth.
-The publish-subscribe model decouples publishers and subscribers in many ways:
+\subsubsection{Plight for Low-level edge device}
 
-\begin{itemize}
-    \item Space decoupling: Both publisher and subscriber don't need to know each other.
-    \item Time decoupling: Publishers and subscribers do not need to run at the same time.
-    \item Synchronization decoupling: Operations are decoupled from the publisher and subscriber.
-If we can decouple the operations, then the endpoint doesn’t need to maintain the connection until receive the response.
-Message from endpoint can be served as send-and-forget fashion.
-\end{itemize}
+\section{Decentralized Subscription-based Data Trading Case Study}
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
 
-\subsubsection{End-to-End-Encryption}
-Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message.
-To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol.
-The plaintext will be encrypted with this lightweight end-to-end-encryption.
-The E2EE process ensures only authorized subscribers can read the messages published on MAM.
+\subsection{Prerequisite}
+All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication.
+An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.
 
-%pic
-\begin{figure*}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{MAM_E2EE}
-    \caption{The process of E2EE.}
-    \label{fig:MAM_E2EE}
-\end{figure*}
+\subsection{Launch Data Products}
+To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
+For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
+And brokers are responsible for Product Contract creation.
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the whole E2EE process we present. The following section addresses the process.
-
-\begin{enumerate}
-    \item Generate symmetric key with unique device identifier and Message Authentication Code (MAC) of the previous message.
-If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message.
-Key Derivation Function (KDF) is used to generate the symmetric keys.
-    \item Compute the Message Authentication Code (MAC) of current message with Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
-    \item Apply the generated symmetric key to encrypt plaintext.
-    \item Concatenate the MAC of current message would and the MAC of previous message, and then the result will be signed with digital signature algorithm.
-    \item Send the ciphertext along with signed MAC.
-\end{enumerate}
-
-\subsubsection{Register Machine}
-User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows tangle-accelerator to publish messages on MAM channel chain.
-Asymmetric encryption is utilizing during the process of exchanging Seed.
-Digital signature should be taken at the same time to ensure data integrity.
-Once seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed isn't needed to be exposed during communication after an edge device is successfully registered.
-
-\subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met a few challenges in the E2EE we proposed.
-
-\paragraph{Linear Time to Read Message}
-It is linear time to decrypt message instead of constant time.
-Nevertheless, there is one way to speed up the message decryption process.
-A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
-This procedure can reduce the time spending on internet communication.
-
-\paragraph{Spam on Message Channel Chain}
-Tampering the messages which have conducted E2EE would be a challenging mission.
-However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
-Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
-Spam would cause subscribers wasting plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
-
-\section{Decentralized Data Marketplace Case Study}
-Trading Models of Decentralized Data Marketplace
-\subsubsection{Set Up}
-All participants need to register on TangleID\cite{TangleID}, a self-sovereign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
-
-\subsubsection{Launch Data Products}
-To launch a data product, data providers need to create a MAM channel/endpoint and a Product Contract.
-However, considering IoT devices have no ability to handle both uploading data to MAM and interacting Ethereum smart contracts while collecting continuous data with low computing power, these works are offloaded to brokers.
-
-The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract.
-As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest data consumers with a wrong one.
+The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract.
+This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
 The workflow is shown in Fig.~\ref{fig:launching_product}.
-
-Data providers start uploading data once the MAM channel/endpoint are created, each MAM message contains encrypted contexts along with signatures which allows data consumers to check the integrity.
-In addition, one can perform the signature validation without the encryption key on MAM.
+Finally, data providers can start uploading data.
 
@@
 
-\subsubsection{Refunding}
-Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after receiving the subscription fee.
-Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective.
-The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
-When the refund procedure is launched, all consumers start voting based on their opinions on the data product.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
+\subsection{Unsubscribe to Data Products}
+Data consumers can unsubscribe to data products when they're not interested anymore.
+Product Contract hold an unsubscriber list to record the unsubscribers.
+When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
+The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract.
+And $F_{cancel}$ is the cancellation fee charged for unsubscription, since brokers need cancellation fee to go through the key changing procedure.
+
+Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
+The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
+
+\begin{equation}
+\label{equation:unsubscribe_provider}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_broker}
+    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_consumer}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{unsubscribe}
+    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
+Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
+    \label{fig:unsubscribe}
+\end{figure}
+
+\subsection{Launch a Refund}
+Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
+Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
+When the refund procedure is launched, all consumers vote to decide whether the refund is established.
+See Fig.~\ref{fig:refund}.
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following:
+
+\begin{equation}
+    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.5in]{refund}
+    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
+Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \label{fig:refund}
+\end{figure}
 

### 2020-07-05 paper.tex
Rephrase & introduce endpoint

--- 2020-07-05 paper.tex
@@
 \subsubsection{Infrastructure}
-To build the system, MQTT\cite{MQTT} is chosen as the communication protocol.
-MQTT protocol utilizes much more lightweight packet than HTTP protocol has.
-The topic-based publish-subscribe pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on low-level edge devices with limited bandwidth.
-The publish-subscribe model decouples publishers and subscribers in many ways:
+In the following sections, we refer the low-level devices as \textbf{endpoint}s.
+MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic.
+The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth.
+The pub/sub model decouples publishers and subscribers in many ways:
 
 \begin{itemize}
-    \item Space decoupling: Both publisher and subscriber don't need to know each other.
-    \item Time decoupling: Publishers and subscribers do not need to run at the same time.
-    \item Synchronization decoupling: Operations are decoupled from the publisher and subscriber.
-If we can decouple the operations, then the endpoint doesn’t need to maintain the connection until receive the response.
-Message from endpoint can be served as send-and-forget fashion.
+    \item Space decoupling: Both publishers and subscribers don't need to know each other.
+    \item Time decoupling: Publishers and subscribers do not need to be active at the same time.
+    \item Synchronization decoupling: Operations are decoupled from the publishers and subscribers.
+The publishers do not need to be alive until the response arrives.
+Messages from publisher can be served as send-and-forget fashion.
 \end{itemize}

### 2020-07-05 paper.tex
Add TA structure figure

@@
 To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
-Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
+Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{ta_structure}
+    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
+It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed.
+Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
+    \label{fig:ta_struct}
+\end{figure}
 
@@
 Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration.
-Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator.
 However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{ta_structure}
-    \caption{The structure of Tangle-accelerator.}
-    \label{fig:ta_struct}
-\end{figure}
 

### 2020-07-05 paper.tex
Add more description of cancellation fee

--- 2020-07-05 paper.tex
@@
 The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract.
-And $F_{cancel}$ is the cancellation fee charged for unsubscription, since brokers need cancellation fee to go through the key changing procedure.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+In SaaS, the cancellation fee is a way to make sure the service providers are protected.
+It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
+However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
 

### 2020-07-06 paper.tex

@@
 $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+
 In SaaS, the cancellation fee is a way to make sure the service providers are protected.

### 2020-07-06 paper.tex
Evaluate for performance between MAM and E2EE

--- 2020-07-05 paper.tex
@@
 \usepackage{float}
+\usepackage{tabularx}
+\usepackage{makecell}
+\usepackage{multirow}
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{algorithmic,algorithm}
 \usepackage{graphicx}
@@
 
-% alternative solution => IPFS(data) + MAM(index)
 \subsection{Digital Identity}
 The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
-In our architecture, a self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
-TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
-The identity information such as public key, unique identifiers of services and metadata consists a DID document.
+We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
+
+\begin{table}[h]
+	\caption{The comparism of centralized and decentralized identity model}
+	\label{tab:did}
+	\begin{tabularx}{\linewidth}{|l|X|X|}
+	\hline
+		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
+		\hline
+		Control & Enterprises control identities & Entities control their identities \\
+		\hline
+		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
+		\hline
+		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
+		\hline
+	\end{tabularx}
+\end{table}
+
+Centralized identity model may have single point failure in identifier management and security issues like data leakage.
+With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
+Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
+
+In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
+The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
+If a VC is verified via issuer's public key, the message will be labelled as trusted.
+Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.in]{DID_VC}
+    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
+    \label{fig:did_vc}
+\end{figure}
+
+In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
 One can easily prove himself by sharing the identifier on MAM without any authority.
 
-Through TangleID, containing public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
+Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
@@
 
-\section{Decentralized Data Marketplace Case Study}
-Trading Models of Decentralized Data Marketplace
-\subsubsection{Set Up}
-All participants need to register on TangleID\cite{TangleID}, a self-sovereign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
+\section{Decentralized Subscription-based Data Trading Case Study}
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
 
-\subsubsection{Launch Data Products}
-To launch a data product, data providers need to create a MAM channel/endpoint and a Product Contract.
-However, considering IoT devices have no ability to handle both uploading data to MAM and interacting Ethereum smart contracts while collecting continuous data with low computing power, these works are offloaded to brokers.
+\subsection{Prerequisite}
+All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication.
+An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.
 
-The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract.
-As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product}.
+\subsection{Launch Data Products}
+To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
+For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
+And brokers are responsible for Product Contract creation.
 
-Data providers start uploading data once the MAM channel/endpoint are created, each MAM message contains encrypted contexts along with signatures which allows data consumers to check the integrity.
-In addition, one can perform the signature validation without the encryption key on MAM.
+The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
+This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
+The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
+Finally, the data product is launched and data providers can start uploading data.
 
@@
 
-\subsubsection{Trading}
-Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retrieve it from Product Contract.
+\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
+    function addHashedKey(
+        string memory _hashedKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add hashed key."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        hashedKey = hashedKey;
+        emit newHashedKey(hashedKey);
+    }
 
-Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants.
+    function addCertifiedKey(
+        string memory _certifiedKey
+    ) public {
+        require(
+            msg.sender == broker,
+            "Only broker can add certifiedKey."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        certifiedKey = _certifiedKey;
+        state = State.KeyCertified;
+        emit newCertifiedKey(certifiedKey);
+    }
+\end{lstlisting}
+
+\subsection{Trading}
+Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
+
+Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public.
 Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
-The key sending process is shown in Fig.~\ref{fig:key_exchange}.
+The key sending process is shown in Fig.~\ref{fig:key_exchange} and Listing.~\ref{lst:key_exchange}.
+The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
 
@@
 
-\subsubsection{Refunding}
-Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after receiving the subscription fee.
-Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective.
-The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
-When the refund procedure is launched, all consumers start voting based on their opinions on the data product.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+
+\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
+    function addEncryptKey(
+        address _consumer,
+        string memory _encryptKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add the encrypted key."
+        );
+        require(
+            consumer2Purchase[_consumer].isKeyAdded == false,
+            "Encryption key has been added."
+        );
+        consumer2Purchase[_consumer].encryptKey = _encryptKey;
+        consumer2Purchase[_consumer].isKeyAdded = true;
+        emit newEncryptKey(_consumer, _encryptKey);
+    }
+\end{lstlisting}
+
+\subsection{Unsubscribe to Data Products}
+Data consumers can unsubscribe to data products when they're not interested anymore.
+Product Contract hold an unsubscriber list to record the unsubscribers.
+When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
+The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+
+In SaaS, the cancellation fee is a way to make sure the service providers are protected.
+It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
+However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
+
+Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
+The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
+
+\begin{equation}
+\label{equation:unsubscribe_provider}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_broker}
+    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_consumer}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{unsubscribe}
+    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
+Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
+    \label{fig:unsubscribe}
+\end{figure}
+
+\subsection{Launch a Refund}
+Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
+Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
+When the refund procedure is launched, all consumers vote to decide whether the refund is established.
+See Fig.~\ref{fig:refund}.
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following:
+
+\begin{equation}
+    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.5in]{refund}
+    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
+Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \label{fig:refund}
+\end{figure}
 
@@
     \includegraphics[width=2.5in]{mam_create}
-    \caption{Time cost of MAM creation.}
+    \caption{Elapsed time of MAM creation.}
     \label{fig:mam_create}
@@
     \includegraphics[width=2.5in]{mam_send}
-    \caption{Time cost of sending a message through MAM.}
+    \caption{Elapsed time of sending a message through MAM.}
     \label{fig:mam_send}
@@
 
+\subsection{Smart Contract}
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
+The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+The Gas usage estimation is shown in Table.~\ref{tab:gas}.
+
+\begin{table*}[h]
+	\caption{Gas consumption for each function of Product Contract}
+	\label{tab:gas}
+	\centering
+	\resizebox{0.7\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
+		\hline
+		generate contract & Broker & 2251002 \\
+		subscribe product & Consumer & 44486 \\
+		upload signed key to consumer & Provider & 147369 \\
+		upload certified key & Broker & 167678 \\
+		upload hased encryption key & Provider & 166784 \\
+		update the amount of uploaded data & Broker & 32825 \\
+		request refund & Consumer & 22545 \\
+		unsubscribe & Consumer & 22641 \\
+		withdraw & Broker/Provider/Consumer & 14719 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Storage on blockchain is expensive.
+For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
+However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+However, using zero-knowledge protocol is out of the scope of this paper.
+
+Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
+We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+
+\begin{equation}
+\label{equa:ether_calculation}
+Ethers = Gas \ Price \times Gas \ Amount
+\end{equation}
+
+When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
+Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
+Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
+
+\begin{table*}[h]
+	\caption{Data Price Estimation}
+	\label{tab:ether}
+	\centering
+	\resizebox{0.8\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.003 & 0.011 \\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.005 & 0.020 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+\subsection{MAM vs. the delegated MAM}
+What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
+In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
+The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+
+The steps counted in MAM benchmark including:
+\begin{itemize}
+	\item Encrypt input payload
+	\item Publish final message on IOTA Tangle
+\end{itemize}
+
+The steps counted in E2EE benchmark including:
+\begin{itemize}
+	\item Generate symmetric key for encryption
+	\item Hash input payload
+	\item Encrypt input payload
+	\item Transmit final message to tangle-accelerator
+\end{itemize}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{mam_vs_e2ee}
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
+    \label{fig:mam_vs_e2ee}
+\end{figure}
+
+On Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
+Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
+The bump of MAM performance around 750 bytes proves this point.
+Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
+
 \section{Conclusions}

### 2020-07-06 paper.tex
Add details of DID and VC

@@
 \usepackage{tabularx}
-\usepackage{makecell}
-\usepackage{multirow}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 
+% alternative solution => IPFS(data) + MAM(index)
 \subsection{Digital Identity}
@@
 		\hline
-		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
+		Security & Identity holded in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\ 
 		\hline
@@
 
-Centralized identity model may have single point failure in identifier management and security issues like data leakage.
+Centralized identity model may have single point failure in identifier management, also security issues like data leakage.
 With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
@@
 
-In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
-The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
-If a VC is verified via issuer's public key, the message will be labelled as trusted.
-Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
+%here, todo
+In the decentralized identity model, the digital footprints of entities is made up of Verifiable Credential (VC) issued by trusted issuer, such as school and government, and VCs are only worthy when verifying party recognize the issuer.
+If the VC is verified, the message will be labelled as trusted.
+Fig.
+shows the relationship of VC issuer, verifier and user.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.in]{DID_VC}
-    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
-    \label{fig:did_vc}
-\end{figure}
-
-In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
+In our architecture, a decentralized self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
+TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
+The identity information such as public key, unique identifiers of services and metadata consists a DID document.
 One can easily prove himself by sharing the identifier on MAM without any authority.
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
+Through TangleID, containing public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
@@
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract.
 This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
-Finally, the data product is launched and data providers can start uploading data.
+The workflow is shown in Fig.~\ref{fig:launching_product}.
+Finally, data providers can start uploading data.
 
@@
 
-\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
-    function addHashedKey(
-        string memory _hashedKey
-    ) public {
-        require(
-            msg.sender == provider,
-            "Only provider can add hashed key."
-        );
-        require(
-            state == State.Launched,
-            "One key has been certified."
-        );
-        hashedKey = hashedKey;
-        emit newHashedKey(hashedKey);
-    }
-
-    function addCertifiedKey(
-        string memory _certifiedKey
-    ) public {
-        require(
-            msg.sender == broker,
-            "Only broker can add certifiedKey."
-        );
-        require(
-            state == State.Launched,
-            "One key has been certified."
-        );
-        certifiedKey = _certifiedKey;
-        state = State.KeyCertified;
-        emit newCertifiedKey(certifiedKey);
-    }
-\end{lstlisting}
-
 \subsection{Trading}
@@
 Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
-The key sending process is shown in Fig.~\ref{fig:key_exchange} and Listing.~\ref{lst:key_exchange}.
+The key sending process is shown in Fig.~\ref{fig:key_exchange}.
 The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
@@
 \end{figure}
-
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
-\lstset{style=solidity}
-
-\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
-    function addEncryptKey(
-        address _consumer,
-        string memory _encryptKey
-    ) public {
-        require(
-            msg.sender == provider,
-            "Only provider can add the encrypted key."
-        );
-        require(
-            consumer2Purchase[_consumer].isKeyAdded == false,
-            "Encryption key has been added."
-        );
-        consumer2Purchase[_consumer].encryptKey = _encryptKey;
-        consumer2Purchase[_consumer].isKeyAdded = true;
-        emit newEncryptKey(_consumer, _encryptKey);
-    }
-\end{lstlisting}
 
@@
     \includegraphics[width=2.5in]{mam_create}
-    \caption{Elapsed time of MAM creation.}
+    \caption{Time cost of MAM creation.}
     \label{fig:mam_create}
@@
     \includegraphics[width=2.5in]{mam_send}
-    \caption{Elapsed time of sending a message through MAM.}
+    \caption{Time cost of sending a message through MAM.}
     \label{fig:mam_send}
@@
 
-\subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
-On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
-The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-The Gas usage estimation is shown in Table.~\ref{tab:gas}.
-
-\begin{table*}[h]
-	\caption{Gas consumption for each function of Product Contract}
-	\label{tab:gas}
-	\centering
-	\resizebox{0.7\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
-		\hline
-		generate contract & Broker & 2251002 \\
-		subscribe product & Consumer & 44486 \\
-		upload signed key to consumer & Provider & 147369 \\
-		upload certified key & Broker & 167678 \\
-		upload hased encryption key & Provider & 166784 \\
-		update the amount of uploaded data & Broker & 32825 \\
-		request refund & Consumer & 22545 \\
-		unsubscribe & Consumer & 22641 \\
-		withdraw & Broker/Provider/Consumer & 14719 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
-Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
-Storage on blockchain is expensive.
-For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
-
-Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
-\label{equa:ether_calculation}
-Ethers = Gas \ Price \times Gas \ Amount
-\end{equation}
-
-When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
-Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
-Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
-
-\begin{table*}[h]
-	\caption{Data Price Estimation}
-	\label{tab:ether}
-	\centering
-	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.003 & 0.011 \\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.004 & 0.016 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.004 & 0.016 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.005 & 0.020 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-\subsection{MAM vs. the delegated MAM}
-What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
-Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-
-The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
-	\item Publish final message on IOTA Tangle
-\end{itemize}
-
-The steps counted in E2EE benchmark including:
-\begin{itemize}
-	\item Generate symmetric key for encryption
-	\item Hash input payload
-	\item Encrypt input payload
-	\item Transmit final message to tangle-accelerator
-\end{itemize}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
-
-On Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
-Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
-The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
-
 \section{Conclusions}

### 2020-07-06 paper.tex

--- 2020-07-06 paper.tex
@@
 
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
-\section{Masked Authenticate Messaging}
-Data storage is the trust basis of data trading platforms where the data assets are reserved.
-Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
-Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
+\section{Masked Authenticated Messaging}
+MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
+The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
+With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
 
-MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Channel and endpoint represent a stream of messages, which functions as singly-linked lists.
-The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point.
-Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID.
-A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint.
-The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.
-
-A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint.
-This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.
+\subsection{The Message Streams}
+A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
+To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
+The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
+Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
+Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
 
@@
     \centering
-    \includegraphics[width=2.5in]{mam_struct}
-    \caption{The concept of MAM.}
-    \label{fig:mam_struct}
+    \includegraphics[width=3.5in]{mam_structure}
+    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints.
+The IDs of channel and endpoint are the roots of different Merkle trees in MSS.
+The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
+    \label{fig:mam_structure}
 \end{figure}
 
+\subsection{Enable Access Control and Authentication}
+The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
+If the message payload is encrypted, subscribers are required for encryption keys to decode messages.
 The authentication in MAM includes two aspects: source and data.
-Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender.
-These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions.
+Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
+These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of MAM bundle.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
 
+\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
 %scalability
-The importance of scalable key and data entry points management increases as the service operating over time.
+\subsubsection{A Scalable Keys and Data Entry Points Management}
+The importance of scalable key and data entry points management increases over time.
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.

### 2020-07-06 paper.tex

--- 2020-07-06 paper.tex
@@
 \usepackage{float}
-\usepackage{tabularx}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
-We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
-
-\begin{table}[h]
-	\caption{The comparism of centralized and decentralized identity model}
-	\label{tab:did}
-	\begin{tabularx}{\linewidth}{|l|X|X|}
-	\hline
-		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
-		\hline
-		Control & Enterprises control identities & Entities control their identities \\ 
-		\hline
-		Security & Identity holded in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\ 
-		\hline
-		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\ 
-		\hline
-	\end{tabularx}
-\end{table}
-
-Centralized identity model may have single point failure in identifier management, also security issues like data leakage.
-With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
-Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
-
-%here, todo
-In the decentralized identity model, the digital footprints of entities is made up of Verifiable Credential (VC) issued by trusted issuer, such as school and government, and VCs are only worthy when verifying party recognize the issuer.
-If the VC is verified, the message will be labelled as trusted.
-Fig.
-shows the relationship of VC issuer, verifier and user.
-
-In our architecture, a decentralized self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
+In our architecture, a self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
 TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.

### 2020-07-06 paper.tex
Strengthen TangleID, update VC figure

--- 2020-07-06 paper.tex
@@
 
-% alternative solution => IPFS(data) + MAM(index)
 \subsection{Digital Identity}
@@
 
-Centralized identity model may have single point failure in identifier management, also security issues like data leakage.
+Centralized identity model may have single point failure in identifier management and security issues like data leakage.
 With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
@@
 
-%here, todo
-In the decentralized identity model, the digital footprints of entities is made up of Verifiable Credential (VC) issued by trusted issuer, such as school and government, and VCs are only worthy when verifying party recognize the issuer.
-If the VC is verified, the message will be labelled as trusted.
-Fig.
-shows the relationship of VC issuer, verifier and user.
+In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
+The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
+If a VC is verified via issuer's public key, the message will be labelled as trusted.
+Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
 
-In our architecture, a decentralized self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority.
-TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable.
-The identity information such as public key, unique identifiers of services and metadata consists a DID document.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.in]{DID_VC}
+    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
+    \label{fig:did_vc}
+\end{figure}
+
+In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
 One can easily prove himself by sharing the identifier on MAM without any authority.
 
-Through TangleID, containing public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
+Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.

### 2020-07-07 paper.tex
Change arrangement of figure key_upload
Fix typo
Add smart contract evaluation

@@
 \usepackage{tabularx}
+\usepackage{makecell}
+\usepackage{multirow}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 		\hline
-		Security & Identity holded in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
+		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
 		\hline
@@
 
+\subsection{Smart Contract}
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
+The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
+In the report of Ethereum network in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+The Gas usage estimation is shown in Table.~\ref{tab:gas}.
+
+\begin{table*}[h]
+	\caption{Gas consumption for each function of Product Contract}
+	\label{tab:gas}
+	\centering
+	\resizebox{0.7\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
+		\hline
+		generate contract & Broker & 2251002 \\
+		subscribe product & Consumer & 44486 \\
+		upload signed key to consumer & Provider & 147369 \\
+		upload certified key & Broker & 167678 \\
+		update encrypt key & Provider & 166784 \\
+		update the amount of uploaded data & Broker & 32825 \\
+		request refund & Consumer & 22545 \\
+		unsubscribe & Consumer & 22641 \\
+		withdraw & Broker/Provider/Consumer & 14719 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Storage on blockchain is expensive.
+For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
+However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+However, using zero-knowledge protocol is out of the scope of this paper that we list it in the future work.
+
+Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
+We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+
+\begin{equation}
+\label{equa:ether_calculation}
+Ethers = Gas \ Price \times Gas \ Amount
+\end{equation}
+
+When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
+Then if the refund esablished, all participants will withdraw the payment, which is already included in the basic cost.
+Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
+
+\begin{table*}[h]
+	\caption{Data Price Estimation}
+	\label{tab:ether}
+	\centering
+	\resizebox{0.8\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.003 & 0.011 \\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.005 & 0.020 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
 \section{Conclusions}

### 2020-07-07 paper.tex
Add citation to Etherscan

@@
 To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-In the report of Ethereum network in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+In the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
 The Gas usage estimation is shown in Table.~\ref{tab:gas}.

### 2020-07-07 paper.tex
Add solidity codes to Chap5

@@
 This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product}.
-Finally, data providers can start uploading data.
+The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
+Finally, the data product is launched and data providers can start uploading data.
 
@@
 
+\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
+	function addHashedKey(
+		string memory _hashedKey
+	) public {
+		require(
+			msg.sender == provider,
+			"Only provider can add hashed key."
+		);
+		require(
+			state == State.Launched,
+			"One key has been certified."
+		);
+		hashedKey = hashedKey;
+		emit newHashedKey(hashedKey);
+	}
+
+	function addCertifiedKey(
+		string memory _certifiedKey
+	) public {
+		require(
+			msg.sender == broker,
+			"Only broker can add certifiedKey."
+		);
+		require(
+			state == State.Launched,
+			"One key has been certified."
+		);
+		certifiedKey = _certifiedKey;
+		state = State.KeyCertified;
+		emit newCertifiedKey(certifiedKey);
+	}
+\end{lstlisting}
+
 \subsection{Trading}
@@
 Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
-The key sending process is shown in Fig.~\ref{fig:key_exchange}.
+The key sending process is shown in Fig.~\ref{fig:key_exchange} and Listing.~\ref{lst:key_exchange}.
 The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.
@@
 \end{figure}
+
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+
+\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
+    function addEncryptKey(
+        address _consumer,
+        string memory _encryptKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add the encrypted key."
+        );
+        require(
+            consumer2Purchase[_consumer].isKeyAdded == false,
+            "Encryption key has been added."
+        );
+        consumer2Purchase[_consumer].encryptKey = _encryptKey;
+        consumer2Purchase[_consumer].isKeyAdded = true;
+        emit newEncryptKey(_consumer, _encryptKey);
+    }
+\end{lstlisting}
 

### 2020-07-07 paper.tex
Fix indent
Update Conclusion

--- 2020-07-07 paper.tex
@@
 
-\subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
-On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
-The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-In the report of Ethereum network in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-The Gas usage estimation is shown in Table.~\ref{tab:gas}.
-
-\begin{table*}[h]
-	\caption{Gas consumption for each function of Product Contract}
-	\label{tab:gas}
-	\centering
-	\resizebox{0.7\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
-		\hline
-		generate contract & Broker & 2251002 \\
-		subscribe product & Consumer & 44486 \\
-		upload signed key to consumer & Provider & 147369 \\
-		upload certified key & Broker & 167678 \\
-		update encrypt key & Provider & 166784 \\
-		update the amount of uploaded data & Broker & 32825 \\
-		request refund & Consumer & 22545 \\
-		unsubscribe & Consumer & 22641 \\
-		withdraw & Broker/Provider/Consumer & 14719 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
-Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
-Storage on blockchain is expensive.
-For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper that we list it in the future work.
-
-Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
-\label{equa:ether_calculation}
-Ethers = Gas \ Price \times Gas \ Amount
-\end{equation}
-
-When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
-Then if the refund esablished, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
-Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
-
-\begin{table*}[h]
-	\caption{Data Price Estimation}
-	\label{tab:ether}
-	\centering
-	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.003 & 0.011 \\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.004 & 0.016 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.004 & 0.016 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.005 & 0.020 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
 \section{Conclusions}
 By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.
+It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
+
+In the subscription-based data trading, there are some issues that worth to discuss and improve.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot Gas due to the frequent store operation.
+Therefore, it is worth studying how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
+Second, brokers are irreplaceable either from the view of architecture design or trading procedures, they are the key to the stable system.
+However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
+
+Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
 

### 2020-07-07 paper.tex
Fix grammar

--- 2020-07-07 paper.tex
@@
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
 This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.

### 2020-07-07 paper.tex
Modify statement

@@
 To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-In the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
 The Gas usage estimation is shown in Table.~\ref{tab:gas}.

### 2020-07-07 paper.tex
Modify column title

@@
 		upload certified key & Broker & 167678 \\
-		update encrypt key & Provider & 166784 \\
+		upload hased encryption key & Provider & 166784 \\
 		update the amount of uploaded data & Broker & 32825 \\

### 2020-07-07 paper.tex
Fix typo
Fix wierd statement

@@
 Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper that we list it in the future work.
+However, using zero-knowledge protocol is out of the scope of this paper.
 
@@
 When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
-Then if the refund esablished, all participants will withdraw the payment, which is already included in the basic cost.
+Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
 Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.

### 2020-07-07 paper.tex
t

@@
 The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
-Finally, the prototype is implemented and evaluated.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Data Marketplace, decentralization, Distributed Ledger Technology
+subscription-based IoT data trading, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically.
-The trading processes are automated with smart contracts, which allows devices focus on their jobs while gaining the rewards.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
@@
 The contributions in the paper are summarized as follow:
+automating the trading of digital assets and services.
+
 \begin{itemize}
-	\item Standing on our proposed decentralized data trading infrastructure, we review several decentralized data trading architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
-    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
-We also compare the performance of exchanging different cryptosystems.
-	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
+	\item We propose a decentralized subscription-based IoT data trading platform, which enables participants to trade the digital assets  .
+	\item We .  
+	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers, the minimum cost for data consumers to interact with date product.
 \end{itemize}

### 2020-07-07 paper.tex
fix typo

--- 2020-07-07 paper.tex
@@
 \begin{table}[h]
-	\caption{The comparism of centralized and decentralized identity model}
+	\caption{The comparison of centralized and decentralized identity model}
 	\label{tab:did}
@@
 		\hline
-		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
+		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
 		\hline
@@
 Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
 Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.

### 2020-07-07 paper.tex
Revise Introduction

@@
 The contributions in the paper are summarized as follow:
-automating the trading of digital assets and services.
-
 \begin{itemize}
-	\item We propose a decentralized subscription-based IoT data trading platform, which enables participants to trade the digital assets  .
-	\item We .  
-	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers, the minimum cost for data consumers to interact with date product.
+	\item We investigate the usage of DLTs and distribute data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
+	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
+	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
+	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
 \end{itemize}
@@
 In Section~\ref{section:relatedWork}, some related work of data exchange mechanisms for IoT, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section ARCHI, the design thinking of proposed data trading architecture.
-In Section ARCHI, the trading models are well explained.
-The analysis and improvement of MAM are given in Section MAM-EXP.
-In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully.
-Finally, we conclude the paper in Section CONCLUSION.
+In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
+In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
+In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
+The analysis results are given in Section~\ref{section:evaluation}.
+Finally, we conclude the paper in Section~\ref{section:conclusion}.
 
@@
 \section{System Design Thinking}
+\label{section:design_thinking}
 \subsection{Data subscription-based trading platform players}
@@
 \section{Masked Authenticated Messaging}
+\label{section:MAM}
 MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
@@
 \section{Decentralized Subscription-based Data Trading Case Study}
+\label{section:trading_model}
 In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
@@
 \section{Evaluations}
+\label{section:evaluation}
 It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
@@
 \section{Conclusions}
+\label{section:conclusion}
 By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.

### 2020-07-07 paper.tex
Revise Related Work

@@
 % pub/sub
-\subsection{Data exchange mechanism for IoT}
-The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
-A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.
+\subsection{The Publish/subscribe Communication Models Over Blockchain}
+The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
+A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
 
@@
 Abdullahi and G.
-Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
+Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
 Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
 Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system.
-Also the storage is not well illustrated in the work.
+However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure.
 G.
@@
 But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
-The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.
 
@@
 Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
@@
 Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
+
+The previous works contribute to different aspects of building a reliable pub/sub system over blockchain.
+However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.
 

### 2020-07-07 paper.tex
Revise Chap 3

@@
 The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum info like its identifier and public key.
-Third, as brokers running on machines in a stable network and electricity environment, besides matching procedures, participants on resource-constrained devices can offload the computation tasks to brokers.
-In our proposed protocol, devices can delegate the uploading and trading processes to brokers after signing the data, and brokers can perform verifiable checks without knowing the contents.
+Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables an proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
+With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
 
@@
 \begin{itemize}
-    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \item \textbf{Scalability}:
+	\begin{itemize}
+		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
+    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \end{itemize}    
     \item \textbf{Integrity}: 
@@
     address[] consumers;
+    address[] unsubscriber;
 
@@
     uint public affirmativeVotes;
-    string blindedKey;
-    string signedBlindedKey;
+    string hashedKey;
+    string certifiedKey;
 

### 2020-07-07 paper.tex
Revise Chap 4

@@
 Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The key upload times is also restricted in order to avoid data provider uploading fake key frequently.
+The key upload time is also restricted in order to avoid data provider uploading fake key frequently.
 If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.
@@
 
-\subsubsection{Infrastructure}
+\subsubsection{Communication Protocol}
 In the following sections, we refer the low-level devices as \textbf{endpoint}s.
@@
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the whole E2EE process we present. The following section addresses the process.
+In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:
 
@@
 
-\subsubsection{Register Machine}
+\subsubsection{Register with Tangle-accelerator}
 User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows tangle-accelerator to publish messages on MAM channel chain.
-Asymmetric encryption is utilizing during the process of exchanging Seed.
+Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
+Asymmetric encryption is utilizing during the process of exchanging seed.
 Digital signature should be taken at the same time to ensure data integrity.
-Once seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed isn't needed to be exposed during communication after an edge device is successfully registered.
+Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
+Thus, seed will not be exposed during communication after an edge device is successfully registered.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met a few challenges in the E2EE we proposed.
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE:
 

### 2020-07-07 paper.tex
Fix typos and grammar

@@
 %cite IoT data subscription economy
-The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
+The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchange among devices are periodically that only data in a specific time period is interested.
+The real-time data exchange among devices are periodical that only data in a specific time period is interested.
 Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
@@
 However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
-Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system.
+Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
 Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.

### 2020-07-07 paper.tex
Add description for hardware acceleration

--- 2020-07-07 paper.tex
@@
 The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
+Finally, the prototype is implemented and evaluated.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-subscription-based IoT data trading, decentralization, Distributed Ledger Technology
+Data Marketplace, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically.
+The trading processes are automated with smart contracts, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
@@
 \begin{itemize}
-	\item We investigate the usage of DLTs and distribute data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
-	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
-	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
-	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
+	\item Standing on our proposed decentralized data trading infrastructure, we review several decentralized data trading architectures as well as the existing distributed storage, and clarify the necessity of using MAM.
+    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation.
+We also compare the performance of exchanging different cryptosystems.
+	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
 \end{itemize}
@@
 In Section~\ref{section:relatedWork}, some related work of data exchange mechanisms for IoT, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
-In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
-In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
-The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion}.
+In Section ARCHI, the design thinking of proposed data trading architecture.
+In Section ARCHI, the trading models are well explained.
+The analysis and improvement of MAM are given in Section MAM-EXP.
+In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully.
+Finally, we conclude the paper in Section CONCLUSION.
 
@@
 % pub/sub
-\subsection{The Publish/subscribe Communication Models Over Blockchain}
-The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
+\subsection{Data exchange mechanism for IoT}
+The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
+A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
+A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.
 
@@
 Abdullahi and G.
-Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
+Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
 Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
 Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure.
+However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system.
+Also the storage is not well illustrated in the work.
 G.
@@
 But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
+The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.
 
@@
 Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
@@
 Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
-
-The previous works contribute to different aspects of building a reliable pub/sub system over blockchain.
-However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.
 
@@
 \section{System Design Thinking}
-\label{section:design_thinking}
 \subsection{Data subscription-based trading platform players}
@@
 The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum info like its identifier and public key.
-Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables an proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
-With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
+Third, as brokers running on machines in a stable network and electricity environment, besides matching procedures, participants on resource-constrained devices can offload the computation tasks to brokers.
+In our proposed protocol, devices can delegate the uploading and trading processes to brokers after signing the data, and brokers can perform verifiable checks without knowing the contents.
 
@@
 \begin{itemize}
-    \item \textbf{Scalability}:
-	\begin{itemize}
-		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
-    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
-    \end{itemize}    
+    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
     \item \textbf{Integrity}: 
@@
 \begin{table}[h]
-	\caption{The comparison of centralized and decentralized identity model}
+	\caption{The comparism of centralized and decentralized identity model}
 	\label{tab:did}
@@
 		\hline
-		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
+		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
 		\hline
@@
     address[] consumers;
-    address[] unsubscriber;
 
@@
     uint public affirmativeVotes;
-    string hashedKey;
-    string certifiedKey;
+    string blindedKey;
+    string signedBlindedKey;
 
@@
 \section{Masked Authenticated Messaging}
-\label{section:MAM}
 MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
@@
 
+The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
+Each of them can be chosen according to the working hardware and scenario.
+On some hardwares, the developers can choose the cryptographic methods with hardware acceleration.
+With hardware acceleration, the elapsed time could be dropped a step more.
+
 \subsubsection{Register Machine}
@@
 \section{Decentralized Subscription-based Data Trading Case Study}
-\label{section:trading_model}
 In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
@@
 \section{Evaluations}
-\label{section:evaluation}
 It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
@@
 Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
 Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
@@
 \end{table*}
+\subsection{MAM vs. the delegated MAM}
+What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
+In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
+The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+
+The steps counted in MAM benchmark including:
+\begin{itemize}
+	\item Encrypt input payload
+	\item Publish final message on IOTA Tangle
+\end{itemize}
+
+The steps counted in E2EE benchmark including:
+\begin{itemize}
+	\item Generate symmetric key for encryption
+	\item Hash input payload
+	\item Encrypt input payload
+	\item Transmit final message to tangle-accelerator
+\end{itemize}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{mam_vs_e2ee}
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
+    \label{fig:mam_vs_e2ee}
+\end{figure}
+
+It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
+Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
+The bump of MAM performance around 750 bytes proves this point.
+Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
 
 \section{Conclusions}
-\label{section:conclusion}
 By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.

### 2020-07-08 paper.tex
Update gas usage estimation

--- 2020-07-07 paper.tex
@@
 		\hline
-		generate contract & Broker & 2251002 \\
-		subscribe product & Consumer & 44486 \\
-		upload signed key to consumer & Provider & 147369 \\
-		upload certified key & Broker & 167678 \\
-		upload hased encryption key & Provider & 166784 \\
-		update the amount of uploaded data & Broker & 32825 \\
-		request refund & Consumer & 22545 \\
-		unsubscribe & Consumer & 22641 \\
-		withdraw & Broker/Provider/Consumer & 14719 \\
+		generate contract & broker & 2558980 \\ 
+		subscribe product & consumer & 72259 \\ 
+		upload hash key & provider & 68276  \\ 
+		upload encryption key to consumer & provider & 86614 \\ 
+		upload certified key & broker & 131535 \\
+		update amount of uploaded data & broker & 32157 \\
+		unsubscribe & consumer & 8234 \\
+		request refund & consumer & 12067 \\
+		withdraw & broker & 11313 \\
 		\hline

### 2020-07-08 paper.tex
Fix grammar

--- 2020-07-07 paper.tex
@@
 
-The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
-Each of them can be chosen according to the working hardware and scenario.
-On some hardwares, the developers can choose the cryptographic methods with hardware acceleration.
-With hardware acceleration, the elapsed time could be dropped a step more.
-
 \subsubsection{Register Machine}
@@
 
-\subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
-On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
-The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-The Gas usage estimation is shown in Table.~\ref{tab:gas}.
-
-\begin{table*}[h]
-	\caption{Gas consumption for each function of Product Contract}
-	\label{tab:gas}
-	\centering
-	\resizebox{0.7\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
-		\hline
-		generate contract & Broker & 2251002 \\
-		subscribe product & Consumer & 44486 \\
-		upload signed key to consumer & Provider & 147369 \\
-		upload certified key & Broker & 167678 \\
-		upload hased encryption key & Provider & 166784 \\
-		update the amount of uploaded data & Broker & 32825 \\
-		request refund & Consumer & 22545 \\
-		unsubscribe & Consumer & 22641 \\
-		withdraw & Broker/Provider/Consumer & 14719 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
-Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
-Storage on blockchain is expensive.
-For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
-
-Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
-\label{equa:ether_calculation}
-Ethers = Gas \ Price \times Gas \ Amount
-\end{equation}
-
-When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
-Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
-Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
-
-\begin{table*}[h]
-	\caption{Data Price Estimation}
-	\label{tab:ether}
-	\centering
-	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.003 & 0.011 \\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.004 & 0.016 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.004 & 0.016 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.005 & 0.020 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-\subsection{MAM vs. the delegated MAM}
-What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
-Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-
-The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
-	\item Publish final message on IOTA Tangle
-\end{itemize}
-
-The steps counted in E2EE benchmark including:
-\begin{itemize}
-	\item Generate symmetric key for encryption
-	\item Hash input payload
-	\item Encrypt input payload
-	\item Transmit final message to tangle-accelerator
-\end{itemize}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
-
-It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
-Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
-The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
-
 \section{Conclusions}
 By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.
+It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
+
+In the subscription-based data trading, there are some issues that worth to discuss and improve.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot Gas due to the frequent store operation.
+Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
+Second, brokers are irreplaceable either from the view of architecture design or trading procedures, they are the key to the stable system.
+However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
+
+Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
 

### 2020-07-08 paper.tex
Fix grammar and keywords

--- 2020-07-08 paper.tex
@@
 \begin{IEEEkeywords}
-subscription-based IoT data trading, decentralization, Distributed Ledger Technology
+publish/subscribe, data trading, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
-The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum info like its identifier and public key.
-Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables an proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
+The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
+Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
 With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
@@
 The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest as well as the signature to brokers.
+To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
 Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process is aborted.
-Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The key upload time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrate the key upload to Product Contract via a broker.
+If it's valid, then the broker uploads the key, otherwise the process will be aborted.
+Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
 

### 2020-07-08 paper.tex
Update ether chart and add USD estimation

@@
 	\centering
-	\resizebox{0.7\textwidth}{!}{
+	\resizebox{0.5\textwidth}{!}{
 	\begin{tabular}{|c|c|c|c|}
@@
 		subscribe product & consumer & 72259 \\ 
-		upload hash key & provider & 68276  \\ 
+		upload hashed key & provider & 68276  \\ 
 		upload encryption key to consumer & provider & 86614 \\ 
@@
 
-When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
+When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
 Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
@@
 	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|}
 		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
+		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
 		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.003 & 0.011 \\
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
 		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
-		 & consumer & 0.004 & 0.016 \\
+		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
 		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.004 & 0.016 \\
+		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
+		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
 		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
-		 & consumer & 0.005 & 0.020 \\
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
+		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
 		\hline

### 2020-07-08 paper.tex
Fix
Fix grammar

--- 2020-07-08 paper.tex
@@
 
-In the subscription-based data trading, there are some issues that worth to discuss and improve.
-Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot Gas due to the frequent store operation.
+In the subscription-based data trading, there are some issues that worth discussing and improving.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
 Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are irreplaceable either from the view of architecture design or trading procedures, they are the key to the stable system.
+Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
 However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

### 2020-07-08 paper.tex

@@
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and written on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
 This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product}.
-Finally, data providers can start uploading data.
+The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
+Finally, the data product is launched and data providers can start uploading data.
 
@@
 
+\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
+    function addHashedKey(
+        string memory _hashedKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add hashed key."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        hashedKey = hashedKey;
+        emit newHashedKey(hashedKey);
+    }
+
+    function addCertifiedKey(
+        string memory _certifiedKey
+    ) public {
+        require(
+            msg.sender == broker,
+            "Only broker can add certifiedKey."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        certifiedKey = _certifiedKey;
+        state = State.KeyCertified;
+        emit newCertifiedKey(certifiedKey);
+    }
+\end{lstlisting}
+
 \subsection{Trading}
@@
 
+\subsection{Smart Contract}
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
+The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+The Gas usage estimation is shown in Table.~\ref{tab:gas}.
+
+\begin{table*}[h]
+	\caption{Gas consumption for each function of Product Contract}
+	\label{tab:gas}
+	\centering
+	\resizebox{0.7\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
+		\hline
+		generate contract & Broker & 2251002 \\
+		subscribe product & Consumer & 44486 \\
+		upload signed key to consumer & Provider & 147369 \\
+		upload certified key & Broker & 167678 \\
+		upload hased encryption key & Provider & 166784 \\
+		update the amount of uploaded data & Broker & 32825 \\
+		request refund & Consumer & 22545 \\
+		unsubscribe & Consumer & 22641 \\
+		withdraw & Broker/Provider/Consumer & 14719 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Storage on blockchain is expensive.
+For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
+However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+However, using zero-knowledge protocol is out of the scope of this paper.
+
+Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
+We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+
+\begin{equation}
+\label{equa:ether_calculation}
+Ethers = Gas \ Price \times Gas \ Amount
+\end{equation}
+
+When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
+Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
+Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
+
+\begin{table*}[h]
+	\caption{Data Price Estimation}
+	\label{tab:ether}
+	\centering
+	\resizebox{0.8\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.003 & 0.011 \\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.005 & 0.020 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
 \section{Conclusions}

### 2020-07-08 paper.tex

--- 2020-07-08 paper.tex
@@
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE:
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
 
@@
 By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.
+It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
+
+In the subscription-based data trading, there are some issues that worth discussing and improving.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
+Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
+Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
+However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
+
+Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
 

### 2020-07-08 paper.tex
Update Product Contract constructor

@@
         bool isKeyAdded;
+        bool isSubscribe;
         string encryptKey;
@@
     uint public brokerage;
+    uint public cancellation;
     uint public threshold;

### 2020-07-08 paper.tex
Update description of Unsubscribe

@@
 
-\subsection{Trading}
+\subsection{Subscribe to Data Product}
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
@@
 Data consumers can unsubscribe to data products when they're not interested anymore.
-Product Contract hold an unsubscriber list to record the unsubscribers.
+Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structre, since the delete function in Solidity does not remove the actual element but reseting it to default value.
 When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
 The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
 
@@
 See Fig.~\ref{fig:refund}.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following:
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
 

### 2020-07-08 paper.tex
Add the remote PoW figure and description of RPi3

@@
 	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
-	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network.
-A computationally hard puzzle to solve, but easy to verify.
-IOTA uses a Hashcash\cite{Hashcash} based puzzle.
+	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
 \end{itemize}
@@
 Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
-The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a possible range.
+The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
 
@@
     \includegraphics[width=2.5in]{mam_send}
-    \caption{Time cost of sending a message through MAM.}
+    \caption{The probability distributed function of time cost for sending a message through MAM.}
     \label{fig:mam_send}
@@
 Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator\cite{TA}.
-Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration.
+Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator.
 However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{rpi3_pow}
+    \caption{Local PoW vs. Remote PoW}
+    \label{fig:rpi3_pow}
+\end{figure}
 

### 2020-07-08 paper.tex
Resize evaluation figures

--- 2020-07-08 paper.tex
@@
 %cite IoT data subscription economy
-The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
+The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchange among devices are periodical that only data in a specific time period is interested.
+The real-time data exchange among devices are periodically that only data in a specific time period is interested.
 Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
@@
 However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
-Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
+Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system.
 Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
@@
 \begin{IEEEkeywords}
-publish/subscribe, data trading, decentralization, Distributed Ledger Technology
+Data Marketplace, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
-The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
-With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
+The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum info like its identifier and public key.
+Third, as brokers running on machines in a stable network and electricity environment, besides matching procedures, participants on resource-constrained devices can offload the computation tasks to brokers.
+In our proposed protocol, devices can delegate the uploading and trading processes to brokers after signing the data, and brokers can perform verifiable checks without knowing the contents.
 
@@
         bool isKeyAdded;
-        bool isSubscribe;
         string encryptKey;
@@
     uint public brokerage;
-    uint public cancellation;
     uint public threshold;
@@
 The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
+To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest as well as the signature to brokers.
 Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+If it's valid, then the broker uploads the key, otherwise the process is aborted.
+Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The key upload times is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrate the key upload to Product Contract via a broker.
 
@@
 
-\subsubsection{Communication Protocol}
+\subsubsection{Infrastructure}
 In the following sections, we refer the low-level devices as \textbf{endpoint}s.
@@
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:
+In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the whole E2EE process we present. The following section addresses the process.
 
@@
 
-\subsubsection{Register with Tangle-accelerator}
+The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
+Each of them can be chosen according to the working hardware and scenario.
+On some hardwares, the developers can choose the cryptographic methods with hardware acceleration.
+With hardware acceleration, the elapsed time could be dropped a step more.
+
+\subsubsection{Register Machine}
 User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
-Asymmetric encryption is utilizing during the process of exchanging seed.
+Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows tangle-accelerator to publish messages on MAM channel chain.
+Asymmetric encryption is utilizing during the process of exchanging Seed.
 Digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed will not be exposed during communication after an edge device is successfully registered.
+Once seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
+Thus, seed isn't needed to be exposed during communication after an edge device is successfully registered.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met a few challenges in the E2EE we proposed.
 
@@
 	\centering
-	\resizebox{0.5\textwidth}{!}{
+	\resizebox{0.7\textwidth}{!}{
 	\begin{tabular}{|c|c|c|c|}
@@
 		\hline
-		generate contract & broker & 2558980 \\ 
-		subscribe product & consumer & 72259 \\ 
-		upload hashed key & provider & 68276  \\ 
-		upload encryption key to consumer & provider & 86614 \\ 
-		upload certified key & broker & 131535 \\
-		update amount of uploaded data & broker & 32157 \\
-		unsubscribe & consumer & 8234 \\
-		request refund & consumer & 12067 \\
-		withdraw & broker & 11313 \\
+		generate contract & Broker & 2251002 \\
+		subscribe product & Consumer & 44486 \\
+		upload signed key to consumer & Provider & 147369 \\
+		upload certified key & Broker & 167678 \\
+		upload hased encryption key & Provider & 166784 \\
+		update the amount of uploaded data & Broker & 32825 \\
+		request refund & Consumer & 22545 \\
+		unsubscribe & Consumer & 22641 \\
+		withdraw & Broker/Provider/Consumer & 14719 \\
 		\hline
@@
 
-When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
+When a consumer request a refund, he/she need to pay 0.001 Ether additionally.
 Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
@@
 	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
-		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
-		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.003 & 0.011 \\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.004 & 0.016 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
+		 & consumer & 0.005 & 0.020 \\
 		\hline

### 2020-07-08 paper.tex

--- 2020-07-08 paper.tex
@@
 
+The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
+Each of them can be chosen according to the working hardware and scenario.
+On some hardwares, the developers can choose the cryptographic methods with hardware acceleration.
+With hardware acceleration, the elapsed time could be dropped a step more.
+
 \subsubsection{Register with Tangle-accelerator}
@@
     \centering
-    \includegraphics[width=2.5in]{mam_create}
+    \includegraphics[width=3.in]{mam_create}
     \caption{Time cost of MAM creation.}
@@
     \centering
-    \includegraphics[width=2.5in]{mam_send}
+    \includegraphics[width=3.in]{mam_send}
     \caption{The probability distributed function of time cost for sending a message through MAM.}
@@
 \end{table*}
+\subsection{MAM vs. the delegated MAM}
+What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
+In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
+The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+
+The steps counted in MAM benchmark including:
+\begin{itemize}
+	\item Encrypt input payload
+	\item Publish final message on IOTA Tangle
+\end{itemize}
+
+The steps counted in E2EE benchmark including:
+\begin{itemize}
+	\item Generate symmetric key for encryption
+	\item Hash input payload
+	\item Encrypt input payload
+	\item Transmit final message to tangle-accelerator
+\end{itemize}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{mam_vs_e2ee}
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
+    \label{fig:mam_vs_e2ee}
+\end{figure}
+
+It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
+Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
+The bump of MAM performance around 750 bytes proves this point.
+Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
 

### 2020-07-08 paper.tex
Fix typos and missing labels

@@
 \begin{itemize}
-	\item We investigate the usage of DLTs and distribute data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
+	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
 	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
@@
 The rest of this paper is organized as follows.
-In Section~\ref{section:relatedWork}, some related work of data exchange mechanisms for IoT, decentralized data trading infrastructures and distributed data storage are analyzed.
+In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
 In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
@@
 
+\subsection{MAM vs. the delegated MAM}
+\label{section:smart_contract_evaluation}
+What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
+In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
+The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+
+The steps counted in MAM benchmark including:
+\begin{itemize}
+	\item Encrypt input payload
+	\item Publish final message on IOTA Tangle
+\end{itemize}
+
+The steps counted in E2EE benchmark including:
+\begin{itemize}
+	\item Generate symmetric key for encryption
+	\item Hash input payload
+	\item Encrypt input payload
+	\item Transmit final message to tangle-accelerator
+\end{itemize}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{mam_vs_e2ee}
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
+    \label{fig:mam_vs_e2ee}
+\end{figure}
+
+It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
+Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
+The bump of MAM performance around 750 bytes proves this point.
+Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
+
 \subsection{Smart Contract}
@@
 \end{table*}
-\subsection{MAM vs. the delegated MAM}
-What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
-Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-
-The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
-	\item Publish final message on IOTA Tangle
-\end{itemize}
-
-The steps counted in E2EE benchmark including:
-\begin{itemize}
-	\item Generate symmetric key for encryption
-	\item Hash input payload
-	\item Encrypt input payload
-	\item Transmit final message to tangle-accelerator
-\end{itemize}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
-
-It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
-Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
-The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
 
@@
 In the subscription-based data trading, there are some issues that worth discussing and improving.
-Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
 Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.

### 2020-07-08 ASRLab_Thesis_Template/thesis/thesis.tex
Start porting to NCKU template

--- 2020-07-08 paper.tex
@@
-\documentclass[conference]{IEEEtran}
-
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{float}
-\usepackage{tabularx}
-\usepackage{makecell}
-\usepackage{multirow}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic,algorithm}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{listings}
-\graphicspath{{./images/}}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+% ------------------------------------------------
+% 常見論文內容次序:
+% 1.口試合格證明(初稿不需要)
+% 2.中英文摘要(論文以中文撰寫者須附英文延伸摘要)
+% 3.誌謝(初稿不需要)
+% 4.目錄
+% 5.表目錄
+% 6.圖目錄
+% 7.符號
+% 8.主文
+% 9.參考文獻
+% 10.附錄
+%
+% 註: 參考文獻書寫注意事項:
+% (1).
+%    文學院之中文文獻依分類及年代順序排列。
+%    其他學院所之文獻依英文姓氏第一個字母
+%    (或中文姓氏第一個字筆劃)及年代順序排列。
+% (2).
+%    期刊文獻之書寫依序為:
+%        姓名、文章名稱、期刊名、卷別、期別、頁別、年代。
+% (3).
+%    書寫之文獻依序為:
+%        姓名、書名、出版商名、出版地、頁別、年代。
+% ------------------------------------------------
+
+% ------------------------------------------------
+%          載入基本設定 Basic configuration
+% ------------------------------------------------
+% Don't need to modify this section.
+\input{configure/configure}
+
+% ------------------------------------------------
+%                   DOI Watermark
+% ------------------------------------------------
+\usepackage{draftwatermark}  % For DOI watermark
+\usepackage{listings, makecell, multirow}
+
+\newcommand{\ShowDOI}[1]{
+	\SetWatermarkText{\textbf{#1}}
+	\SetWatermarkColor{black}
+	\SetWatermarkFontSize{0.5 cm}
+	\SetWatermarkScale{0.58}
+	\SetWatermarkAngle{0}
+	\SetWatermarkLightness{0}
+	\SetWatermarkHorCenter{18 cm}
+	\SetWatermarkVerCenter{28.4 cm}
+}
+
 \begin{document}
-
-\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
-% Chinese title: 針對物聯網資料交易的去中心化基礎建設
-
-\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jkrvivian@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jserv@ccns.ncku.edu.tw}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-chiaheng@gmail.com}
+\ShowDOI{doi:XXXX/NCKU2019XXXXX}
+
+% ------------------------------------------------
+%                封面內頁 Inner Cover
+% ------------------------------------------------
+\singlespacing 
+\newpage
+\phantomsection
+\thispagestyle{empty}
+\newgeometry{top=2.3cm,bottom=3cm,left=2cm,right=2cm,nohead,nofoot}
+
+\begin{center}
+
+\begin{minipage}[c][5cm][t]{\textwidth}
+  \begin{center}
+    \makebox[10cm][s]{\Huge 國立成功大學}\vspace{1cm}		\\
+    \makebox[8cm][s]{\Huge 資訊工程研究所}\vspace{1cm}		\\
+    \makebox[5cm][s]{\Huge 碩士論文}\vspace{1cm}			\\
+    \makebox[5cm][c]{\Huge (初稿)}
+  \end{center}
+\end{minipage}
+
+\vspace{5.5cm}
+
+\begin{minipage}[c][5cm][t]{\textwidth}
+  \begin{center}
+    \makebox[\textwidth][c]{\parbox{\paperwidth}
+    {\center \Large 針對物聯網資料交易的 \\ 去中心化基礎建設}}
+    \vspace{0.5cm}\\
+    \makebox[\textwidth][c]{\parbox{\paperwidth}
+    {\center \Large A Fully Decentralized Infrastructure for \\ Subscription-based IoT Data Trading}}
+  \end{center}
+\end{minipage}
+
+\vspace{1.0cm}
+
+\begin{minipage}[c][4.5cm][t]{\textwidth}
+  \begin{center}
+    {
+      % -------------Student-------------
+      \hspace{2.0em}
+      \makebox[4.0em][r]{\Large 學生：}
+      \makebox[6.0em][l]{\Large 林京樺}
+      \makebox[8.0em][c]{}
+      \makebox[4.0em][r]{\Large Student：}
+      \makebox[8.0em][l]{\Large Ching-Hua Lin}
+      \vspace{0.5cm}\\
+      % -------------Advisor-------------
+      \hspace{2.0em}
+      \makebox[4.0em][r]{\Large 指導老師：}
+      \makebox[6.0em][l]{\Large 涂嘉恒 博士}
+      \makebox[8.0em][c]{}
+      \makebox[4.0em][r]{\Large Advisor：}
+      \makebox[8.0em][l]{\Large Dr. Chia-Heng Tu}
+      \vspace{0.1cm}\\
+      % -------------Co-Advisor-1-------------
+      \hspace{2.0em}
+      \makebox[4.0em][r]{\Large 共同指導：}
+      \makebox[6.0em][l]{\Large 黃敬群}
+      \makebox[8.0em][c]{}
+      \makebox[4.0em][r]{\Large Co-Advisor：}
+      \makebox[8.0em][l]{\Large Ching-Chun Huang}
+      \vspace{0.1cm}\\
     }
-
-\maketitle
-
-\begin{abstract} 
-%cite IoT data subscription economy
+  \end{center}
+\end{minipage}
+
+\vspace{0.5cm}
+
+\makebox[8cm][s]{\Large 中華民國109年7月}
+
+\end{center}
+\restoregeometry
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%  學位考試論文證明書 Defense Certificate (初稿不需要)
+% ------------------------------------------------
+%\newpage
+%\phantomsection
+%\thispagestyle{empty}
+%\includepdf[pages=-]{context/oral/oral_example.pdf}
+%\clearpage
+
+% ------------------------------------------------
+%                  摘要 Abstract
+% ------------------------------------------------
+% 除了外籍生, 本地生和僑生都要同時編寫中文和英文摘要
+% 論文以中文撰寫須以英文補寫 800 至 1200 字數的英文延伸摘要 (Extended Abstract)
+% 詳細可看附件的學校要求或看example中的英文延伸摘要
+
+% -------------中文摘要-------------
+\setcounter{page}{1}
+\pagenumbering{roman}
+\newpage
+\phantomsection
+\chapter*{摘要}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
+除了外籍生, 本地生和僑生都是要編寫中文和英文摘要. 論文以中文撰寫須以英文補寫 800 至 1200 字數的英文延伸摘要 (Extended Abstract), 如需要的話請修改`./context/abstract/extended.tex'.
+
+外籍生則可免填中文摘要, 而在上傳時網頁資訊需填上`NONE'.
+
+\end{spacing}
+
+\par{\noindent \bf 關鍵字:}{關鍵字1, 關鍵字2, 關鍵字3, 關鍵字4}
+\clearpage
+\setstretch{1.2}
+
+% -------------English Abstract-------------
+\newpage
+\phantomsection
+\chapter*{Abstract}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
 The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
@@
 The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
-\end{abstract}
-
-\begin{IEEEkeywords}
-publish/subscribe, data trading, decentralization, Distributed Ledger Technology
-\end{IEEEkeywords}
-
-\section{Introduction}
+
+\end{spacing}
+
+\par{\noindent \bf Keyword:}{ publish/subscribe, data trading, decentralization, Distributed Ledger Technology }
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%           誌謝 Acknowledgments(初稿不需要)
+% ------------------------------------------------
+%\newpage
+%\phantomsection
+%\chapter*{誌謝}
+%\pagestyle{plain}
+
+%\begin{spacing}{2.0}
+
+%在這邊寫你的感謝 (對父母, 老師, 同學, 朋友等的感謝).
+
+%\end{spacing}
+
+%\clearpage
+%\setstretch{1.2}
+
+% ------------------------------------------------
+%              目錄 Index of contents
+% ------------------------------------------------
+% 目錄有三種，分為內容、表格及圖片索引
+
+% -------------內容索引-------------
+\renewcommand*\contentsname{Table of Contents}
+\singlespacing
+\newpage
+\phantomsection
+\pagestyle{plain}
+\tableofcontents
+\clearpage
+\setstretch{1.2}
+
+% -------------表格索引-------------
+\listoftables
+% -------------圖片索引-------------
+\listoffigures
+
+% ------------------------------------------------
+%                   Introduction
+% ------------------------------------------------
+\setcounter{page}{1}
+\pagenumbering{arabic}
+\newpage
+\phantomsection
+\chapter{Introduction}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
 In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly.
@@
     \centering
-    \includegraphics[width=3.in]{system_design}
+    \includegraphics[width=3.in]{img/system_design}
     \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
@@
 
-%TODO: cite IOTAIndustryMarketplace
-\section{Related Work}
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%                  Related Work
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{Related Work}
 \label{section:relatedWork}
-% pub/sub
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
 \subsection{The Publish/subscribe Communication Models Over Blockchain}
@@
 
-\section{System Design Thinking}
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%               System Design Thinking
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{System Design Thinking}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
 \label{section:design_thinking}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{pub_sub_model}
+\begin{figure}
+    \centering
+    \includegraphics[width=15cm]{img/pub_sub_model}
     \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
@@
 With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
-
-\begin{figure*}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
-Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
-    \label{fig:channel_and_key}
-\end{figure*}
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=15cm]{img/channel_and_key}
+    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
+Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
+    \label{fig:channel_and_key}
+\end{figure}
+\clearpage
+
 Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
@@
 	\label{tab:did}
-	\begin{tabularx}{\linewidth}{|l|X|X|}
+	\begin{tabular}{|c|c|c|}
 	\hline
@@
 		\hline
-	\end{tabularx}
+	\end{tabular}
 \end{table}
@@
     \centering
-    \includegraphics[width=3.in]{DID_VC}
+    \includegraphics[width=3.in]{img/DID_VC}
     \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
@@
     \centering
-    \includegraphics[width=3.5in]{TangleID}
+    \includegraphics[width=3.5in]{img/TangleID}
     \caption{To participate the data trading, players are required to have DID document issued by TangleID.
@@
     \centering
-    \includegraphics[width=4in]{smart_contract_mam}
+    \includegraphics[width=4in]{img/smart_contract_mam}
     \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
@@
     \centering
-    \includegraphics[width=3.5in]{key_upload}
+    \includegraphics[width=3.5in]{img/key_upload}
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
@@
 
-\section{Masked Authenticated Messaging}
+\end{spacing}
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%                 Masked Authenticated Messaging
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{Masked Authenticated Messaging}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
 \label{section:MAM}
@@
     \centering
-    \includegraphics[width=3.5in]{mam_structure}
+    \includegraphics[width=3.5in]{img/mam_structure}
     \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints.
@@
     \centering
-    \includegraphics[width=3.5in]{ta_structure}
+    \includegraphics[width=3.5in]{img/ta_structure}
     \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
@@
     \centering
-    \includegraphics[width=\linewidth]{delegation}
+    \includegraphics[width=\linewidth]{img/delegation}
     \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
@@
     \centering
-    \includegraphics[width=\linewidth]{MAM_E2EE}
+    \includegraphics[width=\linewidth]{img/MAM_E2EE}
     \caption{The process of E2EE.}
@@
 
-\section{Decentralized Subscription-based Data Trading Case Study}
+\end{spacing}
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%  Decentralized Subscription-based Data Trading Case Study
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{Decentralized Subscription-based Data Trading Case Study}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
 \label{section:trading_model}
@@
     \centering
-    \includegraphics[width=2.5in]{launching_product}
+    \includegraphics[width=2.5in]{img/launching_product}
     \caption{The process of launching a product.}
@@
     \centering
-    \includegraphics[width=3.5in]{key_exchange}
+    \includegraphics[width=3.5in]{img/key_exchange}
     \caption{Encryption key exchange process.}
@@
     \centering
-    \includegraphics[width=3.5in]{unsubscribe}
+    \includegraphics[width=3.5in]{img/unsubscribe}
     \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
@@
     \centering
-    \includegraphics[width=1.5in]{refund}
+    \includegraphics[width=1.5in]{img/refund}
     \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
@@
 
-\section{Evaluations}
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%                   Evaluation
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{Conclusion}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
 \label{section:evaluation}
@@
     \centering
-    \includegraphics[width=3.in]{mam_create}
+    \includegraphics[width=3.in]{img/mam_create}
     \caption{Time cost of MAM creation.}
@@
     \centering
-    \includegraphics[width=3.in]{mam_send}
+    \includegraphics[width=3.in]{img/mam_send}
     \caption{The probability distributed function of time cost for sending a message through MAM.}
@@
     \centering
-    \includegraphics[width=3.5in]{rpi3_pow}
+    \includegraphics[width=3.5in]{img/rpi3_pow}
     \caption{Local PoW vs. Remote PoW}
@@
     \centering
-    \includegraphics[width=3in]{mam_vs_e2ee}
+    \includegraphics[width=3in]{img/mam_vs_e2ee}
     \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
@@
 
-\section{Conclusions}
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%                   Conclusion
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{Conclusion}
 \label{section:conclusion}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
 By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
@@
 Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
+Second, brokers are the key to operate a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
 However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
@@
 Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%               參考文獻 References
+% ------------------------------------------------
+% References and bibliography
+
+% Import the files that contain your references.
+% If you set some references file,
+% you need to use at least one cite to make Latex work.
+\singlespacing
+\newpage
+\phantomsection
+\renewcommand\bibname{References}	% references title
+
+% 學校規定以作者英文姓氏第一字排列順序，故使用 plain ，如果要按照引用順序，可改用 ieeetr
+\bibliographystyle{plain}			% reference style
+\bibliography{thesis}				% target .bib file
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%                   附錄 Appendix
+% ------------------------------------------------
+\BeginAppendixChapter				% User-defined function
+\SetupAppendixNumberingFormat		% User-defined function
+\newpage
+\phantomsection
+\chapter{Title of Appendix A}
+
+\begin{spacing}{2.0}
+
+Write your Appendix here.
+
+  \section{Dolor sit amet}
+    Appendix
+
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
 

### 2020-07-08 paper.tex
Hardware acceleration with referrence

--- 2020-07-08 paper.tex
@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{AES-NI}
+    \caption{AES256 Encryption/Decryption Performance Numbers}
+    \label{fig:AES-NI}
+\end{figure}
+
 The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
-Each of them can be chosen according to the working hardware and scenario.
-On some hardwares, the developers can choose the cryptographic methods with hardware acceleration.
+Each of them can be chosen on the basis of the working hardware and scenario by developers.
+On some certain devices, hardware acceleration would be supported.
 With hardware acceleration, the elapsed time could be dropped a step more.
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Fig.~\ref{fig:AES-NI} shows the performance of Encryption/Decryption of AES256 with and without hardware acceleration.
 

### 2020-07-09 ASRLab_Thesis_Template/thesis/thesis.tex
Adjust typesetting

@@
 % ------------------------------------------------
-\usepackage{draftwatermark}  % For DOI watermark
+%\usepackage{draftwatermark}  % For DOI watermark
 \usepackage{listings, makecell, multirow}
@@
 \begin{document}
-\ShowDOI{doi:XXXX/NCKU2019XXXXX}
+%\ShowDOI{doi:XXXX/NCKU2019XXXXX}
 
@@
     \centering
-    \includegraphics[width=3.in]{img/system_design}
+    \includegraphics[width=5.in]{img/system_design}
     \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=15cm]{img/pub_sub_model}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=4.5in]{img/pub_sub_model}
     \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
@@
 
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
+Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+
 \begin{figure}
     \centering
-    \includegraphics[width=15cm]{img/channel_and_key}
+    \includegraphics[width=6.5in]{img/channel_and_key}
     \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
@@
 \clearpage
-
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
-Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
 
@@
 		\hline
-		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
-		\hline
-		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
+		Security & \makecell{Identity held in a centralized service \\ is a  honeypot for cyber attacks} & \makecell{Decentralized identity \\ limits data exposure} \\
+		\hline
+		Portability & \makecell{Identity is fragmented \\ across enterprises} & \makecell{Identity can be portable \\ across enterprises} \\
 		\hline
@@
     \centering
-    \includegraphics[width=3.in]{img/DID_VC}
+    \includegraphics[width=4.5in]{img/DID_VC}
     \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
@@
     \centering
-    \includegraphics[width=3.5in]{img/TangleID}
+    \includegraphics[width=5.5in]{img/TangleID}
     \caption{To participate the data trading, players are required to have DID document issued by TangleID.
@@
 \end{figure}
+\clearpage
 
 \subsection{Enable Automated Trading Process}
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=4in]{img/smart_contract_mam}
-    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.
-For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color.
-The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
-    \label{fig:smart_contract_mam}
-\end{figure*}
-
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=5.5in]{img/smart_contract_mam}
+    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
+Participants can easily retrieve information via Product Contract and proceed trading.
+For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color.
+The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
+    \label{fig:smart_contract_mam}
+\end{figure}
+\clearpage
+
 The transparency of smart contracts bring advantages for data providers and consumers.
@@
 \lstdefinestyle{solidity}{
+	numbers=left,
+    numbersep=1em,
 	captionpos=b,
 	tabsize=4,
-	basicstyle=\scriptsize
+	basicstyle=\linespread{0.9}\small
 }
@@
 \end{lstlisting}
+\clearpage
 
@@
     \centering
-    \includegraphics[width=3.5in]{img/key_upload}
+    \includegraphics[width=5.5in]{img/key_upload}
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
@@
     \centering
-    \includegraphics[width=3.5in]{img/mam_structure}
+    \includegraphics[width=5.5in]{img/mam_structure}
     \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints.
@@
 \end{figure}
+\clearpage
 
@@
 Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{img/ta_structure}
+\clearpage
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=5.5in]{img/ta_structure}
     \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
@@
 
-\begin{figure}[!t]
+\begin{figure}[b]
     \centering
@@
 %pic
-\begin{figure*}[!t]
+\begin{figure}[h]
     \centering
@@
     \label{fig:MAM_E2EE}
-\end{figure*}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=5in]{img/launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
+\end{figure}
+\clearpage
+
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{img/launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
-
+\lstset{style=solidity}
 \begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{img/key_exchange}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5.5in]{img/key_exchange}
     \caption{Encryption key exchange process.}
@@
 \end{figure}
-
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
+\clearpage
+
 \lstset{style=solidity}
-
 \begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
@@
     \centering
-    \includegraphics[width=3.5in]{img/unsubscribe}
+    \includegraphics[width=5.5in]{img/unsubscribe}
     \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
@@
     \centering
-    \includegraphics[width=1.5in]{img/refund}
+    \includegraphics[width=2.5in]{img/refund}
     \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
@@
 \phantomsection
-\chapter{Conclusion}
+\chapter{Evaluation}
 \pagestyle{plain}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{img/mam_create}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=5.in]{img/mam_create}
     \caption{Time cost of MAM creation.}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{img/mam_send}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5.in]{img/mam_send}
     \caption{The probability distributed function of time cost for sending a message through MAM.}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{img/rpi3_pow}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5in]{img/rpi3_pow}
     \caption{Local PoW vs. Remote PoW}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{img/mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
-
 It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
@@
 Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=4.5in]{img/mam_vs_e2ee}
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
+    \label{fig:mam_vs_e2ee}
+\end{figure}
+\clearpage
 
@@
 
-\begin{table*}[h]
+\begin{table}[h]
 	\caption{Gas consumption for each function of Product Contract}
@@
 	}
-\end{table*}
+\end{table}
 
@@
 
-\begin{table*}[h]
+\begin{table}[h]
 	\caption{Data Price Estimation}
@@
 	\centering
-	\resizebox{0.8\textwidth}{!}{
+	\resizebox{0.98\linewidth}{!}{
 	\begin{tabular}{|c|c|c|c|c|c|}
@@
 
-% ------------------------------------------------
-%                   附錄 Appendix
-% ------------------------------------------------
-\BeginAppendixChapter				% User-defined function
-\SetupAppendixNumberingFormat		% User-defined function
-\newpage
-\phantomsection
-\chapter{Title of Appendix A}
-
-\begin{spacing}{2.0}
-
-Write your Appendix here.
-
-  \section{Dolor sit amet}
-    Appendix
-
-\end{spacing}
-
-\clearpage
-\setstretch{1.2}
-
 \end{document}

### 2020-07-09 ASRLab_Thesis_Template/thesis/thesis.tex
Update professor title
Add Chinese Abstract

@@
       \makebox[4.0em][r]{\Large 指導老師：}
-      \makebox[6.0em][l]{\Large 涂嘉恒 博士}
+      \makebox[6.0em][l]{\Large 涂嘉恒 教授}
       \makebox[8.0em][c]{}
       \makebox[4.0em][r]{\Large Advisor：}
-      \makebox[8.0em][l]{\Large Dr. Chia-Heng Tu}
+      \makebox[8.0em][l]{\Large Prof. Chia-Heng Tu}
       \vspace{0.1cm}\\
@@
       \makebox[4.0em][r]{\Large 共同指導：}
-      \makebox[6.0em][l]{\Large 黃敬群}
+      \makebox[6.0em][l]{\Large 黃敬群 教授}
       \makebox[8.0em][c]{}
       \makebox[4.0em][r]{\Large Co-Advisor：}
-      \makebox[8.0em][l]{\Large Ching-Chun Huang}
+      \makebox[8.0em][l]{\Large Prof. Ching-Chun Huang}
       \vspace{0.1cm}\\
@@
 
-除了外籍生, 本地生和僑生都是要編寫中文和英文摘要. 論文以中文撰寫須以英文補寫 800 至 1200 字數的英文延伸摘要 (Extended Abstract), 如需要的話請修改`./context/abstract/extended.tex'.
-
-外籍生則可免填中文摘要, 而在上傳時網頁資訊需填上`NONE'.
+物聯網 (Internet-of-Things) 連結起不同裝置並自動化許多繁瑣流程，使我們的生活變得更加便捷。而在物聯網場景中，machine-to-machine（M2M）的發展勢不可檔，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。裝置間的資料交換是即時且短暫的，往往特定時段內的資料對當下的應用才有意義，而有效靈活的資料流發布/訂閱 (publish/subscribe) 通訊機制便十分符合這種場景。此外，在此模型之上引入訂閱服務的定價模型（如軟體即服務 (Software-as-a-Service)) 可以使訂閱資料產生價值，讓訂閱者得以根據資料使用量計價。另外，這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。但與靜態資料集不同的是，動態的資料流提升了資料所有權和身份驗證的重要性和難度，僅採用憑證頒發機構（Certificate Authority）的中心化服務進行身份驗證有淺在的資安風險，會進而威脅到整個系統的信任基礎。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了讓參與者可以在不信任任何服務或他人的情況下進行交易，還能驗證資料所有權和完整性。此外，考慮到物聯網設備難以同時進行指定工作和交易流程，訂閱流程的自動化是必要的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在發布/訂閱的基礎架構之上構建去中心化且受信任的資料交易平台，除了能有效地提高運作透明度和系統可擴展性，更利用點對點的加密通訊機制允許在分散式帳本儲存、傳輸、存取和驗證資料流，亦透過智能合約 (smart contract) 實現交易自動化。
 
@@
 
-\par{\noindent \bf 關鍵字:}{關鍵字1, 關鍵字2, 關鍵字3, 關鍵字4}
+\par{\noindent \bf 關鍵字:}{發布/訂閱, 資料交易, 去中心化, 分散式帳本技術}
 \clearpage

### 2020-07-09 paper.tex
Remove MAM description
remove MQTT

Linear time to read

Register with tangle-accelerator

@@
 
-\subsubsection{Communication Protocol}
-In the following sections, we refer the low-level devices as \textbf{endpoint}s.
-MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic.
-The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth.
-The pub/sub model decouples publishers and subscribers in many ways:
-
-\begin{itemize}
-    \item Space decoupling: Both publishers and subscribers don't need to know each other.
-    \item Time decoupling: Publishers and subscribers do not need to be active at the same time.
-    \item Synchronization decoupling: Operations are decoupled from the publishers and subscribers.
-The publishers do not need to be alive until the response arrives.
-Messages from publisher can be served as send-and-forget fashion.
-\end{itemize}
-
 \subsubsection{End-to-End-Encryption}
@@
 
-\subsubsection{Register with Tangle-accelerator}
-User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
-Asymmetric encryption is utilizing during the process of exchanging seed.
-Digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed will not be exposed during communication after an edge device is successfully registered.
-
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
-
-\paragraph{Linear Time to Read Message}
-It is linear time to decrypt message instead of constant time.
-Nevertheless, there is one way to speed up the message decryption process.
-A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
-This procedure can reduce the time spending on internet communication.
-
-\paragraph{Spam on Message Channel Chain}
+E2EE helps a lot for low-level edge device utilizing blockchain service.
+It dramatically reduces execution time encryption takes.
+However, there are some challenges in the E2EE process.
 Tampering the messages which have conducted E2EE would be a challenging mission.

### 2020-07-09 paper.tex

--- 2020-07-08 paper.tex
@@
 \label{section:smart_contract_evaluation}
-What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Applying remote PoW greatly reduce the elapsed time.
+Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is an account of performance comparison between MAM and delegated MAM for different payload sizes.
 Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.

### 2020-07-09 paper.tex

@@
 \label{section:smart_contract_evaluation}
+
+\subsubsection{Experiment}
 Applying remote PoW greatly reduce the elapsed time.
@@
 With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is an account of performance comparison between MAM and delegated MAM for different payload sizes.
+What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
 Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
@@
 The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+In the E2EE protocol framework, we choose sha256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 
@@
 The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
+
+\subsubsection{Time Complexity}
+With given E2EE protocol framework.
+ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with sha256 is O(n).\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is O(n), too.
+Therefore, the E2EE protocol framework takes only linear time.
+Applying mature cryptographic functions (e.g.
+sha256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.
 

### 2020-07-10 paper.tex
Return user key after registering Seed
Remove smart contract evaluation

--- 2020-07-09 paper.tex
@@
 
-\subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
-On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
-The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-The Gas usage estimation is shown in Table.~\ref{tab:gas}.
-
-\begin{table*}[h]
-	\caption{Gas consumption for each function of Product Contract}
-	\label{tab:gas}
-	\centering
-	\resizebox{0.5\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
-		\hline
-		generate contract & broker & 2558980 \\ 
-		subscribe product & consumer & 72259 \\ 
-		upload hashed key & provider & 68276  \\ 
-		upload encryption key to consumer & provider & 86614 \\ 
-		upload certified key & broker & 131535 \\
-		update amount of uploaded data & broker & 32157 \\
-		unsubscribe & consumer & 8234 \\
-		request refund & consumer & 12067 \\
-		withdraw & broker & 11313 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
-Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
-Storage on blockchain is expensive.
-For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
-
-Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
-\label{equa:ether_calculation}
-Ethers = Gas \ Price \times Gas \ Amount
-\end{equation}
-
-When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
-Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
-Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
-
-\begin{table*}[h]
-	\caption{Data Price Estimation}
-	\label{tab:ether}
-	\centering
-	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
-		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
-		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
 \section{Conclusions}

### 2020-07-10 paper.tex
Remove paper organization

@@
 \end{itemize}
-
-\subsection{Paper Organization}
-The rest of this paper is organized as follows.
-In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
-In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
-In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
-The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion}.
 

### 2020-07-10 paper.tex
Remove distributed storage

@@
 With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
-
-\subsection{Distributed Storage System}
-Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-However, no cryptographic system is applied for user-uploaded files.
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
-Files are duplicated in multiple nodes to prevent data loss.
 

### 2020-07-10 paper.tex
Remove figures and tables

@@
 But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-As shown in Fig.~\ref{fig:pub_sub_model}.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{pub_sub_model}
-    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
-    \label{fig:pub_sub_model}
-\end{figure}
 
@@
 During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
-See Fig.~\ref{fig:TangleID}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{TangleID}
-    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
-The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
-When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
-The data provider can then retrieve the consumer's public key and encrypt the content with it.
-After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
-    \label{fig:TangleID}
-\end{figure}
 
@@
 To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
-Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{ta_structure}
-    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
-It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed.
-Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
-    \label{fig:ta_struct}
-\end{figure}
+Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
 
@@
 The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
-Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
 
@@
 \end{equation}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{unsubscribe}
-    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
-Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
-    \label{fig:unsubscribe}
-\end{figure}
 
@@
 
-\begin{table}[htbp]
-	\caption{Time measurement of channel creation}
-	\label{tab:channel_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.26183 & 2.908702 \\ 
-		2 & 0.524076 & 5.805524 \\ 
-		3 & 1.045942 & 11.555660 \\ 
-		4 & 2.092989 & 23.178036 \\ 
-		5 & 4.19515 & 46.164079\\ 
-		6 & 8.361586 & 92.320173\\ 
-		7 & 16.651607 & 185.292243\\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Time measurement of endpoint creation}
-	\label{tab:endpoint_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.256425 & 2.887064 \\ 
-		2 & 0.505679 & 5.767912 \\ 
-		3 & 0.999524 & 11.550455 \\ 
-		4 & 1.994017 & 23.260508 \\ 
-		5 & 3.965007 & 46.748366 \\ 
-		6 & 7.918925 & 93.182975 \\ 
-		7 & 16.561419 & 186.064562 \\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}.
+Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation.
 Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.

### 2020-07-10 paper.tex
Remove listings

@@
 The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
-Listing.
-\ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
@@
 For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
-The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
-
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
-\lstset{style=solidity}
-\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
-contract Product {
-    address public broker;
-    address public provider;
-    bool isBrokerWithdraw;
-    bool isProviderWithdraw;
-    address[] consumers;
-
-    struct Purchase {
-        bool affirmativeVote;
-        bool isConsumerWithdraw;
-        bool isKeyAdded;
-        bool isSubscribe;
-        string encryptKey;
-    }
-    mapping(address => Purchase) public consumer2Purchase;
-
-    uint public price;
-    uint public totalAmount;
-    uint public brokerage;
-    uint public cancellation;
-    uint public threshold;
-    string public channelRoot;
-    string public endPoint;
-    uint public totalNumber;
-    uint public uploadedNumber;
-    uint public affirmativeVotes;
-    string hashedKey;
-    string certifiedKey;
-
-    enum State {Launched, KeyCertified, Finished, Refunded}
-    State public state;
-}
-\end{lstlisting}
+The consumer list and the states of products are key reputation referenced for data consumers to decide whether to subscribe.
 
@@
 This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
+The workflow is shown in Fig.~\ref{fig:launching_product}.
 Finally, the data product is launched and data providers can start uploading data.
@@
 
-\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
-    function addHashedKey(
-        string memory _hashedKey
-    ) public {
-        require(
-            msg.sender == provider,
-            "Only provider can add hashed key."
-        );
-        require(
-            state == State.Launched,
-            "One key has been certified."
-        );
-        hashedKey = hashedKey;
-        emit newHashedKey(hashedKey);
-    }
-
-    function addCertifiedKey(
-        string memory _certifiedKey
-    ) public {
-        require(
-            msg.sender == broker,
-            "Only broker can add certifiedKey."
-        );
-        require(
-            state == State.Launched,
-            "One key has been certified."
-        );
-        certifiedKey = _certifiedKey;
-        state = State.KeyCertified;
-        emit newCertifiedKey(certifiedKey);
-    }
-\end{lstlisting}
-
 \subsection{Subscribe to Data Product}

### 2020-07-10 paper.tex
Remove sentence that references missing tables

--- 2020-07-10 paper.tex
@@
 
+\subsection{Paper Organization}
+The rest of this paper is organized as follows.
+In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
+In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
+In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
+In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
+The analysis results are given in Section~\ref{section:evaluation}.
+Finally, we conclude the paper in Section~\ref{section:conclusion}.
+
 \begin{figure}[!t]
@@
 With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
+
+\subsection{Distributed Storage System}
+Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
+Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
+Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
+IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
+However, no cryptographic system is applied for user-uploaded files.
+Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
+Files are duplicated in multiple nodes to prevent data loss.
 
@@
 
+\subsubsection{Communication Protocol}
+In the following sections, we refer the low-level devices as \textbf{endpoint}s.
+MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic.
+The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth.
+The pub/sub model decouples publishers and subscribers in many ways:
+
+\begin{itemize}
+    \item Space decoupling: Both publishers and subscribers don't need to know each other.
+    \item Time decoupling: Publishers and subscribers do not need to be active at the same time.
+    \item Synchronization decoupling: Operations are decoupled from the publishers and subscribers.
+The publishers do not need to be alive until the response arrives.
+Messages from publisher can be served as send-and-forget fashion.
+\end{itemize}
+
 \subsubsection{End-to-End-Encryption}
@@
 
+\subsubsection{Register with Tangle-accelerator}
+User with channel seed can acquire channel chain ownership.
+Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
+Asymmetric encryption is utilizing during the process of exchanging seed.
+Digital signature should be taken at the same time to ensure data integrity.
+Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
+Thus, seed will not be exposed during communication after an edge device is successfully registered.
+
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service.
-It dramatically reduces execution time encryption takes.
-However, there are some challenges in the E2EE process.
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
+
+\paragraph{Linear Time to Read Message}
+It is linear time to decrypt message instead of constant time.
+Nevertheless, there is one way to speed up the message decryption process.
+A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
+This procedure can reduce the time spending on internet communication.
+
+\paragraph{Spam on Message Channel Chain}
 Tampering the messages which have conducted E2EE would be a challenging mission.
@@
 \label{section:smart_contract_evaluation}
-What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+
+\subsubsection{Experiment}
+Applying remote PoW greatly reduce the elapsed time.
+Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
 Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
@@
 The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 
@@
 The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
+
+\subsubsection{Time Complexity}
+With given E2EE protocol framework.
+ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is O(n).\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is O(n), too.
+Therefore, the E2EE protocol framework takes only linear time.
+Applying mature cryptographic functions (e.g.
+SHA-256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.
+
+\subsection{Smart Contract}
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
+The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+The Gas usage estimation is shown in Table.~\ref{tab:gas}.
+
+\begin{table*}[h]
+	\caption{Gas consumption for each function of Product Contract}
+	\label{tab:gas}
+	\centering
+	\resizebox{0.5\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
+		\hline
+		generate contract & broker & 2558980 \\ 
+		subscribe product & consumer & 72259 \\ 
+		upload hashed key & provider & 68276  \\ 
+		upload encryption key to consumer & provider & 86614 \\ 
+		upload certified key & broker & 131535 \\
+		update amount of uploaded data & broker & 32157 \\
+		unsubscribe & consumer & 8234 \\
+		request refund & consumer & 12067 \\
+		withdraw & broker & 11313 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Storage on blockchain is expensive.
+For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
+However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+However, using zero-knowledge protocol is out of the scope of this paper.
+
+Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
+We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+
+\begin{equation}
+\label{equa:ether_calculation}
+Ethers = Gas \ Price \times Gas \ Amount
+\end{equation}
+
+When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
+Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
+Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
+
+\begin{table*}[h]
+	\caption{Data Price Estimation}
+	\label{tab:ether}
+	\centering
+	\resizebox{0.8\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
+		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
+		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
 
@@
 Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are the key to operate a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
+Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
 However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

### 2020-07-10 paper.tex
Reduce contents in Related Work

--- 2020-07-10 paper.tex
@@
 \label{section:relatedWork}
-% pub/sub
-\subsection{The Publish/subscribe Communication Models Over Blockchain}
-The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
-
-M.
-B.
-Abdullahi and G.
-Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
-Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
-Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure.
 G.
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
-But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
+The data validation and traceability are achieved via Ethereum smart contract.
+But data is plaintext on blockchain that the system is not appropriate for sensitive data.
 
-In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
-The subscribers request publisher directly and ask them to save a cache space for interested data.
-The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
-Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-The reputation system and the punishment rules against malicious acts of subscribers and publishers.
-Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
-Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
-
-The previous works contribute to different aspects of building a reliable pub/sub system over blockchain.
-However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.
-
-\subsection{Trusted IoT Trading Infrastructure}
-Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
+Yet, without brokers, participants may need to reveal more sensitive information in order to communicate.
+By Paolo Missier et.
 al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
-However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
-
-A.
-Colman et al.
-\cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
-While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
+However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
 
@@
 Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
-This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
-Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+With encrypted data contents storing on IPFS, and add the encrypted IPFS link to MAM for further exchange.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold, and enable trading and perform access control on Ethereum smart contract.
+However, the details of trading and interactions between providers and consumers are not illustrated in this paper.
 
-Researches below adopt MAM as data storage and a secure data transmission layer.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
-Service requesters call for proposal of interested data and accept/reject proposals from service providers.
-After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
-This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
-Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
-
-O.
-Lamtzidis and J.
-Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
-Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
-The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.
 
@@
 In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
-The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}.
-The time duration for each \textit{height} is the average time of running 100 rounds.
 
 Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation.
+The time duration for each \textit{height} is the average time of running 100 rounds.
 Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.

### 2020-07-10 paper.tex
Reduce contents in Conclusion

@@
 
-\section{Conclusions}
+\section{Conclusion and Future Work}
 \label{section:conclusion}
@@
 
-In the subscription-based data trading, there are some issues that worth discussing and improving.
-Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
-Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are the key to operate a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
-However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
-
-Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
-The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
-Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
+Some issues are worth discussing and improving.
+Brokers are the key to operate a stable system.
+However, we do not discuss the conditions that brokers are not responsive during trading process.
+It is worth studying the necessity of adoptin gossip protocol among brokers, which enables other brokers to continue the undone works.
+Search engine is needed to let consumers search and find interested data products, which might need an authority to design and run the service.
 

### 2020-07-10 paper.tex
Add AES accelerator table

--- 2020-07-10 paper.tex
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{AES-NI}
-    \caption{AES256 Encryption/Decryption Performance Numbers}
-    \label{fig:AES-NI}
-\end{figure}
+\begin{table}[htbp]
+	\caption{AES256 Encryption Performance Numbers}
+	\label{tab:AES_NI}
+	\begin{center}
+        \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|  }
+            %\hline
+            %\multicolumn{4}{|c|}{} \\
+            \hline
+            Size& NON AES-NI (msecs) & AES-NI (msecs) & Encryption Acceleration (\%) \\
+            \hline
+            50 MB  & 1026  & 563   & 45.13 \\
+            100 MB & 2036  & 1297  & 36.30 \\
+            200 MB & 4282  & 2984  & 30.31 \\
+            512 MB & 10754 & 6401  & 40.48 \\
+            1 GB   & 23976 & 15721 & 34.43 \\
+            \hline
+        \end{tabular}
+    \end{center}
+\end{table}
 
@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Fig.~\ref{fig:AES-NI} shows the performance of Encryption/Decryption of AES256 with and without hardware acceleration.
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
 

### 2020-07-10 paper.tex
Use figure with less point to remove bump
Use table instead of figure

@@
 In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
+In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
 In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
@@
 	\begin{center}
-        \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|  }
+        \begin{tabular}{ |c||c|c|c|  }
             %\hline
@@
             \hline
-            Size& NON AES-NI (msecs) & AES-NI (msecs) & Encryption Acceleration (\%) \\
+            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
             \hline
@@
 \label{section:evaluation}
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
+2) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+
+\subsection{MAM Performance Evaluation}
+\label{section:mam_performance}
 It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
@@
 
-\subsection{MAM Performance Evaluation}
-\label{section:mam_performance}
 MAM is a secure and validatable data storage of the proposed architecture.
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3in]{mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
-
-It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
-Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
-The bump of MAM performance around 750 bytes proves this point.
+\begin{table}[htbp]
+	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+    \label{tab:mam_vs_e2ee}
+    \resizebox{0.5\textwidth}{!}{
+        \begin{tabular}{|c||c|c|}
+        \hline
+            \textbf{size (bytes)} & \textbf{MAM(ms)} & \textbf{E2EE(ms)} \\
+            \hline
+            100 & 20.28 & 9.21 \\ 
+            500 &  26.92 & 9.27 \\ 
+            900 & 32.02 &  9.35  \\ 
+            1300 & 36.67 & 9.41 \\ 
+            1700 & 40.55 & 9.54 \\
+            \hline
+        \end{tabular}
+    }
+\end{table}
+
+It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+
+\begin{equation}
+    \label{eq:lin_mam}
+    y=0.0126 x+19.979  
+\end{equation}
+
+\begin{equation}
+    \label{eq:lin_e2ee}
+    y=0.0002 x+9.174
+\end{equation}
+
+The Eq.~\ref{eq:lin_mam} and Eq.~\ref{eq:lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
+Apparently, the slope of the result of MAM is much greater than the result of E2EE.
+The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.
 
 \subsubsection{Time Complexity}
-With given E2EE protocol framework.
-ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
 HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is O(n).\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is O(n), too.
-Therefore, the E2EE protocol framework takes only linear time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
 Applying mature cryptographic functions (e.g.
-SHA-256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.
+SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
 
@@
 	\label{tab:gas}
-	\centering
 	\resizebox{0.5\textwidth}{!}{

### 2020-07-11 paper.tex
Fix typesetting for consistency

--- 2020-07-10 paper.tex
@@
 \subsubsection{Time Complexity}
-With given E2EE protocol framework.
-ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
 HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is O(n).\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is O(n), too.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
 Therefore, the E2EE protocol framework takes only linear time.

### 2020-07-11 paper.tex
Add the objective of evaluation

@@
 \label{section:evaluation}
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
+2) Evaluate the minimum cost for participants to sustain or subscribe to a data product on Product Contract.
+
+\subsection{MAM Performance Evaluation}
+\label{section:mam_performance}
 It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.

### 2020-07-14 paper.tex
Use the correct preposition
Redraw and resize figures

--- 2020-07-11 paper.tex
@@
 
-\subsection{Paper Organization}
-The rest of this paper is organized as follows.
-In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
-In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
-In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
-The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion}.
-
 \begin{figure}[!t]
@@
 Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
-This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
-Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+With encrypted data contents storing on IPFS, and add the encrypted IPFS link to MAM for further exchange.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold, and enable trading and perform access control on Ethereum smart contract.
+However, the details of trading and interactions between providers and consumers are not illustrated in this paper.
 
-Researches below adopt MAM as data storage and a secure data transmission layer.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
-Service requesters call for proposal of interested data and accept/reject proposals from service providers.
-After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
-This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
-Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
-
-O.
-Lamtzidis and J.
-Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
-Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
-The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
-
-\subsection{Distributed Storage System}
-Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-However, no cryptographic system is applied for user-uploaded files.
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
-Files are duplicated in multiple nodes to prevent data loss.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.
 
@@
 
-\begin{figure*}[!t]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\linewidth]{channel_and_key}
+    \includegraphics[width=3.5in]{channel_and_key_fold}
     \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
@@
     \label{fig:channel_and_key}
-\end{figure*}
+\end{figure}
 
@@
 During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
-See Fig.~\ref{fig:TangleID}
 
+\subsection{Enable Automated Trading Process}
 \begin{figure}[h]
     \centering
-    \includegraphics[width=3.5in]{TangleID}
-    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
-The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
-When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
-The data provider can then retrieve the consumer's public key and encrypt the content with it.
-After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
-    \label{fig:TangleID}
-\end{figure}
-
-\subsection{Enable Automated Trading Process}
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=4in]{smart_contract_mam}
+    \includegraphics[width=3.5in]{smart_contract_mam_shrink}
     \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
@@
     \label{fig:smart_contract_mam}
-\end{figure*}
+\end{figure}
 
@@
 %pic
-\begin{figure*}[!t]
+\begin{figure}[!h]
     \centering
-    \includegraphics[width=\linewidth]{MAM_E2EE}
+    \includegraphics[width=3in]{MAM_E2EE_fold}
     \caption{The process of E2EE.}
     \label{fig:MAM_E2EE}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{table}[htbp]
-	\caption{AES256 Encryption Performance Numbers}
-	\label{tab:AES_NI}
-	\begin{center}
-        \begin{tabular}{ |c||c|c|c|  }
-            %\hline
-            %\multicolumn{4}{|c|}{} \\
-            \hline
-            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
-            \hline
-            50 MB  & 1026  & 563   & 45.13 \\
-            100 MB & 2036  & 1297  & 36.30 \\
-            200 MB & 4282  & 2984  & 30.31 \\
-            512 MB & 10754 & 6401  & 40.48 \\
-            1 GB   & 23976 & 15721 & 34.43 \\
-            \hline
-        \end{tabular}
-    \end{center}
-\end{table}
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{AES-NI}
+    \caption{AES256 Encryption/Decryption Performance Numbers}
+    \label{fig:AES-NI}
+\end{figure}
 
@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
-
-\subsubsection{Register with Tangle-accelerator}
-User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
-Asymmetric encryption is utilizing during the process of exchanging seed.
-Digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed will not be exposed during communication after an edge device is successfully registered.
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Fig.~\ref{fig:AES-NI} shows the performance of Encryption/Decryption of AES256 with and without hardware acceleration.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
-
-\paragraph{Linear Time to Read Message}
-It is linear time to decrypt message instead of constant time.
-Nevertheless, there is one way to speed up the message decryption process.
-A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
-This procedure can reduce the time spending on internet communication.
-
-\paragraph{Spam on Message Channel Chain}
+E2EE helps a lot for low-level edge device utilizing blockchain service.
+It dramatically reduces execution time encryption takes.
+However, there are some challenges in the E2EE process.
 Tampering the messages which have conducted E2EE would be a challenging mission.
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{unsubscribe}
-    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
-Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
-    \label{fig:unsubscribe}
-\end{figure}
-
 \subsection{Launch a Refund}
@@
 When the refund procedure is launched, all consumers vote to decide whether the refund is established.
-See Fig.~\ref{fig:refund}.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
 
@@
 \end{equation}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=1.5in]{refund}
-    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
-Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
-    \label{fig:refund}
-\end{figure}
 
@@
 In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
-The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}.
+
+Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation.
 The time duration for each \textit{height} is the average time of running 100 rounds.
-
-\begin{table}[htbp]
-	\caption{Time measurement of channel creation}
-	\label{tab:channel_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.26183 & 2.908702 \\ 
-		2 & 0.524076 & 5.805524 \\ 
-		3 & 1.045942 & 11.555660 \\ 
-		4 & 2.092989 & 23.178036 \\ 
-		5 & 4.19515 & 46.164079\\ 
-		6 & 8.361586 & 92.320173\\ 
-		7 & 16.651607 & 185.292243\\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Time measurement of endpoint creation}
-	\label{tab:endpoint_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.256425 & 2.887064 \\ 
-		2 & 0.505679 & 5.767912 \\ 
-		3 & 0.999524 & 11.550455 \\ 
-		4 & 1.994017 & 23.260508 \\ 
-		5 & 3.965007 & 46.748366 \\ 
-		6 & 7.918925 & 93.182975 \\ 
-		7 & 16.561419 & 186.064562 \\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}.
 Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
@@
 \label{section:smart_contract_evaluation}
-
-\subsubsection{Experiment}
-Applying remote PoW greatly reduce the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
 Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
@@
 The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 
@@
 The bump of MAM performance around 750 bytes proves this point.
+Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
 
-\subsubsection{Time Complexity}
-With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
-HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
-Therefore, the E2EE protocol framework takes only linear time.
-Applying mature cryptographic functions (e.g.
-SHA-256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.
-
-\subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
-On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
-The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-The Gas usage estimation is shown in Table.~\ref{tab:gas}.
-
-\begin{table*}[h]
-	\caption{Gas consumption for each function of Product Contract}
-	\label{tab:gas}
-	\centering
-	\resizebox{0.5\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
-		\hline
-		generate contract & broker & 2558980 \\ 
-		subscribe product & consumer & 72259 \\ 
-		upload hashed key & provider & 68276  \\ 
-		upload encryption key to consumer & provider & 86614 \\ 
-		upload certified key & broker & 131535 \\
-		update amount of uploaded data & broker & 32157 \\
-		unsubscribe & consumer & 8234 \\
-		request refund & consumer & 12067 \\
-		withdraw & broker & 11313 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
-Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
-Storage on blockchain is expensive.
-For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
-
-Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
-\label{equa:ether_calculation}
-Ethers = Gas \ Price \times Gas \ Amount
-\end{equation}
-
-When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
-Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
-Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
-
-\begin{table*}[h]
-	\caption{Data Price Estimation}
-	\label{tab:ether}
-	\centering
-	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
-		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
-		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-\section{Conclusions}
+\section{Conclusion and Future Work}
 \label{section:conclusion}
@@
 
-In the subscription-based data trading, there are some issues that worth discussing and improving.
-Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
-Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
-However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
-
-Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
-The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
-Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
+Some issues are worth discussing and improving.
+Brokers are the key to operate a stable system.
+However, we do not discuss the conditions that brokers are not responsive during trading process.
+It is worth studying the necessity of adoptin gossip protocol among brokers, which enables other brokers to continue the undone works.
+Search engine is needed to let consumers search and find interested data products, which might need an authority to design and run the service.
 

### 2020-07-14 paper.tex

@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{AES-NI}
-    \caption{AES256 Encryption/Decryption Performance Numbers}
-    \label{fig:AES-NI}
-\end{figure}
+\begin{table}[htbp]
+	\caption{AES256 Encryption Performance Numbers}
+	\label{tab:AES_NI}
+	\begin{center}
+        \begin{tabular}{ |c||c|c|c|  }
+            %\hline
+            %\multicolumn{4}{|c|}{} \\
+            \hline
+            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
+            \hline
+            50 MB  & 1026  & 563   & 45.13 \\
+            100 MB & 2036  & 1297  & 36.30 \\
+            200 MB & 4282  & 2984  & 30.31 \\
+            512 MB & 10754 & 6401  & 40.48 \\
+            1 GB   & 23976 & 15721 & 34.43 \\
+            \hline
+        \end{tabular}
+    \end{center}
+\end{table}
 
@@
 
-\begin{figure}[!t]
+\begin{table}[htbp]
+	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+    \label{tab:mam_vs_e2ee}
     \centering
-    \includegraphics[width=3in]{mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
+        \begin{tabular}{|c||c|c|}
+        \hline
+            \textbf{size (bytes)} & \textbf{MAM(ms)} & \textbf{E2EE(ms)} \\
+            \hline
+            100 & 20.28 & 9.21 \\ 
+            500 &  26.92 & 9.27 \\ 
+            900 & 32.02 &  9.35  \\ 
+            1300 & 36.67 & 9.41 \\ 
+            1700 & 40.55 & 9.54 \\
+            \hline
+        \end{tabular}
+\end{table}
 
-It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
-Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
-The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
+It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+
+\begin{gather}
+    \label{eq:lin_mam_e2ee}
+    y=0.0126 x+19.979 \\
+    y=0.0002 x+9.174
+\end{gather}
+
+The equations in Eq.~\ref{eq:lin_mam_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
+Apparently, the slope of the result of MAM is much greater than the result of E2EE.
+The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.
+
+\subsubsection{Time Complexity}
+With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
+Applying mature cryptographic functions (e.g.
+SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
 

### 2020-07-14 paper.tex
Use minipage to reorganize evaluation result figures

@@
 When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
-The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
+The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe}.
 $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
@@
 
-\begin{equation}
-\label{equation:unsubscribe_provider}
-    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
-\end{equation}
-
-\begin{equation}
-\label{equation:unsubscribe_broker}
-    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
-\end{equation}
-
-\begin{equation}
-\label{equation:unsubscribe_consumer}
+\begin{gather}
+\label{equation:unsubscribe}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \\
+    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t} \\
     F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
-\end{equation}
+\end{gather}
 
@@
 When the refund procedure is launched, all consumers vote to decide whether the refund is established.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
-
-\begin{equation}
-    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
-\end{equation}
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following.
 
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{mam_create}
-    \caption{Time cost of MAM creation.}
-    \label{fig:mam_create}
-\end{figure}
+\begin{figure*}[!htb]
+\minipage{0.32\textwidth}
+  \includegraphics[width=\linewidth]{mam_create}
+  \caption{Time cost of MAM creation.}\label{fig:mam_create}
+\endminipage\hfill
+\minipage{0.32\textwidth}
+  \includegraphics[width=\linewidth]{mam_send}
+  \caption{The probability distributed function of time cost for sending a message through MAM.}\label{fig:mam_send}
+\endminipage\hfill
+\minipage{0.32\textwidth}%
+  \includegraphics[width=\linewidth]{rpi3_pow}
+  \caption{Local PoW vs. Remote PoW}\label{fig:rpi3_pow}
+\endminipage
+\end{figure*}
 
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{mam_send}
-    \caption{The probability distributed function of time cost for sending a message through MAM.}
-    \label{fig:mam_send}
-\end{figure}
-
 The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
@@
 However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{rpi3_pow}
-    \caption{Local PoW vs. Remote PoW}
-    \label{fig:rpi3_pow}
-\end{figure}
 

### 2020-07-14 paper.tex
Remove MAM key comparison table

@@
 \subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
-%scalability
 \subsubsection{A Scalable Keys and Data Entry Points Management}
@@
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
 Assuming the length of data stream is 7, and each record is encrypted with the same key.
@@
 
-\begin{table}[htbp]
-	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
-	\label{tab:mam_scalability}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
-		\hline
-		keys & 1 & 1 \\ 
-		\hline
-		entry points & 1 & 7 \\ 
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-%classify
 \subsubsection{Data Sreams Classification}
@@
 
-%data trace
 \subsubsection{A Traceable Data Stream}
@@
 The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
-
 \begin{gather}
@@
 \end{gather}
-
 \subsection{Launch a Refund}
@@
 The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
-
 \begin{figure*}[!htb]
@@
 \end{itemize}
-
 \begin{table}[htbp]
@@
 It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
-
 \begin{gather}
@@
 \end{gather}
-
 The equations in Eq.~\ref{eq:lin_mam_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.

### 2020-07-14 paper.tex
Remove the paper using IPFS + MAM

@@
 
-%TODO: cite IOTAIndustryMarketplace
 \section{Related Work}
@@
 In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
-Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-With encrypted data contents storing on IPFS, and add the encrypted IPFS link to MAM for further exchange.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold, and enable trading and perform access control on Ethereum smart contract.
-However, the details of trading and interactions between providers and consumers are not illustrated in this paper.
-
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.

### 2020-07-14 paper.tex
Combine Chap3 MAM and delegation and align equations by equal sign

@@
 
+However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+The details would be further illustrated in Section.\ref{section:ta_endpoint}.
+
 \subsection{Digital Identity}
@@
 The consumer list and the states of products are key reputation referenced for data consumers to decide whether to subscribe.
-
-\subsection{Enable computation tasks delegation to broker with privacy}
-To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the resources of low-level devices are precious which should be used to focus on its jobs.
-Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
-
-The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
-    \label{fig:key_upload}
-\end{figure}
-
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
-The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
@@
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product}.
+As regard to the encryption key of data product, brokers are asked to  record encryption keys to smart contracts.
+To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
+Broker can first verify the signature from data provider with the public key on DID document.
+If it's valid, then the broker uploads the key, otherwise the process will be aborted.
+Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker, and the overall workflow is shown in Fig.~\ref{fig:launching_product}.
 Finally, the data product is launched and data providers can start uploading data.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{key_upload}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
+After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
+    \label{fig:key_upload}
+\end{figure}
 
@@
 The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
-\begin{gather}
+\begin{align}
 \label{equation:unsubscribe}
-    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \\
-    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t} \\
-    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
-\end{gather}
+    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \\
+    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \\
+    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+\end{align}
 \subsection{Launch a Refund}
@@
 It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
-\begin{gather}
+\begin{align}
 \label{eq:lin_mam_e2ee}
-    y=0.0126 x+19.979 \\
-    y=0.0002 x+9.174
-\end{gather}
+    y &= 0.0126 x+19.979 \\
+    y &= 0.0002 x+9.174
+\end{align}
 The equations in Eq.~\ref{eq:lin_mam_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.

### 2020-07-14 paper.tex
Fix reference error on equations
Drop AES-NI table

@@
 
-\begin{table}[htbp]
-	\caption{AES256 Encryption Performance Numbers}
-	\label{tab:AES_NI}
-	\begin{center}
-        \begin{tabular}{ |c||c|c|c|  }
-            %\hline
-            %\multicolumn{4}{|c|}{} \\
-            \hline
-            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
-            \hline
-            50 MB  & 1026  & 563   & 45.13 \\
-            100 MB & 2036  & 1297  & 36.30 \\
-            200 MB & 4282  & 2984  & 30.31 \\
-            512 MB & 10754 & 6401  & 40.48 \\
-            1 GB   & 23976 & 15721 & 34.43 \\
-            \hline
-        \end{tabular}
-    \end{center}
-\end{table}
-
 The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration}
 
@@
 \begin{align}
-\label{eq:lin_mam_e2ee}
-    y &= 0.0126 x+19.979 \\
-    y &= 0.0002 x+9.174
+    y &= 0.0126 x+19.979 \label{lin_mam} \\
+    y &= 0.0002 x+9.174 \label{lin_e2ee}
 \end{align}
-The equations in Eq.~\ref{eq:lin_mam_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
+The equations in Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
 Apparently, the slope of the result of MAM is much greater than the result of E2EE.

### 2020-07-14 paper.tex
Shorten the abstract

@@
 %cite IoT data subscription economy
-The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
-Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchange among devices are periodical that only data in a specific time period is interested.
-Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
-Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
+On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.

### 2020-07-14 paper.tex
Reoganize description of experiement

@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jkrvivian@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jserv@ccns.ncku.edu.tw}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-chiaheng@gmail.com}
+\author{
+\IEEEauthorblockN{Anonymous}
+\IEEEauthorblockA{
+         \textit{Anonymous Organization}\\
+        ***@***.***}
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
+%\IEEEauthorblockA{\textit{dept. of CSIE} \\
+%\textit{National Cheng Kung University}\\
+%Tainan City, Taiwan (R.O.C.) \\
+%jkrvivian@gmail.com}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
+%\IEEEauthorblockA{\textit{dept. of CSIE} \\
+%\textit{National Cheng Kung University}\\
+%Tainan City, Taiwan (R.O.C.) \\
+%jserv@ccns.ncku.edu.tw}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
+%\IEEEauthorblockA{\textit{dept. of CSIE} \\
+%\textit{National Cheng Kung University}\\
+%Tainan City, Taiwan (R.O.C.) \\
+%chiaheng@gmail.com}
 }
@@
 
-The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
+The E2EE protocol framework presented in this paper combines a series of different cryptographic procedures.
 Each of them can be chosen on the basis of the working hardware and scenario by developers.
@@
 For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration}
+
+\subsubsection{Time Complexity}
+In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature.
+In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
 
@@
 With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the processes after sending message to tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
 In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
@@
 
-The steps counted in E2EE benchmark including:
+The steps counted in delegated MAM (E2EE) benchmark including:
 \begin{itemize}
@@
 
-It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
 \begin{align}
@@
 \end{align}
-The equations in Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
-Apparently, the slope of the result of MAM is much greater than the result of E2EE.
-The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.
 
-\subsubsection{Time Complexity}
-With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
-HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
-Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
-Applying mature cryptographic functions (e.g.
-SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
+Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods.
+Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively.
+The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
 

### 2020-07-14 paper.tex
Remove author information
Be anonymous for reviewing.
Reoganize experiment and move time complexity

@@
 
-The E2EE protocol framework presented in this paper combines a series of different cryptographic procedures.
+The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
 Each of them can be chosen on the basis of the working hardware and scenario by developers.
@@
 Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
-Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
+Therefore, the E2EE protocol takes only linear time versus arbitrary string length.
 
@@
 \subsubsection{Experiment}
-Applying remote PoW greatly reduce the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+Applying remote PoW greatly reduces the elapsed time.
+Channel creation is the next primary barrier for low-level devices to broadcast MAM messages.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
 What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the processes after sending message to tangle-accelerator are the common steps.
+Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
-In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
+In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 

### 2020-07-14 paper.tex
Remove Contribution

--- 2020-07-14 paper.tex
@@
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
-
-\subsection{Contributions}
-The contributions in the paper are summarized as follow:
-\begin{itemize}
-	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
-	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
-	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
-	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
-\end{itemize}
 

### 2020-07-14 paper.tex
Refactor Chap 3 MAM

@@
 MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
-
-In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
-
-\begin{itemize}
-    \item \textbf{Scalability}:
-	\begin{itemize}
-		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
-    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
-    \end{itemize}    
-    \item \textbf{Integrity}: 
-	\begin{itemize}    	
-        \item Messages published to the Tangle are tamper-proof that against malicious modification.
-    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
-    \end{itemize}
-    \item \textbf{Confidentiality}:
-    \begin{itemize}    	
-    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
-    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
-    	\item MAM provides forward-secrecy.
-The entry points of future data can be derived, but it's impossible to trace back those in the past.
-This feature prevents adversaries from retrieving published history even if the key is revealed.
-    \end{itemize}
-\end{itemize}
-
-MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle.
-This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source.
+In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1.) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
+2.) \textbf{Integrity}, messages are written on the Tangle network that are not immutable.
+3.) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
+4.) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
 See Fig.~\ref{fig:channel_and_key} for illustration.

### 2020-07-14 paper.tex
Add description for MAM benchmark

@@
 \subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+There are three major participants, data providers, data consumers and brokers in our proposed architecture.
 
@@
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets.
+Purchase is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
-Brokers are responsible for building an agreement between data providers and consumers.
-Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
+Brokers are responsible for building an agreement and handling trading processes between data providers and consumers.
+Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
 \end{itemize}
 
-We adopt the brokered infrastructure for three reasons.
-Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system.
-Furthermore, if either side is offline, the proceeding tasks have to stop and start over.
-With brokers, the unfinished work can be cached or accomplished.
+Adopting brokers between providers and consumers has three advantages.
+First, considering the entities could be machines that are not online anytime, brokers can continue the trading process if either side is offline.
 Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
-The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
-With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
+Brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
+Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
 
@@
 
+\subsubsection{Time Complexity}
+In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature.
+In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol takes only linear time versus arbitrary string length.
+
 \subsubsection{Issues in End-to-End-Encryption}
@@
 \end{align}
-\subsection{Launch a Refund}
+\subsection{Refund}
+\label{section:refund}
 Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
@@
   \includegraphics[width=\linewidth]{rpi3_pow}
-  \caption{Local PoW vs. Remote PoW}\label{fig:rpi3_pow}
+  \caption{Local PoW vs. Remote PoW vs. E2EE}\label{fig:rpi3_pow}
 \endminipage
@@
 
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
+Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
 Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator.
-However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local Pow on Raspberry Pi 3, remote Pow on Tangle-accelerator and E2EE on Raspberry Pi 3.
+However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.
 
@@
 \subsubsection{Experiment}
-Applying remote PoW greatly reduce the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
+Applying remote PoW greatly reduces the elapsed time.
+To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
+In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 
 The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
+\begin{enumerate}
+    \item Write key information in header
+	\item Write and encrypt input payload
 	\item Publish final message on IOTA Tangle
-\end{itemize}
+\end{enumerate}
 
-The steps counted in E2EE benchmark including:
-\begin{itemize}
+The steps counted in delegated MAM (E2EE) benchmark including:
+\begin{enumerate}
 	\item Generate symmetric key for encryption
@@
 	\item Transmit final message to tangle-accelerator
-\end{itemize}
+\end{enumerate}
+
 \begin{table}[htbp]

### 2020-07-14 paper.tex
Refactor Chap 3 Roles

--- 2020-07-14 paper.tex
@@
 \subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+There are three major roles, data providers, data consumers and brokers in our proposed architecture.
 
@@
 \subsection{Launch a Refund}
+\label{section:refund}
 Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.

### 2020-07-14 paper.tex

--- 2020-07-14 paper.tex
@@
 
-\author{
-\IEEEauthorblockN{Anonymous}
-\IEEEauthorblockA{
-         \textit{Anonymous Organization}\\
-        ***@***.***}
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%jkrvivian@gmail.com}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%jserv@ccns.ncku.edu.tw}
-%\and
-%\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%chiaheng@gmail.com}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
+\IEEEauthorblockA{\textit{dept. of CSIE} \\
+\textit{National Cheng Kung University}\\
+Tainan City, Taiwan (R.O.C.) \\
+jkrvivian@gmail.com}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
+\IEEEauthorblockA{\textit{dept. of CSIE} \\
+\textit{National Cheng Kung University}\\
+Tainan City, Taiwan (R.O.C.) \\
+jserv@ccns.ncku.edu.tw}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
+\IEEEauthorblockA{\textit{dept. of CSIE} \\
+\textit{National Cheng Kung University}\\
+Tainan City, Taiwan (R.O.C.) \\
+chiaheng@gmail.com}
 }
@@
 %cite IoT data subscription economy
-On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set.
+The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
+The real-time data exchange among devices are periodical that only data in a specific time period is interested.
+Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
+Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
@@
 
+\subsection{Contributions}
+The contributions in the paper are summarized as follow:
+\begin{itemize}
+	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
+	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
+	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
+	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
+\end{itemize}
+
+\subsection{Paper Organization}
+The rest of this paper is organized as follows.
+In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
+In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
+In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
+In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
+The analysis results are given in Section~\ref{section:evaluation}.
+Finally, we conclude the paper in Section~\ref{section:conclusion}.
+
 \begin{figure}[!t]
@@
 
+%TODO: cite IOTAIndustryMarketplace
 \section{Related Work}
 \label{section:relatedWork}
+% pub/sub
+\subsection{The Publish/subscribe Communication Models Over Blockchain}
+The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
+A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
+
+M.
+B.
+Abdullahi and G.
+Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
+Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
+Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
+However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure.
 G.
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-The data validation and traceability are achieved via Ethereum smart contract.
-But data is plaintext on blockchain that the system is not appropriate for sensitive data.
+With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
+But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
 
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
+In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
+The subscribers request publisher directly and ask them to save a cache space for interested data.
+The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
+Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
+Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-Yet, without brokers, participants may need to reveal more sensitive information in order to communicate.
-By Paolo Missier et.
+The reputation system and the punishment rules against malicious acts of subscribers and publishers.
+Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
+Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
+
+The previous works contribute to different aspects of building a reliable pub/sub system over blockchain.
+However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.
+
+\subsection{Trusted IoT Trading Infrastructure}
+Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
 al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
+Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
+However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
+
+A.
+Colman et al.
+\cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
 
 In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.
+Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
+Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
+This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
+Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+
+Researches below adopt MAM as data storage and a secure data transmission layer.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
+Service requesters call for proposal of interested data and accept/reject proposals from service providers.
+After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
+This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
+Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
+
+O.
+Lamtzidis and J.
+Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
+The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
+Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
+The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
+And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
+
+\subsection{Distributed Storage System}
+Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
+Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
+Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
+IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
+However, no cryptographic system is applied for user-uploaded files.
+Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
+Files are duplicated in multiple nodes to prevent data loss.
 
@@
 But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+As shown in Fig.~\ref{fig:pub_sub_model}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{pub_sub_model}
+    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
+    \label{fig:pub_sub_model}
+\end{figure}
 
@@
 
-\begin{figure}[h]
+\begin{figure*}[!t]
     \centering
-    \includegraphics[width=3.5in]{channel_and_key_fold}
+    \includegraphics[width=\linewidth]{channel_and_key}
     \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
@@
     \label{fig:channel_and_key}
-\end{figure}
+\end{figure*}
 
@@
 MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1.) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
-2.) \textbf{Integrity}, messages are written on the Tangle network that are not immutable.
-3.) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
-4.) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
+Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
+
+In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
+
+\begin{itemize}
+    \item \textbf{Scalability}:
+	\begin{itemize}
+		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
+    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \end{itemize}    
+    \item \textbf{Integrity}: 
+	\begin{itemize}    	
+        \item Messages published to the Tangle are tamper-proof that against malicious modification.
+    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
+    \end{itemize}
+    \item \textbf{Confidentiality}:
+    \begin{itemize}    	
+    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
+    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
+    	\item MAM provides forward-secrecy.
+The entry points of future data can be derived, but it's impossible to trace back those in the past.
+This feature prevents adversaries from retrieving published history even if the key is revealed.
+    \end{itemize}
+\end{itemize}
+
+MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
+The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle.
+This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source.
 See Fig.~\ref{fig:channel_and_key} for illustration.
@@
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-
-However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
-The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
@@
 During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
+See Fig.~\ref{fig:TangleID}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{TangleID}
+    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
+The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
+When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
+The data provider can then retrieve the consumer's public key and encrypt the content with it.
+After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
+    \label{fig:TangleID}
+\end{figure}
 
 \subsection{Enable Automated Trading Process}
-\begin{figure}[h]
+\begin{figure*}[t]
     \centering
-    \includegraphics[width=3.5in]{smart_contract_mam_shrink}
+    \includegraphics[width=4in]{smart_contract_mam}
     \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
@@
     \label{fig:smart_contract_mam}
-\end{figure}
+\end{figure*}
 
@@
 The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
-Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+Listing.
+\ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
@@
 For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
-The consumer list and the states of products are key reputation referenced for data consumers to decide whether to subscribe.
+The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
+
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
+contract Product {
+    address public broker;
+    address public provider;
+    bool isBrokerWithdraw;
+    bool isProviderWithdraw;
+    address[] consumers;
+
+    struct Purchase {
+        bool affirmativeVote;
+        bool isConsumerWithdraw;
+        bool isKeyAdded;
+        bool isSubscribe;
+        string encryptKey;
+    }
+    mapping(address => Purchase) public consumer2Purchase;
+
+    uint public price;
+    uint public totalAmount;
+    uint public brokerage;
+    uint public cancellation;
+    uint public threshold;
+    string public channelRoot;
+    string public endPoint;
+    uint public totalNumber;
+    uint public uploadedNumber;
+    uint public affirmativeVotes;
+    string hashedKey;
+    string certifiedKey;
+
+    enum State {Launched, KeyCertified, Finished, Refunded}
+    State public state;
+}
+\end{lstlisting}
+
+\subsection{Enable computation tasks delegation to broker with privacy}
+To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
+However, the resources of low-level devices are precious which should be used to focus on its jobs.
+Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
+
+The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
+To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
+Broker can first verify the signature from data provider with the public key on DID document.
+If it's valid, then the broker uploads the key, otherwise the process will be aborted.
+Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{key_upload}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
+After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
+    \label{fig:key_upload}
+\end{figure}
+
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
@@
 \subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
+%scalability
 \subsubsection{A Scalable Keys and Data Entry Points Management}
@@
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
 Assuming the length of data stream is 7, and each record is encrypted with the same key.
@@
 
+\begin{table}[htbp]
+	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
+	\label{tab:mam_scalability}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
+		\hline
+		keys & 1 & 1 \\ 
+		\hline
+		entry points & 1 & 7 \\ 
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+%classify
 \subsubsection{Data Sreams Classification}
@@
 
+%data trace
 \subsubsection{A Traceable Data Stream}
@@
 %pic
-\begin{figure}[!h]
+\begin{figure*}[!t]
     \centering
-    \includegraphics[width=3in]{MAM_E2EE_fold}
+    \includegraphics[width=\linewidth]{MAM_E2EE}
     \caption{The process of E2EE.}
     \label{fig:MAM_E2EE}
-\end{figure}
+\end{figure*}
 
@@
 
+\begin{table}[htbp]
+	\caption{AES256 Encryption Performance Numbers}
+	\label{tab:AES_NI}
+	\begin{center}
+        \begin{tabular}{ |c||c|c|c|  }
+            %\hline
+            %\multicolumn{4}{|c|}{} \\
+            \hline
+            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
+            \hline
+            50 MB  & 1026  & 563   & 45.13 \\
+            100 MB & 2036  & 1297  & 36.30 \\
+            200 MB & 4282  & 2984  & 30.31 \\
+            512 MB & 10754 & 6401  & 40.48 \\
+            1 GB   & 23976 & 15721 & 34.43 \\
+            \hline
+        \end{tabular}
+    \end{center}
+\end{table}
+
 The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration}
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
+
+\subsubsection{Register with Tangle-accelerator}
+User with channel seed can acquire channel chain ownership.
+Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
+Once tangle-accelerator receive the Seed from edge device, it would return a unique user identifier which can be mapping to corresponding Seed when edge devices send requests.
+Asymmetric encryption is utilizing during the process of exchanging seed.
+Digital signature should be taken at the same time to ensure data integrity.
+Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
+Thus, seed will not be exposed during communication after an edge device is successfully registered.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service.
-It dramatically reduces execution time encryption takes.
-However, there are some challenges in the E2EE process.
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
+
+\paragraph{Linear Time to Read Message}
+It is linear time to decrypt message instead of constant time.
+Nevertheless, there is one way to speed up the message decryption process.
+A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
+This procedure can reduce the time spending on internet communication.
+
+\paragraph{Spam on Message Channel Chain}
 Tampering the messages which have conducted E2EE would be a challenging mission.
@@
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, brokers are asked to  record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker, and the overall workflow is shown in Fig.~\ref{fig:launching_product}.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
+This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
+The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
 Finally, the data product is launched and data providers can start uploading data.
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
-    \label{fig:key_upload}
-\end{figure}
 
@@
 
+\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
+    function addHashedKey(
+        string memory _hashedKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add hashed key."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        hashedKey = hashedKey;
+        emit newHashedKey(hashedKey);
+    }
+
+    function addCertifiedKey(
+        string memory _certifiedKey
+    ) public {
+        require(
+            msg.sender == broker,
+            "Only broker can add certifiedKey."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        certifiedKey = _certifiedKey;
+        state = State.KeyCertified;
+        emit newCertifiedKey(certifiedKey);
+    }
+\end{lstlisting}
+
 \subsection{Subscribe to Data Product}
@@
 
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+
+\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
+    function addEncryptKey(
+        address _consumer,
+        string memory _encryptKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add the encrypted key."
+        );
+        require(
+            consumer2Purchase[_consumer].isKeyAdded == false,
+            "Encryption key has been added."
+        );
+        consumer2Purchase[_consumer].encryptKey = _encryptKey;
+        consumer2Purchase[_consumer].isKeyAdded = true;
+        emit newEncryptKey(_consumer, _encryptKey);
+    }
+\end{lstlisting}
+
 \subsection{Unsubscribe to Data Products}
@@
 When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
-The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe}.
+The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
 $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
@@
 The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
-\begin{align}
-\label{equation:unsubscribe}
-    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \\
-    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \\
-    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
-\end{align}
+Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
+
+\begin{equation}
+\label{equation:unsubscribe_provider}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_broker}
+    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_consumer}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{unsubscribe}
+    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
+Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
+    \label{fig:unsubscribe}
+\end{figure}
+
 \subsection{Launch a Refund}
@@
 When the refund procedure is launched, all consumers vote to decide whether the refund is established.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following.
+See Fig.~\ref{fig:refund}.
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
+
+\begin{equation}
+    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.5in]{refund}
+    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
+Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \label{fig:refund}
+\end{figure}
 
@@
 In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
+The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}.
+The time duration for each \textit{height} is the average time of running 100 rounds.
 
-Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation.
-The time duration for each \textit{height} is the average time of running 100 rounds.
+\begin{table}[htbp]
+	\caption{Time measurement of channel creation}
+	\label{tab:channel_create}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
+		\hline
+		1 & 0.26183 & 2.908702 \\ 
+		2 & 0.524076 & 5.805524 \\ 
+		3 & 1.045942 & 11.555660 \\ 
+		4 & 2.092989 & 23.178036 \\ 
+		5 & 4.19515 & 46.164079\\ 
+		6 & 8.361586 & 92.320173\\ 
+		7 & 16.651607 & 185.292243\\
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Time measurement of endpoint creation}
+	\label{tab:endpoint_create}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
+		\hline
+		1 & 0.256425 & 2.887064 \\ 
+		2 & 0.505679 & 5.767912 \\ 
+		3 & 0.999524 & 11.550455 \\ 
+		4 & 1.994017 & 23.260508 \\ 
+		5 & 3.965007 & 46.748366 \\ 
+		6 & 7.918925 & 93.182975 \\ 
+		7 & 16.561419 & 186.064562 \\
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}.
 Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
@@
 The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
-\begin{figure*}[!htb]
-\minipage{0.32\textwidth}
-  \includegraphics[width=\linewidth]{mam_create}
-  \caption{Time cost of MAM creation.}\label{fig:mam_create}
-\endminipage\hfill
-\minipage{0.32\textwidth}
-  \includegraphics[width=\linewidth]{mam_send}
-  \caption{The probability distributed function of time cost for sending a message through MAM.}\label{fig:mam_send}
-\endminipage\hfill
-\minipage{0.32\textwidth}%
-  \includegraphics[width=\linewidth]{rpi3_pow}
-  \caption{Local PoW vs. Remote PoW}\label{fig:rpi3_pow}
-\endminipage
-\end{figure*}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{mam_create}
+    \caption{Time cost of MAM creation.}
+    \label{fig:mam_create}
+\end{figure}
 
@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{mam_send}
+    \caption{The probability distributed function of time cost for sending a message through MAM.}
+    \label{fig:mam_send}
+\end{figure}
+
 The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
@@
 However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{rpi3_pow}
+    \caption{Local PoW vs. Remote PoW}
+    \label{fig:rpi3_pow}
+\end{figure}
 
@@
 \end{itemize}
+
 \begin{table}[htbp]
@@
     \label{tab:mam_vs_e2ee}
-    \centering
+    \resizebox{0.5\textwidth}{!}{
         \begin{tabular}{|c||c|c|}
@@
         \end{tabular}
+    }
 \end{table}
@@
 It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
-\begin{align}
-    y &= 0.0126 x+19.979 \label{lin_mam} \\
-    y &= 0.0002 x+9.174 \label{lin_e2ee}
-\end{align}
-The equations in Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
+
+\begin{equation}
+    \label{eq:lin_mam}
+    y=0.0126 x+19.979  
+\end{equation}
+
+\begin{equation}
+    \label{eq:lin_e2ee}
+    y=0.0002 x+9.174
+\end{equation}
+
+The Eq.~\ref{eq:lin_mam} and Eq.~\ref{eq:lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
 Apparently, the slope of the result of MAM is much greater than the result of E2EE.
@@
 
-\section{Conclusion and Future Work}
+\subsection{Smart Contract}
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
+The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+The Gas usage estimation is shown in Table.~\ref{tab:gas}.
+
+\begin{table*}[h]
+	\caption{Gas consumption for each function of Product Contract}
+	\label{tab:gas}
+	\resizebox{0.5\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
+		\hline
+		generate contract & broker & 2558980 \\ 
+		subscribe product & consumer & 72259 \\ 
+		upload hashed key & provider & 68276  \\ 
+		upload encryption key to consumer & provider & 86614 \\ 
+		upload certified key & broker & 131535 \\
+		update amount of uploaded data & broker & 32157 \\
+		unsubscribe & consumer & 8234 \\
+		request refund & consumer & 12067 \\
+		withdraw & broker & 11313 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Storage on blockchain is expensive.
+For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
+However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+However, using zero-knowledge protocol is out of the scope of this paper.
+
+Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
+We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+
+\begin{equation}
+\label{equa:ether_calculation}
+Ethers = Gas \ Price \times Gas \ Amount
+\end{equation}
+
+When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
+Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
+Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
+
+\begin{table*}[h]
+	\caption{Data Price Estimation}
+	\label{tab:ether}
+	\centering
+	\resizebox{0.8\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
+		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
+		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+\section{Conclusions}
 \label{section:conclusion}
@@
 
-Some issues are worth discussing and improving.
-Brokers are the key to operate a stable system.
-However, we do not discuss the conditions that brokers are not responsive during trading process.
-It is worth studying the necessity of adoptin gossip protocol among brokers, which enables other brokers to continue the undone works.
-Search engine is needed to let consumers search and find interested data products, which might need an authority to design and run the service.
+In the subscription-based data trading, there are some issues that worth discussing and improving.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
+Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
+Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
+However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
+
+Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
 

### 2020-07-15 paper.tex
Change a term

--- 2020-07-14 paper.tex
@@
 \subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers in our proposed architecture.
+There are three major participants, data providers, data consumers and brokers in our proposed architecture.
 

### 2020-07-15 paper.tex
Change title of Refund section
Clarify wording

--- 2020-07-14 paper.tex
@@
 \subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers in our proposed architecture.
+There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
 
@@
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets.
-Purchase is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
-Brokers are responsible for building an agreement and handling trading processes between data providers and consumers.
-Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
+Brokers are responsible for building an agreement between data providers and consumers.
+Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
 \end{itemize}
 
-Adopting brokers between providers and consumers has three advantages.
-First, considering the entities could be machines that are not online anytime, brokers can continue the trading process if either side is offline.
+We adopt the brokered infrastructure for three reasons.
+Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system.
+Furthermore, if either side is offline, the proceeding tasks have to stop and start over.
+With brokers, the unfinished work can be cached or accomplished.
 Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
-Brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
+The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
+Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
+With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
 
@@
 \subsection{Launch a Refund}
-\label{section:refund}
 Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
@@
 Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local PoW on Raspberry Pi 3 and remote PoW on Tangle-accelerator.
 However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.

### 2020-07-15 paper.tex

@@
 \subsubsection{Experiment}
-Applying remote PoW greatly reduce the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+Applying remote PoW greatly reduces the elapsed time.
+Channel creation is the next primary barrier for low-level devices to broadcast MAM messages.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
+In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 

### 2020-07-15 paper.tex
Mention ARM-based HW acceleration

@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration}
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}
 

### 2020-07-15 paper.tex
Remove VC description in digital identity

--- 2020-07-15 paper.tex
@@
 We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
-
 \begin{table}[h]
-	\caption{The comparison of centralized and decentralized identity model}
+	\caption{Identity models: centralized vs. decentralized}
 	\label{tab:did}
@@
 
-In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
-The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
-If a VC is verified via issuer's public key, the message will be labelled as trusted.
-Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.in]{DID_VC}
-    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
-    \label{fig:did_vc}
-\end{figure}
-
 In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
@@
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
+During data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.
 

### 2020-07-15 paper.tex
Refactor Chap 3 smart contract

@@
 \subsection{Enable Automated Trading Process}
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{smart_contract_mam_shrink}
-    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.
-For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color.
-The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
-    \label{fig:smart_contract_mam}
-\end{figure}
-
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
-It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines.
-A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
+It provides the smart contract that can make decisions, store data and transfer cryptocurrency.
 All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
@@
 In our system, \textbf{Product Contract} is made for the product launching and trading.
-The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
-Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+The information of data products such as address and DID document address of the data provider, subscription and brokerage fee, MAM channel/endpoint ID (the data entry point), and the broker-certified encryption key are listed on Product Contract.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.
+Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.
 
@@
 One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
-For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
-The consumer list and the states of products are key reputation referenced for data consumers to decide whether to subscribe.
+Preserving a consumer list on Product Contract functions like the reputation of the product, the better the quality the more the consumers he/her has, which are key references for data consumers to decide whether to subscribe.
 

### 2020-07-15 paper.tex
Remove Ethereum introduction

--- 2020-07-15 paper.tex
@@
 \subsection{Enable Automated Trading Process}
-Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
-It provides the smart contract that can make decisions, store data and transfer cryptocurrency.
+Ethereum smart contract can make decisions, store data and transfer cryptocurrency.
 All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
@@
 With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
-In our system, \textbf{Product Contract} is made for the product launching and trading.
-The information of data products such as address and DID document address of the data provider, subscription and brokerage fee, MAM channel/endpoint ID (the data entry point), and the broker-certified encryption key are listed on Product Contract.
+In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures.
+Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream.
+The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.

### 2020-07-15 paper.tex
Remove useless introduction and rewrite the advantage of transparency

@@
 \subsection{Enable Automated Trading Process}
-Ethereum smart contract can make decisions, store data and transfer cryptocurrency.
-All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
-
 With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
@@
 The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.
+
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
 Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.
-
-The transparency of smart contracts bring advantages for data providers and consumers.
-One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
-Preserving a consumer list on Product Contract functions like the reputation of the product, the better the quality the more the consumers he/her has, which are key references for data consumers to decide whether to subscribe.
+Moreover, binding the encryption key with the transparent subscription procedure on Product Contract allows data providers to track and manage the authorized user list, and allows data consumers to always have access after payment, even if the key is lost.
 

### 2020-07-15 paper.tex
Simplify the wording

--- 2020-07-15 paper.tex
@@
 \section{Introduction}
-In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly.
-As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
+As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
 With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
@@
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}.
+In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, we aim for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.
-Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.
-
-% SaaS
-The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage.
-The subscription-based models (e.g.
-SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
-And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
-The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 

### 2020-07-15 paper.tex
Avoid discussing incentive
Refactor Chap 4 MAM

@@
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
-However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
-Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
-Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
-Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
-In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
+However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification.
+A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
+In addition, an automated subscription procedure is also demanded for the sake of data monetization.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
+The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-publish/subscribe, data trading, decentralization, Distributed Ledger Technology
+subscription model, decentralization, data monetization
 \end{IEEEkeywords}
@@
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, we aim for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}.
+In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
-Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
-In current systems, trusted third-party authority like CA is widely adopted to certify each member.
-However, building trust upon CA is dangerous and fragile.
-The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion.
-Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
-The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
-
-Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
+Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
 \begin{itemize}
@@
 	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
-	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
 \end{itemize}
 
-Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
-In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
-See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
+Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
@@
 
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
@@
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.
 
-In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
+Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.
+The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.
 
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1.) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
-2.) \textbf{Integrity}, messages are written on the Tangle network that are not immutable.
-3.) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
-4.) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
+In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, which introduces properties like publishing, classifying and tracking authenticated message streams.
+It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
+2) \textbf{Integrity}, messages written on the Tangle are immutable.
+3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
+4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
 See Fig.~\ref{fig:channel_and_key} for illustration.
 
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
+Using MAM as a data storage benefits from the underlying IOTA network as well as the decentralized and fault-tolerant characteristics, which reduce the risks of centralized storage services.
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
 
-However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
@@
 
-In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
+In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where change logs of DIDs are traceable.
 One can easily prove himself by sharing the identifier on MAM without any authority.
@@
 \label{section:MAM}
-MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
-The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
@@
 The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
-Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+
+The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
 Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data.
+Though combining other distributed storage like IPFS with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
 
@@
 
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
-\subsubsection{A Scalable Keys and Data Entry Points Management}
-The importance of scalable key and data entry points management increases over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Assuming the length of data stream is 7, and each record is encrypted with the same key.
-With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
-
-\subsubsection{Data Sreams Classification}
-The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem.
-
-\subsubsection{A Traceable Data Stream}
-Data traceability is an important security issue that allows users to track the changes of data.
-Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
-MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
-
-\subsection{Delegate MAM operations to Tangle-accelerator}
+\subsection{Delegate MAM operations to Accel}
 \label{section:ta_endpoint}
 MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
@@
     \includegraphics[width=\linewidth]{delegation}
-    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
+    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Accel.}
     \label{fig:delegation}
@@
 However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
+It is risky for an edge device connects to a Accel which is operated by unknown third-party.
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
 Spam would cause subscribers wasting plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
+To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.
 
@@
 To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
-For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
+For those resource-constraint IoT devices, the MAM related operations can be delegated to Accel, as mentioned in Section.~\ref{section:ta_endpoint}.
 And brokers are responsible for Product Contract creation.
@@
 Data consumers can unsubscribe to data products when they're not interested anymore.
-Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structre, since the delete function in Solidity does not remove the actual element but reseting it to default value.
+Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structure, since the delete function in Solidity does not remove the actual element but resetting it to default value.
 When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
@@
 The interactions between data providers and MAM can be frequent.
-Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+Data providers can either uploadd data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
 
 In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and data attachment to endpoints.
-To perform the evaluation assessment, a personal computer (PC, 3.2GHz 64-bit 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (1.2 GHz 64-bit quad-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
+To perform the evaluation assessment, a personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
 
@@
 Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
-On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above.
+On the other hand, the performance of RPi is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above.
 And the performance of PC remains acceptable even \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
+The results indicate that MAM channel/endpoint creation is a laborious job for a RPi when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
 \begin{figure*}[!htb]
@@
 Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
-The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
+The time of RPi distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
 
@@
 
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local PoW on Raspberry Pi 3 and remote PoW on Tangle-accelerator.
-However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
+Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
+Brokers can be PCs or powerful machines that runs Ethereum client and Accel, where Ethereum client is used to interact with Ethereum, and Accel provides PoW acceleration and MAM delegation.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
+However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.
 
@@
 \subsubsection{Experiment}
+PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
 Applying remote PoW greatly reduces the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM messages.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.
 What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps.
+Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
@@
 The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
-	\item Publish final message on IOTA Tangle
-\end{itemize}
+\begin{enumerate}
+    \item Write key information in header
+	\item Write and encrypt input payload
+	\item Publish final message on Tangle
+\end{enumerate}
 
 The steps counted in delegated MAM (E2EE) benchmark including:
-\begin{itemize}
+\begin{enumerate}
 	\item Generate symmetric key for encryption
@@
 	\item Encrypt input payload
-	\item Transmit final message to tangle-accelerator
-\end{itemize}
+	\item Transmit final message to Accel
+\end{enumerate}
+
 \begin{table}[htbp]
-	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+	\caption{Compare the performance between MAM and E2EE on RPi}
     \label{tab:mam_vs_e2ee}
@@
 The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
+Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
+E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
 
@@
 \label{section:conclusion}
-By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
+This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design.
+Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.
 
-Some issues are worth discussing and improving.
-Brokers are the key to operate a stable system.
-However, we do not discuss the conditions that brokers are not responsive during trading process.
-It is worth studying the necessity of adoptin gossip protocol among brokers, which enables other brokers to continue the undone works.
-Search engine is needed to let consumers search and find interested data products, which might need an authority to design and run the service.
+However, this work has a main focus on the subscription-based model and relative experiments. Consequently, the next step is extending the work to:
+\begin{enumerate}
+	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
+	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
+	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
+\end{enumerate}
+
+Finally, a decentralized model enables the data stream trading by shifting risks, and correspondingly, the digital rights of its participants deserve a guarantee, which is provided with the automated system.
 

### 2020-07-15 paper.tex
Cite IPFS

@@
 Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data.
-Though combining other distributed storage like IPFS with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
+Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
 

### 2020-07-15 paper.tex
Consistent use of "Fig" rather than "Figure"
Simplify the statement

--- 2020-07-15 paper.tex
@@
 	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
-	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
 \end{itemize}
@@
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
-Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Fig.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
 

### 2020-07-15 paper.tex

@@
 
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
+Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
 Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local PoW on Raspberry Pi 3 and remote PoW on Tangle-accelerator.
-However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local Pow on Raspberry Pi 3, remote Pow on Tangle-accelerator and E2EE on Raspberry Pi 3.
+However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.
 
@@
 \subsubsection{Experiment}
+PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
 Applying remote PoW greatly reduces the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM messages.
+To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed.
 With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
@@
 The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
+\begin{enumerate}
+    \item Write key information in header
+	\item Write and encrypt input payload
 	\item Publish final message on IOTA Tangle
-\end{itemize}
+\end{enumerate}
 
 The steps counted in delegated MAM (E2EE) benchmark including:
-\begin{itemize}
+\begin{enumerate}
 	\item Generate symmetric key for encryption

### 2020-07-15 paper.tex
Simplify citation

@@
 
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless desig, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
@@
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.
 

### 2020-07-15 paper.tex
Simplify the keywords
Add conclusion for experiement

@@
 The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
+Under our design which delegate MAM operations with Tangle-accelerator and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
+E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
 

### 2020-07-15 paper.tex
Fix typo

--- 2020-07-15 paper.tex
@@
 The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.
+Nevertheless, the works above does not take into account the refund and unsubscribe mechanism of trading model.
 

### 2020-07-15 paper.tex
Revise conclusion

@@
 \label{section:conclusion}
-By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
+This paper aims to proposes a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design.
+Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.
 
-Some issues are worth discussing and improving.
-Brokers are the key to operate a stable system.
-However, we do not discuss the conditions that brokers are not responsive during trading process.
-It is worth studying the necessity of adoptin gossip protocol among brokers, which enables other brokers to continue the undone works.
-Search engine is needed to let consumers search and find interested data products, which might need an authority to design and run the service.
+However, this work has a main focus on the subscription-based model and relative experiment. Therefore, the next step is to extend the work to:
+\begin{enumerate}
+	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
+	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
+	\item develope a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
+\end{enumerate}
 

### 2020-07-15 paper.tex
Fix typo

@@
 \label{section:conclusion}
-This paper aims to proposes a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
 To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design.
@@
 	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
-	\item develope a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
+	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
 \end{enumerate}

### 2020-07-15 paper.tex
fix typo

--- 2020-07-15 paper.tex
@@
 
-Secure Pub-Sub model\cite{SPS}, a brokerless desig, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.

### 2020-07-15 paper.tex
Always use Tangle while referring the network
Refactor Chap 5 launch data product

--- 2020-07-15 paper.tex
@@
 
-Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
-In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
-See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
+Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
@@
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-Nevertheless, the works above does not take into account the refund and unsubscribe mechanism of trading model.
+The decentralized data marketplace \cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.
 
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1.) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
-2.) \textbf{Integrity}, messages are written on the Tangle network that are not immutable.
-3.) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
-4.) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
+In our proposed architecture, we adapt MAM as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
+2) \textbf{Integrity}, messages written on the Tangle are immutable.
+3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
+4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
 See Fig.~\ref{fig:channel_and_key} for illustration.
@@
 
-However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
@@
 
-\subsection{Delegate MAM operations to Tangle-accelerator}
+\subsection{Delegate MAM operations to Accel}
 \label{section:ta_endpoint}
 MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
 Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
@@
 However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
+It is risky for an edge device connects to a Accel which is operated by unknown third-party.
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
 Spam would cause subscribers wasting plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
+To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.
 
-\section{Decentralized Subscription-based Data Trading Case Study}
+\section{Decentralized Subscription-based Data Trading Models}
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.
 
@@
 \subsection{Launch Data Products}
-To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
-For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
-And brokers are responsible for Product Contract creation.
-
-The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, brokers are asked to  record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker, and the overall workflow is shown in Fig.~\ref{fig:launching_product}.
+To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers.
+The Product Contract will not accept subscriptions until brokers certify the encryption key.
+To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers.
+The broker verify the signature with the public key on provider's DID document.
+If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted.
+The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently.
+If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
 Finally, the data product is launched and data providers can start uploading data.
@@
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
+After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
     \label{fig:key_upload}
-\end{figure}
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
 \end{figure}
@@
 Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local Pow on Raspberry Pi 3, remote Pow on Tangle-accelerator and E2EE on Raspberry Pi 3.
+Brokers can be PCs or powerful machines that runs Ethereum client and Accel, where Ethereum client is used to interact with Ethereum, and Accel provides PoW acceleration and MAM delegation.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
 However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.
@@
 To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.
 What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps.
+Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
@@
 	\item Write and encrypt input payload
-	\item Publish final message on IOTA Tangle
+	\item Publish final message on Tangle
 \end{enumerate}
@@
 	\item Encrypt input payload
-	\item Transmit final message to tangle-accelerator
+	\item Transmit final message to Accel
 \end{enumerate}
@@
 \begin{table}[htbp]
-	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+	\caption{Compare the performance between MAM and E2EE on RPi}
     \label{tab:mam_vs_e2ee}
@@
 
-However, this work has a main focus on the subscription-based model and relative experiment. Therefore, the next step is to extend the work to:
+However, this work has a main focus on the subscription-based model and relative experiments. Consequently, the next step is extending the work to:
 \begin{enumerate}
@@
 
+Finally, a decentralized model enables the data stream trading by shifting risks, and correspondingly, the digital rights of its participants deserve a guarantee, which is provided with the automated system.
+
 \bibliographystyle{IEEEtran}

### 2020-07-15 paper.tex
Fix comparison figure and add figure for operation percentage

@@
 
-\section{Decentralized Subscription-based Data Trading Models}
+\section{Decentralized Subscription-based Data Trading Case Study}
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
 
@@
 \subsection{Launch Data Products}
-To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers.
-The Product Contract will not accept subscriptions until brokers certify the encryption key.
-To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers.
-The broker verify the signature with the public key on provider's DID document.
-If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted.
-The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently.
-If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
+For those resource-constraint IoT devices, the MAM related operations can be delegated to Accel, as mentioned in Section.~\ref{section:ta_endpoint}.
+And brokers are responsible for Product Contract creation.
+
+The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, brokers are asked to  record encryption keys to smart contracts.
+To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
+Broker can first verify the signature from data provider with the public key on DID document.
+If it's valid, then the broker uploads the key, otherwise the process will be aborted.
+Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker, and the overall workflow is shown in Fig.~\ref{fig:launching_product}.
 Finally, the data product is launched and data providers can start uploading data.
@@
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
+After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
     \label{fig:key_upload}
+\end{figure}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
 \end{figure}
@@
 \minipage{0.32\textwidth}
-  \includegraphics[width=\linewidth]{mam_send}
-  \caption{The probability distributed function of time cost for sending a message through MAM.}\label{fig:mam_send}
+  \includegraphics[width=\linewidth]{rpi3_pow}
+  \caption{MAM with local PoW \newline vs. MAM with remote PoW \newline vs. Delegated MAM with E2EE}\label{fig:rpi3_pow}  
 \endminipage\hfill
 \minipage{0.32\textwidth}%
-  \includegraphics[width=\linewidth]{rpi3_pow}
-  \caption{Local PoW vs. Remote PoW vs. E2EE}\label{fig:rpi3_pow}
+  \includegraphics[width=\linewidth]{op_share}
+  \caption{The percentage each operation takes in total elapsed time.}\label{fig:op_share}  
 \endminipage
@@
 \subsubsection{Experiment}
-PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
-Applying remote PoW greatly reduces the elapsed time.
-To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed.
+According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
+The result directs a way to improve MAM.
+Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier should be removed.
 With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.

### 2020-07-15 paper.tex
Shorten Raspberry Pi

@@
 Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local Pow on Raspberry Pi 3, remote Pow on Tangle-accelerator and E2EE on Raspberry Pi 3.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote Pow on Tangle-accelerator and E2EE on RPi.
 However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.

### 2020-07-15 paper.tex
Use "Accel" for Tangle-accelerator

@@
 Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote Pow on Tangle-accelerator and E2EE on RPi.
+Brokers can be PCs or powerful machines that runs Ethereum client and Accel, where Ethereum client is used to interact with Ethereum, and Accel provides PoW acceleration and MAM delegation.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
 However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.
@@
 The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
-Under our design which delegate MAM operations with Tangle-accelerator and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
+Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
 E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.

### 2020-07-15 paper.tex
Refactor Chap 5 and rewrite refund

@@
 
-\section{Decentralized Subscription-based Data Trading Case Study}
+\section{Decentralized Subscription-based Data Trading Models}
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.
 
@@
 \subsection{Launch Data Products}
-To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
-For those resource-constraint IoT devices, the MAM related operations can be delegated to Accel, as mentioned in Section.~\ref{section:ta_endpoint}.
-And brokers are responsible for Product Contract creation.
-
-The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, brokers are asked to  record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker, and the overall workflow is shown in Fig.~\ref{fig:launching_product}.
+To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers.
+The Product Contract will not accept subscriptions until brokers certify the encryption key.
+To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers.
+The broker verify the signature with the public key on provider's DID document.
+If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted.
+The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently.
+If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
 Finally, the data product is launched and data providers can start uploading data.
@@
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it.
 
@@
 \subsection{Unsubscribe to Data Products}
-Data consumers can unsubscribe to data products when they're not interested anymore.
-Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structure, since the delete function in Solidity does not remove the actual element but resetting it to default value.
-When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
-The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
-
-In SaaS, the cancellation fee is a way to make sure the service providers are protected.
-It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
-However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
-
-Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
-The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage.
+However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied.
+Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data.
+The new key should be updated for the remaining subscribers.
 \begin{align}
-\label{equation:unsubscribe}
-    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \\
-    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \\
-    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
+    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
+    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
 \end{align}
@@
 \label{section:refund}
-Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
-Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
-When the refund procedure is launched, all consumers vote to decide whether the refund is established.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following.
+The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section.
+As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee.
+However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
+Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
+If they can't reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
+Third, the refund could launch by providers when they can't maintain products as committed.
 

### 2020-07-15 paper.tex
Simplify the use of MAM

--- 2020-07-15 paper.tex
@@
 
-In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
+Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
-The decentralized data marketplace \cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
 Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adapt MAM as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
+In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, which introduces properties like publishing, classifying and tracking authenticated message streams.
+It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
 2) \textbf{Integrity}, messages written on the Tangle are immutable.
@@
 
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
+Using MAM as a data storage benefits from the underlying IOTA network as well as the decentralized and fault-tolerant characteristics, which reduce the risks of centralized storage services.
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
@@
 \subsubsection{A Traceable Data Stream}
-Data traceability is an important security issue that allows users to track the changes of data.
-Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+It allows users to track the changes of data.
+The hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it is not straightforward to point out the differences between versions.
 MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

### 2020-07-15 paper.tex
Reorganize key exchange figure
Add Gas evaluation

@@
 \label{section:evaluation}
-We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
-2) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+2) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
+
+\subsection{Gas usage of the Product Contract}
+We investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix.
+On top of this evaluation, data providers can consider how to set the subscription and brokereage fee to eventually generate profits.
+The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, we analyze with a fixed range of Gas price.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+
+\begin{table}[h]
+	\caption{Transaction fees for each participant}
+	\label{tab:gas}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{participant} & \textbf{Gas used} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
+		\hline
+		provider & 166203 & 0.288 & 1.048 \\ 
+		broker & 2733985 & 4.750 & 17.243 \\ 
+		consumer & 83572 & 0.145 & 0.527  \\ 
+		\hline
+	\end{tabular}
+\end{table}
 

### 2020-07-15 paper.tex
Refactor MAM evaluations

@@
 \label{section:mam_performance}
-It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
-Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle.
-Therefore, in the following evaluations, all devices run with client library only.
-
-MAM is a secure and validatable data storage of the proposed architecture.
-And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections.
-The interactions between data providers and MAM can be frequent.
-Data providers can either uploadd data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-
-In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and data attachment to endpoints.
+In the following evaluations, all devices run with IOTA client library instead of IOTA full nodes.
+MAM is the primary key to resolve all the storage difficulties discussed in previous sections.
+The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment.
 To perform the evaluation assessment, a personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
@@
 \subsubsection{Channel / Endpoint Creation}
-The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint.
-A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total.
-The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required.
+The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint.
+The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power is required.
 In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
@@
 The time duration for each \textit{height} is the average time of running 100 rounds.
-Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
-On the other hand, the performance of RPi is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above.
-And the performance of PC remains acceptable even \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for a RPi when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
+Since the workflow of channel and endpoint creation are identical, the curves of the same hardware are almost matched.
+On the other hand, the elapsed time of RPi is grows rapidly when \textit{height} is 5 or above.
+And the elapsed time of PC remains acceptable even the \textit{height} gets to 7.
+The results indicate that MAM channel/endpoint creation is a laborious job for RPi when data providers need a longer channel/endpoint, which can considered delegating to Accel.
 \begin{figure*}[!htb]
@@
 \subsubsection{Messages Publishment}
-Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
-\begin{itemize}
-	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
-	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
-\end{itemize}
+Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes: 1.) \textbf{Tips selection}: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify.
+The tips are provided by IOTA full nodes.
+2.) \textbf{Proof-of-Work (PoW)}: An algorithm which prevents Denial of Service and spam attacks on a network.
 
 Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
-The time of RPi distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
-
-The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
-Furthermore, sensors with the low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM and even trading process with subscribers simultaneously.
-
-Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Accel, where Ethereum client is used to interact with Ethereum, and Accel provides PoW acceleration and MAM delegation.
+The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has huge impact.
+The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
+Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such framework.
 Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
@@
 \label{section:smart_contract_evaluation}
-
 \subsubsection{Experiment}

### 2020-07-15 paper.tex

--- 2020-07-15 paper.tex
@@
     \centering
-    \includegraphics[width=3.5in]{key_exchange}
+    \includegraphics[width=3.5in]{key_exchange_reorganize}
     \caption{Encryption key exchange process.}

### 2020-07-15 paper.tex

@@
 The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
-Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+
+The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
-Fig.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data.
+Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
 
@@
 Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.
-
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
-\subsubsection{A Scalable Keys and Data Entry Points Management}
-The importance of scalable key and data entry points management increases over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Assuming the length of data stream is 7, and each record is encrypted with the same key.
-With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
-
-\subsubsection{Data Sreams Classification}
-The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem.
-
-\subsubsection{A Traceable Data Stream}
-It allows users to track the changes of data.
-The hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it is not straightforward to point out the differences between versions.
-MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
 

### 2020-07-16 paper.tex
Mention Tangle for the network of IOTA. Mention IOTA for the ecosystem

@@
 Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer.
 The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, which introduces properties like publishing, classifying and tracking authenticated message streams.
+In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams.
 It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
@@
 
-However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy.
+However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM requires lots of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy.
 The details would be further illustrated in Section.\ref{section:ta_endpoint}.
@@
 
-In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where change logs of DIDs are traceable.
+In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where audit logs of DIDs are traceable.
 One can easily prove himself by sharing the identifier on MAM without any authority.
@@
 \subsection{The Message Streams}
-A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
+A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload.
 To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
-The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
+The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle, represents the ownership of all things associated with the user in the IOTA ecosystem.
 
@@
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
+MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating system.
 To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
@@
 According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Note that data uploading is only related to MAM operations on the Tangle without transaction fee.
 Therefore, the Gas estimation only includes trading processes.
 The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
 

### 2020-07-16 paper.tex
Tweak wording

@@
 Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
-If they can't reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
-Third, the refund could launch by providers when they can't maintain products as committed.
+If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
+Third, the refund could launch by providers when they fail to maintain products as committed.
 
@@
 We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
-2) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
+2) Evaluate the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data provider.
 
@@
 Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
-However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.
+However, MAM operations are fairly time-consuming, and improving the performance of MAM is an essential issue that needs to be done for the next step.
 
@@
 
-However, this work has a main focus on the subscription-based model and relative experiments. Consequently, the next step is extending the work to:
+Our work has a main focus on the subscription-based model and relative experiments. And the next step is extending it to:
 \begin{enumerate}
-	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
-	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
-	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
+	\item reduce the use of Gas in key-agreement protocol and consider the possibility of the zero-knowledge proof to lower transaction costs;
+	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
+	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
 \end{enumerate}

### 2020-07-16 paper.tex
Clarify the privacy concerns

@@
 	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
-	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
+	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality, without violating the privacy.
 \end{enumerate}

### 2020-07-28 paper.tex
Add more description of not using IPFS

--- 2020-07-16 paper.tex
@@
 \title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
-% Chinese title: 針對物聯網資料交易的去中心化基礎建設
+% Chinese title: 針對物聯網訂閱型資料交易的去中心化基礎建設
 
-\author{
-\IEEEauthorblockN{Anonymous}
-\IEEEauthorblockA{
-         \textit{Anonymous Organization}\\
-        ***@***.***}
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%jkrvivian@gmail.com}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%jserv@ccns.ncku.edu.tw}
-%\and
-%\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%chiaheng@gmail.com}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
+\IEEEauthorblockA{\textit{dept. of CSIE} \\
+\textit{National Cheng Kung University}\\
+Tainan City, Taiwan (R.O.C.) \\
+jkrvivian@gmail.com}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
+\IEEEauthorblockA{\textit{dept. of CSIE} \\
+\textit{National Cheng Kung University}\\
+Tainan City, Taiwan (R.O.C.) \\
+jserv@ccns.ncku.edu.tw}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
+\IEEEauthorblockA{\textit{dept. of CSIE} \\
+\textit{National Cheng Kung University}\\
+Tainan City, Taiwan (R.O.C.) \\
+chiaheng@gmail.com}
 }
@@
 %cite IoT data subscription economy
-On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set.
+The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
+The real-time data exchange among devices are periodical that only data in a specific time period is interested.
+Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
+Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
-However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification.
-A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
-In addition, an automated subscription procedure is also demanded for the sake of data monetization.
-In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
+However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
+Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
+Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
+Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
+The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-subscription model, decentralization, data monetization
+publish/subscribe, data trading, decentralization, Distributed Ledger Technology
 \end{IEEEkeywords}
@@
 \section{Introduction}
-As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
+In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly.
+As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
 With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
@@
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}.
+In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.
+Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.
+
+% SaaS
+The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage.
+The subscription-based models (e.g.
+SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
+And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
+The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
+In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 
@@
 In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
-Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
+Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
+In current systems, trusted third-party authority like CA is widely adopted to certify each member.
+However, building trust upon CA is dangerous and fragile.
+The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion.
+Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
+Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
+The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
+
+Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
 \begin{itemize}
@@
 	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
+	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
 \end{itemize}
 
-Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
+Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
+In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
+See Fig.~\ref{fig:system_design}.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+
+\subsection{Contributions}
+The contributions in the paper are summarized as follow:
+\begin{itemize}
+	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
+	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
+	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
+	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
+\end{itemize}
+
+\subsection{Paper Organization}
+The rest of this paper is organized as follows.
+In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
+In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
+In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
+In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
+The analysis results are given in Section~\ref{section:evaluation}.
+Finally, we conclude the paper in Section~\ref{section:conclusion}.
 
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-The data validation and traceability are achieved via Ethereum smart contract.
-But data is plaintext on blockchain that the system is not appropriate for sensitive data.
+With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
+But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
 
-Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
+In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
+The subscribers request publisher directly and ask them to save a cache space for interested data.
+The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
+Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
+Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-Yet, without brokers, participants may need to reveal more sensitive information in order to communicate.
-By Paolo Missier et.
+The reputation system and the punishment rules against malicious acts of subscribers and publishers.
+Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
+Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
+
+The previous works contribute to different aspects of building a reliable pub/sub system over blockchain.
+However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.
+
+\subsection{Trusted IoT Trading Infrastructure}
+Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
 al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.
+Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
+However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
 
-Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer.
-The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.
+A.
+Colman et al.
+\cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
+
+In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
+Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
+Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
+This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
+Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
+
+Researches below adopt MAM as data storage and a secure data transmission layer.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
+Service requesters call for proposal of interested data and accept/reject proposals from service providers.
+After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
+This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
+Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
+
+O.
+Lamtzidis and J.
+Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
+The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
+Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
+The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
+And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
+
+\subsection{Distributed Storage System}
+\label{section:distributed_storage}
+Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
+Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
+
+Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
+IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
+Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
+However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
+Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents.
+Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.
+
+Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
+Files are duplicated in multiple nodes to prevent data loss.
 
@@
 \subsection{Data subscription-based trading platform players}
-There are three major participants, data providers, data consumers and brokers in our proposed architecture.
+There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+As shown in Fig.~\ref{fig:pub_sub_model}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{pub_sub_model}
+    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
+    \label{fig:pub_sub_model}
+\end{figure}
 
@@
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets.
-Purchase is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
-Brokers are responsible for building an agreement and handling trading processes between data providers and consumers.
-Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
+Brokers are responsible for building an agreement between data providers and consumers.
+Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
 \end{itemize}
 
-Adopting brokers between providers and consumers has three advantages.
-First, considering the entities could be machines that are not online anytime, brokers can continue the trading process if either side is offline.
+We adopt the brokered infrastructure for three reasons.
+Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system.
+Furthermore, if either side is offline, the proceeding tasks have to stop and start over.
+With brokers, the unfinished work can be cached or accomplished.
 Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
-Brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
+The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
+Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
+With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
 
-\begin{figure}[h]
+\begin{figure*}[!t]
     \centering
-    \includegraphics[width=3.5in]{channel_and_key_fold}
+    \includegraphics[width=\linewidth]{channel_and_key}
     \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams.
-It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
-2) \textbf{Integrity}, messages written on the Tangle are immutable.
-3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
-4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
+In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
+MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
+Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
+One can easily prove himself by sharing the identifier on MAM without any authority.
+
+In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
+
+\begin{itemize}
+    \item \textbf{Scalability}:
+	\begin{itemize}
+		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
+    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
+    \end{itemize}    
+    \item \textbf{Integrity}: 
+	\begin{itemize}    	
+        \item Messages published to the Tangle are tamper-proof that against malicious modification.
+    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
+    \end{itemize}
+    \item \textbf{Confidentiality}:
+    \begin{itemize}    	
+    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
+    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
+    	\item MAM provides forward-secrecy.
+The entry points of future data can be derived, but it's impossible to trace back those in the past.
+This feature prevents adversaries from retrieving published history even if the key is revealed.
+    \end{itemize}
+\end{itemize}
+
+MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
+The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle.
+This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source.
 See Fig.~\ref{fig:channel_and_key} for illustration.
 
-Using MAM as a data storage benefits from the underlying IOTA network as well as the decentralized and fault-tolerant characteristics, which reduce the risks of centralized storage services.
+Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
 Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-
-However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM requires lots of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy.
-The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
@@
 We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
+
 \begin{table}[h]
-	\caption{Identity models: centralized vs. decentralized}
+	\caption{The comparison of centralized and decentralized identity model}
 	\label{tab:did}
@@
 
-In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where audit logs of DIDs are traceable.
+In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
+The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
+If a VC is verified via issuer's public key, the message will be labelled as trusted.
+Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.in]{DID_VC}
+    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
+    \label{fig:did_vc}
+\end{figure}
+
+In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
 One can easily prove himself by sharing the identifier on MAM without any authority.
@@
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.
+During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
+See Fig.~\ref{fig:TangleID}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{TangleID}
+    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
+The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
+When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
+The data provider can then retrieve the consumer's public key and encrypt the content with it.
+After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
+    \label{fig:TangleID}
+\end{figure}
 
 \subsection{Enable Automated Trading Process}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=4in]{smart_contract_mam}
+    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
+Participants can easily retrieve information via Product Contract and proceed trading.
+For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color.
+The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
+    \label{fig:smart_contract_mam}
+\end{figure*}
+
+Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
+It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines.
+A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
+All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
+
 With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
-In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures.
-Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream.
-The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.
+In our system, \textbf{Product Contract} is made for the product launching and trading.
+The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
+Listing.
+\ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
+Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.
 
-Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.
-Moreover, binding the encryption key with the transparent subscription procedure on Product Contract allows data providers to track and manage the authorized user list, and allows data consumers to always have access after payment, even if the key is lost.
+The transparency of smart contracts bring advantages for data providers and consumers.
+One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
+For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
+The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
+
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
+contract Product {
+    address public broker;
+    address public provider;
+    bool isBrokerWithdraw;
+    bool isProviderWithdraw;
+    address[] consumers;
+
+    struct Purchase {
+        bool affirmativeVote;
+        bool isConsumerWithdraw;
+        bool isKeyAdded;
+        bool isSubscribe;
+        string encryptKey;
+    }
+    mapping(address => Purchase) public consumer2Purchase;
+
+    uint public price;
+    uint public totalAmount;
+    uint public brokerage;
+    uint public cancellation;
+    uint public threshold;
+    string public channelRoot;
+    string public endPoint;
+    uint public totalNumber;
+    uint public uploadedNumber;
+    uint public affirmativeVotes;
+    string hashedKey;
+    string certifiedKey;
+
+    enum State {Launched, KeyCertified, Finished, Refunded}
+    State public state;
+}
+\end{lstlisting}
+
+\subsection{Enable computation tasks delegation to broker with privacy}
+To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
+However, the resources of low-level devices are precious which should be used to focus on its jobs.
+Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
+
+The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
+To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
+Broker can first verify the signature from data provider with the public key on DID document.
+If it's valid, then the broker uploads the key, otherwise the process will be aborted.
+Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{key_upload}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
+After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
+    \label{fig:key_upload}
+\end{figure}
+
+As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
+The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
@@
 \label{section:MAM}
+MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
+The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
@@
 \subsection{The Message Streams}
-A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload.
+A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
 To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
-The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle, represents the ownership of all things associated with the user in the IOTA ecosystem.
-
-The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
+Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
 Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
-Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data.
-Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
 
@@
 
-\subsection{Delegate MAM operations to Accel}
+\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
+%scalability
+\subsubsection{A Scalable Keys and Data Entry Points Management}
+The importance of scalable key and data entry points management increases over time.
+In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
+Assuming the length of data stream is 7, and each record is encrypted with the same key.
+With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
+
+\begin{table}[htbp]
+	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
+	\label{tab:mam_scalability}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
+		\hline
+		keys & 1 & 1 \\ 
+		\hline
+		entry points & 1 & 7 \\ 
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+%classify
+\subsubsection{Data Sreams Classification}
+The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
+For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem.
+
+%data trace
+\subsubsection{A Traceable Data Stream}
+Data traceability is an important security issue that allows users to track the changes of data.
+Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
+
+\subsection{Delegate MAM operations to Tangle-accelerator}
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
-Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
+MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{ta_structure}
+    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
+It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed.
+Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
+    \label{fig:ta_struct}
+\end{figure}
 
@@
     \includegraphics[width=\linewidth]{delegation}
-    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Accel.}
+    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
     \label{fig:delegation}
 \end{figure}
+
+\subsubsection{Communication Protocol}
+In the following sections, we refer the low-level devices as \textbf{endpoint}s.
+MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic.
+The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth.
+The pub/sub model decouples publishers and subscribers in many ways:
+
+\begin{itemize}
+    \item Space decoupling: Both publishers and subscribers don't need to know each other.
+    \item Time decoupling: Publishers and subscribers do not need to be active at the same time.
+    \item Synchronization decoupling: Operations are decoupled from the publishers and subscribers.
+The publishers do not need to be alive until the response arrives.
+Messages from publisher can be served as send-and-forget fashion.
+\end{itemize}
 
@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
 
-\subsubsection{Time Complexity}
-In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature.
-In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length.
-HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
-Therefore, the E2EE protocol takes only linear time versus arbitrary string length.
+\subsubsection{Register with Tangle-accelerator}
+User with channel seed can acquire channel chain ownership.
+Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
+Once tangle-accelerator receive the Seed from edge device, it would return a unique user identifier which can be mapping to corresponding Seed when edge devices send requests.
+Asymmetric encryption is utilizing during the process of exchanging seed.
+Digital signature should be taken at the same time to ensure data integrity.
+Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
+Thus, seed will not be exposed during communication after an edge device is successfully registered.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service.
-It dramatically reduces execution time encryption takes.
-However, there are some challenges in the E2EE process.
+E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
+
+\paragraph{Linear Time to Read Message}
+It is linear time to decrypt message instead of constant time.
+Nevertheless, there is one way to speed up the message decryption process.
+A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
+This procedure can reduce the time spending on internet communication.
+
+\paragraph{Spam on Message Channel Chain}
 Tampering the messages which have conducted E2EE would be a challenging mission.
 However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a Accel which is operated by unknown third-party.
+It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
 Spam would cause subscribers wasting plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.
+To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
 
-\section{Decentralized Subscription-based Data Trading Models}
+\section{Decentralized Subscription-based Data Trading Case Study}
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
 
@@
 \subsection{Launch Data Products}
-To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers.
-The Product Contract will not accept subscriptions until brokers certify the encryption key.
-To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers.
-The broker verify the signature with the public key on provider's DID document.
-If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted.
-The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently.
-If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
+For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
+And brokers are responsible for Product Contract creation.
+
+The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
+This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
+The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
 Finally, the data product is launched and data providers can start uploading data.
-\begin{figure}[h]
+
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
-    \label{fig:key_upload}
+    \includegraphics[width=2.5in]{launching_product}
+    \caption{The process of launching a product.}
+    \label{fig:launching_product}
 \end{figure}
+
+\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
+    function addHashedKey(
+        string memory _hashedKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add hashed key."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        hashedKey = hashedKey;
+        emit newHashedKey(hashedKey);
+    }
+
+    function addCertifiedKey(
+        string memory _certifiedKey
+    ) public {
+        require(
+            msg.sender == broker,
+            "Only broker can add certifiedKey."
+        );
+        require(
+            state == State.Launched,
+            "One key has been certified."
+        );
+        certifiedKey = _certifiedKey;
+        state = State.KeyCertified;
+        emit newCertifiedKey(certifiedKey);
+    }
+\end{lstlisting}
 
@@
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
 
@@
     \centering
-    \includegraphics[width=3.5in]{key_exchange_reorganize}
+    \includegraphics[width=3.5in]{key_exchange}
     \caption{Encryption key exchange process.}
@@
 
+\lstdefinestyle{solidity}{
+	captionpos=b,
+	tabsize=4,
+	basicstyle=\scriptsize
+}
+\lstset{style=solidity}
+
+\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
+    function addEncryptKey(
+        address _consumer,
+        string memory _encryptKey
+    ) public {
+        require(
+            msg.sender == provider,
+            "Only provider can add the encrypted key."
+        );
+        require(
+            consumer2Purchase[_consumer].isKeyAdded == false,
+            "Encryption key has been added."
+        );
+        consumer2Purchase[_consumer].encryptKey = _encryptKey;
+        consumer2Purchase[_consumer].isKeyAdded = true;
+        emit newEncryptKey(_consumer, _encryptKey);
+    }
+\end{lstlisting}
+
 \subsection{Unsubscribe to Data Products}
-When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
-In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage.
-However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied.
-Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data.
-The new key should be updated for the remaining subscribers.
-\begin{align}
-    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
-    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
-    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
-\end{align}
-\subsection{Refund}
-\label{section:refund}
-The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section.
-As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee.
-However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
-Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
-If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
-Third, the refund could launch by providers when they fail to maintain products as committed.
+Data consumers can unsubscribe to data products when they're not interested anymore.
+Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structre, since the delete function in Solidity does not remove the actual element but reseting it to default value.
+When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
+The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+
+In SaaS, the cancellation fee is a way to make sure the service providers are protected.
+It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
+However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
+
+Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
+The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
+
+\begin{equation}
+\label{equation:unsubscribe_provider}
+    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_broker}
+    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+\label{equation:unsubscribe_consumer}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{unsubscribe}
+    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
+Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
+    \label{fig:unsubscribe}
+\end{figure}
+
+\subsection{Launch a Refund}
+Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
+Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
+When the refund procedure is launched, all consumers vote to decide whether the refund is established.
+See Fig.~\ref{fig:refund}.
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
+
+\begin{equation}
+    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
+\end{equation}
+
+\begin{equation}
+    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.5in]{refund}
+    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
+Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \label{fig:refund}
+\end{figure}
 
@@
 \label{section:evaluation}
-We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
-2) Evaluate the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data provider.
-
-\subsection{Gas usage of the Product Contract}
-We investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix.
-On top of this evaluation, data providers can consider how to set the subscription and brokereage fee to eventually generate profits.
-The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, we analyze with a fixed range of Gas price.
-According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-Note that data uploading is only related to MAM operations on the Tangle without transaction fee.
-Therefore, the Gas estimation only includes trading processes.
-The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
-Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-
-\begin{table}[h]
-	\caption{Transaction fees for each participant}
-	\label{tab:gas}
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{participant} & \textbf{Gas used} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
-		\hline
-		provider & 166203 & 0.288 & 1.048 \\ 
-		broker & 2733985 & 4.750 & 17.243 \\ 
-		consumer & 83572 & 0.145 & 0.527  \\ 
-		\hline
-	\end{tabular}
-\end{table}
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
+2) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
 
@@
 \label{section:mam_performance}
-In the following evaluations, all devices run with IOTA client library instead of IOTA full nodes.
-MAM is the primary key to resolve all the storage difficulties discussed in previous sections.
-The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment.
-To perform the evaluation assessment, a personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
+It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
+Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle.
+Therefore, in the following evaluations, all devices run with client library only.
+
+MAM is a secure and validatable data storage of the proposed architecture.
+And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections.
+The interactions between data providers and MAM can be frequent.
+Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+
+In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and data attachment to endpoints.
+To perform the evaluation assessment, a personal computer (PC, 3.2GHz 64-bit 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (1.2 GHz 64-bit quad-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
 
 \subsubsection{Channel / Endpoint Creation}
-The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint.
-The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power is required.
+The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint.
+A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total.
+The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required.
 In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
+The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}.
+The time duration for each \textit{height} is the average time of running 100 rounds.
 
-Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation.
-The time duration for each \textit{height} is the average time of running 100 rounds.
-Since the workflow of channel and endpoint creation are identical, the curves of the same hardware are almost matched.
-On the other hand, the elapsed time of RPi is grows rapidly when \textit{height} is 5 or above.
-And the elapsed time of PC remains acceptable even the \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for RPi when data providers need a longer channel/endpoint, which can considered delegating to Accel.
-\begin{figure*}[!htb]
-\minipage{0.32\textwidth}
-  \includegraphics[width=\linewidth]{mam_create}
-  \caption{Time cost of MAM creation.}\label{fig:mam_create}
-\endminipage\hfill
-\minipage{0.32\textwidth}
-  \includegraphics[width=\linewidth]{rpi3_pow}
-  \caption{MAM with local PoW \newline vs. MAM with remote PoW \newline vs. Delegated MAM with E2EE}\label{fig:rpi3_pow}  
-\endminipage\hfill
-\minipage{0.32\textwidth}%
-  \includegraphics[width=\linewidth]{op_share}
-  \caption{The percentage each operation takes in total elapsed time.}\label{fig:op_share}  
-\endminipage
-\end{figure*}
+\begin{table}[htbp]
+	\caption{Time measurement of channel creation}
+	\label{tab:channel_create}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
+		\hline
+		1 & 0.26183 & 2.908702 \\ 
+		2 & 0.524076 & 5.805524 \\ 
+		3 & 1.045942 & 11.555660 \\ 
+		4 & 2.092989 & 23.178036 \\ 
+		5 & 4.19515 & 46.164079\\ 
+		6 & 8.361586 & 92.320173\\ 
+		7 & 16.651607 & 185.292243\\
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Time measurement of endpoint creation}
+	\label{tab:endpoint_create}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
+		\hline
+		1 & 0.256425 & 2.887064 \\ 
+		2 & 0.505679 & 5.767912 \\ 
+		3 & 0.999524 & 11.550455 \\ 
+		4 & 1.994017 & 23.260508 \\ 
+		5 & 3.965007 & 46.748366 \\ 
+		6 & 7.918925 & 93.182975 \\ 
+		7 & 16.561419 & 186.064562 \\
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
+
+The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}.
+Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
+On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above.
+And the performance of PC remains acceptable even \textit{height} gets to 7.
+The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{mam_create}
+    \caption{Time cost of MAM creation.}
+    \label{fig:mam_create}
+\end{figure}
 
 \subsubsection{Messages Publishment}
-Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes: 1.) \textbf{Tips selection}: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify.
-The tips are provided by IOTA full nodes.
-2.) \textbf{Proof-of-Work (PoW)}: An algorithm which prevents Denial of Service and spam attacks on a network.
+Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
+\begin{itemize}
+	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
+	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
+\end{itemize}
 
 Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has huge impact.
-The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
-Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such framework.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
-However, MAM operations are fairly time-consuming, and improving the performance of MAM is an essential issue that needs to be done for the next step.
+Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
+The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.in]{mam_send}
+    \caption{The probability distributed function of time cost for sending a message through MAM.}
+    \label{fig:mam_send}
+\end{figure}
+
+The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
+Furthermore, sensors with the low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM and even trading process with subscribers simultaneously.
+
+Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
+Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator.
+However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3.5in]{rpi3_pow}
+    \caption{Local PoW vs. Remote PoW}
+    \label{fig:rpi3_pow}
+\end{figure}
 
@@
 \label{section:smart_contract_evaluation}
+
 \subsubsection{Experiment}
-According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
-The result directs a way to improve MAM.
-Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier should be removed.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps.
+Applying remote PoW greatly reduce the elapsed time.
+Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
-In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
+The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 
 The steps counted in MAM benchmark including:
-\begin{enumerate}
-    \item Write key information in header
-	\item Write and encrypt input payload
-	\item Publish final message on Tangle
-\end{enumerate}
+\begin{itemize}
+	\item Encrypt input payload
+	\item Publish final message on IOTA Tangle
+\end{itemize}
 
-The steps counted in delegated MAM (E2EE) benchmark including:
-\begin{enumerate}
+The steps counted in E2EE benchmark including:
+\begin{itemize}
 	\item Generate symmetric key for encryption
@@
 	\item Encrypt input payload
-	\item Transmit final message to Accel
-\end{enumerate}
+	\item Transmit final message to tangle-accelerator
+\end{itemize}
 
 \begin{table}[htbp]
-	\caption{Compare the performance between MAM and E2EE on RPi}
+	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
     \label{tab:mam_vs_e2ee}
-    \centering
+    \resizebox{0.5\textwidth}{!}{
         \begin{tabular}{|c||c|c|}
@@
         \end{tabular}
+    }
 \end{table}
 
-\begin{align}
-    y &= 0.0126 x+19.979 \label{lin_mam} \\
-    y &= 0.0002 x+9.174 \label{lin_e2ee}
-\end{align}
+It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
 
-Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods.
-Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively.
-The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
-The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
-Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
-E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
+\begin{equation}
+    \label{eq:lin_mam}
+    y=0.0126 x+19.979  
+\end{equation}
 
-\section{Conclusion and Future Work}
+\begin{equation}
+    \label{eq:lin_e2ee}
+    y=0.0002 x+9.174
+\end{equation}
+
+The Eq.~\ref{eq:lin_mam} and Eq.~\ref{eq:lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
+Apparently, the slope of the result of MAM is much greater than the result of E2EE.
+The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.
+
+\subsubsection{Time Complexity}
+With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
+Applying mature cryptographic functions (e.g.
+SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
+
+\subsection{Smart Contract}
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
+The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+The Gas usage estimation is shown in Table.~\ref{tab:gas}.
+
+\begin{table*}[h]
+	\caption{Gas consumption for each function of Product Contract}
+	\label{tab:gas}
+	\resizebox{0.5\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
+		\hline
+		generate contract & broker & 2558980 \\ 
+		subscribe product & consumer & 72259 \\ 
+		upload hashed key & provider & 68276  \\ 
+		upload encryption key to consumer & provider & 86614 \\ 
+		upload certified key & broker & 131535 \\
+		update amount of uploaded data & broker & 32157 \\
+		unsubscribe & consumer & 8234 \\
+		request refund & consumer & 12067 \\
+		withdraw & broker & 11313 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
+Therefore, the Gas estimation only includes trading processes.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Storage on blockchain is expensive.
+For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
+However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+However, using zero-knowledge protocol is out of the scope of this paper.
+
+Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
+We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+
+\begin{equation}
+\label{equa:ether_calculation}
+Ethers = Gas \ Price \times Gas \ Amount
+\end{equation}
+
+When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
+Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
+Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
+
+\begin{table*}[h]
+	\caption{Data Price Estimation}
+	\label{tab:ether}
+	\centering
+	\resizebox{0.8\textwidth}{!}{
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
+		\hline
+		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
+		\hline
+		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
+		\hline
+		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
+		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
+		\hline
+		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
+		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
+		\hline
+	\end{tabular}
+	}
+\end{table*}
+
+\section{Conclusions}
 \label{section:conclusion}
-This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
-To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design.
-Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem.
-Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
-In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.
+By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
+It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
 
-Our work has a main focus on the subscription-based model and relative experiments. And the next step is extending it to:
-\begin{enumerate}
-	\item reduce the use of Gas in key-agreement protocol and consider the possibility of the zero-knowledge proof to lower transaction costs;
-	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
-	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
-\end{enumerate}
+In the subscription-based data trading, there are some issues that worth discussing and improving.
+Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
+Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
+Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
+However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
 
-Finally, a decentralized model enables the data stream trading by shifting risks, and correspondingly, the digital rights of its participants deserve a guarantee, which is provided with the automated system.
+Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
 

### 2020-07-28 paper.tex
Explain the privacy protection by exchanging key with Product Contract

@@
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.
+Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
 

### 2020-07-28 paper.tex
Reduce the description of Chap4 MAM

@@
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
-Assuming the length of data stream is 7, and each record is encrypted with the same key.
-With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
-
-\begin{table}[htbp]
-	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
-	\label{tab:mam_scalability}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
-		\hline
-		keys & 1 & 1 \\ 
-		\hline
-		entry points & 1 & 7 \\ 
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
+To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
 
 %classify
-\subsubsection{Data Sreams Classification}
+\subsubsection{Data Sreams Classification and Traceability}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem.
-
-%data trace
-\subsubsection{A Traceable Data Stream}
-Data traceability is an important security issue that allows users to track the changes of data.
-Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
-MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
+For instance, sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
 

### 2020-07-28 deprecated.tex
Add broker and refund description

@@
 The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
+
+\section{MAM: traceability}
+
+Data traceability is an important security issue that allows users to track the changes of data.
+Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

### 2020-07-28 paper.tex
Add broker and refund description

@@
 Brokers are responsible for building an agreement between data providers and consumers.
-Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
+Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
 \end{itemize}
@@
 The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
-With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
+Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
 
@@
 
-\section{Decentralized Subscription-based Data Trading Case Study}
+\section{Decentralized Subscription-based Data Trading Models}
 \label{section:trading_model}
@@
 
+However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
+Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
+Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
+If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
+Third, the refund could launch by providers when they fail to maintain products as committed.
+
 \section{Evaluations}

### 2020-07-28 paper.tex
Fix grammar

@@
 And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
-The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
+The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
+In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depend on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 
@@
 In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
-Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
+Proving the identity as well as the ownership of data are challenging issues among various roles in a large scale platform.
 In current systems, trusted third-party authority like CA is widely adopted to certify each member.
@@
 
-Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
+Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
 \begin{itemize}
@@
 	\item \textbf{Confidentiality}. 
-1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
+1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.	
 	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
@@
 See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
@@
 \begin{itemize}
-	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
+	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
 	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
@@
 \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components aiming for different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
 While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
@@
 Data providers are the ones that generate streaming data and set the data price based on the different types of data.
-With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
+Subscription fees can motivate data providers to maintain and improve the quality of data.
 \item \textbf{Data Consumer: }
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch and it is also difficult to find desired data sets, purchase is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
@@
     \includegraphics[width=\linewidth]{channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
+    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures.
 Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
@@
 \subsection{Digital Identity}
-The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
+The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
 We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
@@
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
+Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
@@
 For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color.
-The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
+The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
     \label{fig:smart_contract_mam}
@@
 One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
-For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
-The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
+For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.
 
@@
 To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the resources of low-level devices are precious which should be used to focus on its jobs.
+However, the limited resources of low-level devices should be used on its jobs instead of handling all trading processes.
 Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
@@
 Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
+If it's valid, then the broker uploads the key; otherwise the process will be aborted.
+Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
+This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription.
 Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
@@
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
+After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
     \label{fig:key_upload}
@@
 See Fig.~\ref{fig:refund}.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
 
@@
     \includegraphics[width=1.5in]{refund}
-    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
-Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \caption{Once a data consumer launch a refund vote, all consumers start voting to decide whether they want a refund.
+Finally, the establishment of refund is determined by Product Contract after checking the number of votes is larger than a threshold or not.}
     \label{fig:refund}

### 2020-07-29 paper.tex
Add digital rights to abstract

@@
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
+The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
 \end{abstract}

### 2020-07-29 paper.tex
Move description of key certification from Chap3 to Chap5

@@
 Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
-
-The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key; otherwise the process will be aborted.
-Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
-This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
-    \label{fig:key_upload}
-\end{figure}
+The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM and record encryption keys to smart contracts without knowing the contents.
+The encryption key upload procedure is illustrated in Section.~\ref{section:launch_data_product}.
 
@@
 \subsection{Launch Data Products}
+\label{section:launch_data_product}
 To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
@@
 The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
+As regard to the encryption key of data product, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
+Broker can first verify the signature from data provider with the public key on DID document.
+If it's valid, then the broker uploads the key; otherwise the process will be aborted.
+Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
+This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription.
+Furthermore, the encryption key can only be uploaded/updated under two circumstances: 1.) the new product launching.
+2.) when data consumer unsubscribe to the product.
 Finally, the data product is launched and data providers can start uploading data.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+The product launching workflow is shown in Fig.~\ref{fig:launching_product} and Listing.~\ref{lst:key_certification} lists the Solidity codes of key certification process.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.5in]{key_upload}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
+After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
+    \label{fig:key_upload}
+\end{figure}
 

### 2020-07-29 paper.tex
Update Conclusion to blockchain2020 and add Future Work section

--- 2020-07-28 paper.tex
@@
 \title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
-% Chinese title: 針對物聯網訂閱型資料交易的去中心化基礎建設
+% Chinese title: 針對物聯網資料交易的去中心化基礎建設
 
@@
 And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
-The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depend on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
+The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
+In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 
@@
 In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
-Proving the identity as well as the ownership of data are challenging issues among various roles in a large scale platform.
+Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
 In current systems, trusted third-party authority like CA is widely adopted to certify each member.
@@
 
-Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
+Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
 \begin{itemize}
@@
 	\item \textbf{Confidentiality}. 
-1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.	
+1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
 	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
@@
 See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
@@
 \begin{itemize}
-	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
+	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
 	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
@@
 \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components aiming for different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
+Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
 While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
@@
 However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
-Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
 
@@
 \subsection{Distributed Storage System}
-\label{section:distributed_storage}
 Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
 Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-
 Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
 IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
-However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
-Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents.
-Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.
-
+However, no cryptographic system is applied for user-uploaded files.
 Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
@@
 Data providers are the ones that generate streaming data and set the data price based on the different types of data.
-Subscription fees can motivate data providers to maintain and improve the quality of data.
+With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
 \item \textbf{Data Consumer: }
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch and it is also difficult to find desired data sets, purchase is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
 Brokers are responsible for building an agreement between data providers and consumers.
-Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
+Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
 \end{itemize}
@@
 The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
+Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}.
+With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.
 
@@
     \includegraphics[width=\linewidth]{channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures.
+    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
 Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
@@
 \subsection{Digital Identity}
-The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
+The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
 We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
@@
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel.
+Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
@@
 For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color.
-The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
+The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
     \label{fig:smart_contract_mam}
@@
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
+Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.
 
@@
 One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
-For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.
+For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
+The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
 
@@
 To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the limited resources of low-level devices should be used on its jobs instead of handling all trading processes.
+However, the resources of low-level devices are precious which should be used to focus on its jobs.
 Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
@@
 Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key; otherwise the process will be aborted.
-Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
-This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription.
+If it's valid, then the broker uploads the key, otherwise the process will be aborted.
+Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
+The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
+If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
 Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
@@
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
+After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
     \label{fig:key_upload}
@@
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
+Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
+Assuming the length of data stream is 7, and each record is encrypted with the same key.
+With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
+
+\begin{table}[htbp]
+	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
+	\label{tab:mam_scalability}
+	\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
+		\hline
+		keys & 1 & 1 \\ 
+		\hline
+		entry points & 1 & 7 \\ 
+		\hline
+	\end{tabular}
+	\end{center}
+\end{table}
 
 %classify
-\subsubsection{Data Sreams Classification and Traceability}
+\subsubsection{Data Sreams Classification}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
+For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
+Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+To do the classification in other distributed storage also encounters the aforementioned scalability problem.
+
+%data trace
+\subsubsection{A Traceable Data Stream}
+Data traceability is an important security issue that allows users to track the changes of data.
+Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
+Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
+MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
 
@@
 
-\section{Decentralized Subscription-based Data Trading Models}
+\section{Decentralized Subscription-based Data Trading Case Study}
 \label{section:trading_model}
@@
 See Fig.~\ref{fig:refund}.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
 
@@
     \includegraphics[width=1.5in]{refund}
-    \caption{Once a data consumer launch a refund vote, all consumers start voting to decide whether they want a refund.
-Finally, the establishment of refund is determined by Product Contract after checking the number of votes is larger than a threshold or not.}
+    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
+Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
     \label{fig:refund}
 \end{figure}
-
-However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
-Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
-Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
-If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
-Third, the refund could launch by providers when they fail to maintain products as committed.
 
@@
 
-\section{Conclusions}
+\section{Conclusion}
 \label{section:conclusion}
-By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
-
+By combining the established standards and openly-developed specifications, this paper proposed a highly decentralized, autonomous publish/subscribe model design that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to enable the data stream trading by shifting risks from centralized services, ensure the authenticity of all participants, clarify the data ownership, enable secure communication and flexible trading mechanisms.
+
+Compared to previous works, we 1.) identify a trustless data trading infrastructure, 2.) ensure the confidentiality of scalable IoT-based sensor data, and 3.) consolidate the economic incentives in the entire ecosystem.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to Tangle-accelerators, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+In particular, this work discusses the workflow for subscription-based IoT data trading: Launching, subscribing, unsubscribing, and refund.
+
+\section{Future Work}
 In the subscription-based data trading, there are some issues that worth discussing and improving.

### 2020-07-31 deprecated.tex
Shorten Abstract

--- 2020-07-01 deprecated.tex
@@
 \begin{abstract} 
-The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us.
-Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources.
-For instance, smart meter data can assist in energy transition.
-Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location.
-Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy.
-In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges.
+The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
+The real-time data exchange among devices are periodical that only data in a specific time period is interested.
+Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
+Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
+This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
+However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
+Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
+Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
+Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers.
-Finally, we implement and evaluate the performance of the prototype.
+The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
 \end{abstract}

### 2020-07-31 paper.tex
Shorten Abstract

@@
 %cite IoT data subscription economy
-The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
-Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchange among devices are periodical that only data in a specific time period is interested.
-Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
-Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy to share and trade their resources.
+Monetizing the real-time data on top of publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
-However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
-Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
-Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
-Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
-In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
+However, streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
+A trustless data trading infrastructure is required where the entities can trade, validate data ownership and integrity without trusting any services.
+In addition, an automated subscription procedure is also demanded for the sake of data monetization.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
+The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
+
 \end{abstract}
@@
 Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
-In current systems, trusted third-party authority like CA is widely adopted to certify each member.
+In current systems, trusted third-party authority like certificate authority (CA) is widely adopted to certify each member.
 However, building trust upon CA is dangerous and fragile.

### 2020-07-31 paper.tex
Add future work in paper organization

@@
 The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion}.
+Finally, we conclude the paper in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.
 
@@
 \section{Future Work}
+\label{section:future_work}
 In the subscription-based data trading, there are some issues that worth discussing and improving.

### 2020-07-31 paper.tex

@@
 \title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
-% Chinese title: 針對物聯網資料交易的去中心化基礎建設
+% Chinese title: 針對物聯網訂閱型資料交易的去中心化基礎建設
 
@@
 The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
-
 \end{abstract}
@@
 However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
 
@@
 \subsection{Distributed Storage System}
+\label{section:distributed_storage}
 Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
 Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
+
 Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
 IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-However, no cryptographic system is applied for user-uploaded files.
+Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
+However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
+Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents.
+Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.
+
 Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
@@
 Data providers are the ones that generate streaming data and set the data price based on the different types of data.
-With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
+Subscription fees can motivate data providers to maintain and improve the quality of data.
 \item \textbf{Data Consumer: }
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch and it is also difficult to find desired data sets, purchase is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
 Brokers are responsible for building an agreement between data providers and consumers.
-Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
+Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
 \end{itemize}
@@
 To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the resources of low-level devices are precious which should be used to focus on its jobs.
+However, the limited resources of low-level devices should be used on its jobs instead of handling all trading processes.
 Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
-
-The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
-    \label{fig:key_upload}
-\end{figure}
+The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM and record encryption keys to smart contracts without knowing the contents.
+The encryption key upload procedure is illustrated in Section.~\ref{section:launch_data_product}.
 
@@
     \includegraphics[width=1.5in]{refund}
-    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
-Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \caption{Once a data consumer launch a refund vote, all consumers start voting to decide whether they want a refund.
+Finally, the establishment of refund is determined by Product Contract after checking the number of votes is larger than a threshold or not.}
     \label{fig:refund}
 \end{figure}
+
+However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
+Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
+Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
+If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
+Third, the refund could launch by providers when they fail to maintain products as committed.
 

### 2020-07-31 paper.tex
Fix the irrelevant context in digital identity

@@
 
-Centralized identity model may have single point failure in identifier management and security issues like data leakage.
-With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
+The centralized identity model may have single point failure in identifier management and security issues like data leakage.
+With sensitive information holding on certain authorities, the leakage caused by cyber attacks or unscrupulous organizations trading user data damage the users' privacy.
 Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
+The decentralized identity model give back the controls of data to users that can resolve the aforementioned concerns in the centralized one.
 

### 2020-07-31 paper.tex
Add more description of why not IPFS in Chap3

@@
 Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.
+Nevertheless, the efficiency problems still occur if the dedicated network grows larger.
 
@@
 One can easily prove himself by sharing the identifier on MAM without any authority.
+
+Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network).
+However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}.
+Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.
 

### 2020-07-31 paper.tex
Add an overview of Chap4 to clarify IF and our work

@@
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Section.~\ref{section:mam_streams} to ~\ref{section:mam_features} explain the structure, fuctions and features of MAM, and our proposed MAM delegation mechanism  is clarified in Section.~\ref{section:ta_endpoint}.
 
 \subsection{The Message Streams}
+\label{section:mam_streams}
 A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
@@
 \subsection{Enable Access Control and Authentication}
+\label{section:mam_functions}
 The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
@@
 \subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
+\label{section:mam_features}
 %scalability

### 2020-08-05 paper.tex

@@
 With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
-In our system, \textbf{Product Contract} is made for the product launching and trading.
+In our system, \textbf{Product Contract} is made for the product launching and subscribing.
 The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
@@
 Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
+Binding trading and data storage to smart contract ensures consumers can always retrieve the encryption key from the Product Contract once they pay.
 
@@
 For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.
+The enforcement of smart contracts also ensures the rights of participants that they fulfill the agreed contract under any circumstances.
 

### 2020-08-05 paper.tex
Update to recent modifications

--- 2020-07-31 paper.tex
@@
 \title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
-% Chinese title: 針對物聯網訂閱型資料交易的去中心化基礎建設
+% Chinese title: 針對物聯網資料交易的去中心化基礎建設
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jkrvivian@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-jserv@ccns.ncku.edu.tw}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-\IEEEauthorblockA{\textit{dept. of CSIE} \\
-\textit{National Cheng Kung University}\\
-Tainan City, Taiwan (R.O.C.) \\
-chiaheng@gmail.com}
+\author{
+\IEEEauthorblockN{Anonymous}
+\IEEEauthorblockA{
+         \textit{Anonymous Organization}\\
+        ***@***.***}
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
+%\IEEEauthorblockA{\textit{dept. of CSIE} \\
+%\textit{National Cheng Kung University}\\
+%Tainan City, Taiwan (R.O.C.) \\
+%jkrvivian@gmail.com}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
+%\IEEEauthorblockA{\textit{dept. of CSIE} \\
+%\textit{National Cheng Kung University}\\
+%Tainan City, Taiwan (R.O.C.) \\
+%jserv@ccns.ncku.edu.tw}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
+%\IEEEauthorblockA{\textit{dept. of CSIE} \\
+%\textit{National Cheng Kung University}\\
+%Tainan City, Taiwan (R.O.C.) \\
+%chiaheng@gmail.com}
 }
@@
 %cite IoT data subscription economy
-Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy to share and trade their resources.
-Monetizing the real-time data on top of publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model.
+On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
-However, streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
-A trustless data trading infrastructure is required where the entities can trade, validate data ownership and integrity without trusting any services.
+However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification.
+A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
 In addition, an automated subscription procedure is also demanded for the sake of data monetization.
@@
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}.
+In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.
-Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.
-
-% SaaS
-The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage.
-The subscription-based models (e.g.
-SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
-And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
-The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depend on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 
@@
 In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
-Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
-In current systems, trusted third-party authority like certificate authority (CA) is widely adopted to certify each member.
-However, building trust upon CA is dangerous and fragile.
-The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion.
-Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
-The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
-
-Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
+Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
 \begin{itemize}
@@
 	\item \textbf{Confidentiality}. 
-1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.	
+1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
 	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
-	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
 \end{itemize}
 
-Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
-In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
-See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected.
+Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
 Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
-
-\subsection{Contributions}
-The contributions in the paper are summarized as follow:
-\begin{itemize}
-	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
-	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
-	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
-	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
-\end{itemize}
-
-\subsection{Paper Organization}
-The rest of this paper is organized as follows.
-In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
-In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
-In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained.
-The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.
 
@@
 
-%TODO: cite IOTAIndustryMarketplace
 \section{Related Work}
 \label{section:relatedWork}
-% pub/sub
-\subsection{The Publish/subscribe Communication Models Over Blockchain}
-The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
-
-M.
-B.
-Abdullahi and G.
-Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues.
-Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests.
-Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure.
 G.
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
-But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
+The data validation and traceability are achieved via Ethereum smart contract.
+But data is plaintext on blockchain that the system is not appropriate for sensitive data.
 
-In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
-The subscribers request publisher directly and ask them to save a cache space for interested data.
-The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
-Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
+Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
 The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
-The reputation system and the punishment rules against malicious acts of subscribers and publishers.
-Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
-Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
-
-The previous works contribute to different aspects of building a reliable pub/sub system over blockchain.
-However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.
-
-\subsection{Trusted IoT Trading Infrastructure}
-Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
+Yet, without brokers, participants may need to reveal more sensitive information in order to communicate.
+By Paolo Missier et.
 al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
-However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.
 
-A.
-Colman et al.
-\cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables.
-Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components aiming for different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts.
-While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
-
-In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
-Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system.
-Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
-This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
-Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
-Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
-
-Researches below adopt MAM as data storage and a secure data transmission layer.
-The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
-Service requesters call for proposal of interested data and accept/reject proposals from service providers.
-After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
-This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
-Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
-
-O.
-Lamtzidis and J.
-Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm.
-The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
-Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
-The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
-
-\subsection{Distributed Storage System}
-\label{section:distributed_storage}
-Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-
-Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
-However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
-Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents.
-Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.
-Nevertheless, the efficiency problems still occur if the dedicated network grows larger.
-
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
-Files are duplicated in multiple nodes to prevent data loss.
+Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
+The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer.
+The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.
 
@@
 \subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
-As shown in Fig.~\ref{fig:pub_sub_model}.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{pub_sub_model}
-    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
-    \label{fig:pub_sub_model}
-\end{figure}
+There are three major participants, data providers, data consumers and brokers in our proposed architecture.
 
@@
 Data providers are the ones that generate streaming data and set the data price based on the different types of data.
-Subscription fees can motivate data providers to maintain and improve the quality of data.
+With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
 \item \textbf{Data Consumer: }
 Data consumers are entities that are willing to buy data streams.
-As it is laborious to widely deploy devices to collect data from scratch and it is also difficult to find desired data sets, purchase is the fastest and efficient way to get the desired data sets.
+As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets.
+Purchase is the fastest and efficient way to get the desired data sets.
 \item \textbf{Broker: }
-Brokers are responsible for building an agreement between data providers and consumers.
+Brokers are responsible for building an agreement and handling trading processes between data providers and consumers.
 Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
@@
 
-We adopt the brokered infrastructure for three reasons.
-Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system.
-Furthermore, if either side is offline, the proceeding tasks have to stop and start over.
-With brokers, the unfinished work can be cached or accomplished.
+Adopting brokers between providers and consumers has three advantages.
+First, considering the entities could be machines that are not online anytime, brokers can continue the trading process if either side is offline.
 Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel.
-The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
+Brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
 Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
 
-\begin{figure*}[!t]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\linewidth]{channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures.
+    \includegraphics[width=3.5in]{channel_and_key_fold}
+    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
 Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
     \label{fig:channel_and_key}
-\end{figure*}
+\end{figure}
 
@@
 Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
-MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.
-Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored.
-One can easily prove himself by sharing the identifier on MAM without any authority.
+In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams.
+It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
+2) \textbf{Integrity}, messages written on the Tangle are immutable.
+3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
+4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents.
+See Fig.~\ref{fig:channel_and_key} for illustration.
+
+Using MAM as a data storage benefits from the underlying IOTA network as well as the decentralized and fault-tolerant characteristics, which reduce the risks of centralized storage services.
+Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+
+However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM requires lots of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy.
+The details would be further illustrated in Section.\ref{section:ta_endpoint}.
 
 Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network).
-However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}.
+However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated.
 Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.
 
-In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
-
-\begin{itemize}
-    \item \textbf{Scalability}:
-	\begin{itemize}
-		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
-    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
-    \end{itemize}    
-    \item \textbf{Integrity}: 
-	\begin{itemize}    	
-        \item Messages published to the Tangle are tamper-proof that against malicious modification.
-    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
-    \end{itemize}
-    \item \textbf{Confidentiality}:
-    \begin{itemize}    	
-    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
-    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
-    	\item MAM provides forward-secrecy.
-The entry points of future data can be derived, but it's impossible to trace back those in the past.
-This feature prevents adversaries from retrieving published history even if the key is revealed.
-    \end{itemize}
-\end{itemize}
-
-MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control.
-The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle.
-This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source.
-See Fig.~\ref{fig:channel_and_key} for illustration.
-
-Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services.
-Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-
 \subsection{Digital Identity}
-The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
+The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
 We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.
-
 \begin{table}[h]
-	\caption{The comparison of centralized and decentralized identity model}
+	\caption{Identity models: centralized vs. decentralized}
 	\label{tab:did}
@@
 
-The centralized identity model may have single point failure in identifier management and security issues like data leakage.
-With sensitive information holding on certain authorities, the leakage caused by cyber attacks or unscrupulous organizations trading user data damage the users' privacy.
+Centralized identity model may have single point failure in identifier management and security issues like data leakage.
+With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
 Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
-The decentralized identity model give back the controls of data to users that can resolve the aforementioned concerns in the centralized one.
 
-In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
-The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
-If a VC is verified via issuer's public key, the message will be labelled as trusted.
-Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.in]{DID_VC}
-    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
-    \label{fig:did_vc}
-\end{figure}
-
-In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable.
+In our architecture, a decentralized identity system TangleID\cite{TangleID} is adopted, built on top of MAM where audit logs of DIDs are traceable.
 One can easily prove himself by sharing the identifier on MAM without any authority.
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel.
+Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
 The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
-See Fig.~\ref{fig:TangleID}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{TangleID}
-    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
-The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
-When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
-The data provider can then retrieve the consumer's public key and encrypt the content with it.
-After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
-    \label{fig:TangleID}
-\end{figure}
+During data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.
 
 \subsection{Enable Automated Trading Process}
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=4in]{smart_contract_mam}
-    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.
-For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color.
-The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
-    \label{fig:smart_contract_mam}
-\end{figure*}
+With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
+In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures.
+Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream.
+The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.
 
-Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
-It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines.
-A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
-All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
-
-With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
-In our system, \textbf{Product Contract} is made for the product launching and trading.
-The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
-Listing.
-\ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
-
-The transparency of smart contracts bring advantages for data providers and consumers.
-One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
-For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.
-
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
-\lstset{style=solidity}
-\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
-contract Product {
-    address public broker;
-    address public provider;
-    bool isBrokerWithdraw;
-    bool isProviderWithdraw;
-    address[] consumers;
-
-    struct Purchase {
-        bool affirmativeVote;
-        bool isConsumerWithdraw;
-        bool isKeyAdded;
-        bool isSubscribe;
-        string encryptKey;
-    }
-    mapping(address => Purchase) public consumer2Purchase;
-
-    uint public price;
-    uint public totalAmount;
-    uint public brokerage;
-    uint public cancellation;
-    uint public threshold;
-    string public channelRoot;
-    string public endPoint;
-    uint public totalNumber;
-    uint public uploadedNumber;
-    uint public affirmativeVotes;
-    string hashedKey;
-    string certifiedKey;
-
-    enum State {Launched, KeyCertified, Finished, Refunded}
-    State public state;
-}
-\end{lstlisting}
-
-\subsection{Enable computation tasks delegation to broker with privacy}
-To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the limited resources of low-level devices should be used on its jobs instead of handling all trading processes.
-Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
-The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM and record encryption keys to smart contracts without knowing the contents.
-The encryption key upload procedure is illustrated in Section.~\ref{section:launch_data_product}.
-
-As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy.
-The details would be further illustrated in Section.\ref{section:ta_endpoint}.
+Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.
+Moreover, binding the encryption key with the transparent subscription procedure on Product Contract allows data providers to track and manage the authorized user list, and allows data consumers to always have access after payment, even if the key is lost.
+The enforcement of smart contracts also ensures the rights of participants that they fulfill the agreed contract under any circumstances and without any authority.
 
@@
 \label{section:MAM}
-MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
-The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Section.~\ref{section:mam_streams} and ~\ref{section:mam_features} explain the structure, fuctions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.
 
 \subsection{The Message Streams}
-A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
+\label{section:mam_streams}
+A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload.
 To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
-The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
-Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
+The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle, represents the ownership of all things associated with the user in the IOTA ecosystem.
+
+The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload.
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
 Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data.
+Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
 
@@
 \subsection{Enable Access Control and Authentication}
+\label{section:mam_features}
 The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels.
@@
 
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
-%scalability
-\subsubsection{A Scalable Keys and Data Entry Points Management}
-The importance of scalable key and data entry points management increases over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
-
-%classify
-\subsubsection{Data Sreams Classification and Traceability}
-The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
-
-\subsection{Delegate MAM operations to Tangle-accelerator}
+\subsection{Delegate MAM operations to Accel}
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
-Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{ta_structure}
-    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
-It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed.
-Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
-    \label{fig:ta_struct}
-\end{figure}
+MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating system.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
 
@@
     \includegraphics[width=\linewidth]{delegation}
-    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
+    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Accel.}
     \label{fig:delegation}
 \end{figure}
-
-\subsubsection{Communication Protocol}
-In the following sections, we refer the low-level devices as \textbf{endpoint}s.
-MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic.
-The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth.
-The pub/sub model decouples publishers and subscribers in many ways:
-
-\begin{itemize}
-    \item Space decoupling: Both publishers and subscribers don't need to know each other.
-    \item Time decoupling: Publishers and subscribers do not need to be active at the same time.
-    \item Synchronization decoupling: Operations are decoupled from the publishers and subscribers.
-The publishers do not need to be alive until the response arrives.
-Messages from publisher can be served as send-and-forget fashion.
-\end{itemize}
 
@@
 With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
+For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}
 
-\subsubsection{Register with Tangle-accelerator}
-User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
-Once tangle-accelerator receive the Seed from edge device, it would return a unique user identifier which can be mapping to corresponding Seed when edge devices send requests.
-Asymmetric encryption is utilizing during the process of exchanging seed.
-Digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed will not be exposed during communication after an edge device is successfully registered.
+\subsubsection{Time Complexity}
+In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature.
+In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol takes only linear time versus arbitrary string length.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
-
-\paragraph{Linear Time to Read Message}
-It is linear time to decrypt message instead of constant time.
-Nevertheless, there is one way to speed up the message decryption process.
-A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
-This procedure can reduce the time spending on internet communication.
-
-\paragraph{Spam on Message Channel Chain}
+E2EE helps a lot for low-level edge device utilizing blockchain service.
+It dramatically reduces execution time encryption takes.
+However, there are some challenges in the E2EE process.
 Tampering the messages which have conducted E2EE would be a challenging mission.
 However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
+It is risky for an edge device connects to a Accel which is operated by unknown third-party.
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
 Spam would cause subscribers wasting plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
+To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.
 
@@
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.
 
@@
 \subsection{Launch Data Products}
-\label{section:launch_data_product}
-To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract.
-For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}.
-And brokers are responsible for Product Contract creation.
-
-The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key; otherwise the process will be aborted.
-Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
-This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription.
-Furthermore, the encryption key can only be uploaded/updated under two circumstances: 1.) the new product launching.
-2.) when data consumer unsubscribe to the product.
+To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers.
+The Product Contract will not accept subscriptions until brokers certify the encryption key.
+To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers.
+The broker verify the signature with the public key on provider's DID document.
+If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted.
+The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently.
+If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
 Finally, the data product is launched and data providers can start uploading data.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
-The product launching workflow is shown in Fig.~\ref{fig:launching_product} and Listing.~\ref{lst:key_certification} lists the Solidity codes of key certification process.
-
 \begin{figure}[h]
@@
     \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
+After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
     \label{fig:key_upload}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=2.5in]{launching_product}
-    \caption{The process of launching a product.}
-    \label{fig:launching_product}
-\end{figure}
-
-\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
-    function addHashedKey(
-        string memory _hashedKey
-    ) public {
-        require(
-            msg.sender == provider,
-            "Only provider can add hashed key."
-        );
-        require(
-            state == State.Launched,
-            "One key has been certified."
-        );
-        hashedKey = hashedKey;
-        emit newHashedKey(hashedKey);
-    }
-
-    function addCertifiedKey(
-        string memory _certifiedKey
-    ) public {
-        require(
-            msg.sender == broker,
-            "Only broker can add certifiedKey."
-        );
-        require(
-            state == State.Launched,
-            "One key has been certified."
-        );
-        certifiedKey = _certifiedKey;
-        state = State.KeyCertified;
-        emit newCertifiedKey(certifiedKey);
-    }
-\end{lstlisting}
-
 \subsection{Subscribe to Data Product}
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it.
 
@@
 
-\lstdefinestyle{solidity}{
-	captionpos=b,
-	tabsize=4,
-	basicstyle=\scriptsize
-}
-\lstset{style=solidity}
-
-\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
-    function addEncryptKey(
-        address _consumer,
-        string memory _encryptKey
-    ) public {
-        require(
-            msg.sender == provider,
-            "Only provider can add the encrypted key."
-        );
-        require(
-            consumer2Purchase[_consumer].isKeyAdded == false,
-            "Encryption key has been added."
-        );
-        consumer2Purchase[_consumer].encryptKey = _encryptKey;
-        consumer2Purchase[_consumer].isKeyAdded = true;
-        emit newEncryptKey(_consumer, _encryptKey);
-    }
-\end{lstlisting}
-
 \subsection{Unsubscribe to Data Products}
-Data consumers can unsubscribe to data products when they're not interested anymore.
-Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structre, since the delete function in Solidity does not remove the actual element but reseting it to default value.
-When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
-The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
-
-In SaaS, the cancellation fee is a way to make sure the service providers are protected.
-It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
-However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
-
-Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
-The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
-Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
-
-\begin{equation}
-\label{equation:unsubscribe_provider}
-    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
-\end{equation}
-
-\begin{equation}
-\label{equation:unsubscribe_broker}
-    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
-\end{equation}
-
-\begin{equation}
-\label{equation:unsubscribe_consumer}
-    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
-\end{equation}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.5in]{unsubscribe}
-    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
-Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
-    \label{fig:unsubscribe}
-\end{figure}
-
-\subsection{Launch a Refund}
+When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}.
+$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage.
+However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied.
+Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data.
+The new key should be updated for the remaining subscribers.
+\begin{align}
+    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
+    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
+    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
+\end{align}
+\subsection{Refund}
 \label{section:refund}
-Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
-Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
-When the refund procedure is launched, all consumers vote to decide whether the refund is established.
-See Fig.~\ref{fig:refund}.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
-
-\begin{equation}
-    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
-\end{equation}
-
-\begin{equation}
-    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
-\end{equation}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=1.5in]{refund}
-    \caption{Once a data consumer launch a refund vote, all consumers start voting to decide whether they want a refund.
-Finally, the establishment of refund is determined by Product Contract after checking the number of votes is larger than a threshold or not.}
-    \label{fig:refund}
-\end{figure}
-
-However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
-Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
+The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section.
+As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee.
+However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
 Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
@@
 \label{section:evaluation}
-We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
-2) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+2) Evaluate the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data provider.
+
+\subsection{Gas usage of the Product Contract}
+We investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix.
+On top of this evaluation, data providers can consider how to set the subscription and brokereage fee to eventually generate profits.
+The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time.
+To conquer this condition, we analyze with a fixed range of Gas price.
+According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
+Note that data uploading is only related to MAM operations on the Tangle without transaction fee.
+Therefore, the Gas estimation only includes trading processes.
+The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
+Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+
+\begin{table}[h]
+	\caption{Transaction fees for each participant}
+	\label{tab:gas}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{participant} & \textbf{Gas used} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
+		\hline
+		provider & 166203 & 0.288 & 1.048 \\ 
+		broker & 2733985 & 4.750 & 17.243 \\ 
+		consumer & 83572 & 0.145 & 0.527  \\ 
+		\hline
+	\end{tabular}
+\end{table}
 
@@
 \label{section:mam_performance}
-It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
-Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle.
-Therefore, in the following evaluations, all devices run with client library only.
-
-MAM is a secure and validatable data storage of the proposed architecture.
-And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections.
-The interactions between data providers and MAM can be frequent.
-Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
-
-In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and data attachment to endpoints.
-To perform the evaluation assessment, a personal computer (PC, 3.2GHz 64-bit 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (1.2 GHz 64-bit quad-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
+In the following evaluations, all devices run with IOTA client library instead of IOTA full nodes.
+MAM is the primary key to resolve all the storage difficulties discussed in previous sections.
+The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment.
+To perform the evaluation assessment, a personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
 
 \subsubsection{Channel / Endpoint Creation}
-The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint.
-A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total.
-The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required.
+The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint.
+The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power is required.
 In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.
-The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}.
+
+Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation.
 The time duration for each \textit{height} is the average time of running 100 rounds.
-
-\begin{table}[htbp]
-	\caption{Time measurement of channel creation}
-	\label{tab:channel_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.26183 & 2.908702 \\ 
-		2 & 0.524076 & 5.805524 \\ 
-		3 & 1.045942 & 11.555660 \\ 
-		4 & 2.092989 & 23.178036 \\ 
-		5 & 4.19515 & 46.164079\\ 
-		6 & 8.361586 & 92.320173\\ 
-		7 & 16.651607 & 185.292243\\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Time measurement of endpoint creation}
-	\label{tab:endpoint_create}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
-		\hline
-		1 & 0.256425 & 2.887064 \\ 
-		2 & 0.505679 & 5.767912 \\ 
-		3 & 0.999524 & 11.550455 \\ 
-		4 & 1.994017 & 23.260508 \\ 
-		5 & 3.965007 & 46.748366 \\ 
-		6 & 7.918925 & 93.182975 \\ 
-		7 & 16.561419 & 186.064562 \\
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
-
-The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}.
-Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical.
-On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above.
-And the performance of PC remains acceptable even \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{mam_create}
-    \caption{Time cost of MAM creation.}
-    \label{fig:mam_create}
-\end{figure}
+Since the workflow of channel and endpoint creation are identical, the curves of the same hardware are almost matched.
+On the other hand, the elapsed time of RPi is grows rapidly when \textit{height} is 5 or above.
+And the elapsed time of PC remains acceptable even the \textit{height} gets to 7.
+The results indicate that MAM channel/endpoint creation is a laborious job for RPi when data providers need a longer channel/endpoint, which can considered delegating to Accel.
+\begin{figure*}[!htb]
+\minipage{0.32\textwidth}
+  \includegraphics[width=\linewidth]{mam_create}
+  \caption{Time cost of MAM creation.}\label{fig:mam_create}
+\endminipage\hfill
+\minipage{0.32\textwidth}
+  \includegraphics[width=\linewidth]{rpi3_pow}
+  \caption{MAM with local PoW \newline vs. MAM with remote PoW \newline vs. Delegated MAM with E2EE}\label{fig:rpi3_pow}  
+\endminipage\hfill
+\minipage{0.32\textwidth}%
+  \includegraphics[width=\linewidth]{op_share}
+  \caption{The percentage each operation takes in total elapsed time.}\label{fig:op_share}  
+\endminipage
+\end{figure*}
 
 \subsubsection{Messages Publishment}
-Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
-\begin{itemize}
-	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
-	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
-\end{itemize}
+Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes: 1.) \textbf{Tips selection}: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify.
+The tips are provided by IOTA full nodes.
+2.) \textbf{Proof-of-Work (PoW)}: An algorithm which prevents Denial of Service and spam attacks on a network.
 
 Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
-The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.in]{mam_send}
-    \caption{The probability distributed function of time cost for sending a message through MAM.}
-    \label{fig:mam_send}
-\end{figure}
-
-The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
-Furthermore, sensors with the low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM and even trading process with subscribers simultaneously.
-
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator.
-However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
-
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=3.5in]{rpi3_pow}
-    \caption{Local PoW vs. Remote PoW}
-    \label{fig:rpi3_pow}
-\end{figure}
+The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has huge impact.
+The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
+Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such framework.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
+However, MAM operations are fairly time-consuming, and improving the performance of MAM is an essential issue that needs to be done for the next step.
 
@@
 \label{section:smart_contract_evaluation}
-
 \subsubsection{Experiment}
-Applying remote PoW greatly reduce the elapsed time.
-Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
+The result directs a way to improve MAM.
+Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier should be removed.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
-The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
+In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
 
 The steps counted in MAM benchmark including:
-\begin{itemize}
-	\item Encrypt input payload
-	\item Publish final message on IOTA Tangle
-\end{itemize}
+\begin{enumerate}
+    \item Write key information in header
+	\item Write and encrypt input payload
+	\item Publish final message on Tangle
+\end{enumerate}
 
-The steps counted in E2EE benchmark including:
-\begin{itemize}
+The steps counted in delegated MAM (E2EE) benchmark including:
+\begin{enumerate}
 	\item Generate symmetric key for encryption
@@
 	\item Encrypt input payload
-	\item Transmit final message to tangle-accelerator
-\end{itemize}
+	\item Transmit final message to Accel
+\end{enumerate}
 
 \begin{table}[htbp]
-	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+	\caption{Compare the performance between MAM and E2EE on RPi}
     \label{tab:mam_vs_e2ee}
-    \resizebox{0.5\textwidth}{!}{
+    \centering
         \begin{tabular}{|c||c|c|}
@@
         \end{tabular}
-    }
 \end{table}
 
-It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+\begin{align}
+    y &= 0.0126 x+19.979 \label{lin_mam} \\
+    y &= 0.0002 x+9.174 \label{lin_e2ee}
+\end{align}
 
-\begin{equation}
-    \label{eq:lin_mam}
-    y=0.0126 x+19.979  
-\end{equation}
+Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods.
+Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively.
+The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
+Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
+E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
 
-\begin{equation}
-    \label{eq:lin_e2ee}
-    y=0.0002 x+9.174
-\end{equation}
+\section{Conclusion and Future Work}
+\label{section:conclusion}
+This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design.
+Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.
 
-The Eq.~\ref{eq:lin_mam} and Eq.~\ref{eq:lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
-Apparently, the slope of the result of MAM is much greater than the result of E2EE.
-The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.
+Our work has a main focus on the subscription-based model and relative experiments. And the next step is extending it to:
+\begin{enumerate}
+	\item reduce the use of Gas in key-agreement protocol and consider the possibility of the zero-knowledge proof to lower transaction costs;
+	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
+	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality, without violating the privacy.
+\end{enumerate}
 
-\subsubsection{Time Complexity}
-With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
-HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
-Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
-Applying mature cryptographic functions (e.g.
-SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
-
-\subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
-On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
-The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated.
-According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-The Gas usage estimation is shown in Table.~\ref{tab:gas}.
-
-\begin{table*}[h]
-	\caption{Gas consumption for each function of Product Contract}
-	\label{tab:gas}
-	\resizebox{0.5\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
-		\hline
-		generate contract & broker & 2558980 \\ 
-		subscribe product & consumer & 72259 \\ 
-		upload hashed key & provider & 68276  \\ 
-		upload encryption key to consumer & provider & 86614 \\ 
-		upload certified key & broker & 131535 \\
-		update amount of uploaded data & broker & 32157 \\
-		unsubscribe & consumer & 8234 \\
-		request refund & consumer & 12067 \\
-		withdraw & broker & 11313 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-Note that data uploading is only related to MAM operations on IOTA, which does not require any fees.
-Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
-Storage on blockchain is expensive.
-For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
-Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
-
-Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
-\label{equa:ether_calculation}
-Ethers = Gas \ Price \times Gas \ Amount
-\end{equation}
-
-When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
-Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
-Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
-
-\begin{table*}[h]
-	\caption{Data Price Estimation}
-	\label{tab:ether}
-	\centering
-	\resizebox{0.8\textwidth}{!}{
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
-		\hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
-		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
-		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
-		\hline
-	\end{tabular}
-	}
-\end{table*}
-
-\section{Conclusion}
-\label{section:conclusion}
-By combining the established standards and openly-developed specifications, this paper proposed a highly decentralized, autonomous publish/subscribe model design that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to enable the data stream trading by shifting risks from centralized services, ensure the authenticity of all participants, clarify the data ownership, enable secure communication and flexible trading mechanisms.
-
-Compared to previous works, we 1.) identify a trustless data trading infrastructure, 2.) ensure the confidentiality of scalable IoT-based sensor data, and 3.) consolidate the economic incentives in the entire ecosystem.
-Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to Tangle-accelerators, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
-In particular, this work discusses the workflow for subscription-based IoT data trading: Launching, subscribing, unsubscribing, and refund.
-
-\section{Future Work}
-\label{section:future_work}
-In the subscription-based data trading, there are some issues that worth discussing and improving.
-Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
-Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
-However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
-
-Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
-The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
-Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
+Finally, a decentralized model enables the data stream trading by shifting risks, and correspondingly, the digital rights of its participants deserve a guarantee, which is provided with the automated system.
 

### 2020-08-05 paper.tex
Minor fixes

--- 2020-08-05 paper.tex
@@
 \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
 Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
-Binding trading and data storage to smart contract ensures consumers can always retrieve the encryption key from the Product Contract once they pay.
+Binding trading and data storage to smart contract ensures consumers can always have access after payment, even if the key is lost, and providers can track and manage the authorized user list.
 
@@
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Section.~\ref{section:mam_streams} to ~\ref{section:mam_features} explain the structure, fuctions and features of MAM, and our proposed MAM delegation mechanism  is clarified in Section.~\ref{section:ta_endpoint}.
+Section.~\ref{section:mam_streams} to ~\ref{section:mam_features} explain the structure, fuctions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.
 

### 2020-08-05 paper.tex
Fix grammar and typos

@@
 Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy to share and trade their resources.
-Monetizing the real-time data on top of publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model.
+Monetizing the real-time data on top of the publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
@@
 In addition, an automated subscription procedure is also demanded for the sake of data monetization.
-In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
+In this paper, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
+The storage built upon cryptographic message protocols allows transmitting, accessing, and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
 \end{abstract}
@@
 As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.
+With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets.
+Therefore, data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.
 
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}.
+In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity, and high variety of real-time "Big Data" streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 % SaaS
-The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage.
+The economic incentive model in our proposed IoT data trading platform works as a subscription service that valuates the payments by data usage.
 The subscription-based models (e.g.
-SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
-And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
-The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
-In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depend on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
+SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming, and software, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
+And for service consumers, they can subscribe and unsubscribe the services at will at any time.
+The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes good circulation of the platform.
+In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
 
@@
 %trust: 對系統、對身份、對資料
-In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
+In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
 Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
-In current systems, trusted third-party authority like certificate authority (CA) is widely adopted to certify each member.
+In current systems, a trusted third-party authority like certificate authority (CA) is widely adopted to certify each member.
 However, building trust upon CA is dangerous and fragile.
-The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion.
-Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
+The compromise of routers or CA can break the trust of the entire system, and the data portability of using third-party services is still under suspicion.
+Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}.
+Besides CA and storage, the subscription history of data consumers may reveal his/her interests and the exposure of personal information during trading process against GDPR as well.
 The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
@@
     \item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
-	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
+    \item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to quality control.
 \end{itemize}
@@
 Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
-In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
+In this paper, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
 See Fig.~\ref{fig:system_design}.
 The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected.
-Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.
 
@@
 \begin{itemize}
-	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
-	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
-	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
-	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
+    \item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
+    \item We apply the subscription-based services economic model to adapt the features of IoT streaming data and clarify the importance of using a decentralized identity system for trading.
+    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy of using the protocol.
+    \item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
 \end{itemize}
@@
 The rest of this paper is organized as follows.
-In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
+In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed.
 In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
@@
 \subsection{The Publish/subscribe Communication Models Over Blockchain}
-The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
-A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.
+The pub/sub service model consists of publishers, subscribers, and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
+A lot of work in the pub/sub system built on top of blockchain focused on the reliability, scalability, and the different security issues such as, encrypted data communication, privacy-preserving data subscription, and access control of the digital asset.
 
@@
 Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised.
-However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure.
+However, the access control and encryption keys of data are enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single-point failure.
 G.
 S.
-Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
-But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.
+Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers and applied DLTs to build a distributed pub/sub system that promotes the transparency of interactions of participants and the status of data.
+With the help of the Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status.
+But data is plaintext on blockchain, in which the privacy problem of sensitive data needs to be considered carefully.
 
 In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
-The subscribers request publisher directly and ask them to save a cache space for interested data.
-The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data.
-Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data.
+The subscribers request publisher directly and ask them to save a cache space for interesting data.
+The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environments to perform such functionalities and preserve data.
+Also, the rights for accessing digital assets are more compatible in the IoT scenarios instead of copying raw data.
 Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
-The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
+The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent.
 The reputation system and the punishment rules against malicious acts of subscribers and publishers.
-Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides.
-Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.
+Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match both sides.
+Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in the ciphertext.
 
@@
 Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
-al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts.
+al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace that enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
 Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other.
-However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of information, such as provider, subscriber, and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single-point failure still exists.
 
@@
 Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
-This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
+This research takes MAM as a data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered key and entry points management with MAM that minimizes the information which data producers need to hold.
 Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
-Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
-
-Researches below adopt MAM as data storage and a secure data transmission layer.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of the system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the efficiency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
+
+The researches below adopt MAM as data storage and a secure data transmission layer.
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
-Service requesters call for proposal of interested data and accept/reject proposals from service providers.
+Service requesters call for proposals of interested data and accept/reject proposals from service providers.
 After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
-This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
+This proposal matching and the trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
 Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
@@
 The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality.
-Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures.
-The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
-And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration.
-The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM.
+Furthermore, the Back-End server operates a user-friendly interface of the marketplace and tackles all trading procedures.
+The heavy loading of Back-End server encounters the system scalability problem, single-point failure as well as malicious attacks which may damage the profits of all players.
+And the pricing strategy allows buyout but does not take subscribe/unsubscribe based diagrams into consideration.
+The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach, and trade data streams via MAM.
 With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
@@
 Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-
-Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
+Nevertheless, DLTs are often used as the backbone of these systems like data storage and also an incentive layer to encourage people to get involved in the network.
+
+Filecoin \cite{FileCoin} in the Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
+IPFS is a content-based addressing storage model in a peer-to-peer network, in which users can obtain the data with the unique hash value through the network.
+Furthermore, considering the data may lose in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
 However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
 Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents.
-Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.
+Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retrieving process.
 Nevertheless, the efficiency problems still occur if the dedicated network grows larger.
 
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
+Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then ciphertext is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
 Files are duplicated in multiple nodes to prevent data loss.
@@
 \subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+There are three major roles, data providers, data consumers, and brokers which are similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each other, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
 As shown in Fig.~\ref{fig:pub_sub_model}.
@@
 Data storage is the trust basis of data trading platforms where the data assets are reserved.
-Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
-Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
+Streaming data unlike a fixed set of data that can be verified by the hash of the whole pack of data, it consists of continually granular records of each time slot.
+Therefore, the verification such as, data integrity and source identity is narrow down to a data point as well.
 In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams.
@@
 However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}.
-Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.
-
-In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
+Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.
+
+In our work, MAM builds the trust of the platform while meeting the requirements of data trading which can be concluded below:
 
@@
     \begin{itemize}
-        \item Messages published to the Tangle are tamper-proof that against malicious modification.
+        \item Messages published to the Tangle are tamper-proof against malicious modification.
         \item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
@@
         \item The encrypted data are uploaded that only participants that have keys can decrypt.
-    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
+        \item The authorized users can retrieve data streams since data is written on the Tangle which can be queried as long as the IOTA network is alive.
         \item MAM provides forward-secrecy.
@@
 
-The centralized identity model may have single point failure in identifier management and security issues like data leakage.
-With sensitive information holding on certain authorities, the leakage caused by cyber attacks or unscrupulous organizations trading user data damage the users' privacy.
+The centralized identity model may have the single-point failure in identifier management and security issues like data leakage.
+With sensitive information holding on certain authorities, the leakage caused by cyber-attacks or unscrupulous organizations trading user data damage the users' privacy.
 Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
@@
 In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
-The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
-If a VC is verified via issuer's public key, the message will be labelled as trusted.
+The digital footprints of entities are made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
+If a VC is verified via the issuer's public key, the message will be labeled as trusted.
 Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
@@
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel.
-The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
+Through TangleID, entities get a public/private key pair, the location of the DID document, and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel.
+The public/private key pair can be used to exchange sensitive data and establish trust communication, where messages that are encrypted with a public key can only be decrypted with the private key owner.
+During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on the DID document which ensures only the subscribed consumers are accessible.
 See Fig.~\ref{fig:TangleID}
@@
     \includegraphics[width=3.5in]{TangleID}
-    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
-The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
-When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
+    \caption{To participate in the data trading, players are required to have DID document issued by TangleID.
+The consumer first needs to send a registration request to TangleID to get the MAM channel ID of the DID document and a public/private key pair for authentication.
+When the trade establishes, the consumer sends the DID MAM channel ID to the provider in order to perform encryption key exchange.
 The data provider can then retrieve the consumer's public key and encrypt the content with it.
-After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
+After the consumer gets the encrypted message, he/she can decrypt the ciphertext with the private key and finally get the encryption key of data product.}
     \label{fig:TangleID}
@@
     \includegraphics[width=4in]{smart_contract_mam}
-    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.
+    \caption{The information of identity and data streams are stored on the Tangle with MAM which is all recorded on Product Contracts.
+Participants can easily retrieve information via the Product Contract and proceed to trade.
 For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color.
@@
 It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines.
-A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency.
+A smart contract can interact with other contracts, make decisions, store data, and transfer cryptocurrency.
 All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.
@@
 In our system, \textbf{Product Contract} is made for the product launching and subscribing.
-The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
+The information on data products such as the address of the data provider, subscription fee, brokerage fee, the threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period, and the broker-verified encryption key are listed on Product Contract.
 Listing.
@@
 Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
-Binding trading and data storage to smart contract ensures consumers can always have access after payment, even if the key is lost, and providers can track and manage the authorized user list.
-
-The transparency of smart contracts bring advantages for data providers and consumers.
-One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
+Binding trading and data storage to smart contracts ensures consumers can always have access after payment, even if the key is lost, and providers can track and manage the authorized user list.
+
+The transparency of smart contracts brings advantages for data providers and consumers.
+One of the advantages is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
 For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.
@@
 To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the limited resources of low-level devices should be used on its jobs instead of handling all trading processes.
+However, the limited resources of low-level devices should be used in their jobs instead of handling all trading processes.
 Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
@@
 \label{section:MAM}
-MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
+MAM enables broadcasting encrypted and authenticated data stream, referring as a channel, on the Tangle.
 The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
@@
 A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
+To publish a MAM message to a channel, MAM deploys MSS to sign the message payload to the channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
 The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
@@
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
-Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Figure.~\ref{fig:mam_structure} shows the structure of the MAM channel/endpoint.
 
@@
 Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender.
-These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of MAM bundle.
+These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of the MAM bundle.
 However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start.
@@
 The importance of scalable key and data entry points management increases over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
+In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of the transaction and retrieve data.
 To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
@@
 %classify
-\subsubsection{Data Sreams Classification and Traceability}
+\subsubsection{Data Streams Classification and Traceability}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+For instance, sensor devices like AirBox\cite{LASS}, collect environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
 As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
@@
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in the regular operating systems.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerate the interactions with Tangle while ensuring the privacy of data providers.
 Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
@@
     \includegraphics[width=3.5in]{ta_structure}
-    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
+    \caption{Tangle-accelerator distributes IOTA API requests to idle IOTA nodes (i.e., full nodes) and provides Proof-of-Work acceleration.
 It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed.
@@
 \subsubsection{Communication Protocol}
-In the following sections, we refer the low-level devices as \textbf{endpoint}s.
+In the following sections, we refer to the low-level devices as \textbf{endpoint}s.
 MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic.
-The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth.
+The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role in endpoints with limited bandwidth.
 The pub/sub model decouples publishers and subscribers in many ways:
@@
 The publishers do not need to be alive until the response arrives.
-Messages from publisher can be served as send-and-forget fashion.
+Messages from the publisher can be served as send-and-forget fashion.
 \end{itemize}
@@
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:
+In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of the steps are addressed below:
 
 \begin{enumerate}
-    \item Generate symmetric keys with unique device identifier and Message Authentication Code (MAC) of the previous message.
-If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message.
+    \item Generate symmetric keys with the unique device identifier and Message Authentication Code (MAC) of the previous message.
+If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message.
 Key Derivation Function (KDF) is used to generate the symmetric keys.
-    \item Compute the Message Authentication Code (MAC) of current message with Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
-    \item Apply the generated symmetric key to encrypt plaintext.
-    \item Concatenate the MAC of current message would and the MAC of previous message, and then the result will be signed with digital signature algorithm.
+    \item Compute the Message Authentication Code (MAC) of current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
+    \item Apply the generated symmetric key to encrypt the plaintext.
+    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
     \item Send the ciphertext along with signed MAC.
@@
 Each of them can be chosen on the basis of the working hardware and scenario by developers.
-On some certain devices, hardware acceleration would be supported.
-With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
+On certain devices, hardware acceleration would be supported.
+With hardware-acceleration, the elapsed time could be dropped a step more.
+For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
 
 \subsubsection{Register with Tangle-accelerator}
-User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
-Once tangle-accelerator receive the Seed from edge device, it would return a unique user identifier which can be mapping to corresponding Seed when edge devices send requests.
+Users with channel seed can acquire channel chain ownership.
+Seed is generated by unique hardware information on the edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on the MAM channel chain.
+Once the Tangle-accelerator receives the Seed from the edge device, it would return a unique user identifier that can be mapped to corresponding Seed when edge devices send requests.
 Asymmetric encryption is utilizing during the process of exchanging seed.
-Digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed will not be exposed during communication after an edge device is successfully registered.
+The digital signature should be taken at the same time to ensure data integrity.
+Once the seed has been successfully exchanged, the edge device is successfully registered on the specific tangle-accelerator.
+Thus, the seed will not be exposed during communication after an edge device is successfully registered.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
+E2EE helps a lot with low-level edge devices utilizing blockchain service. It dramatically reduces the execution time encryption takes. However, we met two challenges in the E2EE process:
 
 \paragraph{Linear Time to Read Message}
-It is linear time to decrypt message instead of constant time.
+It is linear time to decrypt messages instead of constant time.
 Nevertheless, there is one way to speed up the message decryption process.
-A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
+A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at the local side.
 This procedure can reduce the time spending on internet communication.
@@
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
-Spam would cause subscribers wasting plenty of time on decrypting useless messages.
+Spam would cause subscribers to waste plenty of time on decrypting useless messages.
 To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
@@
 \subsection{Prerequisite}
-All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication.
+All participants are required to register on TangleID to get a DID document and public/private key pair for sensitive contents exchange and authentication.
 An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.
@@
 
-The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key; otherwise the process will be aborted.
+The details of data products, such as data price, MAM channel/endpoint ID, and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, data provider computes the digest of sensitive contents with a hash function, and sends the digest as well as the signature to brokers.
+The broker can first verify the signature from data provider with the public key on the DID document.
+If it's valid, then the broker uploads the key; otherwise, the process will be aborted.
 Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
-This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription.
+This procedure allows data consumers to check whether the encryption key is uploaded by the committed data provider and broker before subscription.
 Furthermore, the encryption key can only be uploaded/updated under two circumstances: 1.) the new product launching.
@@
 Finally, the data product is launched and data providers can start uploading data.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
-The product launching workflow is shown in Fig.~\ref{fig:launching_product} and Listing.~\ref{lst:key_certification} lists the Solidity codes of key certification process.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to the Product Contract via a broker.
+The product launching workflow is shown in Fig.~\ref{fig:launching_product} and Listing.~\ref{lst:key_certification} lists the Solidity codes of the key certification process.
 
@@
     \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of the encryption key and the one that signed with his/her private key.
+After the broker receive the request, he/she performs digital signature as well to prove the encryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
     \label{fig:key_upload}
@@
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
-
-Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public.
-Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by the data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.
+
+Transferring the encryption key on smart contracts instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to the public.
+Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed with the trading process.
 The key sending process is shown in Fig.~\ref{fig:key_exchange} and Listing.~\ref{lst:key_exchange}.
@@
 Data consumers can unsubscribe to data products when they're not interested anymore.
-Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structre, since the delete function in Solidity does not remove the actual element but reseting it to default value.
-When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
+Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structure since the delete function in Solidity does not remove the actual element but resetting it to default value.
+When data consumers trigger the unsubscribe event, a withdraw function is executed to pay a subscription fee to providers and return the rest of the fee back to consumers.
 The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
@@
 In SaaS, the cancellation fee is a way to make sure the service providers are protected.
-It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
-However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
-
-Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
-The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+It is commonly used in pre-paid subscription-based services that allows service providers to charge cancellation fee if subscribers drop out at the early stage.
+However, asking the cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
+
+Also, data providers will change the encryption key of the data product to prevent unsubscribers access to the rest of the data.
+The new key should be updated to the remaining subscribers in the $consumer2Purchase$ list in the Product Contract.
 Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
@@
 \label{section:refund}
-Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
+Data subscription is a high risk in which data provider may not upload data as the agreement set after receiving the subscription fee.
 Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
@@
 Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
-If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
+If they can not reach a consensus of the brokerage fee during the subscription period, brokers can launch a refund and refuse to handle the product.
 Third, the refund could launch by providers when they fail to maintain products as committed.
@@
 \label{section:mam_performance}
-It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
+It is worth making a claim that all participants in the data subscription platform do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
 Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle.
@@
 The interactions between data providers and MAM can be frequent.
-Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottlenecks in the data subscription platform.
 
@@
     \item    Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
-	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
+    \item    Proof-of-Work (PoW): An algorithm that prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
 \end{itemize}
 
-Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint.
-The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.
+Tips selection requires a stable network connection to wait for the response from IOTA full nodes, and PoW requires enough computation resources to perform.
+Fig.~\ref{fig:mam_send} shows the probability distribution function of publishing a message to MAM endpoint.
+The time of Raspberry Pi 3 distributed widely since the randomness of PoW has a huge impact while all the tests on PC remain in an acceptable range.
 
@@
 
-The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
-Furthermore, sensors with the low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM and even trading process with subscribers simultaneously.
-
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework.
-Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
+The simulation results above indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority of hardware in the IoT scenarios.
+Furthermore, sensors with low computing power and unstable internet connection are not able to have enough resources to handle data collection, data transmission on MAM, and even trading process with subscribers simultaneously.
+
+Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such a framework.
+Brokers can be PCs or powerful machines that run Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
 Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator.
@@
 \subsubsection{Experiment}
-Applying remote PoW greatly reduce the elapsed time.
+Applying remote PoW greatly reduces the elapsed time.
 Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
@@
 What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending messages to tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
@@
 The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
-In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA, respectively.
 
@@
     \label{tab:mam_vs_e2ee}
-    \resizebox{0.5\textwidth}{!}{
+		\centering
         \begin{tabular}{|c||c|c|}
@@
         \end{tabular}
-    }
 \end{table}
@@
 \subsubsection{Time Complexity}
-With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+With the given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
 HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which causes the time complexity is $O(n)$, too.
 Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
@@
 \subsection{Smart Contract}
-In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.
+In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser-based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing trade.
 On top of this evaluation, data providers can consider how to set the price to eventually generate profits.
@@
 
-\begin{table*}[h]
+\begin{table}[h]
     \caption{Gas consumption for each function of Product Contract}
@@
     }
-\end{table*}
+\end{table}
 
@@
 Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at the start.
 Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
@@
 For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+However, in our trading model, we preserve a lot of information in the Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers, and data consumers via storing states to Product Contract.
 Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
+However, using the zero-knowledge protocol is out of the scope of this paper.
 
 Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
+We combine the Gas usage of providers and brokers since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe, and w/ refund and unsubscribe.
 The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
@@
 Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
+However, the data provider needs to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the number of remaining subscribers.
 This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Hence, an efficient, low-cost, and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
 Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
@@
 Compared to previous works, we 1.) identify a trustless data trading infrastructure, 2.) ensure the confidentiality of scalable IoT-based sensor data, and 3.) consolidate the economic incentives in the entire ecosystem.
-Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to Tangle-accelerators, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to Tangle-accelerators, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
 In particular, this work discusses the workflow for subscription-based IoT data trading: Launching, subscribing, unsubscribing, and refund.
@@
 \label{section:future_work}
-In the subscription-based data trading, there are some issues that worth discussing and improving.
+In the subscription-based data trading, there are some issues worth discussing and improving.
 Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
-Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
+Therefore, it is worth discussing how zero-knowledge protocol could used to exchange the key with lower cost, and even validate the key within transfers.
 Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
-However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
-
-Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+However, issues such as the minimum number of brokers needed to operate the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading processes when on crashed.
+
+Third, to let consumers search and find interesting data products, a search engine is needed to collect all distributed data products, which might need the authority to design and run the service.
 The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
-Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently, and it is also an interesting issue to discuss.
 

### 2020-08-05 paper.tex
Fix grammar and typos

--- 2020-08-05 paper.tex
@@
 As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.
+With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets.
+Therefore, the data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.
 
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}.
+In contrast to the existing solutions targeting static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity, and high variety of real-time data streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 %trust: 對系統、對身份、對資料
-In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
+In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
 Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
@@
 Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
-Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices to focus on their jobs while gaining the rewards.
+Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.
 
@@
 Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data.
-The data validation and traceability are achieved via Ethereum smart contract.
+Data validation and traceability are achieved via the Ethereum smart contract.
 But data is plaintext on blockchain that the system is not appropriate for sensitive data.
@@
 Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
-The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent.
+The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent.
 Yet, without brokers, participants may need to reveal more sensitive information in order to communicate.
@@
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
-However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.
+However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single-point failure still exists.
 
-Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel.
+Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof, and authentication functionalities by tailoring messages to a channel.
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer.
-The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM.
-Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.
+The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach, and trade data streams via MAM.
+Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of the trading model.
 
@@
 Data storage is the trust basis of data trading platforms where the data assets are reserved.
-Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots.
-Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well.
-In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams.
+Streaming data unlike a fixed set of data that can be verified by the hash of the whole pack of data consists of continually granular records of each time slot.
+Therefore, the verification such as data integrity and source identity is narrow down to a data point as well.
+In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of the IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams.
 It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible.
-2) \textbf{Integrity}, messages written on the Tangle are immutable.
+2) \textbf{Integrity}, messages were written on the Tangle are immutable.
 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents.
@@
 
-Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network).
+Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing content to the IOTA network).
 However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated.
-Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.
+Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.
 
@@
 
-Centralized identity model may have single point failure in identifier management and security issues like data leakage.
-With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
+A centralized identity model may have the single-point failure in identifier management and security issues like data leakage.
+With sensitive information holding on certain authorities, whether the data leakage is caused by cyber-attacks or unscrupulous organizations trading user data, the users' privacy is damaged.
 Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
@@
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
-The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.
+Through TangleID, entities get a public/private key pair, the location of DID document, and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
+The public/private key pair can be used to exchange sensitive data and establish trust communication, where messages that are encrypted with a public key can only be decrypted with the private key owner.
+During the data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.
 
@@
 In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures.
-Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream.
-The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.
+Product Contract records the MAM channel/endpoint ID of both the DID document of participants and the data stream.
+The subscription and brokerage fee, and the broker-certified encryption key are listed on the Product Contract as well.
 
@@
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
-Section.~\ref{section:mam_streams} and ~\ref{section:mam_features} explain the structure, fuctions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.
+Section.~\ref{section:mam_streams} and ~\ref{section:mam_features} explain the structure, functions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.
 
@@
 A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
-The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle, represents the ownership of all things associated with the user in the IOTA ecosystem.
+To publish a MAM message to the channel, MAM deploys MSS to sign the message payload to the channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
+The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle represents the ownership of all things associated with the user in the IOTA ecosystem.
 
@@
 This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.
-Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.
+Figure.~\ref{fig:mam_structure} shows the structure of the MAM channel/endpoint.
 Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data.
@@
 \label{section:ta_endpoint}
-MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating system.
-To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
+MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating systems.
+To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerate the interactions with Tangle while ensuring the privacy of data providers.
 Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
@@
 The plaintext will be encrypted with this lightweight end-to-end-encryption.
-The E2EE process ensures only authorized subscribers can read the messages published on MAM.
+The E2EE process ensures that only authorized subscribers can read the messages published on MAM.
 
@@
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:
+In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of the steps are addressed below:
 
 \begin{enumerate}
-    \item Generate symmetric keys with unique device identifier and Message Authentication Code (MAC) of the previous message.
-If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message.
+    \item Generate symmetric keys with a unique device identifier and Message Authentication Code (MAC) of the previous message.
+If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message.
 Key Derivation Function (KDF) is used to generate the symmetric keys.
-    \item Compute the Message Authentication Code (MAC) of current message with Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
-    \item Apply the generated symmetric key to encrypt plaintext.
-    \item Concatenate the MAC of current message would and the MAC of previous message, and then the result will be signed with digital signature algorithm.
+    \item Compute the Message Authentication Code (MAC) of the current message with the Hash-based Message Authentication Code(HMAC).
+Both plaintext and the symmetric key would be given as parameters in HMAC.
+    \item Apply the generated symmetric key to encrypt the plaintext.
+    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
     \item Send the ciphertext along with signed MAC.
@@
 Each of them can be chosen on the basis of the working hardware and scenario by developers.
-On some certain devices, hardware acceleration would be supported.
-With hardware acceleration, the elapsed time could be dropped a step more.
-For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}
+On certain devices, hardware acceleration would be supported.
+With hardware-acceleration, the elapsed time could be dropped a step more.
+For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}
 
 \subsubsection{Time Complexity}
-In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature.
+In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and ECDSA P-256 for digital signature.
 In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length.
 HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which causes the time complexity is $O(n)$, too.
 Therefore, the E2EE protocol takes only linear time versus arbitrary string length.
@@
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service.
-It dramatically reduces execution time encryption takes.
+E2EE helps a lot for low-level edge devices utilizing blockchain service.
+It dramatically reduces the execution time encryption takes.
 However, there are some challenges in the E2EE process.
@@
 However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a Accel which is operated by unknown third-party.
+It is risky for an edge device connects to an Accel which is operated by an unknown third-party.
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
-Spam would cause subscribers wasting plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.
+Spam would cause subscribers to waste plenty of time on decrypting useless messages.
+To prevent edge devices from the annoying attack, connecting to a known, trustworthy Accel would be the easiest solution.
 
@@
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel the subscription. A discussion of refunds is illustrated.
 
 \subsection{Prerequisite}
-All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication.
+All participants are required to register on TangleID to get a DID document and public/private key pair for sensitive contents exchange and authentication.
 An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.
@@
 \subsection{Launch Data Products}
-To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers.
+To launch a data product, brokers are responsible to create a Product Contract and record the metadata of the data product for data providers.
 The Product Contract will not accept subscriptions until brokers certify the encryption key.
-To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers.
-The broker verify the signature with the public key on provider's DID document.
-If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted.
-The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently.
+To certify the encryption key, the data provider first computes its digest with the hash function and sends the digest as well as the signature to brokers.
+The broker verifies the signature with the public key on the provider's DID document.
+If it's valid, the broker will sign and upload the key to the Product Contract, otherwise, the process will be aborted.
+The number of key uploading times is restricted in order to avoid data provider uploading fake keys frequently.
 If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to the Product Contract via a broker.
 Finally, the data product is launched and data providers can start uploading data.
@@
     \includegraphics[width=3.5in]{key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of the encryption key and the one that signed with his/her private key.
 After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
@@
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
-The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it.
+The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by the data provider and written on the Product Contract, which ensures only data consumers can decode it.
 
-Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public.
-Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process.
+Transferring the encryption key on smart contracts instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to the public.
+Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed with the trading process.
 The key sending process is shown in Fig.~\ref{fig:key_exchange}.
@@
 \label{section:refund}
-The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section.
-As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee.
-However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
+The refund topics are complicated in subscription services, therefore, we illustrated the challenges in this section.
+As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee.
+However, issues such as consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
 Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
-If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product.
+If they can not reach a consensus of the brokerage fee during the subscription period, brokers can launch a refund and refuse to handle the product.
 Third, the refund could launch by providers when they fail to maintain products as committed.
@@
 \subsection{Gas usage of the Product Contract}
-We investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix.
-On top of this evaluation, data providers can consider how to set the subscription and brokereage fee to eventually generate profits.
+We investigate the cost of executing a Product Contract with Ethereum web browser-based IDE Remix.
+On top of this evaluation, data providers can consider how to set the subscription and brokerage fee to eventually generate profits.
 The estimated cost is in USD, where $1\ Ether = 238\ USD$ at the time of writing, yet the price is dynamic from time to time.
-To conquer this condition, we analyze with a fixed range of Gas price.
+To conquer this condition, we analyze with a fixed range of Gas prices.
 According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price.
-Note that data uploading is only related to MAM operations on the Tangle without transaction fee.
+Note that data uploading is only related to MAM operations on the Tangle without transaction fees.
 Therefore, the Gas estimation only includes trading processes.
-The high transaction fee for brokers are due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
+The high transaction fee for brokers is due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
 Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
@@
 \label{section:mam_performance}
-In the following evaluations, all devices run with IOTA client library instead of IOTA full nodes.
+In the following evaluations, all devices run with the IOTA client library instead of IOTA full nodes.
 MAM is the primary key to resolve all the storage difficulties discussed in previous sections.
-The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottleneck in data marketplace.
+The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottlenecks in the data subscription platform.
 In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment.
@@
 The tips are provided by IOTA full nodes.
-2.) \textbf{Proof-of-Work (PoW)}: An algorithm which prevents Denial of Service and spam attacks on a network.
+2.) \textbf{Proof-of-Work (PoW)}: An algorithm that prevents Denial of Service and spam attacks on a network.
 
-Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has huge impact.
-The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios.
-Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such framework.
+Tips selection requires a stable network connection to wait for the response from IOTA full nodes, and PoW requires enough computation resources to perform.
+The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has a huge impact.
+The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority of hardware in the IoT scenarios.
+Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such a framework.
 Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
@@
 The result directs a way to improve MAM.
-Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier should be removed.
+Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier that should be removed.
 With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.
@@
 In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
-In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
+In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA, respectively.
 
@@
 \begin{enumerate}
-    \item Write key information in header
+    \item Write key information in the header
     \item Write and encrypt input payload
@@
 Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively.
-The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
-The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
-Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy.
+The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+The slope of the result of E2EE is much flatter than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
+Under our design which delegates MAM operations with Accel and the presented E2EE protocol, the data providers can include resource-constrained hardware into the data subscription economy.
 E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
@@
 This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
-To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design.
+To clarify the data ownership and identity verification, the data stream is stored on the Tangle, transmitted through MAM, and automated by Ethereum smart contracts in our design.
 Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem.
-Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
-In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting, and implementing the refunding procedure.
 

### 2020-08-07 paper.tex
Fix font type error

@@
 \usepackage{listings}
+\usepackage[T1]{fontenc}
 \graphicspath{{./images/}}
@@
 In addition, an automated subscription procedure is also demanded for the sake of data monetization.
-In this paper, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
+In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage built upon cryptographic message protocols allows transmitting, accessing, and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
+The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
 \end{abstract}

### 2020-08-11 paper.tex

--- 2020-08-05 paper.tex
@@
 \usepackage{multirow}
+\usepackage{hhline}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets.
+With the diverse data streams generated by different entities and carried across organizations among expanding number of interconnected devices, it is a challenge for data holders to share and track their data assets.
 Therefore, data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.
@@
 The subscription-based models (e.g.
-SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming, and software, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
+SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming, and software, which can bring enormous operating incomes and offer advantages that allows service providers to have the flexibility in resource planning as well as a better prediction of revenue streams.
 And for service consumers, they can subscribe and unsubscribe the services at will at any time.
@@
 The compromise of routers or CA can break the trust of the entire system, and the data portability of using third-party services is still under suspicion.
-Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}.
+Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or a cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}.
 Besides CA and storage, the subscription history of data consumers may reveal his/her interests and the exposure of personal information during trading process against GDPR as well.
@@
 \subsection{Contributions}
-The contributions in the paper are summarized as follow:
+The contributions in the thesis are summarized as follow:
 \begin{itemize}
@@
     \item We apply the subscription-based services economic model to adapt the features of IoT streaming data and clarify the importance of using a decentralized identity system for trading.
-    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy of using the protocol.
-    \item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
+    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy.
+    \item We analyze the cost of the designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
 \end{itemize}
 
-\subsection{Paper Organization}
-The rest of this paper is organized as follows.
+\subsection{Thesis Organization}
+The rest of this thesis is organized as follows.
 In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed.
@@
 The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.
+Finally, we conclude the thesis in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.
 
@@
 However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
-Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents.
+Also, users can have a hard time finding the contents quickly if data is not widely available, and the large amount of IPFS nodes and contents.
 Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retrieving process.
@@
 The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+$i$ is the number of data when unsubscription request is launched, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
 
@@
 Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at the start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification} (0.022 - 0.0834 Ether)) that are related to key certification and key exchange need a lot of gas as well.
 Storage on blockchain is expensive.
@@
 We combine the Gas usage of providers and brokers since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe, and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
+We conclude the three situations during the trading process: 1.) basic cost of a trade, including product launching, subscribing, encryption key uploading and withdraw.
+2.) refund operation, the fees needed for launching refund.
+3.) unsubscribe operation, the fees needed for launching unsubscription.
 
@@
 
-When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
+When a consumer request a refund, he/she need to pay 0.0008 - 0.0003 Ether additionally.
 Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
+Observing the situation of unsubscribe operation, it does not cost much Ether for consumers.
 However, the data provider needs to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the number of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
+This would cost data providers a lot if the unsubscription is frequent or many remaining consumers are left.
 Hence, an efficient, low-cost, and secure way to perform access control while recording the unsubscription process transparent is important.
@@
         \hline
-        \multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+        \multirow{2}{*}{basic cost} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
          & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
-        \hline
-        \multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-         & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
-        \hline
-        \multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
-         & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
-        \hline
-        \multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
-         & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
+        \hhline{|=|=|=|=|=|=|}
+        \multirow{2}{*}{refund} & provider & 0 & 0 & 0 & 0 \\
+         & consumer & 0.00008 & 0.0209 & 0.0003 & 0.0761 \\
+        \hline
+        \multirow{2}{*}{unsubscribe} & provider & 0.002N & 0.497N & 0.007N & 1.806N \\
+         & consumer & 0.00006 & 0.0143 & 0.0002 & 0.0519 \\
         \hline

### 2020-08-11 ASRLab_Thesis_Template/thesis/thesis.tex
Update to the latest changes

--- 2020-07-09 ASRLab_Thesis_Template/thesis/thesis.tex
@@
 %\usepackage{draftwatermark}  % For DOI watermark
-\usepackage{listings, makecell, multirow}
+\usepackage{listings, makecell, multirow, hhline}
+\usepackage{amsmath}
+\usepackage[customcolors]{hf-tikz}
 
@@
     \makebox[8cm][s]{\Huge 資訊工程研究所}\vspace{1cm}		\\
-    \makebox[5cm][s]{\Huge 碩士論文}\vspace{1cm}			\\
-    \makebox[5cm][c]{\Huge (初稿)}
+    \makebox[5cm][s]{\Huge 碩士論文}\vspace{1cm}			%\\
+    %\makebox[5cm][c]{\Huge (初稿)}
   \end{center}
@@
     \makebox[\textwidth][c]{\parbox{\paperwidth}
-    {\center \Large 針對物聯網資料交易的 \\ 去中心化基礎建設}}
+    {\center \Large 針對物聯網訂閱型資料交易的 \\ 去中心化基礎建設}}
     \vspace{0.5cm}\\
@@
 % ------------------------------------------------
-%\newpage
-%\phantomsection
-%\thispagestyle{empty}
-%\includepdf[pages=-]{context/oral/oral_example.pdf}
-%\clearpage
+\newpage
+\phantomsection
+\thispagestyle{empty}
+\includepdf[pages=-]{context/oral/oral_vvn.pdf}
+\clearpage
 
@@
 
-除了外籍生, 本地生和僑生都是要編寫中文和英文摘要. 論文以中文撰寫須以英文補寫 800 至 1200 字數的英文延伸摘要 (Extended Abstract), 如需要的話請修改`./context/abstract/extended.tex'.
-
-外籍生則可免填中文摘要, 而在上傳時網頁資訊需填上`NONE'.
+在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量來計費，這類似於軟體即服務 (Software-as-a-Service)，一種基於訂閱的定價模型。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料所有權和完整性。此外，訂閱流程的自動化亦是資料貨幣化中不可或缺的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。
 
@@
 
-The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us.
-Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources.
-The real-time data exchange among devices are periodical that only data in a specific time period is interested.
-Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case.
-Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set.
+Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy to share and trade their resources.
+Monetizing the real-time data on top of the publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model.
 This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe.
-However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
-Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system.
-Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants.
-Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required.
-In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure.
+However, streaming data increases the importance and difficulties of dynamic data ownership and identity verification.
+A trustless data trading infrastructure is required where the entities can trade, validate data ownership and integrity without trusting any services.
+In addition, an automated subscription procedure is also demanded for the sake of data monetization.
+In this paper, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.
-The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
+The storage built upon cryptographic message protocols allows transmitting, accessing, and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
 
@@
 As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
-With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets.
-Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.
+With the diverse data streams generated by different entities and carried across organizations among expanding number of interconnected devices, it is a challenge for data holders to share and track their data assets.
+Therefore, data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.
 
 %publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
-In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}.
+In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity, and high variety of real-time "Big Data" streams\cite{BigData}.
 As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline.
@@
 % SaaS
-The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage.
+The economic incentive model in our proposed IoT data trading platform works as a subscription service that valuates the payments by data usage.
 The subscription-based models (e.g.
-SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams.
-And for service consumers, they can subscribe and unsubscribe the services at will at anytime.
-The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform.
+SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming, and software, which can bring enormous operating incomes and offer advantages that allows service providers to have the flexibility in resource planning as well as a better prediction of revenue streams.
+And for service consumers, they can subscribe and unsubscribe the services at will at any time.
+The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes good circulation of the platform.
 In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
@@
 %trust: 對系統、對身份、對資料
-In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
+In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
 Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform.
-In current systems, trusted third-party authority like CA is widely adopted to certify each member.
+In current systems, a trusted third-party authority like certificate authority (CA) is widely adopted to certify each member.
 However, building trust upon CA is dangerous and fragile.
-The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion.
-Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well.
+The compromise of routers or CA can break the trust of the entire system, and the data portability of using third-party services is still under suspicion.
+Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or a cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}.
+Besides CA and storage, the subscription history of data consumers may reveal his/her interests and the exposure of personal information during trading process against GDPR as well.
 The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
 
-Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
+Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
 \begin{itemize}
@@
     \item \textbf{Confidentiality}.
-1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
+1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.
     \item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
-	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
+    \item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to quality control.
 \end{itemize}
@@
 Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
-In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
+In this paper, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
 See Fig.~\ref{fig:system_design}.
-The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards.
-Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.
+The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected.
+Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.
 
 \subsection{Contributions}
-The contributions in the paper are summarized as follow:
+The contributions in the thesis are summarized as follow:
 \begin{itemize}
-	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
-	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
-	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
-	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
+    \item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
+    \item We apply the subscription-based services economic model to adapt the features of IoT streaming data and clarify the importance of using a decentralized identity system for trading.
+    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy.
+    \item We analyze the cost of the designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
 \end{itemize}
-
-\subsection{Paper Organization}
-The rest of this paper is organized as follows.
-In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated.
+\clearpage
+
+\subsection{Thesis Organization}
+The rest of this thesis is organized as follows.
+In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed.
+In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
 In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
@@
 The analysis results are given in Section~\ref{section:evaluation}.
-Finally, we conclude the paper in Section~\ref{section:conclusion}.
+Finally, we conclude the thesis in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.
 
@@
 Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange.
-This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
-A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold.
+This research takes MAM as a data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.
+A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered key and entry points management with MAM that minimizes the information which data producers need to hold.
 Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading.
-However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
-
-Researches below adopt MAM as data storage and a secure data transmission layer.
+However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of the system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.
+Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the efficiency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.
+
+The researches below adopt MAM as data storage and a secure data transmission layer.
 The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading.
-Service requesters call for proposal of interested data and accept/reject proposals from service providers.
+Service requesters call for proposals of interested data and accept/reject proposals from service providers.
 After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens.
-This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
+This proposal matching and the trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}.
 Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.
@@
 \subsection{Distributed Storage System}
+\label{section:distributed_storage}
 Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
-Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.
-Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
-IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network.
-However, no cryptographic system is applied for user-uploaded files.
-Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
+Nevertheless, DLTs are often used as the backbone of these systems like data storage and also an incentive layer to encourage people to get involved in the network.
+
+Filecoin \cite{FileCoin} in the Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage.
+IPFS is a content-based addressing storage model in a peer-to-peer network, in which users can obtain the data with the unique hash value through the network.
+Furthermore, considering the data may lose in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed.
+However, the IoT sensor devices have limited space which is not appropriate to preserve generated data.
+Also, users can have a hard time finding the contents quickly if data is not widely available, and the large amount of IPFS nodes and contents.
+Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retrieving process.
+Nevertheless, the efficiency problems still occur if the dedicated network grows larger.
+
+Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then ciphertext is sent to the Sia nodes that rent the storage in Siacoin through smart contracts.
 Files are duplicated in multiple nodes to prevent data loss.
@@
 \label{section:design_thinking}
-\subsection{Data subscription-based trading platform players}
-There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model.
-But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
+\subsection{Data Subscription-based Trading Platform Players}
+There are three major roles, data providers, data consumers, and brokers which are similar to the pub/sub messaging model.
+But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each other, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.
 As shown in Fig.~\ref{fig:pub_sub_model}.
@@
 
-In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:
+Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network).
+However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}.
+Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.
+
+In our work, MAM builds the trust of the platform while meeting the requirements of data trading which can be concluded below:
 
@@
     \includegraphics[width=6.5in]{img/channel_and_key}
-    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures.
+    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures.
 Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
@@
 
-Centralized identity model may have single point failure in identifier management and security issues like data leakage.
-With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged.
+The centralized identity model may have the single-point failure in identifier management and security issues like data leakage.
+With sensitive information holding on certain authorities, the leakage caused by cyber-attacks or unscrupulous organizations trading user data damage the users' privacy.
 Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.
+The decentralized identity model give back the controls of data to users that can resolve the aforementioned concerns in the centralized one.
 
 In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata.
-The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
-If a VC is verified via issuer's public key, the message will be labelled as trusted.
+The digital footprints of entities are made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments.
+If a VC is verified via the issuer's public key, the message will be labeled as trusted.
 Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.
@@
 
-Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel.
-The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner.
-During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.
-See Fig.~\ref{fig:TangleID}
+Through TangleID, entities get a public/private key pair, the location of the DID document, and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel.
+The public/private key pair can be used to exchange sensitive data and establish trust communication, where messages that are encrypted with a public key can only be decrypted with the private key owner.
+During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on the DID document which ensures only the subscribed consumers are accessible.
+See Fig.~\ref{fig:TangleID}.
 
@@
     \includegraphics[width=5.5in]{img/TangleID}
-    \caption{To participate the data trading, players are required to have DID document issued by TangleID.
-The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication.
-When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange.
+    \caption{To participate in the data trading, players are required to have DID document issued by TangleID.
+The consumer first needs to send a registration request to TangleID to get the MAM channel ID of the DID document and a public/private key pair for authentication.
+When the trade establishes, the consumer sends the DID MAM channel ID to the provider in order to perform encryption key exchange.
 The data provider can then retrieve the consumer's public key and encrypt the content with it.
-After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
+After the consumer gets the encrypted message, he/she can decrypt the ciphertext with the private key and finally get the encryption key of data product.}
     \label{fig:TangleID}
@@
 With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved.
-In our system, \textbf{Product Contract} is made for the product launching and trading.
-The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract.
+In our system, \textbf{Product Contract} is made for the product launching and subscribing.
+The information on data products such as the address of the data provider, subscription fee, brokerage fee, the threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period, and the broker-verified encryption key are listed on Product Contract.
 Listing.
 \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM.
+
 Furthermore, the participants can exchange encryption keys without any authorities via smart contracts.
-Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.
+Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.
+Binding trading and data storage to smart contracts ensures consumers can always have access after payment, even if the key is lost, and providers can track and manage the authorized user list.
 
@@
     \includegraphics[width=5.5in]{img/smart_contract_mam}
-    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts.
-Participants can easily retrieve information via Product Contract and proceed trading.
+    \caption{The information of identity and data streams are stored on the Tangle with MAM which is all recorded on Product Contracts.
+Participants can easily retrieve information via the Product Contract and proceed to trade.
 For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color.
-The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
+The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
     \label{fig:smart_contract_mam}
@@
 
-The transparency of smart contracts bring advantages for data providers and consumers.
-One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
-For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has.
-The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.
+The transparency of smart contracts brings advantages for data providers and consumers.
+One of the advantages is that the trading states and progress are visible and verifiable which profits providers and consumers respectively.
+For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.
+The enforcement of smart contracts also ensures the rights of participants that they fulfill the agreed contract under any circumstances.
 
@@
 
-\subsection{Enable computation tasks delegation to broker with privacy}
+\subsection{Enable Computation Tasks Delegation to Broker with Privacy}
 To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
-However, the resources of low-level devices are precious which should be used to focus on its jobs.
+However, the limited resources of low-level devices should be used in their jobs instead of handling all trading processes.
 Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.
-
-The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts.
-To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers.
-Broker can first verify the signature from data provider with the public key on DID document.
-If it's valid, then the broker uploads the key, otherwise the process will be aborted.
-Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract.
-The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently.
-If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds.
-Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=5.5in]{img/key_upload}
-    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key.
-After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
-    \label{fig:key_upload}
-\end{figure}
+The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM and record encryption keys to smart contracts without knowing the contents.
+The encryption key upload procedure is illustrated in Section.~\ref{section:launch_data_product}.
 
@@
 \label{section:MAM}
-MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle.
+MAM enables broadcasting encrypted and authenticated data stream, referring as a channel, on the Tangle.
 The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only.
 With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.
+Section.~\ref{section:mam_streams} to ~\ref{section:mam_features} explain the structure, fuctions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.
 
 \subsection{The Message Streams}
+\label{section:mam_streams}
 A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload.
-To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
+To publish a MAM message to a channel, MAM deploys MSS to sign the message payload to the channel, where $channel\ ID = root$ i.e., the MSS Merkle root.
 The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.
@@
 The importance of scalable key and data entry points management increases over time.
-In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data.
-Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems.
-Assuming the length of data stream is 7, and each record is encrypted with the same key.
-With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.
-
-\begin{table}[htbp]
-	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
-	\label{tab:mam_scalability}
-	\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
-		\hline
-		keys & 1 & 1 \\ 
-		\hline
-		entry points & 1 & 7 \\ 
-		\hline
-	\end{tabular}
-	\end{center}
-\end{table}
+In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of the transaction and retrieve data.
+To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
+\clearpage
 
 %classify
-\subsubsection{Data Sreams Classification}
+\subsubsection{Data Streams Classification and Traceability}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
-For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs.
-Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
-To do the classification in other distributed storage also encounters the aforementioned scalability problem.
-
-%data trace
-\subsubsection{A Traceable Data Stream}
-Data traceability is an important security issue that allows users to track the changes of data.
-Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity.
-Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions.
-MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
+For instance, sensor devices like AirBox\cite{LASS}, collect environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products.
+As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
 
@@
     \includegraphics[width=5.5in]{img/ta_structure}
-    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration.
+    \caption{Tangle-accelerator distributes IOTA API requests to idle IOTA nodes (i.e., full nodes) and provides Proof-of-Work acceleration.
 It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed.
@@
 \begin{enumerate}
-    \item Generate symmetric keys with unique device identifier and Message Authentication Code (MAC) of the previous message.
-If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message.
+    \item Generate symmetric keys with the unique device identifier and Message Authentication Code (MAC) of the previous message.
+If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message.
 Key Derivation Function (KDF) is used to generate the symmetric keys.
-    \item Compute the Message Authentication Code (MAC) of current message with Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
-    \item Apply the generated symmetric key to encrypt plaintext.
-    \item Concatenate the MAC of current message would and the MAC of previous message, and then the result will be signed with digital signature algorithm.
+    \item Compute the Message Authentication Code (MAC) of current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
+    \item Apply the generated symmetric key to encrypt the plaintext.
+    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
     \item Send the ciphertext along with signed MAC.
@@
 
+\begin{table}[htbp]
+    \caption{AES256 Encryption Performance Numbers}
+    \label{tab:AES_NI}
+    \begin{center}
+        \begin{tabular}{ |c||c|c|c|  }
+            %\hline
+            %\multicolumn{4}{|c|}{} \\
+            \hline
+            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
+            \hline
+            50 MB  & 1026  & 563   & 45.13 \\
+            100 MB & 2036  & 1297  & 36.30 \\
+            200 MB & 4282  & 2984  & 30.31 \\
+            512 MB & 10754 & 6401  & 40.48 \\
+            1 GB   & 23976 & 15721 & 34.43 \\
+            \hline
+        \end{tabular}
+    \end{center}
+\end{table}
+
 The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
-Each of them can be chosen according to the working hardware and scenario.
-On some hardwares, the developers can choose the cryptographic methods with hardware acceleration.
-With hardware acceleration, the elapsed time could be dropped a step more.
+Each of them can be chosen on the basis of the working hardware and scenario by developers.
+On certain devices, hardware acceleration would be supported.
+With hardware-acceleration, the elapsed time could be dropped a step more.
+For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
 
 \subsubsection{Register with Tangle-accelerator}
-User with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain.
+Users with channel seed can acquire channel chain ownership.
+Seed is generated by unique hardware information on the edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on the MAM channel chain.
+Once the Tangle-accelerator receives the Seed from the edge device, it would return a unique user identifier that can be mapped to corresponding Seed when edge devices send requests.
 Asymmetric encryption is utilizing during the process of exchanging seed.
-Digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator.
-Thus, seed will not be exposed during communication after an edge device is successfully registered.
+The digital signature should be taken at the same time to ensure data integrity.
+Once the seed has been successfully exchanged, the edge device is successfully registered on the specific tangle-accelerator.
+Thus, the seed will not be exposed during communication after an edge device is successfully registered.
 
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE process:
-
-\paragraph{Linear Time to Read Message}
-It is linear time to decrypt message instead of constant time.
+E2EE helps a lot with low-level edge devices utilizing blockchain service. It dramatically reduces the execution time encryption takes. However, we met two challenges in the E2EE process:
+
+\paragraph{Time to Read Message}
+It is linear time to decrypt messages instead of constant time.
 Nevertheless, there is one way to speed up the message decryption process.
-A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at local side.
+A subscriber can fetch multiple MAM messages with one API call, then the subscriber can decrypt the ciphertext at the local side.
 This procedure can reduce the time spending on internet communication.
@@
 \phantomsection
-\chapter{Decentralized Subscription-based Data Trading Case Study}
+\chapter{Decentralized Subscription-based Data Trading Models}
 \pagestyle{plain}
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=5in]{img/launching_product}
+The details of data products, such as data price, MAM channel/endpoint ID, and the length of data stream are listed on the Product Contract.
+As regard to the encryption key of data product, data provider computes the digest of sensitive contents with a hash function, and sends the digest as well as the signature to brokers.
+The broker can first verify the signature from data provider with the public key on the DID document.
+If it's valid, then the broker uploads the key; otherwise, the process will be aborted.
+Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker.
+This procedure allows data consumers to check whether the encryption key is uploaded by the committed data provider and broker before subscription.
+Furthermore, the encryption key can only be uploaded/updated under two circumstances: 1.) the new product launching.
+2.) when data consumer unsubscribe to the product.
+Finally, the data product is launched and data providers can start uploading data.
+Fig.~\ref{fig:key_upload} demonstrates the key uploading process to the Product Contract via a broker.
+The product launching workflow is shown in Fig.~\ref{fig:launching_product} and Listing.~\ref{lst:key_certification} lists the Solidity codes of the key certification process.
+\clearpage
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=5.5in]{img/key_upload}
+    \caption{To add encryption key to Product Contract, the data provider sends the digest of the encryption key and the one that signed with his/her private key.
+After the broker receive the request, he/she performs digital signature as well to prove the encryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
+    \label{fig:key_upload}
+\end{figure}
+
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=4.5in]{img/launching_product}
     \caption{The process of launching a product.}
@@
 \clearpage
-
-The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract.
-This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one.
-The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}.
-Finally, the data product is launched and data providers can start uploading data.
 
@@
 Data consumers can unsubscribe to data products when they're not interested anymore.
-Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structre, since the delete function in Solidity does not remove the actual element but reseting it to default value.
-When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers.
+Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structure since the delete function in Solidity does not remove the actual element but resetting it to default value.
+When data consumers trigger the unsubscribe event, a withdraw function is executed to pay a subscription fee to providers and return the rest of the fee back to consumers.
 The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}.
-$i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
+$i$ is the number of data when unsubscription request is launched, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.
 
 In SaaS, the cancellation fee is a way to make sure the service providers are protected.
-It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage.
-However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
-
-Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data.
-The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
+It is commonly used in pre-paid subscription-based services that allows service providers to charge cancellation fee if subscribers drop out at the early stage.
+However, asking the cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
+
+Also, data providers will change the encryption key of the data product to prevent unsubscribers access to the rest of the data.
+The new key should be updated to the remaining subscribers in the $consumer2Purchase$ list in the Product Contract.
 Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.
 
-\begin{equation}
+\hfsetfillcolor{white!10}
+\hfsetbordercolor{white}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
 \label{equation:unsubscribe_provider}
     F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t}
+    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
 \label{equation:unsubscribe_broker}
     F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
+    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
 \label{equation:unsubscribe_consumer}
     F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
+    \tikzmarkend{a}
 \end{equation}
@@
 \subsection{Launch a Refund}
-Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee.
+\label{section:refund}
+Data subscription is a high risk in which data provider may not upload data as the agreement set after receiving the subscription fee.
 Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
@@
 See Fig.~\ref{fig:refund}.
-Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:
-
-\begin{equation}
+Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:
+
+\hfsetfillcolor{white!10}
+\hfsetbordercolor{white}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
     F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
+    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
     F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
+    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
     F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
+    \tikzmarkend{a}
 \end{equation}
@@
     \includegraphics[width=2.5in]{img/refund}
-    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers.
-Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
+    \caption{Once a data consumer launch a refund vote, all consumers start voting to decide whether they want a refund.
+Finally, the establishment of refund is determined by Product Contract after checking the number of votes is larger than a threshold or not.}
     \label{fig:refund}
 \end{figure}
+
+However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
+Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
+Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
+If they can not reach a consensus of the brokerage fee during the subscription period, brokers can launch a refund and refuse to handle the product.
+Third, the refund could launch by providers when they fail to maintain products as committed.
 
@@
 \label{section:evaluation}
-It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.
+2) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+
+\subsection{MAM Performance Evaluation}
+\label{section:mam_performance}
+It is worth making a claim that all participants in the data subscription platform do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle.
 Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle.
@@
 
-\subsection{MAM vs. the delegated MAM}
+\subsection{MAM vs. the Delegated MAM}
 \label{section:smart_contract_evaluation}
-What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps.
+
+\subsubsection{Experiment}
+Applying remote PoW greatly reduces the elapsed time.
+Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending messages to tangle-accelerator are the common steps.
 Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
@@
 The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
+In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA, respectively.
 
@@
 
-It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data.
-Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range.
-The bump of MAM performance around 750 bytes proves this point.
-Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=4.5in]{img/mam_vs_e2ee}
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
-    \label{fig:mam_vs_e2ee}
-\end{figure}
+\begin{table}[htbp]
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+    \label{tab:mam_vs_e2ee}
+		\centering
+        \begin{tabular}{|c||c|c|}
+        \hline
+            \textbf{size (bytes)} & \textbf{MAM(ms)} & \textbf{E2EE(ms)} \\
+            \hline
+            100 & 20.28 & 9.21 \\
+            500 &  26.92 & 9.27 \\
+            900 & 32.02 &  9.35  \\
+            1300 & 36.67 & 9.41 \\
+            1700 & 40.55 & 9.54 \\
+            \hline
+        \end{tabular}
+\end{table}
+
+It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+
+\begin{equation}
+\label{eq:lin_mam}
+y=0.0126 x+19.979
+\end{equation}
+
+\begin{equation}
+\label{eq:lin_e2ee}
+y=0.0002 x+9.174
+\end{equation}
+
+The Eq.~\ref{eq:lin_mam} and Eq.~\ref{eq:lin_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively.
+Apparently, the slope of the result of MAM is much greater than the result of E2EE.
+The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.
+
+\subsubsection{Time Complexity}
+With the given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
+HMAC and AES-CBC are the procedures that cost most of the elapsed time.
+Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which causes the time complexity is $O(n)$, too.
+Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.
+Applying mature cryptographic functions (e.g.
+SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
 \clearpage
@@
 Therefore, the Gas estimation only includes trading processes.
-Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start.
-Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well.
+Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at the start.
+Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification} (0.022 - 0.0834 Ether)) that are related to key certification and key exchange need a lot of gas as well.
 Storage on blockchain is expensive.
 For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}.
-However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
-Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract.
+However, in our trading model, we preserve a lot of information in the Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange.
+Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers, and data consumers via storing states to Product Contract.
 Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using zero-knowledge protocol is out of the scope of this paper.
+However, using the zero-knowledge protocol is out of the scope of this paper.
 
 Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}.
-We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
-We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe.
-The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.
-
-\begin{equation}
+We combine the Gas usage of providers and brokers since the brokerage fee is also a critical cost to sustain the trade, which providers should considered.
+We conclude the three situations during the trading process: 1.) basic cost of a trade, including product launching, subscribing, encryption key uploading and withdraw.
+2.) refund operation, the fees needed for launching refund.
+3.) unsubscribe operation, the fees needed for launching unsubscription.
+
+\hfsetfillcolor{white!10}
+\hfsetbordercolor{white}
+\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
 \label{equa:ether_calculation}
 Ethers = Gas \ Price \times Gas \ Amount
+\tikzmarkend{a}
 \end{equation}
 
-When a consumer request a refund, he/she need to pay 0.0003 Ether additionally.
+When a consumer request a refund, he/she need to pay 0.0008 - 0.0003 Ether additionally.
 Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost.
-Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers.
-However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers.
-This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product.
-Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important.
-An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
+Observing the situation of unsubscribe operation, it does not cost much Ether for consumers.
+However, the data provider needs to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the number of remaining subscribers.
+This would cost data providers a lot if the unsubscription is frequent or many remaining consumers are left.
+Hence, an efficient, low-cost, and secure way to perform access control while recording the unsubscription process transparent is important.
+An alternative strategy coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract.
 Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.
@@
     \centering
-	\resizebox{0.98\linewidth}{!}{
+    \resizebox{1.\textwidth}{!}{
     \begin{tabular}{|c|c|c|c|c|c|}
@@
         \hline
-		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
+        \multirow{2}{*}{basic cost} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
          & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
-		\hline
-		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
-		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
-		\hline
-		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
-		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
-		\hline
-		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
-		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
+        \hhline{|=|=|=|=|=|=|}
+        \multirow{2}{*}{refund} & provider & 0 & 0 & 0 & 0 \\
+         & consumer & 0.00008 & 0.0209 & 0.0003 & 0.0761 \\
+        \hline
+        \multirow{2}{*}{unsubscribe} & provider & 0.002N & 0.497N & 0.007N & 1.806N \\
+         & consumer & 0.00006 & 0.0143 & 0.0002 & 0.0519 \\
         \hline
@@
 
-By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services.
-It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.
-
-In the subscription-based data trading, there are some issues that worth discussing and improving.
+By combining the established standards and openly-developed specifications, this paper proposed a highly decentralized, autonomous publish/subscribe model design that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to enable the data stream trading by shifting risks from centralized services, ensure the authenticity of all participants, clarify the data ownership, enable secure communication and flexible trading mechanisms.
+
+Compared to previous works, we 1.) identify a trustless data trading infrastructure, 2.) ensure the confidentiality of scalable IoT-based sensor data, and 3.) consolidate the economic incentives in the entire ecosystem.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to Tangle-accelerators, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+In particular, this work discusses the workflow for subscription-based IoT data trading: Launching, subscribing, unsubscribing, and refund.
+
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
+
+% ------------------------------------------------
+%                   Future Work
+% ------------------------------------------------
+\newpage
+\phantomsection
+\chapter{Future Work}
+\label{section:future_work}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
+In the subscription-based data trading, there are some issues worth discussing and improving.
 Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation.
-Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers.
-Second, brokers are the key to operate a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
-However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
-
-Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service.
+Therefore, it is worth discussing how zero-knowledge protocol could used to exchange the key with lower cost, and even validate the key within transfers.
+Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures.
+However, issues such as the minimum number of brokers needed to operate the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading processes when on crashed.
+
+Third, to let consumers search and find interesting data products, a search engine is needed to collect all distributed data products, which might need the authority to design and run the service.
 The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers.
-Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
+Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently, and it is also an interesting issue to discuss.
+
 \end{spacing}

### 2020-08-12 ASRLab_Thesis_Template/thesis/thesis.tex
Add acknowledgements

@@
 % ------------------------------------------------
-\newpage
-\phantomsection
-\thispagestyle{empty}
-\includepdf[pages=-]{context/oral/oral_vvn.pdf}
-\clearpage
-
+%\newpage
+%\phantomsection
+%\thispagestyle{empty}
+%\includepdf[pages=-]{context/oral/oral_vvn_zh.pdf}
+%\clearpage
 % ------------------------------------------------
@@
 
-在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量來計費，這類似於軟體即服務 (Software-as-a-Service)，一種基於訂閱的定價模型。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料所有權和完整性。此外，訂閱流程的自動化亦是資料貨幣化中不可或缺的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。
+在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量來計費，這類似於軟體即服務 (Software-as-a-Service)，一種基於訂閱的定價模型。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料所有權和完整性。此外，訂閱流程的自動化亦是資料貨幣化中至關重要的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。
 
@@
 % ------------------------------------------------
-%\newpage
-%\phantomsection
-%\chapter*{誌謝}
-%\pagestyle{plain}
-
-%\begin{spacing}{2.0}
-
-%在這邊寫你的感謝 (對父母, 老師, 同學, 朋友等的感謝).
-
-%\end{spacing}
-
-%\clearpage
-%\setstretch{1.2}
+\newpage
+\phantomsection
+\chapter*{誌謝}
+\pagestyle{plain}
+
+\begin{spacing}{2.0}
+
+兩年的研究所生涯落幕，集結所學所究成此論文。首先，感謝兩位恩師 \ \ 涂嘉恒教授和 \ \ 黃敬群教授，研究上從題目鎖定、問題釐清、系統架構、實驗分析等，老師們都給了我寶貴的建議與啟發。此外，老師們也鼓勵投稿研討會、參與比賽並積極對外分享研究成果，除了在研討會和比賽中得到認可，更讓我有機會到香港、上海及東京的開源年會擔任講者，與當地高手交流。不知不覺間，逐步積累的專案與研究甚至讓我爭取成為 IOTA 基金會的研究部門實習生，能夠直接與核心的研發人員學習。我能有今日發展，二位老師在這段旅途中給我的支持及鼓舞是不可或缺的。其次，感謝校內口試委員 \ \ 張大緯教授與國網中心 \ \ 葉羅堯教授的提點，引導學生更深入的思索關鍵議題，收穫良多，並使本論文更加完整。
+
+另外，也要感謝我的好戰友王贊鈞，與我一同討論系統架構和流程，相互激盪出更完善做法；以及和我一起探討 MAM delegation 議題的袁揚皓；感謝袁子琁協助校閱論文，精進用詞；也感謝張友誠協助我調整圖表繪製；再來感謝所有實驗室的成員，你們的幫忙及相互扶持激勵，都是本論文能完成的一大動力。
+
+最後，謝謝我摯愛的父母與弟弟，我一直以來最堅強的後盾，不僅鼓勵我全力以赴，更讓我在求學過程中無後顧之憂。僅以本文獻給每個曾關心我的家人、師長與朋友。
+
+\end{spacing}
+
+\clearpage
+\setstretch{1.2}
 

### 2020-08-12 ASRLab_Thesis_Template/thesis/thesis.tex
Change paper to thesis

@@
 %\thispagestyle{empty}
-%\includepdf[pages=-]{context/oral/oral_vvn_zh.pdf}
+%\includepdf[pages=-]{context/oral/oral.pdf}
 %\clearpage
@@
 In addition, an automated subscription procedure is also demanded for the sake of data monetization.
-In this paper, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
+In this thesis, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure.
 This approach can efficiently enhance the degree of transparency and scalability.

### 2020-08-13 ASRLab_Thesis_Template/thesis/thesis.tex
Update Acknowledgements

@@
 % ------------------------------------------------
-%\newpage
-%\phantomsection
-%\thispagestyle{empty}
-%\includepdf[pages=-]{context/oral/oral.pdf}
-%\clearpage
+\newpage
+\phantomsection
+\thispagestyle{empty}
+\includepdf[pages=-]{context/oral/oral_zh.pdf}
+\clearpage
+\includepdf[pages=-]{context/oral/oral_eng.pdf}
+\clearpage
 % ------------------------------------------------
@@
 
-兩年的研究所生涯落幕，集結所學所究成此論文。首先，感謝兩位恩師 \ \ 涂嘉恒教授和 \ \ 黃敬群教授，研究上從題目鎖定、問題釐清、系統架構、實驗分析等，老師們都給了我寶貴的建議與啟發。此外，老師們也鼓勵投稿研討會、參與比賽並積極對外分享研究成果，除了在研討會和比賽中得到認可，更讓我有機會到香港、上海及東京的開源年會擔任講者，與當地高手交流。不知不覺間，逐步積累的專案與研究甚至讓我爭取成為 IOTA 基金會的研究部門實習生，能夠直接與核心的研發人員學習。我能有今日發展，二位老師在這段旅途中給我的支持及鼓舞是不可或缺的。其次，感謝校內口試委員 \ \ 張大緯教授與國網中心 \ \ 葉羅堯教授的提點，引導學生更深入的思索關鍵議題，收穫良多，並使本論文更加完整。
-
-另外，也要感謝我的好戰友王贊鈞，與我一同討論系統架構和流程，相互激盪出更完善做法；以及和我一起探討 MAM delegation 議題的袁揚皓；感謝袁子琁協助校閱論文，精進用詞；也感謝張友誠協助我調整圖表繪製；再來感謝所有實驗室的成員，你們的幫忙及相互扶持激勵，都是本論文能完成的一大動力。
-
-最後，謝謝我摯愛的父母與弟弟，我一直以來最堅強的後盾，不僅鼓勵我全力以赴，更讓我在求學過程中無後顧之憂。僅以本文獻給每個曾關心我的家人、師長與朋友。
+兩年的研究所生涯落幕，集結所學所究成此論文。首先，感謝兩位恩師 \ \ 涂嘉恒教授和 \ \ 黃敬群教授，研究上從題目鎖定、問題釐清、架構設計、實驗分析等，都給了我寶貴的建議與啟發。此外，老師們也鼓勵我投稿研討會、參加比賽並積極對外分享研究成果，除了在研討會和比賽中得到認可，更讓我有機會到香港、上海及東京的開源年會擔任講者，與當地高手交流。不知不覺間，逐步積累的專案與研究甚至讓我爭取成為 IOTA 基金會的研究部門實習生，能夠直接與核心研發人員學習。能有今日發展，二位老師在這段旅途中給我的支持及鼓舞是不可或缺的。其次，感謝校內口試委員 \ \ 張大緯教授與國網中心 \ \ 葉羅堯教授的提點，引導學生更深入的思索關鍵議題，收穫良多，並使本論文更加完整。
+
+另外，感謝我的好戰友王贊鈞，與我一同討論系統架構和流程，相互激盪出更完善做法；以及和我一起探討 MAM delegation 議題的袁揚皓；感謝袁子琁協助校閱論文，精進用詞；也感謝張友誠協助我調整圖表繪製；再來感謝所有實驗室的成員，你們的幫忙及相互扶持激勵，都是本論文能完成的一大助力。
+
+最後，謝謝我摯愛的父母與弟弟，是我一直以來最堅強的後盾，不僅鼓勵我全力以赴，更讓我在求學過程中無後顧之憂。一路上多有貴人相助，願日後得湧泉以報，僅以本文獻給每個關心我的家人、師長與朋友。
 

### 2020-08-14 ASRLab_Thesis_Template/thesis/thesis.tex
Add DOI
Chinese comma tweak
Minor fixes

@@
 % ------------------------------------------------
-%\usepackage{draftwatermark}  % For DOI watermark
+\usepackage{draftwatermark}  % For DOI watermark
 \usepackage{listings, makecell, multirow, hhline}
@@
 \begin{document}
-%\ShowDOI{doi:XXXX/NCKU2019XXXXX}
+\ShowDOI{doi:10.6844/NCKU202001948}
 
@@
 
-在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量來計費，這類似於軟體即服務 (Software-as-a-Service)，一種基於訂閱的定價模型。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料所有權和完整性。此外，訂閱流程的自動化亦是資料貨幣化中至關重要的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。
+在物聯網場景中，machine-to-machine（M2M）的發展勢不可擋，它允許機器擁有自己的數位資產並開始參與經濟活動，讓裝置間可以共享和交易其資源。在發布/訂閱（publish/subscribe）通訊模型上將及時資料貨幣化，就可以依據資料使用量計費，這是一種基於訂閱的定價模型，類似於軟體即服務 (Software-as-a-Service)。這種定價模型讓資料提供者可以更好地管理預算，且資料消費者可以隨興的訂閱和退訂。然而，動態的資料流提升了資料所有權和身份驗證的重要性和難度。因此，一個不需信任單一機構的資料交易基礎建設是必需的，除了能允許參與者進行交易，還能驗證資料來源和完整性。此外，訂閱流程的自動化亦是資料貨幣化中至關重要的。在本文中，我們利用分散式帳本技術 (Distributed Ledger Techonology)，在 IoT 中介基礎架構之上構建去中心化資料交易平台。這種方法可以有效地提高運作透明度和系統可擴展性，建立在加密訊息協議之上的存儲允許在沒有權限的情況下通過分散式帳本儲存、傳輸、存取和驗證資料流，在我們的設計中也讓交易參與者的數位權益得到保證。
 
@@
 
-\par{\noindent \bf 關鍵字:}{發布/訂閱, 資料交易, 去中心化, 分散式帳本技術}
+\par{\noindent \bf 關鍵字:}{發布/訂閱，資料交易，去中心化，分散式帳本技術}
 \clearpage
@@
 Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or a cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}.
-Besides CA and storage, the subscription history of data consumers may reveal his/her interests and the exposure of personal information during trading process against GDPR as well.
+Besides CA and storage, the subscription history of data consumers may reveal his/her interests, and the exposure of personal information during the trading process against GDPR as well.
 The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.
@@
 Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design.
-In this paper, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
+In this thesis, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure.
 See Fig.~\ref{fig:system_design}.
@@
 
-\subsection{Contributions}
+\section{Contributions}
 The contributions in the thesis are summarized as follow:
@@
 
-\subsection{Thesis Organization}
+\section{Thesis Organization}
 The rest of this thesis is organized as follows.
 In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed.
-In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated.
+In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture are illustrated.
 In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices.
@@
 
-\subsection{The Publish/subscribe Communication Models Over Blockchain}
+\section{The Publish/subscribe Communication Models Over Blockchain}
 The pub/sub service model consists of publishers, subscribers, and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications.
@@
 In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties.
-The subscribers request publisher directly and ask them to save a cache space for interesting data.
+The subscribers request publishers directly and ask them to save a cache space for interesting data.
 The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environments to perform such functionalities and preserve data.
 Also, the rights for accessing digital assets are more compatible in the IoT scenarios instead of copying raw data.
-Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
-The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent.
-The reputation system and the punishment rules against malicious acts of subscribers and publishers.
+Secure Pub-Sub model\cite{SPS}, a brokerless pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain.
+The privacy and data security are considered thoroughly with the encryption scheme, while the reputation system, the punishment rules against malicious acts of subscribers and publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent.
 Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match both sides.
@@
 
-\subsection{Trusted IoT Trading Infrastructure}
-Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et.
-al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace that enables trading with Ethereum smart contracts.
+\section{Trusted IoT Trading Infrastructure}
+Multiple infrastructures for trusted IoT data trading have been proposed.
+Paolo Missier et.
+al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace that enables trading with Ethereum smart contracts.
 The brokers are only responsible for data transmission in order to adapt flexible agreement between participants.
@@
 
-\subsection{Distributed Storage System}
+\section{Distributed Storage System}
 \label{section:distributed_storage}
-Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider.
+Decentralized storage systems allow users to store files in a distributed network that maintained by individual nodes around the world instead of a central service provider.
 Nevertheless, DLTs are often used as the backbone of these systems like data storage and also an incentive layer to encourage people to get involved in the network.
@@
 \label{section:design_thinking}
-\subsection{Data Subscription-based Trading Platform Players}
+\section{Data Subscription-based Trading Platform Players}
 There are three major roles, data providers, data consumers, and brokers which are similar to the pub/sub messaging model.
@@
 The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key.
-Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
-
-\subsection{Choice of Data Storage}
+Third, a refund process needs a broker to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.
+
+\section{Choice of Data Storage}
 Data storage is the trust basis of data trading platforms where the data assets are reserved.
@@
 Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network).
-However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}.
+However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which will be illustrated in Section.~\ref{section:ta_endpoint}.
 Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.
@@
     \begin{itemize}
-        \item Messages published to the Tangle are tamper-proof against malicious modification.
+        \item Messages published to the Tangle are tamper-proof against malicious modifications.
         \item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
@@
     \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures.
-Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
+Subscribers can validate the messages with signature keys and decrypt them with the encryption key.}
     \label{fig:channel_and_key}
@@
 
-\subsection{Digital Identity}
+\section{Digital Identity}
 The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions.
@@
 
-\subsection{Enable Automated Trading Process}
+\section{Enable Automated Trading Process}
 Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger.
@@
 Participants can easily retrieve information via the Product Contract and proceed to trade.
-For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color.
+For signature validation check and further encryption key exchange, the MAM channel ID of participants' DID document are written down, presented in blue color.
 The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
@@
 
-\subsection{Enable Computation Tasks Delegation to Broker with Privacy}
+\section{Enable Computation Tasks Delegation to Broker with Privacy}
 To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks.
@@
 
-\subsection{The Message Streams}
+\section{The Message Streams}
 \label{section:mam_streams}
@@
 
-\subsection{Enable Access Control and Authentication}
+\section{Enable Access Control and Authentication}
 \label{section:mam_functions}
@@
 
-\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
+\section{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
 \label{section:mam_features}
 %scalability
-\subsubsection{A Scalable Keys and Data Entry Points Management}
+\subsection{A Scalable Keys and Data Entry Points Management}
 The importance of scalable key and data entry points management increases over time.
 In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of the transaction and retrieve data.
-To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.
+To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storages.
 \clearpage
@@
 %classify
-\subsubsection{Data Streams Classification and Traceability}
+\subsection{Data Streams Classification and Traceability}
 The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages.
@@
 
-\subsection{Delegate MAM operations to Tangle-accelerator}
+\section{Delegate MAM Operations to Tangle-accelerator}
 \label{section:ta_endpoint}
@@
 
-\subsubsection{Communication Protocol}
+\subsection{Communication Protocol}
 In the following sections, we refer to the low-level devices as \textbf{endpoint}s.
@@
 
-\subsubsection{End-to-End-Encryption}
+\subsection{End-to-End-Encryption}
 Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message.
@@
     \centering
-    \includegraphics[width=\linewidth]{img/MAM_E2EE}
+    \includegraphics[width=6.5in]{img/MAM_E2EE}
     \caption{The process of E2EE.}
@@
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:
+In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step of the presented E2EE process. The details of steps are addressed below:
 
@@
     \item Generate symmetric keys with the unique device identifier and Message Authentication Code (MAC) of the previous message.
-If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message.
+If the message is the first one, then sharing secret initialization information would serve as the MAC of the previous message.
 Key Derivation Function (KDF) is used to generate the symmetric keys.
-    \item Compute the Message Authentication Code (MAC) of current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
+    \item Compute the MAC of the current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and the symmetric key would be given as parameters in HMAC.
     \item Apply the generated symmetric key to encrypt the plaintext.
-    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
-    \item Send the ciphertext along with signed MAC.
+    \item Concatenate the MAC of the current message and the MAC of the previous message, then the result will be signed with a digital signature algorithm.
+    \item Send the ciphertext along with the signed MAC.
 \end{enumerate}
@@
 
-The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
+The E2EE protocol presented in this thesis combines a series of different cryptographic procedures.
 Each of them can be chosen on the basis of the working hardware and scenario by developers.
@@
 
-\subsubsection{Register with Tangle-accelerator}
+\subsection{Register with Tangle-accelerator}
 Users with channel seed can acquire channel chain ownership.
-Seed is generated by unique hardware information on the edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on the MAM channel chain.
+Seed is generated by unique hardware information on the edge device, so it should be transmitted to Tangle-accelerator to publish messages on the MAM channel chain.
 Once the Tangle-accelerator receives the Seed from the edge device, it would return a unique user identifier that can be mapped to corresponding Seed when edge devices send requests.
 Asymmetric encryption is utilizing during the process of exchanging seed.
-The digital signature should be taken at the same time to ensure data integrity.
-Once the seed has been successfully exchanged, the edge device is successfully registered on the specific tangle-accelerator.
-Thus, the seed will not be exposed during communication after an edge device is successfully registered.
-
-\subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot with low-level edge devices utilizing blockchain service. It dramatically reduces the execution time encryption takes. However, we met two challenges in the E2EE process:
-
-\paragraph{Time to Read Message}
+The digital signature should be performed at the same time to ensure data integrity.
+Once the seed has been successfully exchanged, the edge device is successfully registered on the specific Tangle-accelerator.
+Thus, the seed will not be exposed during communication in further usages.
+
+\subsection{Issues in End-to-End-Encryption}
+E2EE helps a lot with low-level edge devices utilizing blockchain service. It dramatically reduces the execution time of encryption. However, we meet two challenges in the E2EE process:
+
+\subsubsection{Time to Read Message}
 It is linear time to decrypt messages instead of constant time.
@@
 
-\paragraph{Spam on Message Channel Chain}
+\subsubsection{Spam on Message Channel Chain}
 Tampering the messages which have conducted E2EE would be a challenging mission.
 However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party.
+It is risky for an edge device connects to a Tangle-accelerator which is operated by unknown third-party.
 Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
-Spam would cause subscribers to waste plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.
+Spam would cause subscribers wasting plenty of time on decrypting useless messages.
+Since Tangle-accelerator can be easily hosted on regular personal computers, the actual device holders can set up an instance to prevent edge devices from such attack.
 
@@
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
-
-\subsection{Prerequisite}
-All participants are required to register on TangleID to get a DID document and public/private key pair for sensitive contents exchange and authentication.
+In this chapter, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.
+
+\section{Prerequisite}
+All participants are required to register on TangleID to get a DID document and a  public/private key pair for sensitive contents exchange and authentication.
 An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.
 
-\subsection{Launch Data Products}
+\section{Launch Data Products}
 \label{section:launch_data_product}
@@
 The details of data products, such as data price, MAM channel/endpoint ID, and the length of data stream are listed on the Product Contract.
-As regard to the encryption key of data product, data provider computes the digest of sensitive contents with a hash function, and sends the digest as well as the signature to brokers.
+As regard to the encryption key of data product, data provider computes the digest of sensitive contents with a hash function, and sends the digest as well as the signature to a  broker.
 The broker can first verify the signature from data provider with the public key on the DID document.
@@
 This procedure allows data consumers to check whether the encryption key is uploaded by the committed data provider and broker before subscription.
-Furthermore, the encryption key can only be uploaded/updated under two circumstances: 1.) the new product launching.
-2.) when data consumer unsubscribe to the product.
+Furthermore, the encryption key can only be uploaded/updated under two circumstances: 1.) the new product launches.
+2.) a data consumer unsubscribe to the product.
 Finally, the data product is launched and data providers can start uploading data.
@@
 
-\subsection{Subscribe to Data Product}
+\section{Subscribe to a Data Product}
 Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers.
@@
 
-\subsection{Unsubscribe to Data Products}
+\section{Unsubscribe to a Data Product}
 Data consumers can unsubscribe to data products when they're not interested anymore.
@@
 It is commonly used in pre-paid subscription-based services that allows service providers to charge cancellation fee if subscribers drop out at the early stage.
-However, asking the cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.
+However, asking the cancellation fee arbitrarily may cause an unfair contract which leads to the legal issue that should be carefully studied.
 
@@
 
-\hfsetfillcolor{white!10}
-\hfsetbordercolor{white}
-\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
+\begin{equation}
 \label{equation:unsubscribe_provider}
     F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t}
-    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
+\begin{equation}
 \label{equation:unsubscribe_broker}
     F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
-    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
+\begin{equation}
 \label{equation:unsubscribe_consumer}
     F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
-    \tikzmarkend{a}
 \end{equation}
@@
     \includegraphics[width=5.5in]{img/unsubscribe}
-    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively.
+    \caption{Once a data consumer launch a unsubscription procedure, he/she is marked as not subscribing and the Product Contract will distribute the funds to provider, broker and consumers respectively.
 Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
@@
 
-\subsection{Launch a Refund}
+\section{Launch a Refund}
 \label{section:refund}
-Data subscription is a high risk in which data provider may not upload data as the agreement set after receiving the subscription fee.
+Data subscription is a high risk in which data provider may not upload data as the agreement after receiving the subscription fee.
 Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective.
@@
 
-\hfsetfillcolor{white!10}
-\hfsetbordercolor{white}
-\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
+\begin{equation}
     F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
-    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
+\begin{equation}
     F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
-    \tikzmarkend{a}
 \end{equation}
 
-\begin{equation}\tikzmarkin{a}(0.2,-0.5)(-0.2,0.65)
+\begin{equation}
     F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
-    \tikzmarkend{a}
 \end{equation}
@@
 
-However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
+However, refund conditions are complicated in subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee.
 Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
@@
 
-\subsection{MAM Performance Evaluation}
+\section{MAM Performance Evaluation}
 \label{section:mam_performance}
@@
 
-\subsubsection{Channel / Endpoint Creation}
+\subsection{Channel / Endpoint Creation}
 The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint.
@@
 And the performance of PC remains acceptable even \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
+The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to the Tangle-accelerator.
 
@@
 
-\subsubsection{Messages Publishment}
+\subsection{Messages Publishment}
 Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
@@
 
-Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such a framework.
+Therefore, transferring MAM operations to Tangle-accelerators while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such a framework.
 Brokers can be PCs or powerful machines that run Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation.
@@
 
-\subsection{MAM vs. the Delegated MAM}
+\section{MAM vs. the Delegated MAM}
 \label{section:smart_contract_evaluation}
 
-\subsubsection{Experiment}
+\subsection{Experiment}
 Applying remote PoW greatly reduces the elapsed time.
 Channel creation is the next primary barrier for low-level devices to broadcast MAM message.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
+With employing delegated MAM and E2EE, MAM channel creation would be delegated to the Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices.
 What follows is the performance comparison between MAM and delegated MAM (E2EE) for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the following processes starting from sending messages to tangle-accelerator are the common steps.
-Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too.
+Elapsed time for internet communication and PoW are not included, because the following processes starting from sending messages to Tangle-accelerator are the common steps.
+Excluding the common steps allows us to compare the performance between MAM and delegated MAM more precisely.
+In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too.
 The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.
@@
 \begin{itemize}
-    \item Encrypt input payload
-    \item Publish final message on IOTA Tangle
+    \item Encrypt the input payload
+    \item Publish the last message to the Tangle network
 \end{itemize}
@@
 \begin{itemize}
-    \item Generate symmetric key for encryption
-    \item Hash input payload
-    \item Encrypt input payload
-    \item Transmit final message to tangle-accelerator
+    \item Generate a symmetric key for encryption
+    \item Hash the input payload
+    \item Encrypt the input payload
+    \item Transmit the last message to the Tangle-accelerator
 \end{itemize}
@@
 \begin{table}[htbp]
-    \caption{Compare the performance between MAM and E2EE on Raspberry Pi}
+    \caption{Compare the performance between MAM and E2EE on Raspberry Pi 3 B+}
     \label{tab:mam_vs_e2ee}
@@
 
-It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
+In the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two results reveals the elapsing time of E2EE is obviously less than that of MAM which shows the E2EE process presented in the thesis is a much more appropriate solution for resource-constrained devices to send authenticated streaming data.
 
@@
 
-\subsubsection{Time Complexity}
+\subsection{Time Complexity}
 With the given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length.
@@
 
-\subsection{Smart Contract}
+\section{Smart Contract}
 In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser-based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing trade.
@@
 Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
-However, using the zero-knowledge protocol is out of the scope of this paper.
+However, using the zero-knowledge protocol is out of the scope of this thesis.
 
@@
 
-By combining the established standards and openly-developed specifications, this paper proposed a highly decentralized, autonomous publish/subscribe model design that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
+By combining the established standards and openly-developed specifications, this thesis proposed a highly decentralized, autonomous publish/subscribe model design that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading.
 It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to enable the data stream trading by shifting risks from centralized services, ensure the authenticity of all participants, clarify the data ownership, enable secure communication and flexible trading mechanisms.

### 2020-09-29 paper.tex
Apply new template and add author information

--- 2020-08-07 paper.tex
@@
-\documentclass[conference]{IEEEtran}
+\documentclass[10pt, conference, compsocconf]{IEEEtran}
 
@@
 \title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
-% Chinese title: 針對物聯網資料交易的去中心化基礎建設
 
-\author{
-\IEEEauthorblockN{Anonymous}
-\IEEEauthorblockA{
-         \textit{Anonymous Organization}\\
-        ***@***.***}
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%jkrvivian@gmail.com}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%jserv@ccns.ncku.edu.tw}
-%\and
-%\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
-%\IEEEauthorblockA{\textit{dept. of CSIE} \\
-%\textit{National Cheng Kung University}\\
-%Tainan City, Taiwan (R.O.C.) \\
-%chiaheng@gmail.com}
+\author{\IEEEauthorblockN{Ching-Hua (Vivian) Lin}
+\IEEEauthorblockA{dept. of CSIE\\
+National Cheng Kung University\\
+Tainan City, Taiwan (R.O.C.)\\
+jkrvivian@gmail.com}
+\and
+\IEEEauthorblockN{Ching-Chun (Jim) Huang}
+\IEEEauthorblockA{dept. of CSIE\\
+National Cheng Kung University\\
+Tainan City, Taiwan (R.O.C.)\\
+jserv@ccns.ncku.edu.tw}
+\and
+\IEEEauthorblockN{Yang-Hao Yuan}
+\IEEEauthorblockA{BiiLabs Co., Ltd.\\
+Taiwan (R.O.C.)\\
+<yanghau@biilabs.io>}
+\and
+\IEEEauthorblockN{Zih-shiuan (Spin) Yuan}
+\IEEEauthorblockA{BiiLabs Co., Ltd.\\
+Taiwan (R.O.C.)\\
+<spin@biilabs.io>}
 }

### 2020-09-29 paper.tex
Minor fixes

@@
 
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 Taiwan (R.O.C.)\\
-<yanghau@biilabs.io>}
+yanghau@biilabs.io}
 \and
@@
 Taiwan (R.O.C.)\\
-<spin@biilabs.io>}
+spin@biilabs.io}
 }
@@
 \begin{abstract}
-%cite IoT data subscription economy
 On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set.
@@
 
-%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
 In contrast to the existing solutions targeting static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity, and high variety of real-time data streams\cite{BigData}.
@@
 
-%trustless & automated
-%trust: 對系統、對身份、對資料
 In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
@@
 
-%pic
 \begin{figure}[!h]

### 2020-09-29 paper.tex
Rephrase and fix grammar

@@
 \label{section:refund}
-The refund topics are complicated in subscription services, therefore, we illustrated the challenges in this section.
+The refund topics are complicated in subscription services; therefore, we illustrate the challenges in this section.
 As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee.
-However, issues such as consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully.
-Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers.
-If they can not reach a consensus of the brokerage fee during the subscription period, brokers can launch a refund and refuse to handle the product.
-Third, the refund could launch by providers when they fail to maintain products as committed.
+It is notable that consumers can only initiate a refund after getting the data or in a certain time period.
+In this situation, the broker should host and set a vote timeline to count the votes, as well as handling the condition that not enough consumers join the vote.
+The process needs to be considered carefully.
+Second, brokers operate the subscription platform by earning brokerage fees, which is a deal between brokers and providers.
+If they cannot reach a consensus on the brokerage fee during the subscription period, brokers can launch a refund and reject to handle the product.
+Third, the refund could be launched by providers when they fail to maintain products as committed.
 
@@
 \subsubsection{Experiment}
-According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message.
+According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating a channel, these three steps take most of the time to broadcast a MAM message.
 The result directs a way to improve MAM.
-Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier that should be removed.
-With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices.
-What follows is the performance comparison between MAM and delegated MAM for different payload sizes.
-Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps.
-Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly.
-In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed.
-In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA, respectively.
+Applying remote PoW greatly reduces the elapsed time; hence, the channel creation is the next primary barrier that should be removed.
+With the adoption of delegated MAM and E2EE, the MAM channel creation would be delegated to Accel, which dramatically enhances the efficiency and makes MAM available for low-level devices.
+In this way, the performance of delegated MAM stands out from the original MAM one, particularly for different payload sizes.
+Elapsed time for internet communication and PoW are not included because the steps are the same after sending messages to Accel.
+Excluding the uniform steps allows us to compare the performance between MAM and delegated MAM clearly.
+In addition, the MAM channel creation and E2EE asymmetric key pair generation are not counted either, since the two operations are rarely executed.
+In the E2EE protocol, we respectively choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA.
 
@@
 Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively.
-The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.
-The slope of the result of E2EE is much flatter than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.
-Under our design which delegates MAM operations with Accel and the presented E2EE protocol, the data providers can include resource-constrained hardware into the data subscription economy.
-E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
+The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM, which shows that the previous process is a much more appropriate solution to resource-constrained systems in sending authenticated streaming data.
+The slope of the E2EE result is much flatter than the result of MAM, which means the former solution can consistently perform in an acceptable time range.
+In summary, our design enables the resource-constrained hardware to be data providers in the data subscription economy due to the efficiency of the delegated MAM operation and E2EE protocol.
+The new protocol ensures tamperless data transmission; meanwhile, only authorized subscribers can read the encrypted information.
 

### 2020-09-30 paper.tex
Rename for consistency and formatting

@@
 \begin{align}
-    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
+    F_{Provider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
     F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\

### 2020-09-30 paper.tex
Rephrase E2EE paragraph

@@
 \subsubsection{End-to-End-Encryption}
-Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message.
-To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol.
-The plaintext will be encrypted with this lightweight end-to-end-encryption.
-The E2EE process ensures that only authorized subscribers can read the messages published on MAM.
+Introducing a proxy server to process all the cryptographic operations increases the risk of messages being tampered during transmission.
+To avoid such malicious operations, we propose another lightweight end-to-end-encryption (E2EE) upon MAM protocol.
+The plaintext will be encrypted with E2EE, which ensures only authorized subscribers can access the messages.
 
@@
 
-In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of the steps are addressed below:
+The presented E2EE process is shown in Fig.~\ref{fig:MAM_E2EE} and illustrated below:
 
 \begin{enumerate}
-    \item Generate symmetric keys with a unique device identifier and Message Authentication Code (MAC) of the previous message.
-If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message.
-Key Derivation Function (KDF) is used to generate the symmetric keys.
-    \item Compute the Message Authentication Code (MAC) of the current message with the Hash-based Message Authentication Code(HMAC).
-Both plaintext and the symmetric key would be given as parameters in HMAC.
-    \item Apply the generated symmetric key to encrypt the plaintext.
-    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
-    \item Send the ciphertext along with signed MAC.
+    \item Generate symmetric keys from the unique device identifier and Message Authentication Code (MAC) of the previous message with Key Derivation Function (KDF).
+For the first message, the sharing secret initialization information is taken as the MAC of the previous message.\label{item:1}
+    \item Compute the MAC of the current message with the Hash-based Message Authentication Code (HMAC) using the symmetric key from \ref{item:1}.
+    \item Apply the generated symmetric key to encrypt the plaintext.\label{item:3}
+    \item Concatenate the MACs of the current and the previous message, then sign it.\label{item:4}
+    \item Send the results of \ref{item:3} and \ref{item:4}.
 \end{enumerate}
 
-The E2EE protocol presented in this paper combines a series of different cryptographic procedures.
-Each of them can be chosen on the basis of the working hardware and scenario by developers.
-On certain devices, hardware acceleration would be supported.
-With hardware-acceleration, the elapsed time could be dropped a step more.
-For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}
+The E2EE protocol combines a series of different cryptographic procedures, which can be swapped by developers to adjust different hardwares or scenarios.
+The elapsed time could be dropped a step more on hardwares that supported acceleration, for example, applying AES-NI can speed up AES operations around 40\% on Intel devices\cite{AES-NI-Acceleration}, and AES accelerators are integrated on some popular microcontrollers as well\cite{stm}.
 

### 2020-09-30 paper.tex
Rephrase Accel time complexity and issues

@@
 In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and ECDSA P-256 for digital signature.
-In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length.
-HMAC and AES-CBC are the procedures that cost most of the elapsed time.
-Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which causes the time complexity is $O(n)$, too.
+EDSA would take constant time, since the input is fixed length.
+The time complexity of HMAC with SHA-256 is $O(n)$\cite{hmac_time_complexity}, and block cipher takes constant time for a single block with time complexity $O(n)$.
 Therefore, the E2EE protocol takes only linear time versus arbitrary string length.
@@
 \subsubsection{Issues in End-to-End-Encryption}
-E2EE helps a lot for low-level edge devices utilizing blockchain service.
-It dramatically reduces the execution time encryption takes.
-However, there are some challenges in the E2EE process.
-Tampering the messages which have conducted E2EE would be a challenging mission.
-However, spamming would be the critical issue participants may meet under this architecture.
-It is risky for an edge device connects to an Accel which is operated by an unknown third-party.
-Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain.
-Spam would cause subscribers to waste plenty of time on decrypting useless messages.
-To prevent edge devices from the annoying attack, connecting to a known, trustworthy Accel would be the easiest solution.
+E2EE dramatically reduces the execution time of encryption that lowers the barries of utilizing blockchain service for low-level devices.
+However, Accel can tamper the messages and even spam on the requester's MAM channel, where its root is given to Accel at start.
+Significantly, it is risky for an edge device to connect to an Accel operating by an unknown third-party, thus connecting to a known, trustworthy Accel would be the easiest solution to prevent such attacks.
 

### 2020-10-01 paper.tex
Rephrase Evaluations

@@
 \section{Introduction}
-As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets.
+As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care, factories, and vehicles, and brings up new business models where data is considered as tradeable digital assets.
 With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets.
@@
     \item Compute the MAC of the current message with the Hash-based Message Authentication Code (HMAC) using the symmetric key from \ref{item:1}.
-    \item Apply the generated symmetric key to encrypt the plaintext.\label{item:3}
+    \item Apply the generated symmetric key to encrypt the message.\label{item:3}
     \item Concatenate the MACs of the current and the previous message, then sign it.\label{item:4}
@@
 \label{section:trading_model}
-In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel the subscription. A discussion of refunds is illustrated.
+In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel the subscription and a discussion of refunds is illustrated.
 
@@
 \label{section:evaluation}
-We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
-2) Evaluate the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data provider.
+We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) the minimum cost for participants to sustain or subscribe to a data product via Product Contract.
+2) the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data providers.
 
@@
 The high transaction fee for brokers is due to the multiple store operations in contract deployment and key certification, which takes high Gas usage according to Ethereum Yellow Paper.
-Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys.
+Therefore, it is worth exploring the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS\cite{Snark} which can generate proofs off-chain and simplify the verification process.
+It can not only reduce network and storage cost but also improve the privacy and security of encryption keys.
 
@@
 \label{section:mam_performance}
-In the following evaluations, all devices run with the IOTA client library instead of IOTA full nodes.
-MAM is the primary key to resolve all the storage difficulties discussed in previous sections.
-The interactions between data providers and MAM can be frequent, hence the operation of MAM is one of the potential bottlenecks in the data subscription platform.
+%In the following evaluations, all devices run with the IOTA client library instead of IOTA full nodes.
+MAM is the primary component to resolve the storage difficulties discussed in previous sections.
+The interactions between data providers and MAM can be frequent, hence it is one of the potential bottlenecks during the subscription processes.
 In this section, time measurement is evaluated in two MAM operations: channel/endpoint creation and message publishment.
-To perform the evaluation assessment, a personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
+A personal computer (PC; 3.2GHz 6-core i7-8700 with 16GB DDR4 RAM) and a Raspberry Pi 3 Model B (RPi; 1.2 GHz 4-core ARM Cortex-A53 with 1GB LPDDR2 RAM) have been used to run MAM.
 
 \subsubsection{Channel / Endpoint Creation}
-The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint.
+The length of a channel/endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in MSS, and the "$-1$" is for announcing the ID of next channel or endpoint.
 The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power is required.
@@
 The time duration for each \textit{height} is the average time of running 100 rounds.
-Since the workflow of channel and endpoint creation are identical, the curves of the same hardware are almost matched.
-On the other hand, the elapsed time of RPi is grows rapidly when \textit{height} is 5 or above.
-And the elapsed time of PC remains acceptable even the \textit{height} gets to 7.
-The results indicate that MAM channel/endpoint creation is a laborious job for RPi when data providers need a longer channel/endpoint, which can considered delegating to Accel.
+Since the workflow of channel and endpoint creation are identical, the curves of the same hardware almost match.
+On the other hand, the elapsed time of RPi grow rapidly when \textit{height} is 5 or above.
+And on PC, all remain acceptable even the \textit{height} gets to 7.
+The results indicate that MAM channel/endpoint creation is a laborious job for data providers, and can be considered delegating to Accel.
 \begin{figure*}[!htb]
@@
 Tips selection requires a stable network connection to wait for the response from IOTA full nodes, and PoW requires enough computation resources to perform.
-The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has a huge impact.
-The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority of hardware in the IoT scenarios.
-Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such a framework.
-Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi.
-However, MAM operations are fairly time-consuming, and improving the performance of MAM is an essential issue that needs to be done for the next step.
+The time of RPi distributed widely, from 5 secs to over 2500 secs, due to the randomness of PoW.
+The simulation results indicate that publishing messages locally is difficult for low-level sensor devices, whereas they are the majority of hardwares in IoT scenarios.
+Therefore, the devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE, which can lower the threshold to participate the subscription platform.
+Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW, remote PoW and E2EE on RPi.
+However, improving the performance of MAM is still a direction that worth working on.
 
@@
 \subsubsection{Experiment}
-According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating a channel, these three steps take most of the time to broadcast a MAM message.
-The result directs a way to improve MAM.
-Applying remote PoW greatly reduces the elapsed time; hence, the channel creation is the next primary barrier that should be removed.
-With the adoption of delegated MAM and E2EE, the MAM channel creation would be delegated to Accel, which dramatically enhances the efficiency and makes MAM available for low-level devices.
-In this way, the performance of delegated MAM stands out from the original MAM one, particularly for different payload sizes.
-Elapsed time for internet communication and PoW are not included because the steps are the same after sending messages to Accel.
-Excluding the uniform steps allows us to compare the performance between MAM and delegated MAM clearly.
-In addition, the MAM channel creation and E2EE asymmetric key pair generation are not counted either, since the two operations are rarely executed.
-In the E2EE protocol, we respectively choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA.
+From Fig.~\ref{fig:op_share}, send to full node (i.e., prepare and attach the message) and create a channel take most of the time to broadcast a MAM message.
+In Fig.~\ref{fig:rpi3_pow}, we apply remote PoW to reduce the time of the former, and we delegate MAM to Accel to improve the later.
+This strategy outperforms the original MAM, particularly for different payload sizes.
+To better understand the time cost of MAM and delegated MAM, the measurement only contains the MAM operations running on device, where PoW and internet transmission are not included.
+Furthermore, the MAM channel creation and E2EE asymmetric key pair generation are not included either, since the two operations are rarely executed.
+In E2EE, we respectively choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA.
 
-The steps counted in MAM benchmark including:
-\begin{enumerate}
-    \item Write key information in the header
-    \item Write and encrypt input payload
-    \item Publish final message on Tangle
-\end{enumerate}
-
-The steps counted in delegated MAM (E2EE) benchmark including:
-\begin{enumerate}
-    \item Generate symmetric key for encryption
-    \item Hash input payload
-    \item Encrypt input payload
-    \item Transmit final message to Accel
-\end{enumerate}
+The measurement for original MAM includes: 1.) write the key information to the header, 2.) encrypt and write the message, 3.) publish final message to the Tangle.
+And the measurement for delegated MAM (E2EE) includes: 1.) generate a symmetric key for encryption, 2.) Hash the message, 3.) encrypt the message, 4.) send the message to Accel.
+The result is shown in Table.~\ref{tab:mam_vs_e2ee}.
 
@@
 
-\begin{align}
-    y &= 0.0126 x+19.979 \label{lin_mam} \\
-    y &= 0.0002 x+9.174 \label{lin_e2ee}
-\end{align}
-
-Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods.
-Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively.
-The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM, which shows that the previous process is a much more appropriate solution to resource-constrained systems in sending authenticated streaming data.
-The slope of the E2EE result is much flatter than the result of MAM, which means the former solution can consistently perform in an acceptable time range.
-In summary, our design enables the resource-constrained hardware to be data providers in the data subscription economy due to the efficiency of the delegated MAM operation and E2EE protocol.
-The new protocol ensures tamperless data transmission; meanwhile, only authorized subscribers can read the encrypted information.
+The result shows that the elapsed time of E2EE is obviously less than MAM, and E2EE results in a slowly increasing time for different data sizes.
+This shows that E2EE enables resource-constrained hardwares to join the data subscription economy as providers and ensures tamperless data transmission to Accel.
 

### 2020-11-12 paper.tex
Use ncku email
Change TA to Accel

@@
 Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem.
-Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
+Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to Accels, and conclude that the performance of the E2EE approach is more fitting than the MAM solution.
 In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting, and implementing the refunding procedure.
